### 2017-11-11 voltagebudget/analysis/sfn_figures.Rmd
SFN poster final

---
title: "Exp1 - Opt w_max and {A,phi)"
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

# Load and process

```{r, message=FALSE}
results <- read_csv("../data/sfn10.csv")
```

```{r, fig.width=1.5, fig.height=1}
results %>% 
  # filter(computation_scores < 0.6, communication_scores > 0) %>%
  ggplot(aes(y=computation_voltages*1e4, x=communication_voltages*1e2, color=As)) +
  scale_color_gradient(low="mediumpurple", high="red3", name="A") +
  xlab("Vo (mvolt)") + ylab("Vc (mvolt)") +
  geom_point(alpha=0.3) + 
  theme_classic()
```

```{r, fig.width=.85, fig.height=.75}
results %>% 
  # filter(computation_scores < 0.6, communication_scores > 0) %>%
  ggplot(aes(x=1e2*communication_voltages, y=communication_scores)) +
  geom_point(color="red3", alpha=0.6) + 
  xlab("Vo (mvolt)") +
  ylab("C (counts)") +
  ylim(0, 20) +
  theme_classic() -> p1
print(p1)
```

```{r, fig.width=.85, fig.height=.75}
results %>% 
  ggplot(aes(x=1e4*computation_voltages, y=30e-3-computation_scores)) +
  geom_point(color="mediumpurple", alpha=0.6) + 
  xlab("Vc (mvolt)") +
  ylab("S (sec)") +
  ylim(0, 0.030) +
  theme_classic() -> p2
print(p2)
```

```{r, fig.width=.95, fig.height=.75}
results %>% 
  filter(computation_scores < 0.6, communication_scores > 0) %>%
  ggplot(aes(x=20+1e2*communication_voltages + 1e4*computation_voltages, y=normalize(communication_scores))) +
  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE) + 
  geom_point(color="red3", alpha=0.2) + 
  xlab("Vf (mvolt)") +
  ylab("Norm. scores") +
  geom_smooth(aes(x=20+1e2*communication_voltages + 1e4*computation_voltages, y=normalize(30e-3-computation_scores)), 
              method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", se=FALSE) + 
  geom_point(aes(x=20+1e2*communication_voltages+ 1e4*computation_voltages, y=normalize(30e-3-computation_scores)), color="mediumpurple", alpha=0.2) + 
  # geom_vline(xintercept = 8.8373, color="black")+
  theme_classic() -> p3
print(p3)
```

```{r, fig.width=.95, fig.height=2}
grid.arrange(p1, p2, p3, ncol=1)

```

### 2017-12-23 voltagebudget/neurons.py
dropped shadow_ad (no ex);
fixed norm/rectification in shadow_adex by adding a V_max kwarg.

@@ -6,19 +6,13 @@ from copy import deepcopy
 from voltagebudget.util import step_waves
 
 
-def shadow_ad(N, time, ns, ts, **adex_kwargs):
-    raise NotImplementedError(
-        "TODO: Shadow adex without the exponential rise.")
-    pass
-
-
 def shadow_adex(N, time, ns, ts, **adex_kwargs):
     """Est. the 'shadow voltage' of the AdEx membrane voltage."""
     # In the neuron can't fire, we're in the shadow realm!
     Et = 1000  # 1000 volts is infinity, for neurons.
     _, _, budget = adex(N, time, ns, ts, budget=True, Et=Et, **adex_kwargs)
 
-    return budget['V_m'], budget
+    return budget
 
 
 # TODO: add sigma
@@ -38,6 +32,7 @@ def adex(N,
          g_l=10e-9,
          V_l=-70e-3,
          V_reset=65e-3,
+         V_max=-50e-3,
          a=0e-9,
          b=10e-12,
          tau_w=30e-3,
@@ -193,21 +188,27 @@ def adex(N,
         E_rheo = float(E_rheo)
         E_t = float(Et)
 
+        V_max = float(V_max)
         V_m = np.asarray(traces_e.v_)
 
+        # Rectify Vm
         V_m_thresh = V_m.copy()
-        V_m_thresh[V_m_thresh > E_t] = E_t
-        V_osc[V_osc > E_t] = E_t
+        V_m_thresh[V_m_thresh > V_max] = V_max
 
-        # and analyze the budget.
+        # Rectify V_osc
+        V_osc[V_osc > V_max] = V_max
+
+        # Est. Comp; 0 rectify
         V_comp = V_osc - V_m_thresh  # swtiched
         V_comp[V_comp > 0] = 0
 
-        V_osc = V_osc
+        # Recenter osc so unit scale matches comp
+        V_osc = E_leak - V_osc
 
-        V_free = E_t - V_m_thresh
+        # Est free.
+        V_free = V_max - V_m_thresh
 
-        # Save it too.
+        # Build vs
         vs = dict(
             tau_m=float(C / g_l),
             times=np.asarray(traces_e.t_),
@@ -217,10 +218,14 @@ def adex(N,
             V_comp=V_comp,
             V_osc=V_osc,
             V_free=V_free,
+            V_max=V_max,
+            E_reset=E_reset,
+            E_rheo=E_rheo,
             E_leak=E_leak,
             E_cut=E_cut,
[…]

### 2017-12-23 voltagebudget/exp/autotune.py
refactor exps into their own .py files, which gets hidden at __init__
the code was getting out of hand in a single file

@@ -1,0 +1,102 @@
+import json
+import csv
+import os
+import numpy as np
+
+import voltagebudget
+from voltagebudget.neurons import adex
+from voltagebudget.neurons import shadow_adex
+from voltagebudget.util import poisson_impulse
+from voltagebudget.util import read_results
+from voltagebudget.util import read_stim
+from voltagebudget.util import read_args
+from voltagebudget.util import read_modes
+
+from voltagebudget.budget import filter_voltages
+from voltagebudget.budget import locate_firsts
+from voltagebudget.budget import locate_peaks
+from voltagebudget.budget import estimate_communication
+from voltagebudget.budget import precision
+
+from voltagebudget.exp import forward
+from voltagebudget.exp import forward_shadow
+from voltagebudget.exp import sweep_power
+from voltagebudget.exp import replay
+from voltagebudget.exp import reverse
+from voltagebudget.exp import create_stim
+
+
+def autotune_w(mode,
+               w_0,
+               rate,
+               t=3,
+               k=20,
+               stim_rate=30,
+               seed_stim=1,
+               max_mult=2):
+    # Load cell params
+    params, _, bias, sigma = read_modes(mode)
+
+    # Create frozen input spikes
+    stim_onset = 0.1
+    stim_offset = t
+    dt = 1e-5
+    ns, ts = poisson_impulse(
+        t,
+        stim_onset,
+        stim_offset - stim_onset,
+        stim_rate,
+        n=k,
+        dt=dt,
+        seed=seed_stim)
+
+    # -
+    def problem(p):
+        w = p[0]
+
+        ns_y, ts_y = adex(
+            1,
+            t,
+            ns,
+            ts,
+            w_max=w,
+            bias=bias,
+            sigma=sigma,
+            report=None,
+            budget=False,
+            **params)
+
+        rate_y = ts_y.size / (stim_offset - stim_onset)
+
+        return rate_y - rate
+
+    p0 = [w_0]
+    sol = least_squares(problem, p0, bounds=(0, w_0 * max_mult))
+
+    return sol
+
+
+def autotune_membrane(mode, bias_0, sigma_0, mean, std, t=1):
+    # Load cell params
+    params, _, _, _ = read_modes(mode)
+
+    # No input spikes
+    ns = np.zeros(1)
+    ts = np.zeros(1)
+    w_max = 0
+
+    # -
+    def problem(p):
[…]

### 2017-12-23 voltagebudget/exp/create_stim.py

@@ -1,6 +1,3 @@
-#!/usr/bin/env python
-
-import fire
 import json
 import csv
 import os
@@ -26,22 +23,33 @@ from voltagebudget.exp import forward_shadow
 from voltagebudget.exp import sweep_power
 from voltagebudget.exp import replay
 from voltagebudget.exp import reverse
-from voltagebudget.exp import create_stim
-from voltagebudget.exp import autotune_membrane
-from voltagebudget.exp import autotune_w
 
-from platypus.algorithms import NSGAII
-from platypus.core import Problem
-from platypus.types import Real
 
-from scipy.optimize import least_squares
+def create_stim(name,
+                t,
+                stim_number=40,
+                stim_onset=0.2,
+                stim_offset=0.250,
+                stim_rate=8,
+                seed_stim=7525,
+                time_step=1e-5,
+                verbose=True):
+    if verbose:
+        print(">>> Building input.")
 
-if __name__ == "__main__":
-    fire.Fire({
-        'create_stim': create_stim,
-        'forward': forward,
-        'forward_shadow': forward_shadow,
-        'sweep_power': sweep_power,
-        'reverse': reverse,
-        'replay': replay
-    })
+    ns, ts = poisson_impulse(
+        t,
+        stim_onset,
+        stim_offset - stim_onset,
+        stim_rate,
+        dt=time_step,
+        n=stim_number,
+        seed=seed_stim)
+
+    if verbose:
+        print(">>> {} spikes generated.".format(ns.size))
+        print(">>> Saving input.")
+    with open("{}.csv".format(name), "w") as fi:
+        writer = csv.writer(fi, delimiter=",")
+        writer.writerow(["ns", "ts"])
+        writer.writerows([[nrn, spk] for nrn, spk in zip(ns, ts)])

### 2017-12-23 voltagebudget/exp/forward.py

@@ -1,0 +1,285 @@
+import fire
+import json
+import csv
+import os
+import numpy as np
+
+import voltagebudget
+from voltagebudget.neurons import adex
+from voltagebudget.neurons import shadow_adex
+from voltagebudget.util import poisson_impulse
+from voltagebudget.util import read_results
+from voltagebudget.util import read_stim
+from voltagebudget.util import read_args
+from voltagebudget.util import read_modes
+
+from voltagebudget.budget import filter_voltages
+from voltagebudget.budget import locate_firsts
+from voltagebudget.budget import locate_peaks
+from voltagebudget.budget import estimate_communication
+from voltagebudget.budget import precision
+
+
+def forward(name,
+            N=50,
+            t=0.4,
+            budget_bias=0,
+            budget_delay=-10e-3,
+            budget_width=2e-3,
+            combine_budgets=False,
+            budget_reduce_fn='mean',
+            stim_number=40,
+            stim_onset=0.2,
+            stim_offset=0.250,
+            stim_rate=8,
+            coincidence_t=1e-3,
+            f=0,
+            A=.05e-9,
+            phi=np.pi,
+            mode='regular',
+            M=100,
+            fix_w=False,
+            seed_prob=42,
+            seed_stim=7525,
+            report=None,
+            save_only=False,
+            verbose=False,
+            time_step=1e-5):
+    """Optimize using the voltage budget."""
+    np.random.seed(seed_prob)
+
+    # --------------------------------------------------------------
+    # Get mode
+    params, w_max, bias, sigma = read_modes(mode)
+
+    # --------------------------------------------------------------
+    # Lookup the reduce function
+    try:
+        budget_reduce_fn = getattr(np, budget_reduce_fn)
+    except AttributeError:
+        raise ValueError("{} is not a numpy function".format(budget_reduce_fn))
+
+    # --------------------------------------------------------------
+    if verbose:
+        print(">>> Building input.")
+    ns, ts = poisson_impulse(
+        t,
+        stim_onset,
+        stim_offset - stim_onset,
+        stim_rate,
+        dt=time_step,
+        n=stim_number,
+        seed=seed_stim)
+
+    if verbose:
+        print(">>> {} spikes generated.".format(ns.size))
+        print(">>> Saving input.")
+    with open("{}_stim.csv".format(name), "w") as fi:
+        writer = csv.writer(fi, delimiter=",")
[…]

### 2017-12-23 voltagebudget/exp/replay.py

@@ -1,0 +1,70 @@
+import fire
+import json
+import csv
+import os
+import numpy as np
+
+import voltagebudget
+from voltagebudget.neurons import adex
+from voltagebudget.neurons import shadow_adex
+from voltagebudget.util import poisson_impulse
+from voltagebudget.util import read_results
+from voltagebudget.util import read_stim
+from voltagebudget.util import read_args
+from voltagebudget.util import read_modes
+
+from voltagebudget.budget import filter_voltages
+from voltagebudget.budget import locate_firsts
+from voltagebudget.budget import locate_peaks
+from voltagebudget.budget import estimate_communication
+from voltagebudget.budget import precision
+
+
+def replay(args, stim, results, i, f, save_npy=None, verbose=False):
+    """Rerun the results of a budget_experiment"""
+
+    # Load parameters, input, and results
+    arg_data = read_args(args)
+    stim_data = read_stim(stim)
+    results_data = read_results(results)
+
+    # Construct a valid kawrgs for adex()
+    exclude = [
+        'N', 'time', 'budget', 'report', 'save_args', 'phi', 'w_max', 'A'
+    ]
+    kwargs = {}
+    for k, v in arg_data.items():
+        if k not in exclude:
+            kwargs[k] = v
+
+    w = results_data['Ws'][i]
+    A = results_data['As'][i]
+    phi = results_data['Phis'][i]
+
+    # drop f=0
+    kwargs.pop("f", None)
+
+    # Replay row i results
+    if verbose:
+        print(">>> Replaying with optimal parameters w:{}, A:{}, phi:{}".
+              format(w, A, phi))
+        print(">>> Default paramerers")
+        print(kwargs)
+
+    ns, ts, budget = adex(
+        arg_data['N'],
+        arg_data['time'],
+        np.asarray(stim_data['ns']),
+        np.asarray(stim_data['ts']),
+        w_max=w,
+        A=A,
+        phi=phi,
+        f=f,
+        budget=True,
+        report=None,
+        **kwargs)
+
+    if save_npy is not None:
+        np.savez(save_npy, ns=ns, ts=ts, budget=budget)
+    else:
+        return ns, ts, budget

### 2017-12-23 voltagebudget/exp/reverse.py

@@ -1,0 +1,25 @@
+import fire
+import json
+import csv
+import os
+import numpy as np
+
+import voltagebudget
+from voltagebudget.neurons import adex
+from voltagebudget.neurons import shadow_adex
+from voltagebudget.util import poisson_impulse
+from voltagebudget.util import read_results
+from voltagebudget.util import read_stim
+from voltagebudget.util import read_args
+from voltagebudget.util import read_modes
+
+from voltagebudget.budget import filter_voltages
+from voltagebudget.budget import locate_firsts
+from voltagebudget.budget import locate_peaks
+from voltagebudget.budget import estimate_communication
+from voltagebudget.budget import precision
+
+
+def reverse():
+    """Optimize using metrics not voltages."""
+    pass

### 2017-12-23 voltagebudget/exp/sweep_power.py

@@ -1,0 +1,191 @@
+import fire
+import json
+import csv
+import os
+import numpy as np
+
+import voltagebudget
+from voltagebudget.neurons import adex
+from voltagebudget.neurons import shadow_adex
+from voltagebudget.util import poisson_impulse
+from voltagebudget.util import read_results
+from voltagebudget.util import read_stim
+from voltagebudget.util import read_args
+from voltagebudget.util import read_modes
+
+from voltagebudget.budget import filter_voltages
+from voltagebudget.budget import locate_firsts
+from voltagebudget.budget import locate_peaks
+from voltagebudget.budget import estimate_communication
+from voltagebudget.budget import precision
+
+
+def sweep_power(name,
+                N=50,
+                t=0.4,
+                budget_delay=-10e-3,
+                budget_width=2e-3,
+                combine_budgets=False,
+                budget_reduce_fn='mean',
+                stim_number=40,
+                stim_onset=0.2,
+                stim_offset=0.250,
+                stim_rate=8,
+                coincidence_t=1e-3,
+                f=10,
+                A_intial=0.0e-9,
+                A_final=.05e-9,
+                M=20,
+                phi=np.pi,
+                mode='regular',
+                report=None,
+                save_only=False,
+                verbose=False,
+                seed_stim=1,
+                time_step=1e-5):
+
+    # --------------------------------------------------------------
+    # Get mode
+    params, w_max, bias, sigma = read_modes(mode)
+
+    # --------------------------------------------------------------
+    # Lookup the reduce function
+    try:
+        budget_reduce_fn = getattr(np, budget_reduce_fn)
+    except AttributeError:
+        raise ValueError("{} is not a numpy function".format(budget_reduce_fn))
+
+    # --------------------------------------------------------------
+    if verbose:
+        print(">>> Building input.")
+    ns, ts = poisson_impulse(
+        t,
+        stim_onset,
+        stim_offset - stim_onset,
+        stim_rate,
+        dt=time_step,
+        n=stim_number,
+        seed=seed_stim)
+
+    if verbose:
+        print(">>> {} spikes generated.".format(ns.size))
+        print(">>> Saving input.")
+    with open("{}_stim.csv".format(name), "w") as fi:
+        writer = csv.writer(fi, delimiter=",")
+        writer.writerow(["ns", "ts"])
+        writer.writerows([[nrn, spk] for nrn, spk in zip(ns, ts)])
+
[…]

### 2017-12-23 voltagebudget/exp/__init__.py
refactor exps into their own .py files, which gets hidden at __init__
the code was getting out of hand in a single file

@@ -1,1 +1,9 @@
 from voltagebudget.exp import budget_experiments
+from voltagebudget.exp.forward_shadow import forward_shadow
+from voltagebudget.exp.forward import forward
+from voltagebudget.exp.reverse import reverse
+from voltagebudget.exp.sweep_power import sweep_power
+from voltagebudget.exp.replay import replay
+from voltagebudget.exp.create_stim import create_stim
+from voltagebudget.exp.autotune import autotune_w
+from voltagebudget.exp.autotune import autotune_membrane

### 2017-12-23 voltagebudget/exp/amp.py

@@ -1,169 +1,0 @@
-"""Usage: amp.py NAME 
-        (--lif | --adex)
-        [-w W] [-s S] [-a A] [-f F] [-n N] [-t T]
-        [--n_grid NGRID]
-
-Explore oscillation amplitude's effect on communication and computation.
-
-    Arguments:
-        NAME    results name (.hdf5)
-
-    Options:
-        -h --help               show this screen
-        -w W                    average input weight [default: 0.2e-9]
-        -s S                    std dev of the input weight [default: 0.5]
-        -a A                    maximum oscillation size (amp) [default: 30e-3]
-        -f F                    oscillation frequency (Hz) [default: 50]
-        -t T                    stim onset time (< 0.2) [default: 0.1]
-        -n N                    number of Y neurons [default: 100]
-        --n_grid NGRID          N pts. for sampling [0, A] [default: 20]
-"""
-
-# %matplotlib inline
-# import matplotlib.pyplot as plt
-from __future__ import division
-
-import csv
-
-import numpy as np
-from docopt import docopt
-
-from fakespikes import util as fsutil
-
-from voltagebudget.neurons import adex
-from voltagebudget.neurons import lif
-
-from voltagebudget.util import k_spikes
-from voltagebudget.util import estimate_rate
-from voltagebudget.util import estimate_communication
-from voltagebudget.util import estimate_computation
-from voltagebudget.util import mean_budget
-
-
-def create_simulation(nrn, time, N, ns, ts, time_step=1e-4, **params):
-    def simulation(A):
-        # Create Y, then Z
-        ns_y, ts_y, vs_y = nrn(time,
-                               N,
-                               ns,
-                               ts,
-                               A=A,
-                               r_b=0,
-                               budget=True,
-                               report=None,
-                               time_step=time_step,
-                               **params)
-
-        return ns_y, ts_y, vs_y
-
-    return simulation
-
-
-if __name__ == "__main__":
-    args = docopt(__doc__, version='alpha')
-    name = args["NAME"]
-
-    N = int(args["-n"])
-    Amax = float(args["-a"])
-    n_grid = int(args["--n_grid"])
-    f = float(args["-f"])
-
-    w_y = float(args["-w"])
-    s_y = float(args["-s"])
-
-    t_stim = float(args["-t"])
-
[…]

### 2017-12-23 voltagebudget/exp/forward_shadow.py

@@ -1,0 +1,262 @@
+import os
+import json
+import csv
+import numpy as np
+
+import voltagebudget
+from voltagebudget.neurons import adex
+from voltagebudget.neurons import shadow_adex
+from voltagebudget.util import poisson_impulse
+from voltagebudget.util import read_results
+from voltagebudget.util import read_stim
+from voltagebudget.util import read_args
+from voltagebudget.util import read_modes
+from voltagebudget.budget import filter_voltages
+from voltagebudget.budget import locate_firsts
+from voltagebudget.budget import budget_window
+from voltagebudget.budget import locate_peaks
+from voltagebudget.budget import estimate_communication
+from voltagebudget.budget import precision
+
+from platypus.algorithms import NSGAII
+from platypus.core import Problem
+from platypus.types import Real
+
+from scipy.optimize import least_squares
+
+
+def forward_shadow(name,
+                   stim,
+                   N=50,
+                   t=0.4,
+                   d=-5e-3,
+                   w=2e-3,
+                   T_onset=0.225,
+                   T_offset=0.250,
+                   coincidence_t=1e-3,
+                   f=0,
+                   A=.05e-9,
+                   phi=np.pi,
+                   mode='regular',
+                   M=100,
+                   fix_w=False,
+                   seed_prob=42,
+                   report=None,
+                   save_only=False,
+                   verbose=False,
+                   budget_reduce_fn='mean',
+                   combine_budgets=False,
+                   time_step=1e-5):
+    """Optimize using the shadow voltage budget."""
+    np.random.seed(seed_prob)
+
+    # --------------------------------------------------------------
+    # Get mode
+    params, w_max, bias, sigma = read_modes(mode)
+
+    # --------------------------------------------------------------
+    # Lookup the reduce function
+    try:
+        budget_reduce_fn = getattr(np, budget_reduce_fn)
+    except AttributeError:
+        raise ValueError("{} is not a numpy function".format(budget_reduce_fn))
+
+    # --------------------------------------------------------------
+    if verbose:
+        print(">>> Importing stimulus.")
+
+    stim_data = read_stim(stim)
+
+    ns = np.asarray(stim_data['ns'])
+    ts = np.asarray(stim_data['ts'])
+
+    # --------------------------------------------------------------
[…]

### 2017-12-23 voltagebudget/analysis/paper_figures.Rmd
vis...

---
title: "Exp1 - Opt w_max and {A,phi)"
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

# Load and process

```{r, message=FALSE}
results <- read_csv("../exp/paper2.csv")
```

```{r, fig.width=1.5, fig.height=1}
results %>% 
  # filter(computation_scores < 0.6, communication_scores > 0) %>%
  ggplot(aes(y=computation_voltages, x=communication_voltages, color=As)) +
  scale_color_gradient(low="mediumpurple", high="red3", name="A") +
  xlab("Vo (mvolt)") + ylab("Vc (mvolt)") +
  geom_point(alpha=0.3) + 
  theme_classic()
```

```{r, fig.width=1.85, fig.height=.75}
results %>% 
  # filter(computation_scores < 0.6, communication_scores > 0) %>%
  ggplot(aes(x=computation_voltages, y=communication_scores)) +
  geom_point(color="red3", alpha=0.6) + 
  xlab("Vc (mvolt)") +
  ylab("C (counts)") +
  ylim(0, 20) +
  theme_classic() -> p1
print(p1)
```

```{r, fig.width=1.85, fig.height=.75}
results %>% 
  ggplot(aes(x=computation_voltages, y=computation_scores)) +
  geom_point(color="mediumpurple", alpha=0.6) + 
  xlab("Vf (mvolt)") +
  ylab("S (sec)") +
  ylim(0, 0.030) +
  theme_classic() -> p2
print(p2)
```

```{r, fig.width=.95, fig.height=.75}
results %>% 
  filter(computation_scores < 0.6, communication_scores > 0) %>%
  ggplot(aes(x=communication_voltages + computation_voltages, y=normalize(communication_scores))) +
  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE) + 
  geom_point(color="red3", alpha=0.2) + 
  xlab("Vf (mvolt)") +
  ylab("Norm. scores") +
  geom_smooth(aes(x=communication_voltages + computation_voltages, y=normalize(computation_scores)), 
              method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", se=FALSE) + 
  geom_point(aes(x=communication_voltages+ computation_voltages, y=normalize(computation_scores)), color="mediumpurple", alpha=0.2) + 
  # geom_vline(xintercept = 8.8373, color="black")+
  theme_classic() -> p3
print(p3)
```

```{r, fig.width=.95, fig.height=2}
grid.arrange(p1, p2, p3, ncol=1)

```

### 2018-01-03 voltagebudget/exp/create_stim.py
refactor spike saving

@@ -11,6 +11,7 @@ from voltagebudget.util import read_results
 from voltagebudget.util import read_stim
 from voltagebudget.util import read_args
 from voltagebudget.util import read_modes
+from voltagebudget.util import write_spikes
 
 from voltagebudget.budget import filter_voltages
 from voltagebudget.budget import locate_firsts
@@ -49,7 +50,5 @@ def create_stim(name,
     if verbose:
         print(">>> {} spikes generated.".format(ns.size))
         print(">>> Saving input.")
-    with open("{}.csv".format(name), "w") as fi:
-        writer = csv.writer(fi, delimiter=",")
-        writer.writerow(["ns", "ts"])
-        writer.writerows([[nrn, spk] for nrn, spk in zip(ns, ts)])
+
+    write_spikes("{}.csv".format(name), ns, ts)

### 2018-01-03 voltagebudget/util.py

@@ -131,6 +131,13 @@ def get_default_modes():
     return modes
 
 
+def write_spikes(name, ns, ts):
+    with open("{}.csv".format(name), "w") as fi:
+        writer = csv.writer(fi, delimiter=",")
+        writer.writerow(["ns", "ts"])
+        writer.writerows([[nrn, spk] for nrn, spk in zip(ns, ts)])
+
+
 def read_stim(stim):
     """Read in budget_experiment stimulation, as a dict"""
     return _read_csv_cols_into_dict(stim)

### 2018-01-18 voltagebudget/exp/autotune.py
Added a two-state lsq sq opt to autotune_V_osc - single opt could not reliably converge given how A/phi interact with power.

@@ -22,6 +22,8 @@ from voltagebudget.util import locate_firsts
 from voltagebudget.util import locate_peaks
 from voltagebudget.util import estimate_communication
 from voltagebudget.util import precision
+from voltagebudget.util import mad
+from pyswarm import pso
 
 
 def autotune_V_osc(N,
@@ -32,7 +34,7 @@ def autotune_V_osc(N,
                    ts,
                    voltage_ref,
                    w=2e-3,
-                   A_0=0.1e-9,
+                   A_0=0.05e-9,
                    A_max=0.5e-9,
                    phi_0=0,
                    f=8,
@@ -48,7 +50,7 @@ def autotune_V_osc(N,
     solutions : list((A, phi, sol), ...)
         A list of N 3-tuples 
     """
-    # -
+    # ---------------------------------------------------------------
     params, w_in, bias_in, sigma = read_modes(mode)
     if not noise:
         sigma = 0
@@ -60,73 +62,105 @@ def autotune_V_osc(N,
     # problem definition
     rescale = 1e10
 
-    p0 = (A_0 * rescale, phi_0)
-    bounds = ([0, 0], [A_max * rescale, np.pi])
+    # ---------------------------------------------------------------
+    # Define a loss func (closing several locals)
+    def est_loss(n, voltage):
+        # Select window
+        budget = budget_window(voltage, E + d, w, select=None)
+
+        # Get budget terms for opt
+        V_free = np.abs(budget_ref['V_free'][n, :])
+        V_osc = np.abs(budget['V_osc'][n, :])
+
+        # loss = np.mean(V_free - V_osc)
+        loss = V_free - V_osc
+
+        return loss
 
     # -
     solutions = []
     for n in range(N):
 
-        def problem(p):
+        # ---------------------------------------------------------------
+        def phi_problem(p, A):
             """A new problem for each neuron"""
-            A = p[0] / rescale
-            phi = p[1]
 
-            # Run into the shadow! realm!
-            if shadow:
-                voltage = shadow_adex(
-                    N,
-                    t,
-                    ns,
-                    ts,
-                    A=A,
-                    phi=phi,
-                    f=f,
-                    w_in=w_in,
-                    bias_in=bias_in,
-                    sigma=sigma,
-                    seed_value=seed_value,
-                    **params)
-            else:
-                _, _, voltage = adex(
-                    N,
-                    t,
-                    ns,
[…]

### 2018-01-18 voltagebudget/exp/forward.py
Added MAD as metric to forward

@@ -20,6 +20,7 @@ from voltagebudget.util import budget_window
 from voltagebudget.util import locate_peaks
 from voltagebudget.util import estimate_communication
 from voltagebudget.util import precision
+from voltagebudget.util import mad
 from voltagebudget.exp.autotune import autotune_V_osc
 
 
@@ -34,7 +35,8 @@ def forward(name,
             f=8,
             A_0=.05e-9,
             A_max=0.5e-9,
-            phi_0=np.pi,
+            phi_0=0,
+            opt_phi=False,
             mode='regular',
             noise=False,
             shadow=False,
@@ -106,6 +108,7 @@ def forward(name,
             f=0,
             A=0,
             phi=0,
+            opt_phi=opt_phi,
             sigma=sigma,
             seed_value=seed_value,
             save_args=None,
@@ -193,7 +196,7 @@ def forward(name,
         ns_n, ts_n = filter_spikes(ns_n, ts_n, (E, E + T))
 
         # Save
-        write_spikes("{}_n_{}_spks".format(n).format(name), ns_n, ts_n)
+        write_spikes("{}_n_{}_spks".format(name, n), ns_n, ts_n)
 
         # Coincidences
         cc = estimate_communication(

### 2018-01-18 voltagebudget/util.py

@@ -180,6 +180,12 @@ def filter_voltages(budget,
     return filtered
 
 
+def mad(x, axis=None):
+    """Mean absolute deviation"""
+
+    return np.mean(np.absolute(x - np.mean(x, axis)), axis)
+
+
 def estimate_communication(ns, ts, window, coincidence_t=1e-3, min_spikes=2):
     # Define overall analysis window
     t0 = window[0]

### 2018-01-18 voltagebudget/exp/reverse.py
Began rev alg implementation.

@@ -1,0 +1,44 @@
+import numpy as np
+from voltagebudget.util import mad
+
+
+def optimal_coordination(ts, p, dt):
+    if dt < 0:
+        raise ValueError("dt must be positive.")
+    if not (0 <= p <= 1):
+        raise ValueError("p must be between (0-1).")
+
+    # Est initial and target
+    initial = mad(ts)
+    target = initial - (initial * p)
+
+    # We'll always want the biggest....
+    deltas = np.absolute(ts - np.mean(ts))
+
+    # Opt!
+    ts_opt = ts.copy()
+
+    while adjusted > target:
+        # Find largest delta 
+        k = np.argmax(deltas)
+
+        # and shift that spike toward the mean
+        if ts_opt[k] < 0:
+            ts_opt[k] += dt
+        else ts_opt[k] > 0:
+            ts_opt[k] -= dt
+        else:
+            pass
+
+        # Recalc the deltas
+        deltas = np.absolute(ts_opt - np.mean(ts_opt))
+
+        # Update rolling MAD
+        adjusted = mad(ts_opt)
+
+    return ts_opt
+
+
+def reverse():
+    # TODO
+    pass

### 2018-01-26 voltagebudget/util.py
bugifx in mae

@@ -186,6 +186,17 @@ def mad(x, axis=None):
     return np.mean(np.absolute(x - np.mean(x, axis)), axis)
 
 
+def mae(x, y, axis=None):
+    """Mean absolute deviation"""
+
+    min_l = min(len(x), len(y))
+
+    x = np.sort(x, axis)
+    y = np.sort(y, axis)
+
+    return np.mean(np.absolute(x[:min_l] - y[:min_l]), axis)
+
+
 def estimate_communication(ns, ts, window, coincidence_t=1e-3, min_spikes=2):
     # Define overall analysis window
     t0 = window[0]

### 2018-01-26 voltagebudget/analysis/paper_figures.Rmd
analysis R code...working commit

@@
 }
+```
+
+# Voltage budget timecourse
+
+```{r}
+vms <- read_csv("vm_comp_timecourse.csv")
+```
+
+```{r, fig.width=1.5, fig.height=1.3}
+vms %>% 
+  filter(t > 0.15, t < 0.35) %>%
+  ggplot(aes(x=t, ymin=-70e-3, ymax=vm)) +
+  geom_ribbon(fill="blue", alpha=0.5) +
+  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
+  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
+  labs(x="", y="Vm") +
+  theme_classic() -> p1
+
+vms %>% 
+  filter(t > 0.15, t < 0.35) %>%
+  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
+  geom_ribbon(fill="red", alpha=0.5) +
+  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
+  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
+  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
+  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
+  # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
+  # geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), color="grey", alpha=0.5) +
+  # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
+  labs(x="Times (s)", y="") +
+  theme_classic() -> p2
+
+vms %>% 
+  filter(t > 0.23652 - 8e-3, t < 0.23652 + 2e-3 + 0.03333333 + 8e-3) %>%
+  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
+  geom_ribbon(fill="red", alpha=0.5) +
+  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
+  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
+  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
+  geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), fill="grey", alpha=0.01) +
+  geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3),  fill="grey", alpha=0.01) +
+  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
+  labs(x="", y="") +
+  theme(axis.line=element_blank(),
+      axis.text.x=element_blank(),
+      axis.text.y=element_blank(),
+      axis.ticks=element_blank(),
+      # axis.title.x=element_blank(),
+      # axis.title.y=element_blank(),
+      legend.position="none",
+      panel.background=element_blank(),
+      panel.border=element_blank(),
+      panel.grid.major=element_blank(),
+      panel.grid.minor=element_blank(),
+      plot.background=element_blank()) -> p3
+
+plot_grid <- rbind(c(1 , 1, NA), c(2, 2, 3))
+grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+```
+
+# Voltage timecourses many neurons
+
+```{r}
+vms <- read_csv("vm_full_examples.csv")
+vms <- gather(vms, "neuron", "vm", 2:21)
+wins <- read_csv("vm_window_examples_d2_w2.csv")
+wins <- gather(wins, "neuron", "vm", 2:21)
+```
+
+```{r, fig.width=1.5, fig.height=1}
+vms %>% 
+  filter(t > 0.15, t < 0.35) %>%
+  ggplot(aes(x=t, y=vm, group=neuron)) +
+  geom_line(color="black", alpha=0.3, size=0.2) +
+  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
+  labs(x="Time (s)", y="Vm (mV)") +
+  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.25) +
+  geom_hline(yintercept=-70e-3, color="black", size=2) +
+  geom_vline(xintercept = 0.25719 + 2e-3, color="darkgreen", alpha=0.5, size=0.2) +
+  geom_vline(xintercept = 0.25719 + 2e-3 +  0.03333333, color="darkgreen", alpha=0.5, size=0.2) +
+  theme_classic()
+```
+```{r, fig.width=0.4, fig.height=0.8}
+vms %>% 
+  filter(t > 0.25, t < 0.27) %>%
+  ggplot(aes(x=t, y=vm, group=neuron)) +
+  geom_line(color="black", alpha=0.3, size=0.2) +
+  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
+  labs(x="Time (s)", y="Vm (mV)") +
+  geom_hline(yintercept=-50e-3, color="black", linetype="dashed", size=1) +
+  geom_hline(yintercept=-70e-3, color="black", size=2) +
+  theme(axis.line=element_blank(),
+      axis.text.x=element_blank(),
+      axis.text.y=element_blank(),
+      axis.ticks=element_blank(),
+      axis.title.x=element_blank(),
+      axis.title.y=element_blank(),
+      legend.position="none",
+      panel.background=element_blank(),
+      panel.border=element_blank(),
+      panel.grid.major=element_blank(),
+      panel.grid.minor=element_blank(),
+      plot.background=element_blank())
+  # theme_classic()
 ```

### 2018-01-27 voltagebudget/analysis/paper_figures.Rmd
Working commit - Rmd files

@@
   geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
-  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
-  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
+  # geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
+  # geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
   geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), fill="grey", alpha=0.01) +
@@
 grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+```
+
+# Bounds
+
+```{r, message=FALSE, fig.width=1.5, fig.height=1.3}
+name <- "../data/exp7_d-2e-3_f20.csv"
+results <- read_csv(paste(name, sep=""))
+
+results %>% 
+  filter(V_free > 0.002) %>% 
+  ggplot(aes(x=V_free*1e3)) +
+  geom_histogram(aes(y=0.5*..density..), bins=50, size=0.2) +
+  geom_density(alpha=0.3, fill="black") +
+  geom_vline(aes(xintercept=min(1e3*V_free - 0.05)), color="darkolivegreen3", alpha=0.6) +
+  geom_vline(aes(xintercept=max(1e3*V_free + 0.01)), color="goldenrod2", alpha=0.5) +
+  labs(x="V_free (mvolt)", y="Density (AU)") +
+  xlim(3, 6) +
+  theme_classic() -> p1
+
+results %>% 
+  filter(V_free > 0.002) %>% 
+  ggplot(aes(x=variances, y=errors, color=V_free)) +
+  geom_point(alpha=0.5) +
+  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
+  theme_classic() -> p2
+```
+
+```{r, message=FALSE, fig.width=3, fig.height=1.7}
+# Load min, max V_free and neighbors
+name <- "../data/exp5_d-2e-3_f8_r1.csv"
+rank1 <- read_csv(paste(name, sep=""))
+rank1$rank <- rep(1, nrow(rank1))
+
+name <- "../data/exp5_d-2e-3_f8_r2.csv"
+rank2 <- read_csv(paste(name, sep=""))
+rank2$rank <- rep(2, nrow(rank2))
+
+name <- "../data/exp5_d-2e-3_f8_r3.csv"
+rank3 <- read_csv(paste(name, sep=""))
+rank3$rank <- rep(3, nrow(rank3))
+
+name <- "../data/exp5_d-2e-3_f8_r50.csv"
+rank50 <- read_csv(paste(name, sep=""))
+rank50$rank <- rep(50, nrow(rank50))
+
+name <- "../data/exp5_d-2e-3_f8_r49.csv"
+rank49 <- read_csv(paste(name, sep=""))
+rank49$rank <- rep(49, nrow(rank49))
+
+name <- "../data/exp5_d-2e-3_f8_r48.csv"
+rank48 <- read_csv(paste(name, sep=""))
+rank48$rank <- rep(48, nrow(rank48))
+
+# Group 'em
+ranked <- rbind(rank1, rank2, rank3, rank50, rank49, rank48)
+
+# -----------------------------------------------------
+# TODO: manual color assignment, setting alphas to rank?
+ranked %>%
+  ggplot(aes(x=N, y=sort(errors), color=rank, group=rank)) +
+  geom_line(alpha=0.4) +
+  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
+  theme_classic() -> p3
+
+ranked %>%
+  ggplot(aes(x=N, y=sort(variances), color=rank, group=rank)) +
+  geom_line(alpha=0.4) +
+  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
+  theme_classic() -> p4
+
+plot_grid <- rbind(c(1 , 1, NA, 3, 3, 3), c(2, 2, 2, 4, 4, 4))
+grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
+```
+
+# Pareto opt
+```{r, message=FALSE, fig.width=2.2, fig.height=1.9}
+name <- "../data/exp4_d-2e-3_f12.csv"
+results <- read_csv(paste(name, sep=""))
+
+results %>% 
+  # filter(errors < 0.6, variances > 0) %>%
+  ggplot(aes(y=V_comp*1e3, x=V_osc*1e3, color=As)) +
+  scale_color_gradient(low="mediumpurple", high="red3", name="A") +
+  xlab("Vc (mvolt)") + ylab("Vo (mvolt)") +
+  geom_point(alpha=0.4) + 
+  theme_classic() + 
+  theme(legend.position="bottom", legend.key.size =  unit(0.3, "in")) -> p1
+
+results %>% 
+  ggplot(aes(x=1e3*V_free, y=normalize(variances))) +
+  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE, linetype="dashed") + 
+  # geom_point(color="red3", alpha=0.2) + 
+  geom_smooth(aes(x=1e3*V_free, y=normalize(errors)), 
+              method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", se=FALSE,linetype="dashed") + 
+  # geom_point(aes(x=1e3*V_free, y=normalize(errors)), color="mediumpurple", alpha=0.2) + 
+  geom_vline(aes(xintercept = mean(1e3*V_free)), color="black") +
+  xlab("Vf (mvolt)") +
+  ylab("Normalized") +
+  theme_classic() -> p2
+
+results %>% 
+  ggplot(aes(x=1e3*V_comp, y=errors)) +
+  geom_point(alpha=0.4, size=.3, color="mediumpurple") +
+  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", alpha=0.2, se=FALSE, linetype="dashed") + 
+  xlab("Vc (mvolt)") +
+  ylab("Errors (s)") +
+  theme_classic() -> p3
+
+results %>% 
+  ggplot(aes(x=1e3*V_osc, y=variances)) +
+  geom_point(alpha=0.3, size=.3, color="red3") +
+  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE, linetype="dashed") + 
+  xlab("Vo (mvolt)") +
+  ylab("Variance (s)") +
+  theme_classic() -> p4
+
+plot_grid <- rbind(c(NA ,NA, 3, 3), c(NA, NA, 3, 3), c(NA, NA, 4, 4), c(1 ,1, 4, 4), c(1, 1, 2, 2), c(1, 1, 2, 2))
+grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
 ```
@@
 ```
-
-# Load and process
-
-```{r, message=FALSE}
-results <- read_csv("../exp/paper2.csv")
-```
-
-```{r, fig.width=1.5, fig.height=1}
-results %>% 
-  # filter(computation_scores < 0.6, communication_scores > 0) %>%
-  ggplot(aes(y=computation_voltages, x=communication_voltages, color=As)) +
-  scale_color_gradient(low="mediumpurple", high="red3", name="A") +
-  xlab("Vo (mvolt)") + ylab("Vc (mvolt)") +
-  geom_point(alpha=0.3) + 
-  theme_classic()
-```
-
-```{r, fig.width=1.85, fig.height=.75}
-results %>% 
-  # filter(computation_scores < 0.6, communication_scores > 0) %>%
-  ggplot(aes(x=computation_voltages, y=communication_scores)) +
-  geom_point(color="red3", alpha=0.6) + 
-  xlab("Vc (mvolt)") +
-  ylab("C (counts)") +
-  ylim(0, 20) +
-  theme_classic() -> p1
-print(p1)
-```
-
-```{r, fig.width=1.85, fig.height=.75}
-results %>% 
-  ggplot(aes(x=computation_voltages, y=computation_scores)) +
-  geom_point(color="mediumpurple", alpha=0.6) + 
-  xlab("Vf (mvolt)") +
-  ylab("S (sec)") +
-  ylim(0, 0.030) +
-  theme_classic() -> p2
-print(p2)
-```
-
-```{r, fig.width=.95, fig.height=.75}
-results %>% 
-  filter(computation_scores < 0.6, communication_scores > 0) %>%
-  ggplot(aes(x=communication_voltages + computation_voltages, y=normalize(communication_scores))) +
-  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE) + 
-  geom_point(color="red3", alpha=0.2) + 
-  xlab("Vf (mvolt)") +
-  ylab("Norm. scores") +
-  geom_smooth(aes(x=communication_voltages + computation_voltages, y=normalize(computation_scores)), 
-              method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", se=FALSE) + 
-  geom_point(aes(x=communication_voltages+ computation_voltages, y=normalize(computation_scores)), color="mediumpurple", alpha=0.2) + 
-  # geom_vline(xintercept = 8.8373, color="black")+
-  theme_classic() -> p3
-print(p3)
-```
-
-```{r, fig.width=.95, fig.height=2}
-grid.arrange(p1, p2, p3, ncol=1)
-
-```

### 2018-01-27 voltagebudget/exp/ranked.py
bugfix: ranked, n now set correctly. All prev runs were in total error.

@@ -44,7 +44,6 @@ def ranked(name,
            opt_phi=False,
            mode='regular',
            noise=False,
-           shadow=False,
            save_only=False,
            verbose=False,
            seed_value=42):
@@ -60,6 +59,9 @@ def ranked(name,
     coincidence_t = 1e-3
 
     # Process rank
+    if verbose:
+        print(">>> Target rank is {}".format(rank))
+
     rank -= 1  # Adj for python zero indexing
 
     if rank > N:
@@ -109,25 +111,6 @@ def ranked(name,
     if ns_ref.size == 0:
         raise ValueError("The reference model didn't spike.")
 
-    # If in shadow mode, replace ref voltages
-    if shadow:
-        voltages_ref = shadow_adex(
-            N,
-            t,
-            ns,
-            ts,
-            w_in=w_in,
-            bias_in=bias_in,
-            f=0,
-            A=0,
-            phi=0,
-            opt_phi=opt_phi,
-            sigma=sigma,
-            seed_value=seed_value,
-            save_args=None,
-            time_step=time_step,
-            **params)
-
     # Find the ref spike closest to E_0
     # and set that as E
     if np.isclose(E_0, 0.0):
@@ -151,9 +134,11 @@ def ranked(name,
     budget_ref = budget_window(voltages_ref, E + d, w, select=None)
 
     # Pick the neuron to optimize, based on its rank
-    n = np.argmin([budget_ref["V_free"][j, :].mean() for j in range(N)])
+    idx = np.argsort([budget_ref["V_free"][j, :].mean() for j in range(N)])
+    n = int(np.where(idx == rank)[0])
     if verbose:
-        print(">>> Rank {} is neuron {}.".format(rank, n))
+        print(">>> The Vf rank index: {}.".format(idx))
+        print(">>> Rank {} is neuron {}.".format(rank + 1, n))
 
     # least_squares() was struggling with small A, so boost it
     # for param search purposes, then divide it back out in the 
@@ -197,7 +182,7 @@ def ranked(name,
         loss = est_loss(voltage)
 
         if verbose:
-            print(">>> (A {:0.12f}, phi {:0.3f})  ->  (loss {})".format(
+            print(">>> (A {:0.14f}, phi {:0.3f})  ->  (loss {})".format(
                 A / rescale, phi, np.sum(loss)))
 
         return loss
@@ -225,7 +210,7 @@ def ranked(name,
[…]

### 2018-01-28 voltagebudget/exp/forward.py
Added flag to opt all_phi to farward exp

@@ -36,7 +36,7 @@ def forward(name,
             A_0=.05e-9,
             A_max=0.5e-9,
             phi_0=0,
-            opt_phi=False,
+            all_phi=False,
             mode='regular',
             noise=False,
             shadow=False,
@@ -151,6 +151,7 @@ def forward(name,
         f=f,
         shadow=shadow,
         noise=noise,
+        all_phi=all_phi,
         seed_value=seed_value,
         verbose=verbose)
 

### 2018-01-28 voltagebudget/analysis/ranked_sum_analysis.Rmd
cleaned up Rmd plotting

---
title: "General analysis notebook for `forward` budget models."
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

# Load and process a series of ranks.

```{r, message=FALSE, fig.width=3, fig.height=1}
# Load min, max V_free and neighbors
exp_name <- "exp18"
freq = "30"

ranked <- NULL

rank <- "1"
name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

# rank <- "2"
# name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
# rdata <- read_csv(paste(name, sep=""))
# rdata$rank <- rep(rank, nrow(rdata))
# ranked <- rbind(ranked, rdata)

rank <- "3"
name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

rank <- "50"
name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

# rank <- "49"
# name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
# rdata <- read_csv(paste(name, sep=""))
# rdata$rank <- rep(rank, nrow(rdata))
# ranked <- rbind(ranked, rdata)

rank <- "48"
name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
rdata <- read_csv(paste(name, sep=""))
rdata$rank <- rep(rank, nrow(rdata))
ranked <- rbind(ranked, rdata)

ranked$rank <- as.numeric(ranked$rank)

# -----------------------------------------------------
# TODO: manual color assignment, setting alphas to rank?
ranked %>%
  filter(N!=2) %>% 
  ggplot(aes(x=N, y=sort(errors), color=rank, group=rank)) +
  geom_line(alpha=0.4) +
  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
  theme_classic() -> p3

ranked %>%
  filter(N!=2) %>% 
  ggplot(aes(x=N, y=sort(variances), color=rank, group=rank)) +
  geom_line(alpha=0.4) +
  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
  theme_classic() -> p4

grid.arrange(p3, p4, nrow=1)
```

### 2018-01-28 voltagebudget/exp/autotune.py
...

@@ -39,6 +39,7 @@ def autotune_V_osc(N,
                    f=8,
                    mode='regular',
                    noise=False,
+                   all_phi=False,
                    seed_value=42,
                    shadow=False,
                    verbose=False):
@@ -144,6 +145,17 @@ def autotune_V_osc(N,
         if n == 0:
             if verbose:
                 print(">>> Optimizing phi (neuron {}).".format(n))
+
+            p0 = [phi_0]
+            bounds = (0, np.pi)
+            sol = least_squares(
+                lambda p: phi_problem(p, A_0 * rescale), p0, bounds=bounds)
+
+            phi_hat = sol.x[0]
+
+        elif n > 0 and all_phi:
+            if verbose:
+                print(">>> Optimizing phi, neuron {}/{}.".format(n + 1, N))
 
             p0 = [phi_0]
             bounds = (0, np.pi)

### 2018-01-29 voltagebudget/exp/pareto.py
Saving bugfix in pareto

@@ -206,6 +206,7 @@ def pareto(name,
     phis = []
     phis_w = []
     for m in range(M):
+        # Extract opt values
         A_m = results['As'][m]
 
         w_max = results['w_max'][m]
@@ -293,7 +294,6 @@ def pareto(name,
         print(">>> Saving results.")
 
     # Build a dict of results,
-    results = {}
     results["N"] = list(range(N))
     results["variances"] = variances
     results["errors"] = errors
@@ -302,8 +302,6 @@ def pareto(name,
     results["V_comp"] = V_comps
     results["V_free"] = V_frees
 
-    results["As"] = As
-    results["w_max"] = w_maxes
     results["phis"] = phis
     results["phis_w"] = phis_w
 

### 2018-01-30 voltagebudget/analysis/ranked_analysis.Rmd

---
title: "General analysis notebook for `forward` budget models."
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

# Load and process indivdual ranks

```{r, message=FALSE}
name <- "../data/exp18_d-2e-3_f12_r50.csv"
results <- read_csv(paste(name, sep=""))
```

```{r, fig.width=2.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=delta_variances)) +
  geom_histogram(bins=20) + 
  xlab("Variance") +
  theme_classic() -> p1

results %>% 
  ggplot(aes(x=errors)) +
  geom_histogram(bins=20) + 
  xlab("Error") +
  theme_classic() -> p2

results %>% 
  ggplot(aes(x=V_osc)) +
  geom_histogram(bins=20) +
  xlab("Vc (volt)") +
  theme_classic() -> p3

results %>% 
  ggplot(aes(x=V_comp)) +
  geom_histogram(bins=20) +
  xlab("Vo (volt)") +
  theme_classic() -> p4

grid.arrange(p1, p2, p3, p4, nrow=2)
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=V_free, y=V_osc, color=errors)) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=N, y=sort(errors))) +
  ylim(0, 0.030) +
  geom_point() + 
  theme_classic()
```

```{r, fig.width=2.5, fig.height=1}
results %>% 
  ggplot(aes(x=N, y=sort(delta_variances))) +
  geom_point() + 
  ylim(-0.030, 0.030) +
  geom_hline(aes(yintercept=0), color="black", alpha=0.6) +
  theme_classic()
```

```{r, fig.width=1.5, fig.height=1}
results %>% 
  # filter(errors < 0.6, coincidence_count > 0) %>%
  ggplot(aes(x=V_comp, y=normalize(delta_variances))) +
  geom_point(color="red", alpha=0.5) + 
  xlab("Vc (mvolt)") +
  ylab("Rel. scores (AU)") +
  geom_point(aes(x=V_comp, y=normalize(errors)), color="purple") + 
  theme_classic()
```

### 2018-01-30 voltagebudget/analysis/ranked_sum_analysis.Rmd

@@
 # Load min, max V_free and neighbors
-exp_name <- "exp18"
-freq = "30"
+exp_name <- "exp29"
+freq = "8"
 
@@
 rank <- "1"
-name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
+name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
+rdata <- read_csv(name)
+rdata$rank <- rep(rank, nrow(rdata))
+ranked <- rbind(ranked, rdata)
+
+rank <- "2"
+name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
 rdata <- read_csv(paste(name, sep=""))
@@
 
-# rank <- "2"
-# name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
-# rdata <- read_csv(paste(name, sep=""))
-# rdata$rank <- rep(rank, nrow(rdata))
-# ranked <- rbind(ranked, rdata)
-
 rank <- "3"
-name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
+name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
 rdata <- read_csv(paste(name, sep=""))
@@
 rank <- "50"
-name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
+name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
 rdata <- read_csv(paste(name, sep=""))
@@
 
-# rank <- "49"
-# name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
-# rdata <- read_csv(paste(name, sep=""))
-# rdata$rank <- rep(rank, nrow(rdata))
-# ranked <- rbind(ranked, rdata)
+rank <- "49"
+name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
+rdata <- read_csv(paste(name, sep=""))
+rdata$rank <- rep(rank, nrow(rdata))
+ranked <- rbind(ranked, rdata)
 
 rank <- "48"
-name <- paste("../data/", exp_name, "_d-2e-3_f", freq, "_r", rank, ".csv", sep="")
+name <- paste("../data/", exp_name, "_d-0.2e-3_f", freq, "_r", rank, ".csv", sep="")
 rdata <- read_csv(paste(name, sep=""))

### 2018-01-31 voltagebudget/analysis/paper_figures.Rmd
Added intial/cartoon PLC opt model figures

@@
 ```
+
 ```{r, fig.width=0.4, fig.height=0.8}
@@
 ```
+
+# Optimal PLC
+
+```{r, message=FALSE}
+plc_spikes <- read_csv("plc_spikes.csv")
+plc_traces <- read_csv("plc_traces.csv")
+```
+
+```{r, fig.width=0.6, fig.height=1}
+plc_spikes %>% 
+  ggplot(aes(x=ts_opt, y=n)) + 
+  geom_point(color="black", size=0.8) +
+  geom_point(data=filter(plc_spikes, ts != ts_opt), aes(x=ts, y=n), color="red", size=1.5, shape=4, alpha=0.6) +
+  xlim(0.2, 0.24) +
+  theme_classic() +
+  # labs(x="Time (s)", y="N") +
+  theme(axis.line=element_blank(),
+      axis.text.x=element_blank(),
+      axis.text.y=element_blank(),
+      axis.ticks=element_blank(),
+      axis.title.x=element_blank(),
+      axis.title.y=element_blank(),
+      legend.position="none",
+      panel.background=element_blank(),
+      panel.border=element_blank(),
+      panel.grid.major.y=element_blank(),
+      panel.grid.minor.y =element_blank(),
+      plot.background=element_blank()) -> p1
+```
+
+```{r, fig.width=1.2, fig.height=1}
+plc_traces %>% 
+  ggplot(aes(x=variances, y=errors)) +
+  geom_line() +
+  theme_classic() +
+  ylab("Errors (s)") +
+  xlab("Variance (s)") -> p2
+```
+
+```{r, fig.width=2.25, fig.height=1}
+plot_grid <- rbind(c(1, 1, NA, 2, 2, 2),c(1, 1, NA, 2, 2, 2),c(1, NA, NA, 2, 2, 2))
+grid.arrange(p1, p2, layout_matrix=plot_grid)
+```

### 2018-01-31 voltagebudget/exp/pareto.py
cleanup

@@ -28,26 +28,24 @@ from platypus.core import Problem
 from platypus.types import Real
 
 
-def pareto(
-        name,
-        stim,
-        E_0,
-        N=10,
-        t=0.4,
-        d=-5e-3,
-        w=2e-3,
-        T=0.0625,
-        f=8,
-        A_max=0.5e-9,
-        M=100,
-        mode='regular',
-        noise=False,
-        #    scale=1.5,
-        save_only=False,
-        save_spikes=False,
-        score_group=False,
-        verbose=False,
-        seed_value=42):
+def pareto(name,
+           stim,
+           E_0,
+           N=10,
+           t=0.4,
+           d=-5e-3,
+           w=2e-3,
+           T=0.0625,
+           f=8,
+           A_max=0.5e-9,
+           M=100,
+           mode='regular',
+           noise=False,
+           save_only=False,
+           save_spikes=False,
+           score_group=False,
+           verbose=False,
+           seed_value=42):
     """Optimize using the voltage budget."""
     np.random.seed(seed_value)
 

### 2018-02-05 voltagebudget/exp/autotune.py
Added flag to adj the bias homeostatically with A.
exp33 is a first try with it.

modes.json sets 'regular' bias back to a scalar.

@@ -40,6 +40,7 @@ def autotune_V_osc(N,
                    mode='regular',
                    select_n=None,
                    noise=False,
+                   correct_bias=False,
                    seed_value=42,
                    shadow=False,
                    verbose=False):
@@ -92,6 +93,14 @@ def autotune_V_osc(N,
             """A new problem for each neuron"""
 
             A = p[0] / rescale
+            if correct_bias:
+                bias = bias_in - (A / 2.0)
+
+                if verbose:
+                    print(
+                        ">>> (bias {}) -> (bias_adj {})".format(bias_in, bias))
+            else:
+                bias = bias_in
 
             _, _, voltage = adex(
                 N,
@@ -102,7 +111,7 @@ def autotune_V_osc(N,
                 phi=phi,
                 f=f,
                 w_in=w_in,
-                bias_in=bias_in,
+                bias_in=bias,
                 sigma=sigma,
                 seed_value=seed_value,
                 budget=True,

### 2018-02-05 voltagebudget/exp/forward.py

@@ -43,6 +43,7 @@ def forward(name,
             save_only=False,
             save_spikes=False,
             score_group=False,
+            correct_bias=False,
             verbose=False,
             seed_value=42):
     """Optimize using the shadow voltage budget.
@@ -141,6 +142,7 @@ def forward(name,
         phi_0=phi_w,
         f=f,
         noise=noise,
+        correct_bias=correct_bias,
         seed_value=seed_value,
         verbose=verbose)
 
@@ -164,13 +166,20 @@ def forward(name,
         if verbose:
             print(">>> Running analysis for neuron {}/{}.".format(n + 1, N))
 
+        if correct_bias:
+            bias = bias_in - (A_opt / 2.0)
+            if verbose:
+                print(">>> (bias {}) -> (bias_adj {})".format(bias_in, bias))
+        else:
+            bias = bias_in
+
         ns_n, ts_n, voltage_n = adex(
             N,
             t,
             ns,
             ts,
             w_in=w_in,
-            bias_in=bias_in,
+            bias_in=bias,
             f=f,
             A=A_opt,
             phi=phi_E,

### 2018-02-23 voltagebudget/analysis/paper_figures.Rmd
vis updates

@@
 
-```{r, message=FALSE, fig.width=1.5, fig.height=1.3}
-name <- "../data/exp7_d-2e-3_f20.csv"
+```{r, message=FALSE, fig.width=3, fig.height=1.7}
+# --------------------------------------------------------------
+# V-fre dist
+name <- "../data/exp28_d-0.2e-3_f20.csv"
 results <- read_csv(paste(name, sep=""))
@@
   labs(x="V_free (mvolt)", y="Density (AU)") +
-  xlim(3, 6) +
+  xlim(1, 6) +
   theme_classic() -> p1
@@
   theme_classic() -> p2
-```
 
-```{r, message=FALSE, fig.width=3, fig.height=1.7}
+# --------------------------------------------------------------
+# rank 1/50
 # Load min, max V_free and neighbors
-name <- "../data/exp5_d-2e-3_f8_r1.csv"
+name <- "../data/exp29_d-0.2e-3_f20_r1.csv"
 rank1 <- read_csv(paste(name, sep=""))
@@
 
-name <- "../data/exp5_d-2e-3_f8_r2.csv"
-rank2 <- read_csv(paste(name, sep=""))
-rank2$rank <- rep(2, nrow(rank2))
+# name <- "../data/exp5_d-2e-3_f8_r2.csv"
+# rank2 <- read_csv(paste(name, sep=""))
+# rank2$rank <- rep(2, nrow(rank2))
+# 
+# name <- "../data/exp5_d-2e-3_f8_r3.csv"
+# rank3 <- read_csv(paste(name, sep=""))
+# rank3$rank <- rep(3, nrow(rank3))
 
-name <- "../data/exp5_d-2e-3_f8_r3.csv"
-rank3 <- read_csv(paste(name, sep=""))
-rank3$rank <- rep(3, nrow(rank3))
-
-name <- "../data/exp5_d-2e-3_f8_r50.csv"
+name <- "../data/exp29_d-0.2e-3_f20_r5.csv"
 rank50 <- read_csv(paste(name, sep=""))
@@
 
-name <- "../data/exp5_d-2e-3_f8_r49.csv"
-rank49 <- read_csv(paste(name, sep=""))
-rank49$rank <- rep(49, nrow(rank49))
-
-name <- "../data/exp5_d-2e-3_f8_r48.csv"
-rank48 <- read_csv(paste(name, sep=""))
-rank48$rank <- rep(48, nrow(rank48))
+# name <- "../data/exp5_d-2e-3_f8_r49.csv"
+# rank49 <- read_csv(paste(name, sep=""))
+# rank49$rank <- rep(49, nrow(rank49))
+# 
+# name <- "../data/exp5_d-2e-3_f8_r48.csv"
+# rank48 <- read_csv(paste(name, sep=""))
+# rank48$rank <- rep(48, nrow(rank48))
 
 # Group 'em
-ranked <- rbind(rank1, rank2, rank3, rank50, rank49, rank48)
-
+# ranked <- rbind(rank1, rank2, rank3, rank50, rank49, rank48)
+ranked <- rbind(rank1, rank50)
+# ranked$rank <- as.factor(ranked$rank)
 # -----------------------------------------------------
@@
   geom_line(alpha=0.4) +
-  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
+  scale_color_continuous(low="darkolivegreen3", high="goldenrod2") +
   theme_classic() -> p3
@@
 
-plot_grid <- rbind(c(1 , 1, NA, 3, 3, 3), c(2, 2, 2, 4, 4, 4))
-grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
+plot_grid <- rbind(c(1 , 1, 1, 3, 3, 3), c(1 , 1, 1, 3, 3, 3), c(1, 1, 1, 4, 4, 4), c(NA, NA, NA, 4, 4, 4))
+grid.arrange(p1, p3, p4, layout_matrix=plot_grid)
 ```
@@
 ```{r, message=FALSE, fig.width=2.2, fig.height=1.9}
-name <- "../data/exp4_d-2e-3_f12.csv"
+name <- "../data/exp36_d-0.2e-3_f20.csv"
 results <- read_csv(paste(name, sep=""))
+results %>% 
+  filter(n_spikes > 0, errors > 1e-5, V_osc < 7e-3) -> results
 
@@
   # filter(errors < 0.6, variances > 0) %>%
-  ggplot(aes(y=V_comp*1e3, x=V_osc*1e3, color=As)) +
-  scale_color_gradient(low="mediumpurple", high="red3", name="A") +
-  xlab("Vc (mvolt)") + ylab("Vo (mvolt)") +
+  ggplot(aes(y=V_comp*1e3, x=V_osc*1e3, color=As*1e9)) +
+  scale_color_gradient(low="mediumpurple", high="red3", name="A\n(namp)") +
+  xlab("Vo (mvolt)") + ylab("Vc (mvolt)") +
   geom_point(alpha=0.4) + 
+  xlim(4.5, 7) +
   theme_classic() + 
-  theme(legend.position="bottom", legend.key.size =  unit(0.3, "in")) -> p1
+  theme(legend.position="bottom", legend.key.size =  unit(0.25, "in")) -> p1
+
+# results %>% 
+#   ggplot(aes(x=1e3*V_free, y=normalize(variances))) +
+#   geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE, linetype="dashed") + 
+#   geom_point(color="red3", alpha=0.2) +
+#   geom_smooth(aes(x=1e3*V_free, y=normalize(errors)), 
+#               method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", se=FALSE,linetype="dashed") + 
+#   geom_point(aes(x=1e3*V_free, y=normalize(errors)), color="mediumpurple", alpha=0.2) +
+#   geom_vline(aes(xintercept = mean(1e3*V_free)), color="black") +
+#   xlab("Vf (mvolt)") +
+#   ylab("Normalized") +
+#   theme_classic() -> p2
 
 results %>% 
-  ggplot(aes(x=1e3*V_free, y=normalize(variances))) +
-  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE, linetype="dashed") + 
-  # geom_point(color="red3", alpha=0.2) + 
-  geom_smooth(aes(x=1e3*V_free, y=normalize(errors)), 
-              method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", se=FALSE,linetype="dashed") + 
-  # geom_point(aes(x=1e3*V_free, y=normalize(errors)), color="mediumpurple", alpha=0.2) + 
-  geom_vline(aes(xintercept = mean(1e3*V_free)), color="black") +
-  xlab("Vf (mvolt)") +
-  ylab("Normalized") +
-  theme_classic() -> p2
-
-results %>% 
-  ggplot(aes(x=1e3*V_comp, y=errors)) +
-  geom_point(alpha=0.4, size=.3, color="mediumpurple") +
-  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", alpha=0.2, se=FALSE, linetype="dashed") + 
-  xlab("Vc (mvolt)") +
-  ylab("Errors (s)") +
+  ggplot(aes(x=1e3*V_osc, y=errors*1e3)) +
+  geom_point(alpha=0.4, size=.5, color="mediumpurple") +
+  geom_smooth(color="mediumpurple", alpha=0.2, size=0.8, se=FALSE, linetype="dashed") +
+  # geom_smooth(method = 'nls', formula = y ~ x, se = FALSE) + #, start=list(b=1)) #, start = list(a=1,b=.1)) +
+  xlab("Vo (mvolt)") +
+  ylab("Error (ms)") +
+  xlim(4.5, 7) +
+  # ylim(0, 1e3*5e-3) +
   theme_classic() -> p3
@@
 results %>% 
-  ggplot(aes(x=1e3*V_osc, y=variances)) +
-  geom_point(alpha=0.3, size=.3, color="red3") +
-  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE, linetype="dashed") + 
+  ggplot(aes(x=1e3*V_osc, y=variances*1e3)) +
+  geom_point(alpha=0.3, size=.5, color="red3") +
+  geom_smooth(color="red3", alpha=0.5, size=0.8, se=FALSE, linetype="dashed", formula = y ~ x, method=lm) +
   xlab("Vo (mvolt)") +
-  ylab("Variance (s)") +
+  ylab("Variance (ms)") +
+  xlim(4.5, 7) +
+  # ylim(1e3*0.0096, 1e3*0.0102) +
   theme_classic() -> p4
 
-plot_grid <- rbind(c(NA ,NA, 3, 3), c(NA, NA, 3, 3), c(NA, NA, 4, 4), c(1 ,1, 4, 4), c(1, 1, 2, 2), c(1, 1, 2, 2))
-grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
-```
+# plot_grid <- rbind(c(NA ,NA, 3, 3), c(NA, NA, 3, 3), c(NA, NA, 4, 4), c(1 ,1, 4, 4), c(1, 1, 2, 2), c(1, 1, 2, 2))
+# grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
 
-# Voltage timecourses many neurons
-
-```{r}
-vms <- read_csv("vm_full_examples.csv")
-vms <- gather(vms, "neuron", "vm", 2:21)
-wins <- read_csv("vm_window_examples_d2_w2.csv")
-wins <- gather(wins, "neuron", "vm", 2:21)
-```
-
-```{r, fig.width=1.5, fig.height=1}
-vms %>% 
-  filter(t > 0.15, t < 0.35) %>%
-  ggplot(aes(x=t, y=vm, group=neuron)) +
-  geom_line(color="black", alpha=0.3, size=0.2) +
-  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
-  labs(x="Time (s)", y="Vm (mV)") +
-  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.25) +
-  geom_hline(yintercept=-70e-3, color="black", size=2) +
-  geom_vline(xintercept = 0.25719 + 2e-3, color="darkgreen", alpha=0.5, size=0.2) +
-  geom_vline(xintercept = 0.25719 + 2e-3 +  0.03333333, color="darkgreen", alpha=0.5, size=0.2) +
-  theme_classic()
-```
-
-```{r, fig.width=0.4, fig.height=0.8}
-vms %>% 
-  filter(t > 0.25, t < 0.27) %>%
-  ggplot(aes(x=t, y=vm, group=neuron)) +
-  geom_line(color="black", alpha=0.3, size=0.2) +
-  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
-  labs(x="Time (s)", y="Vm (mV)") +
-  geom_hline(yintercept=-50e-3, color="black", linetype="dashed", size=1) +
-  geom_hline(yintercept=-70e-3, color="black", size=2) +
-  theme(axis.line=element_blank(),
-      axis.text.x=element_blank(),
-      axis.text.y=element_blank(),
-      axis.ticks=element_blank(),
-      axis.title.x=element_blank(),
-      axis.title.y=element_blank(),
-      legend.position="none",
-      panel.background=element_blank(),
-      panel.border=element_blank(),
-      panel.grid.major=element_blank(),
-      panel.grid.minor=element_blank(),
-      plot.background=element_blank())
-  # theme_classic()
+plot_grid <- rbind(c(NA ,NA, 2, 2), 
+                   c(NA, NA, 2, 2), 
+                   c(NA, NA, 2, 2), 
+                   c(1, 1, 2, 2), 
+                   c(1, 1, 3, 3), 
+                   c(1, 1, 3, 3), 
+                   c(1, 1, 3, 3), 
+                   c(1 ,1, 3, 3),
+                   c(NA ,NA, NA, NA))
+grid.arrange(p1, p3, p4, layout_matrix=plot_grid)
 ```
@@
 ```{r, fig.width=2.25, fig.height=1}
-plot_grid <- rbind(c(1, 1, NA, 2, 2, 2),c(1, 1, NA, 2, 2, 2),c(1, NA, NA, 2, 2, 2))
+plot_grid <- rbind(c(1, 1, NA, 2, 2, 2),c(1, 1, NA, 2, 2, 2),c(NA, NA, NA, 2, 2, 2))
 grid.arrange(p1, p2, layout_matrix=plot_grid)

### 2018-02-23 voltagebudget/analysis/ranked_analysis.Rmd
vis updates

@@
 ```{r, message=FALSE}
-name <- "../data/exp18_d-2e-3_f12_r50.csv"
+name <- "../data/exp44_d-0.2e-3_f12_r300.csv"
 results <- read_csv(paste(name, sep=""))
+print(range(results$rank))
+results %>%
+  filter(n_spikes > 0, rank==299) -> results
 ```
@@
 results %>% 
-  ggplot(aes(x=delta_variances)) +
+  ggplot(aes(x=variances)) +
   geom_histogram(bins=20) + 
@@
 
+## A and V
+
 ```{r, fig.width=2.5, fig.height=1}
 results %>% 
-  ggplot(aes(x=V_free, y=V_osc, color=errors)) +
+  # filter(errors < 0.6, coincidence_count > 0) %>%
+  ggplot(aes(x=sort(V_free), y=errors, color=As)) +
   geom_point() + 
@@
 results %>% 
-  ggplot(aes(x=N, y=sort(errors))) +
-  ylim(0, 0.030) +
+  # filter(errors < 0.6, coincidence_count > 0) %>%
+  ggplot(aes(x=As, y=V_osc/V_b)) +
   geom_point() + 
@@
 results %>% 
-  ggplot(aes(x=N, y=sort(delta_variances))) +
+  # filter(errors < 0.6, coincidence_count > 0) %>%
+  ggplot(aes(x=V_osc, y=V_comp, color=As)) +
   geom_point() + 
-  ylim(-0.030, 0.030) +
-  geom_hline(aes(yintercept=0), color="black", alpha=0.6) +
   theme_classic()
@@
 
-```{r, fig.width=1.5, fig.height=1}
+### As
+
+```{r, fig.width=2.5, fig.height=1}
 results %>% 
   # filter(errors < 0.6, coincidence_count > 0) %>%
-  ggplot(aes(x=V_comp, y=normalize(delta_variances))) +
-  geom_point(color="red", alpha=0.5) + 
-  xlab("Vc (mvolt)") +
-  ylab("Rel. scores (AU)") +
-  geom_point(aes(x=V_comp, y=normalize(errors)), color="purple") + 
+  ggplot(aes(x=As, y=variances)) +
+  geom_point() + 
   theme_classic()
 ```
+
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  # filter(errors < 0.6, coincidence_count > 0) %>%
+  ggplot(aes(x=As, y=errors)) +
+  geom_point() + 
+  theme_classic()
+```
+
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  # filter(errors < 0.6, coincidence_count > 0) %>%
+  ggplot(aes(x=As, y=n_spikes)) +
+  geom_point() + 
+  theme_classic()
+```
+
+### V_f
+
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  # filter(errors < 0.6, coincidence_count > 0) %>%
+  ggplot(aes(x=sort(V_free), y=variances)) +
+  geom_point() + 
+  theme_classic()
+```
+
+### V_osc/V_B
+
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  # filter(errors < 0.6, coincidence_count > 0) %>%
+  ggplot(aes(x=V_osc, y=variances)) +
+  geom_point() + 
+  theme_classic()
+```
+
+```{r, fig.width=2.5, fig.height=1.5}
+results %>% 
+  # filter(errors < 0.6, coincidence_count > 0) %>%
+  ggplot(aes(x=V_osc/V_b, y=errors)) +
+  geom_point() + 
+  theme_classic()
+```
+
+```{r, fig.width=2.5, fig.height=1.5}
+results %>% 
+  # filter(errors < 0.6, coincidence_count > 0) %>%
+  ggplot(aes(x=errors, y=variances, color=As)) +
+  geom_point() + 
+  theme_classic()
+```

### 2018-02-26 voltagebudget/analysis/ranked_analysis.Rmd
Improved rank vis

--- 2018-01-30 voltagebudget/analysis/ranked_analysis.Rmd
@@
 ```{r, message=FALSE}
-name <- "../data/exp18_d-2e-3_f12_r50.csv"
-results <- read_csv(paste(name, sep=""))
+name1 <- "../data/exp48_d-0.2e-3_f4_r1.csv"
+name2 <- "../data/exp48_d-0.2e-3_f4_r100.csv"
+
+results1 <- read_csv(paste(name1, sep=""))
+results2 <- read_csv(paste(name2, sep=""))
+
+results1 %>%
+  mutate(rank = rep("1", nrow(results1))) %>% filter(n_spikes > 0) -> results1
+results2 %>%
+  mutate(rank = rep("100", nrow(results2))) %>% filter(n_spikes > 0) -> results2
+
+results <- rbind(results1, results2)
+rm(results1, results2)
 ```
@@
 results %>% 
-  ggplot(aes(x=delta_variances)) +
+  ggplot(aes(x=variances, fill=rank)) +
   geom_histogram(bins=20) + 
@@
 results %>% 
-  ggplot(aes(x=errors)) +
+  ggplot(aes(x=errors, fill=rank)) +
   geom_histogram(bins=20) + 
@@
 results %>% 
-  ggplot(aes(x=V_osc)) +
+  ggplot(aes(x=V_osc/V_b, fill=rank)) +
   geom_histogram(bins=20) +
@@
 results %>% 
-  ggplot(aes(x=V_comp)) +
+  ggplot(aes(x=V_comp/V_b, fill=rank)) +
   geom_histogram(bins=20) +
@@
 results %>% 
-  ggplot(aes(x=V_free, y=V_osc, color=errors)) +
+  ggplot(aes(x=As, y=V_osc/V_b, color=rank)) +
   geom_point() + 
@@
 results %>% 
-  ggplot(aes(x=N, y=sort(errors))) +
-  ylim(0, 0.030) +
+  ggplot(aes(x=As, y=V_comp/V_b, color=rank)) +
   geom_point() + 
@@
 results %>% 
-  ggplot(aes(x=N, y=sort(delta_variances))) +
+  ggplot(aes(x=V_osc/V_b, y=V_comp/V_b, color=rank)) +
   geom_point() + 
-  ylim(-0.030, 0.030) +
-  geom_hline(aes(yintercept=0), color="black", alpha=0.6) +
   theme_classic()
@@
 
-```{r, fig.width=1.5, fig.height=1}
+```{r, fig.width=2.5, fig.height=1}
 results %>% 
-  # filter(errors < 0.6, coincidence_count > 0) %>%
-  ggplot(aes(x=V_comp, y=normalize(delta_variances))) +
-  geom_point(color="red", alpha=0.5) + 
-  xlab("Vc (mvolt)") +
-  ylab("Rel. scores (AU)") +
-  geom_point(aes(x=V_comp, y=normalize(errors)), color="purple") + 
+  ggplot(aes(x=V_free/V_b, y=n_spikes, color=rank)) +
+  geom_point() + 
   theme_classic()
 ```
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  ggplot(aes(x=n_spikes, y=errors, color=rank)) +
+  geom_point() + 
+  theme_classic()
+```
+
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  ggplot(aes(x=n_spikes, y=variances, color=rank)) +
+  geom_point() + 
+  theme_classic()
+```
+
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  ggplot(aes(x=V_free/V_b, y=variances, color=rank)) +
+  geom_point() + 
+  theme_classic()
+```
+
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  ggplot(aes(x=V_free/V_b, y=errors, color=rank)) +
+  geom_point() + 
+  theme_classic()
+```
+
+### As
+
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  ggplot(aes(x=V_osc/V_b, y=variances, color=rank)) +
+  geom_point() + 
+  theme_classic()
+```
+
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  ggplot(aes(x=V_osc/V_b, y=errors, color=rank)) +
+  geom_point() + 
+  theme_classic()
+```
+
+```{r, fig.width=2.5, fig.height=1}
+results %>% 
+  ggplot(aes(x=V_osc/V_b, y=n_spikes, color=rank)) +
+  geom_point() + 
+  theme_classic()
+```
+
+```{r, fig.width=1.75, fig.height=1.25}
+results %>% 
+  filter(variances > 0, errors > 0) %>% 
+  ggplot(aes(x=variances, y=errors, color=rank)) +
+  geom_point() + 
+  theme_classic()
+```

### 2018-02-26 voltagebudget/exp/population.py
bugfix in population -budget terms were wrong when not using ranked analyses.

@@ -232,6 +232,10 @@ def population(name,
         if save_spikes:
             write_spikes("{}_n_{}_spks".format(name, n), ns_n, ts_n)
 
+        # Get budget terms
+        budget_n = budget_window(voltage_n, E + d, w, select=None)
+        V_b = float(voltage_n['V_budget'])
+
         # Pick the neuron to analyze, defaults to n
         if analyze_rank is None:
             # Analyze for population avgs.
@@ -240,6 +244,10 @@ def population(name,
             if verbose:
                 print(">>> Analyzing sol {} by population".format(n))
 
+            # Extract nth budget values
+            V_osc = np.abs(np.mean(budget_n['V_osc'][n, :]))
+            V_comp = np.abs(np.mean(budget_n['V_comp'][n, :]))
+            V_free = np.abs(np.mean(budget_n['V_free'][n, :]))
         else:
             # Filter for k-only analysis
             ns_ref_k, ts_ref_k = select_n(k, ns_ref, ts_ref)
@@ -251,12 +259,10 @@ def population(name,
             if verbose:
                 print(">>> Analyzing sol {} at neuron {}".format(n, k))
 
-        # Extract kth budget values
-        budget_n = budget_window(voltage_n, E + d, w, select=None)
-        V_osc = np.abs(np.mean(budget_n['V_osc'][k, :]))
-        V_comp = np.abs(np.mean(budget_n['V_comp'][k, :]))
-        V_free = np.abs(np.mean(budget_n['V_free'][k, :]))
-        V_b = float(voltage_n['V_budget'])
+            # Extract kth budget values
+            V_osc = np.abs(np.mean(budget_n['V_osc'][k, :]))
+            V_comp = np.abs(np.mean(budget_n['V_comp'][k, :]))
+            V_free = np.abs(np.mean(budget_n['V_free'][k, :]))
 
         # Store all stats for n
         variances.append(var)

### 2018-02-27 voltagebudget/exp/min_max.py
docs - min_max

@@ -245,10 +245,10 @@ def min_max(name,
         ns_ref, ts_ref = filter_spikes(ns_ref, ts_ref, (E, E + T))
         ns_i, ts_i = filter_spikes(ns_i, ts_i, (E, E + T))
 
-        # Want group var(ts_i)
+        # Want group var(ts_i),
         var, _ = score_by_group(ts_ref, ts_i)
 
-        # But individual n error
+        # but individual error for only n.
         _, ts_ref_n = select_n(n, ns_ref, ts_ref)
         _, ts_i_n = select_n(n, ns_i, ts_i)
         _, error = score_by_group(ts_ref_n, ts_i_n)
@@ -256,7 +256,7 @@ def min_max(name,
         # Save scores
         variances.append(var)
         errors.append(np.mean(error))
-        n_spikes.append(ts_i.size)
+        n_spikes.append(ts_i_n.size)
 
         # Extract budget values and save 'em
         budget_i = budget_window(voltage_i, E + d, w, select=None)
@@ -279,7 +279,7 @@ def min_max(name,
         if verbose:
             print(
                 ">>> (A {:0.18f})  ->  (N spks, {}, mae {:0.5f}, mad, {:0.5f})".
-                format(A_i, ns_i.size / float(N), error, var))
+                format(A_i, ts_i_n.size / float(N), error, var))
 
     # --------------------------------------------------------------
     if verbose:

### 2018-03-02 voltagebudget/analysis/min_max_delay_analysis.Rmd
tweaks to vis

---
title: "min/max V_f - delay (d) experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

# Load and process

```{r, message=FALSE}
exp <- "62"
freq <- c("20")

delays <- c("-2e-3", "-4e-3", "-6e-3", "-8e-3", "-10e-3")

results <- NULL
for(d in delays){
  name <- paste("../data/exp", exp, "_d", d, "_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df %>%
    filter(n_spikes > 0) -> df

  df$delay <- rep(d, nrow(df))

  results <- rbind(results, df)
}

results$delay <- factor(results$delay, levels=delays)
rm(df, exp, delays, d, name, freq)
```

# Overall distributions

```{r, fig.width=2.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=variances)) +
  geom_histogram(bins=20) + 
  xlab("Variance") +
  theme_classic() -> p1

results %>% 
  ggplot(aes(x=errors)) +
  geom_histogram(bins=20) + 
  xlab("Error") +
  theme_classic() -> p2

results %>% 
  ggplot(aes(x=V_osc/V_b)) +
  geom_histogram(bins=20) +
  xlab("Vc (volt)") +
  theme_classic() -> p3

results %>% 
  ggplot(aes(x=V_comp/V_b)) +
  geom_histogram(bins=20) +
  xlab("Vo (volt)") +
  theme_classic() -> p4

grid.arrange(p1, p2, p3, p4, nrow=2)
rm(p1, p2, p3, p4)
```

# As

```{r, fig.width=1.2, fig.height=2.5}
results %>% 
  ggplot(aes(x=As*1e9, y=n_spikes, color=delay)) +
  geom_line() + 
  theme_classic() +
  facet_grid(delay~.) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=As*1e9, y=variances, color=delay)) +
  facet_grid(delay~.) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

- why is var so variable?

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=As*1e9, y=errors, color=delay)) +
  facet_grid(delay~.) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=V_comp/V_b, y=errors, color=delay)) +
  facet_grid(delay~.) +
  geom_point(size=0.1) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=3}
results %>% 
  ggplot(aes(x=variances, y=errors, color=delay)) +
  geom_line() + 
  theme_classic() +
  facet_grid(delay~.) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=n_spikes, y=variances, color=delay)) +
  geom_point(size=0.1) + 
  theme_classic() +
  facet_grid(delay~.) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=n_spikes, y=errors, color=delay)) +
  geom_point(size=0.1) + 
  theme_classic() +
  facet_grid(delay~.) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

# Budget

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=As*1e9, y=V_osc/V_b, color=delay)) +
  geom_line() + 
  theme_classic() +
  facet_grid(delay~.) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=As*1e9, y=V_comp/V_b, color=delay)) +
  geom_line() + 
  theme_classic() +
  facet_grid(delay~.) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=V_comp/V_b, color=delay)) +
  geom_line() +
  theme_classic() +
  facet_grid(delay~.) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=n_spikes, color=delay)) +
  geom_line() + 
  theme_classic() +
  facet_grid(delay~.) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=variances, color=delay)) +
  geom_line() + 
  theme_classic() +
  facet_grid(delay~.) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=2.5}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=errors, color=delay)) +
  geom_line() + 
  theme_classic() +
  facet_grid(delay~.) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

### 2018-03-02 voltagebudget/analysis/sweep_A_analysis.Rmd
tweaks to vis

---
title: "Sweep A - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

# Load and process

```{r, message=FALSE}
exp <- "58"
freqs <- c("4", "8", "12", "20", "24", "30")

results <- NULL
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-0.2e-3_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df %>%
    filter(n_spikes > 0) -> df

  df$freq <- rep(freq, nrow(df))
  results <- rbind(results, df)
}

results$freq <- factor(results$freq, levels=freqs)
rm(df, exp, freq, freqs, levels, name)
```

# Overall distributions

```{r, fig.width=2.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=variances)) +
  geom_histogram(bins=20) + 
  xlab("Variance") +
  theme_classic() -> p1

results %>% 
  ggplot(aes(x=errors)) +
  geom_histogram(bins=20) + 
  xlab("Error") +
  theme_classic() -> p2

results %>% 
  ggplot(aes(x=V_osc/V_b)) +
  geom_histogram(bins=20) +
  xlab("Vc (volt)") +
  theme_classic() -> p3

results %>% 
  ggplot(aes(x=V_comp/V_b)) +
  geom_histogram(bins=20) +
  xlab("Vo (volt)") +
  theme_classic() -> p4

grid.arrange(p1, p2, p3, p4, nrow=2)
rm(p1, p2, p3, p4)
```

# As

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=As, y=n_spikes, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=As, y=variances, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

- why is var so variable?

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=As, y=errors, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=variances, y=errors, color=freq)) +
  geom_point(size=.05) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=3.5}
results %>% 
  ggplot(aes(x=variances, y=errors, color=freq)) +
  geom_point(size=.05) + 
  facet_grid(freq~.) +
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

# Number spikes

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=n_spikes, y=variances, color=freq)) +
  geom_point(size=0.1) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=n_spikes, y=errors, color=freq)) +
  geom_point(size=0.1) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

# Budget

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=As, y=V_osc, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=2, fig.height=1.5}
results %>% 
  ggplot(aes(x=V_osc, y=V_comp, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=3.5}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=V_comp/V_b, color=As)) +
  geom_line() + 
  theme_classic() +
  facet_grid(freq~.) +
  # scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=n_spikes, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=variances, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=errors, color=freq)) +
  geom_line() + 
  theme_classic() +
  xlim(0, 1.5) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_comp/V_b, y=errors, color=freq)) +
  geom_point(size=0.05) + 
  theme_classic() +
  xlim(0, 0.7) +
  ylim(0, 0.010) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(V_comp <= V_osc - min(V_osc)) %>% 
  ggplot(aes(x=V_comp/V_b, y=errors, color=freq)) +
  geom_point(size=0.05) + 
  theme_classic() +
  xlim(0, 0.7) +
  ylim(0, 0.010) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_comp/V_osc, y=variances, color=freq)) +
  geom_point(size=0.05) + 
  theme_classic() +
  # xlim(0, 0.7) +
  # ylim(0, 0.010) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_comp/V_osc, y=errors, color=freq)) +
  geom_point(size=0.05) + 
  theme_classic() +
  # xlim(0, 0.7) +
  # ylim(0, 0.010) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_comp/V_b, y=variances, color=freq)) +
  geom_point(size=0.05) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

### 2018-03-02 voltagebudget/exp/min_max.py
sweep_A + min_max - Refactor E, phi; properly norming V_osc

@@ -25,6 +25,9 @@ from voltagebudget.util import mae
 from voltagebudget.util import select_n
 from voltagebudget.util import score_by_group
 from voltagebudget.util import score_by_n
+from voltagebudget.util import find_E
+from voltagebudget.util import find_phis
+
 from voltagebudget.exp.autotune import autotune_V_osc
 
 from scipy.optimize import least_squares
@@ -48,6 +51,7 @@ def min_max(name,
             target='min',
             noise=False,
             scale_w_in=1,
+            no_lock=False,
             correct_bias=False,
             save_only=False,
             verbose=False,
@@ -108,23 +112,9 @@ def min_max(name,
         raise ValueError("The reference model didn't spike.")
 
     # --------------------------------------------------------------
-    # Find the ref spike closest to E_0
-    # and set that as E
-    if np.isclose(E_0, 0.0):
-        _, E = locate_firsts(ns_ref, ts_ref, combine=True)
-        if verbose:
-            print(">>> Locking on first spike. E was {}.".format(E))
-    else:
-        E = nearest_spike(ts_ref, E_0)
-        if verbose:
-            print(
-                ">>> ts_ref min {}, max {}".format(ts_ref.min(), ts_ref.max()))
-            print(">>> E_0 was {}, using closest at {}.".format(E_0, E))
-
-    # --------------------------------------------------------------
-    # Find the phase begin a osc cycle at E 
-    phi_E = float(-E * 2 * np.pi * f)
-    phi_w = float((-(E + d) * 2 * np.pi * f) + np.pi / 2)
+    # Find E and phis
+    E = find_E(E_0, ns_ref, ts_ref, no_lock=no_lock, verbose=verbose)
+    phi_w, phi_E = find_phis(E, f, d, verbose=verbose)
 
     # --------------------------------------------------------------
     # Filter ref spikes into the window of interest
@@ -258,7 +248,7 @@ def min_max(name,
 
         # Extract budget values and save 'em
         budget_i = budget_window(voltage_i, E + d, w, select=None)
-        V_osc = np.abs(np.mean(budget_i['V_osc'][n, :]))
+        V_osc = np.abs(np.mean(budget_i['V_osc'][n, :]) - budget_ref['V_osc'][n, :]))
         V_comp = np.abs(np.mean(budget_i['V_comp'][n, :]))
         V_free = np.abs(np.mean(budget_i['V_free'][n, :]))
         V_free_ref = np.abs(np.mean(budget_ref['V_free'][n, :]))

### 2018-03-02 voltagebudget/exp/sweep_A.py

@@ -25,6 +25,9 @@ from voltagebudget.util import mae
 from voltagebudget.util import select_n
 from voltagebudget.util import score_by_group
 from voltagebudget.util import score_by_n
+from voltagebudget.util import find_E
+from voltagebudget.util import find_phis
+
 from voltagebudget.exp.autotune import autotune_V_osc
 
 from scipy.optimize import least_squares
@@ -44,6 +47,7 @@ def sweep_A(name,
             N=10,
             mode='regular',
             noise=False,
+            no_lock=False,
             verbose=False,
             save_only=False,
             seed_value=42):
@@ -97,20 +101,10 @@ def sweep_A(name,
     if ns_ref.size == 0:
         raise ValueError("The reference model didn't spike.")
 
-    # Find the ref spike closest to E_0
-    # and set that as E
-    if np.isclose(E_0, 0.0):
-        _, E = locate_firsts(ns_ref, ts_ref, combine=True)
-        if verbose:
-            print(">>> Locking on first spike. E was {}.".format(E))
-    else:
-        E = nearest_spike(ts_ref, E_0)
-        if verbose:
-            print(">>> E_0 was {}, using closest at {}.".format(E_0, E))
-
-    # Find the phase begin a osc cycle at E 
-    phi_E = float(-E * 2 * np.pi * f)
-    phi_w = float((-(E + d) * 2 * np.pi * f) + np.pi / 2)
+    # --------------------------------------------------------------
+    # Find E and phis
+    E = find_E(E_0, ns_ref, ts_ref, no_lock=no_lock, verbose=verbose)
+    phi_w, phi_E = find_phis(E, f, d, verbose=verbose)
 
     # Filter ref spikes into the window of interest
     ns_ref, ts_ref = filter_spikes(ns_ref, ts_ref, (E, E + T))
@@ -180,11 +174,10 @@ def sweep_A(name,
         # Analyze!
 
         # Filter spikes in E    
-        ns_ref, ts_ref = filter_spikes(ns_ref, ts_ref, (E, E + T))
         ns_i, ts_i = filter_spikes(ns_i, ts_i, (E, E + T))
 
         # Want group var(ts_i)
-        var, _ = score_by_group(ts_ref, ts_i)
+        var = mad(ts_i)
 
         # But avg of individual {n in N} errors
         _, error = score_by_n(N, ns_ref, ts_ref, ns_i, ts_i)
[…]

### 2018-03-02 voltagebudget/util.py

@@ -207,6 +207,35 @@ def mae(x, y, axis=None):
     return np.mean(np.absolute(x[:min_l] - y[:min_l]), axis)
 
 
+def find_E(E_0, ns_ref, ts_ref, no_lock=False, verbose=False):
+    """Find the ref spike closest to E_0"""
+
+    if no_lock:
+        return E_0
+
+    if np.isclose(E_0, 0.0):
+        _, E = locate_firsts(ns_ref, ts_ref, combine=True)
+        if verbose:
+            print(">>> Locking on first spike. E was {}.".format(E))
+    else:
+        E = nearest_spike(ts_ref, E_0)
+        if verbose:
+            print(">>> E_0 was {}, using closest at {}.".format(E_0, E))
+
+    return E
+
+
+def find_phis(E, f, d, verbose=False):
+    """Find the phase begin a osc cycle at (E + d)"""
+    phi_E = float(-E * 2 * np.pi * f)
+    phi_w = float((-(E + d) * 2 * np.pi * f) + np.pi / 2)
+
+    if verbose:
+        print(">>> phi_w {}, phi_E {}".format(phi_w, phi_E))
+
+    return phi_w, phi_E
+
+
 def score_by_group(ts_ref, ts_n):
     var = mad(ts_n)
     error = mae(ts_n, ts_ref)

### 2018-03-07 voltagebudget/exp/min_max.py
bugfix - sweep_A/min_max

@@ -54,6 +54,7 @@ def min_max(name,
             no_lock=False,
             correct_bias=False,
             save_only=False,
+            save_details=False,
             verbose=False,
             seed_value=42):
     """Fit A to the min free voltage, then explore a 
@@ -178,7 +179,9 @@ def min_max(name,
     errors = []
     n_spikes = []
     V_oscs = []
+    V_osc_refs = []
     V_comps = []
+    V_comp_refs = []
     V_frees = []
     V_free_refs = []
     V_budgets = []
@@ -246,19 +249,28 @@ def min_max(name,
         errors.append(np.mean(error))
         n_spikes.append(ts_i_n.size)
 
+        # -------------------------------------------------------------------
         # Extract budget values and save 'em
+        # ith
         budget_i = budget_window(voltage_i, E + d, w, select=None)
-        V_osc = np.abs(
-            np.mean(budget_i['V_osc'][n, :] - budget_ref['V_osc'][n, :]))
+
+        V_b = float(voltage_i['V_budget'])
+        V_osc = np.abs(np.mean(budget_i['V_osc'][n, :]))
         V_comp = np.abs(np.mean(budget_i['V_comp'][n, :]))
         V_free = np.abs(np.mean(budget_i['V_free'][n, :]))
-        V_free_ref = np.abs(np.mean(budget_ref['V_free'][n, :]))
-        V_b = float(voltage_i['V_budget'])
 
+        # ref
+        V_comp_ref = np.abs(np.mean(budget_ref['V_comp'][n, :]))
+        V_osc_ref = np.abs(np.mean(budget_ref['V_osc'][n, :]))
+
+        # Save 'em all
         V_oscs.append(V_osc)
+        V_osc_refs.append(V_osc_ref)
+
         V_comps.append(V_comp)
+        V_comp_refs.append(V_comp_ref)
+
         V_frees.append(V_free)
-        V_free_refs.append(V_free_ref)
         V_budgets.append(V_b)
         As.append(A_i)
 
@@ -267,10 +279,23 @@ def min_max(name,
         phis.append(phi_E)
         phis_w.append(phi_w)
 
+        # -------------------------------------------------------------------
         if verbose:
             print(
-                ">>> (A {:0.18f})  ->  (N spks, {}, mae {:0.5f}, mad, {:0.5f})".
-                format(A_i, ts_i_n.size / float(N), error, var))
[…]

### 2018-03-07 voltagebudget/exp/sweep_A.py

@@ -18,8 +18,8 @@ from voltagebudget.util import locate_firsts
 from voltagebudget.util import filter_spikes
 from voltagebudget.util import budget_window
 from voltagebudget.util import locate_peaks
-from voltagebudget.util import estimate_communication
-from voltagebudget.util import precision
+from voltagebudget.util import write_spikes
+from voltagebudget.util import write_voltages
 from voltagebudget.util import mad
 from voltagebudget.util import mae
 from voltagebudget.util import select_n
@@ -50,6 +50,7 @@ def sweep_A(name,
             no_lock=False,
             verbose=False,
             save_only=False,
+            save_details=False,
             seed_value=42):
     """Optimize using the shadow voltage budget."""
 
@@ -122,7 +123,9 @@ def sweep_A(name,
     errors = []
     n_spikes = []
     V_oscs = []
+    V_osc_refs = []
     V_comps = []
+    V_comp_refs = []
     V_frees = []
     V_budgets = []
     As = []
@@ -187,15 +190,27 @@ def sweep_A(name,
         errors.append(np.mean(error))
         n_spikes.append(ts_i.size)
 
+        # -------------------------------------------------------------------
         # Extract budget values and save 'em
+        # ith
         budget_i = budget_window(voltage_i, E + d, w, select=None)
-        V_osc = np.abs(np.mean(budget_i['V_osc'] - budget_ref['V_osc']))
+
+        V_b = float(voltage_i['V_budget'])
+        V_osc = np.abs(np.mean(budget_i['V_osc']))
         V_comp = np.abs(np.mean(budget_i['V_comp']))
         V_free = np.abs(np.mean(budget_i['V_free']))
-        V_b = float(voltage_i['V_budget'])
 
+        # ref
+        V_comp_ref = np.abs(np.mean(budget_ref['V_comp']))
+        V_osc_ref = np.abs(np.mean(budget_ref['V_osc']))
+
+        # Save 'em all
         V_oscs.append(V_osc)
+        V_osc_refs.append(V_osc_ref)
+
         V_comps.append(V_comp)
+        V_comp_refs.append(V_comp_ref)
+
         V_frees.append(V_free)
         V_budgets.append(V_b)
         As.append(A_i)
@@ -205,10 +220,23 @@ def sweep_A(name,
         phis.append(phi_E)
         phis_w.append(phi_w)
 
+        # -------------------------------------------------------------------
         if verbose:
[…]

### 2018-03-07 voltagebudget/analysis/sweep_A_analysis.Rmd
update vis

@@
 results %>% 
-  ggplot(aes(x=As, y=V_osc, color=freq)) +
+  ggplot(aes(x=As*1e9, y=V_osc, color=freq)) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  ggplot(aes(x=As*1e9, y=V_comp, color=freq)) +
   geom_line() + 

### 2018-03-10 voltagebudget/analysis/sweep_A_analysis.Rmd
Update sweep_A vis

--- 2018-03-02 voltagebudget/analysis/sweep_A_analysis.Rmd
@@
 ```{r, message=FALSE}
-exp <- "58"
-freqs <- c("4", "8", "12", "20", "24", "30")
+exp <- "71"
+freqs <- c("8", "12", "20", "24", "30")
 
@@
 for(freq in freqs){
-  name <- paste("../data/exp", exp, "_d-0.2e-3_f", freq, ".csv", sep="")
+  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
   df <- read_csv(paste(name, sep=""))
@@
 results$freq <- factor(results$freq, levels=freqs)
-rm(df, exp, freq, freqs, levels, name)
+rm(df, exp, freq, freqs, name)
 ```
@@
 results %>% 
-  ggplot(aes(x=As, y=n_spikes, color=freq)) +
+  filter(rank == 0) %>% 
+  ggplot(aes(x=As, y=n_spikes_pop, color=freq)) +
   geom_line() + 
@@
 results %>% 
-  ggplot(aes(x=As, y=variances, color=freq)) +
+  filter(rank == 0) %>% 
+  ggplot(aes(x=As, y=variances_pop, color=freq)) +
   geom_line() + 
@@
 
-- why is var so variable?
-
 ```{r, fig.width=1.6, fig.height=1.6}
 results %>% 
-  ggplot(aes(x=As, y=errors, color=freq)) +
+  filter(rank == 0) %>% 
+  ggplot(aes(x=As, y=errors_pop, color=freq)) +
   geom_line() + 
@@
 results %>% 
-  ggplot(aes(x=variances, y=errors, color=freq)) +
+  filter(rank == 0) %>% 
+  ggplot(aes(x=variances_pop, y=errors_pop, color=freq)) +
   geom_point(size=.05) + 
@@
 results %>% 
-  ggplot(aes(x=variances, y=errors, color=freq)) +
+  ggplot(aes(x=variances_pop, y=errors_pop, color=freq)) +
   geom_point(size=.05) + 
@@
 results %>% 
-  ggplot(aes(x=n_spikes, y=variances, color=freq)) +
+  filter(rank == 0) %>% 
+  ggplot(aes(x=n_spikes_pop, y=variances_pop, color=freq)) +
   geom_point(size=0.1) + 
@@
 results %>% 
-  ggplot(aes(x=n_spikes, y=errors, color=freq)) +
+  filter(rank == 0) %>% 
+  ggplot(aes(x=n_spikes_pop, y=errors_pop, color=freq)) +
   geom_point(size=0.1) + 
@@
 results %>% 
-  ggplot(aes(x=As, y=V_osc, color=freq)) +
-  geom_line() + 
+  ggplot(aes(x=As*1e9, y=V_osc, color=freq)) +
+  geom_point() + 
   theme_classic() +
@@
 
-```{r, fig.width=2, fig.height=1.5}
-results %>% 
-  ggplot(aes(x=V_osc, y=V_comp, color=freq)) +
-  geom_line() + 
-  theme_classic() +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
-```{r, fig.width=1.25, fig.height=3.5}
-results %>% 
-  ggplot(aes(x=V_osc/V_b, y=V_comp/V_b, color=As)) +
-  geom_line() + 
-  theme_classic() +
-  facet_grid(freq~.) +
-  # scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
-```{r, fig.width=1.6, fig.height=1.6}
-results %>% 
-  ggplot(aes(x=V_osc/V_b, y=n_spikes, color=freq)) +
-  geom_line() + 
-  theme_classic() +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
-```{r, fig.width=1.6, fig.height=1.6}
-results %>% 
-  ggplot(aes(x=V_osc/V_b, y=variances, color=freq)) +
-  geom_line() + 
-  theme_classic() +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
-```{r, fig.width=1.6, fig.height=1.6}
-results %>% 
-  ggplot(aes(x=V_osc/V_b, y=errors, color=freq)) +
-  geom_line() + 
-  theme_classic() +
-  xlim(0, 1.5) +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
-```{r, fig.width=1.6, fig.height=1.6}
-results %>% 
-  ggplot(aes(x=V_comp/V_b, y=errors, color=freq)) +
-  geom_point(size=0.05) + 
-  theme_classic() +
-  xlim(0, 0.7) +
-  ylim(0, 0.010) +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
-```{r, fig.width=1.6, fig.height=1.6}
-results %>% 
-  filter(V_comp <= V_osc - min(V_osc)) %>% 
-  ggplot(aes(x=V_comp/V_b, y=errors, color=freq)) +
-  geom_point(size=0.05) + 
-  theme_classic() +
-  xlim(0, 0.7) +
-  ylim(0, 0.010) +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
-```{r, fig.width=1.6, fig.height=1.6}
-results %>% 
-  ggplot(aes(x=V_comp/V_osc, y=variances, color=freq)) +
-  geom_point(size=0.05) + 
-  theme_classic() +
-  # xlim(0, 0.7) +
-  # ylim(0, 0.010) +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
-```{r, fig.width=1.6, fig.height=1.6}
-results %>% 
-  ggplot(aes(x=V_comp/V_osc, y=errors, color=freq)) +
-  geom_point(size=0.05) + 
-  theme_classic() +
-  # xlim(0, 0.7) +
-  # ylim(0, 0.010) +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
-```{r, fig.width=1.6, fig.height=1.6}
-results %>% 
-  ggplot(aes(x=V_comp/V_b, y=variances, color=freq)) +
-  geom_point(size=0.05) + 
-  theme_classic() +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
+- TODO: port over Vo/Vc plots....

### 2018-03-11 voltagebudget/analysis/sweep_Z_analysis.Rmd
Adding sweep_Z vis

---
title: "Sweep Z - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
data_summary <- function(x) {
   m <- mean(x)
   ymin <- m-mad(x)
   ymax <- m+mad(x)
   return(c(y=m,ymin=ymin,ymax=ymax))
}
mean_summary <- function(x) {
   m <- mean(x)
   return(c(y=m))
}
```

# Load and process

```{r, message=FALSE}
# Osc
freq <- "40"

# Zs scan
exp <- "74"
Zs <- c("0.1", "0.2", "0.3")

results <- NULL
for(Z in Zs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, "_Z", Z, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))

  df$Zs <- rep(as.numeric(Z), nrow(df))
  results <- rbind(results, df)
}

# Ref (Z=0)
exp <- "72"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$Zs <- rep(0, nrow(df))
results <- rbind(df, results)

# Process
results %>% 
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  mutate(V_osc = V_osc - V_osc_ref) %>% 
  mutate(silent = n_spikes_ref == 0) -> results

rm(df, exp, freq, Zs, Z, name)
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As, y=n_spikes_pop, color=factor(Zs))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As, y=errors_pop, color=factor(Zs))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As, y=variances_pop, color=factor(Zs))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=errors_pop, y=variances_pop, color=factor(Zs))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=2.25, fig.height=1}
results %>% 
  ggplot(aes(x=delta_spikes, y=errors)) +
  facet_grid(.~Zs) +
  lims(y=c(0, 0.03)) +
  geom_jitter(size=0.1, alpha=0.01) +
  stat_summary(fun.data=data_summary, color="darkgrey", size=0.6, geom="linerange") +
  stat_summary(fun.data=mean_summary, color="darkgrey", size=0.4, geom="point") +
  theme_classic() 
```

```{r, fig.width=2.25, fig.height=1}
results %>% 
  ggplot(aes(x=delta_spikes, y=variances)) +
  facet_grid(.~Zs) +
  # lims(y=c(0, 0.03)) +
  geom_jitter(size=0.1, alpha=0.01) +
  stat_summary(fun.data=data_summary, color="darkgrey", size=0.6, geom="linerange") +
  stat_summary(fun.data=mean_summary, color="darkgrey", size=0.4, geom="point") +
  theme_classic() 
```

### 2018-03-11 voltagebudget/analysis/paper_figures.Rmd
Updating paper figs (in progress)

--- 2018-01-27 voltagebudget/analysis/paper_figures.Rmd
@@
 
-# Voltage budget timecourse
+# Read and process all data
 
-```{r}
-vms <- read_csv("vm_comp_timecourse.csv")
+```{r, message=FALSE}
+# -
+# Example voltage timecourses
+results0 <- read_csv("vm_comp_timecourse.csv")
+
+# -
+# Sweep A
+exp <- "72"
+freqs <- c(8, 12, 20, 30)
+
+# Load
+results1 <- NULL
+for(freq in freqs){
+  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+  df <- read_csv(paste(name, sep=","))
+  df %>%
+    filter(n_spikes > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  results1 <- rbind(results1, df)
+}
+
+# Process
+results1 %>% 
+  # Add delta_spikes
+  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
+  # Re-norm V_osc
+  mutate(V_osc = V_osc - V_osc_ref) -> results1
+
+rm(df, exp, freq, freqs, name)
 ```
 
+# Budget intro
+
 ```{r, fig.width=1.5, fig.height=1.3}
-vms %>% 
+results0 %>% 
   filter(t > 0.15, t < 0.35) %>%
@@
 
-vms %>% 
+results0 %>% 
   filter(t > 0.15, t < 0.35) %>%
@@
 
-vms %>% 
+results0 %>% 
   filter(t > 0.23652 - 8e-3, t < 0.23652 + 2e-3 + 0.03333333 + 8e-3) %>%
@@
 grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+rm(p1, p2, p3, plot_grid)
 ```
 
-# Bounds
+# Trade-off
 
-```{r, message=FALSE, fig.width=1.5, fig.height=1.3}
-name <- "../data/exp7_d-2e-3_f20.csv"
-results <- read_csv(paste(name, sep=""))
+```{r, fig.width=1.3, fig.height=1.9}
+results1 %>% 
+  filter(rank == 0) %>% 
+  ggplot(aes(x=As*1e9, y=errors_pop*1e3, color=freq)) +
+  geom_point(size=0.05, alpha=0.6) + 
+  labs(x="A (namp)", y="Error (ms)") +
+  theme_classic() +
+  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
+  theme(legend.position="none") -> p1
 
-results %>% 
-  filter(V_free > 0.002) %>% 
-  ggplot(aes(x=V_free*1e3)) +
-  geom_histogram(aes(y=0.5*..density..), bins=50, size=0.2) +
-  geom_density(alpha=0.3, fill="black") +
-  geom_vline(aes(xintercept=min(1e3*V_free - 0.05)), color="darkolivegreen3", alpha=0.6) +
-  geom_vline(aes(xintercept=max(1e3*V_free + 0.01)), color="goldenrod2", alpha=0.5) +
-  labs(x="V_free (mvolt)", y="Density (AU)") +
-  xlim(3, 6) +
+results1 %>% 
+  filter(rank == 0) %>% 
+  ggplot(aes(x=As*1e9, y=variances_pop*1e3, color=freq)) +
+  geom_point(size=0.05, alpha=0.6) + 
+  labs(x="A (namp)", y="Variance (ms)") +
+  lims(y=c(0, 12)) +
+  theme_classic() +
+  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
+  theme(legend.position="right") -> p2
+
+results1 %>% 
+  filter(rank == 0) %>% 
+  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=freq)) +
+  geom_point(size=0.05, alpha=0.6) + 
+  labs(x="Error (ms)", y="Variance (ms)") +
+  theme_classic() +
+  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
+  theme(legend.position="none") +
+  labs(x="Error (ms)", y="Variance (ms)") -> p3
+
+plot_grid <- rbind(c(1, 1, NA), c(2, 2, 2), c(3, 3, NA))
+grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+```
+
+# Bound 1 - V_osc/V_comp (f = 20)
+
+```{r, fig.width=1.25, fig.height=1.15}
+results1 %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=As*1e9, y=1e3*V_osc)) +
+  geom_point(size=0.1, alpha=0.01) + 
+  labs(x="A (namp)", y="V_osc (mvolt)") +
   theme_classic() -> p1
 
-results %>% 
-  filter(V_free > 0.002) %>% 
-  ggplot(aes(x=variances, y=errors, color=V_free)) +
-  geom_point(alpha=0.5) +
-  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
-  theme_classic() -> p2
+plot_grid <- rbind(c(1))
+grid.arrange(p1, layout_matrix=plot_grid)
 ```
-
-```{r, message=FALSE, fig.width=3, fig.height=1.7}
-# Load min, max V_free and neighbors
-name <- "../data/exp5_d-2e-3_f8_r1.csv"
-rank1 <- read_csv(paste(name, sep=""))
-rank1$rank <- rep(1, nrow(rank1))
-
-name <- "../data/exp5_d-2e-3_f8_r2.csv"
-rank2 <- read_csv(paste(name, sep=""))
-rank2$rank <- rep(2, nrow(rank2))
-
-name <- "../data/exp5_d-2e-3_f8_r3.csv"
-rank3 <- read_csv(paste(name, sep=""))
-rank3$rank <- rep(3, nrow(rank3))
-
-name <- "../data/exp5_d-2e-3_f8_r50.csv"
-rank50 <- read_csv(paste(name, sep=""))
-rank50$rank <- rep(50, nrow(rank50))
-
-name <- "../data/exp5_d-2e-3_f8_r49.csv"
-rank49 <- read_csv(paste(name, sep=""))
-rank49$rank <- rep(49, nrow(rank49))
-
-name <- "../data/exp5_d-2e-3_f8_r48.csv"
-rank48 <- read_csv(paste(name, sep=""))
-rank48$rank <- rep(48, nrow(rank48))
-
-# Group 'em
-ranked <- rbind(rank1, rank2, rank3, rank50, rank49, rank48)
-
-# -----------------------------------------------------
-# TODO: manual color assignment, setting alphas to rank?
-ranked %>%
-  ggplot(aes(x=N, y=sort(errors), color=rank, group=rank)) +
-  geom_line(alpha=0.4) +
-  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
-  theme_classic() -> p3
-
-ranked %>%
-  ggplot(aes(x=N, y=sort(variances), color=rank, group=rank)) +
-  geom_line(alpha=0.4) +
-  scale_color_gradient(low="darkolivegreen3", high="goldenrod2") +
-  theme_classic() -> p4
-
-plot_grid <- rbind(c(1 , 1, NA, 3, 3, 3), c(2, 2, 2, 4, 4, 4))
-grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
-```
-
-# Pareto opt
-```{r, message=FALSE, fig.width=2.2, fig.height=1.9}
-name <- "../data/exp4_d-2e-3_f12.csv"
-results <- read_csv(paste(name, sep=""))
-
-results %>% 
-  # filter(errors < 0.6, variances > 0) %>%
-  ggplot(aes(y=V_comp*1e3, x=V_osc*1e3, color=As)) +
-  scale_color_gradient(low="mediumpurple", high="red3", name="A") +
-  xlab("Vc (mvolt)") + ylab("Vo (mvolt)") +
-  geom_point(alpha=0.4) + 
-  theme_classic() + 
-  theme(legend.position="bottom", legend.key.size =  unit(0.3, "in")) -> p1
-
-results %>% 
-  ggplot(aes(x=1e3*V_free, y=normalize(variances))) +
-  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE, linetype="dashed") + 
-  # geom_point(color="red3", alpha=0.2) + 
-  geom_smooth(aes(x=1e3*V_free, y=normalize(errors)), 
-              method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", se=FALSE,linetype="dashed") + 
-  # geom_point(aes(x=1e3*V_free, y=normalize(errors)), color="mediumpurple", alpha=0.2) + 
-  geom_vline(aes(xintercept = mean(1e3*V_free)), color="black") +
-  xlab("Vf (mvolt)") +
-  ylab("Normalized") +
-  theme_classic() -> p2
-
-results %>% 
-  ggplot(aes(x=1e3*V_comp, y=errors)) +
-  geom_point(alpha=0.4, size=.3, color="mediumpurple") +
-  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="mediumpurple", alpha=0.2, se=FALSE, linetype="dashed") + 
-  xlab("Vc (mvolt)") +
-  ylab("Errors (s)") +
-  theme_classic() -> p3
-
-results %>% 
-  ggplot(aes(x=1e3*V_osc, y=variances)) +
-  geom_point(alpha=0.3, size=.3, color="red3") +
-  geom_smooth(method = "glm",  method.args = list(family = "binomial"), color="red3", alpha=0.5, se=FALSE, linetype="dashed") + 
-  xlab("Vo (mvolt)") +
-  ylab("Variance (s)") +
-  theme_classic() -> p4
-
-plot_grid <- rbind(c(NA ,NA, 3, 3), c(NA, NA, 3, 3), c(NA, NA, 4, 4), c(1 ,1, 4, 4), c(1, 1, 2, 2), c(1, 1, 2, 2))
-grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
-```
-
-# Voltage timecourses many neurons
-
-```{r}
-vms <- read_csv("vm_full_examples.csv")
-vms <- gather(vms, "neuron", "vm", 2:21)
-wins <- read_csv("vm_window_examples_d2_w2.csv")
-wins <- gather(wins, "neuron", "vm", 2:21)
-```
-
-```{r, fig.width=1.5, fig.height=1}
-vms %>% 
-  filter(t > 0.15, t < 0.35) %>%
-  ggplot(aes(x=t, y=vm, group=neuron)) +
-  geom_line(color="black", alpha=0.3, size=0.2) +
-  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
-  labs(x="Time (s)", y="Vm (mV)") +
-  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.25) +
-  geom_hline(yintercept=-70e-3, color="black", size=2) +
-  geom_vline(xintercept = 0.25719 + 2e-3, color="darkgreen", alpha=0.5, size=0.2) +
-  geom_vline(xintercept = 0.25719 + 2e-3 +  0.03333333, color="darkgreen", alpha=0.5, size=0.2) +
-  theme_classic()
-```
-```{r, fig.width=0.4, fig.height=0.8}
-vms %>% 
-  filter(t > 0.25, t < 0.27) %>%
-  ggplot(aes(x=t, y=vm, group=neuron)) +
-  geom_line(color="black", alpha=0.3, size=0.2) +
-  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
-  labs(x="Time (s)", y="Vm (mV)") +
-  geom_hline(yintercept=-50e-3, color="black", linetype="dashed", size=1) +
-  geom_hline(yintercept=-70e-3, color="black", size=2) +
-  theme(axis.line=element_blank(),
-      axis.text.x=element_blank(),
-      axis.text.y=element_blank(),
-      axis.ticks=element_blank(),
-      axis.title.x=element_blank(),
-      axis.title.y=element_blank(),
-      legend.position="none",
-      panel.background=element_blank(),
-      panel.border=element_blank(),
-      panel.grid.major=element_blank(),
-      panel.grid.minor=element_blank(),
-      plot.background=element_blank())
-  # theme_classic()
-```

### 2018-03-11 voltagebudget/analysis/paper_figures.Rmd
draft 1 for bound 1 fig complete

@@
 }
+data_summary <- function(x) {
+   m <- mean(x)
+   ymin <- m-mad(x)
+   ymax <- m+mad(x)
+   return(c(y=m,ymin=ymin,ymax=ymax))
+}
+mean_summary <- function(x) {
+   m <- mean(x)
+   return(c(y=m))
+}
 ```
@@
 ```{r, message=FALSE}
-# -
+# --------------------------------------------------------------------
 # Example voltage timecourses
-results0 <- read_csv("vm_comp_timecourse.csv")
+fig0 <- read_csv("vm_comp_timecourse.csv")
 
-# -
+# --------------------------------------------------------------------
 # Sweep A
@@
 # Load
-results1 <- NULL
+fig1 <- NULL
 for(freq in freqs){
@@
   df$freq <- rep(freq, nrow(df))
-  results1 <- rbind(results1, df)
+  fig1 <- rbind(fig1, df)
 }
@@
 # Process
-results1 %>% 
+fig1 %>% 
   # Add delta_spikes
@@
   # Re-norm V_osc
-  mutate(V_osc = V_osc - V_osc_ref) -> results1
+  mutate(V_osc = V_osc - V_osc_ref) -> fig1
+
+# --------------------------------------------------------------------
+# Summarize over As
+fig1 %>% 
+  group_by(As) %>% 
+  summarise(
+    V_osc = mean(V_osc), 
+    V_comp = mean(V_comp), 
+    errors = mean(errors), 
+    variances = mean(variances)) -> fig2
 
@@
 ```{r, fig.width=1.5, fig.height=1.3}
-results0 %>% 
+fig0 %>% 
   filter(t > 0.15, t < 0.35) %>%
@@
 
-results0 %>% 
+fig0 %>% 
   filter(t > 0.15, t < 0.35) %>%
@@
 
-results0 %>% 
+fig0 %>% 
   filter(t > 0.23652 - 8e-3, t < 0.23652 + 2e-3 + 0.03333333 + 8e-3) %>%
@@
 
-```{r, fig.width=1.3, fig.height=1.9}
-results1 %>% 
+```{r, fig.width=1.5, fig.height=2.0}
+fig1 %>% 
   filter(rank == 0) %>% 
@@
   theme_classic() +
-  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
+  scale_color_gradient(low="grey", high="black") +
   theme(legend.position="none") -> p1
 
-results1 %>% 
+fig1 %>% 
   filter(rank == 0) %>% 
@@
   theme_classic() +
-  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
+  scale_color_gradient(low="grey", high="black", name="Freq. (Hz)") +
   theme(legend.position="right") -> p2
 
-results1 %>% 
+fig1 %>% 
   filter(rank == 0) %>% 
@@
   theme_classic() +
-  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
+  scale_color_gradient(low="grey", high="black") +
   theme(legend.position="none") +
@@
 grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+rm(p1, p2, p3, plot_grid)
 ```
@@
 
-```{r, fig.width=1.25, fig.height=1.15}
-results1 %>% 
-  filter(freq == 20) %>% 
-  ggplot(aes(x=As*1e9, y=1e3*V_osc)) +
-  geom_point(size=0.1, alpha=0.01) + 
+```{r, fig.width=2.7, fig.height=2.3}
+fig1 %>% 
+  filter(rank == 0, freq == 20) %>% 
+  ggplot(aes(x=As*1e9, y=V_osc*1e3)) +
+  geom_point(size=0.1, alpha=0.6, color="black") + 
   labs(x="A (namp)", y="V_osc (mvolt)") +
@@
 
-plot_grid <- rbind(c(1))
-grid.arrange(p1, layout_matrix=plot_grid)
+fig1 %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
+  geom_point(size=0.01, alpha=0.01, color="grey") + 
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  theme_classic() +
+  geom_line(data=fig2, 
+            aes(x=V_osc/V_comp, y=errors*1e3), 
+            color="black", size=0.5) +
+  labs(x="V_osc/V_comp", y="Error (ms)") -> p2
+
+fig1 %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
+  geom_point(size=0.01, alpha=0.01, color="grey") + 
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  theme_classic() +
+  geom_line(data=fig2, 
+            aes(x=V_osc/V_comp, y=variances*1e3), 
+            color="black", size=0.7, alpha=1) +
+  labs(x="V_osc/V_comp", y="Variance (ms)") -> p3
+
+max_N <- max(fig1$N)
+
+fig1 %>% 
+  filter(freq==20) %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  filter(N %in% sample(1:max_N, 16, replace = FALSE)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
+  geom_point(size=.1, alpha=0.1, color="grey") + 
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  facet_wrap(~rank, nrow=2) +
+  theme_classic() + 
+  scale_x_continuous(breaks=c(0, 1, 2)) +
+  scale_y_continuous(breaks=c(0, 10)) +
+  theme(
+    strip.text.x = element_text(size=0),
+    strip.background = element_blank(),
+    # axis.line=element_blank(),
+    # axis.text.x=element_blank(),
+    # axis.text.y=element_blank(),
+    # axis.ticks=element_blank(),
+    # axis.title.x=element_blank(),
+    # axis.title.y=element_blank(),
+    panel.background=element_blank(),
+    # panel.border=element_blank(),
+    # panel.grid.major=element_blank(),
+    # panel.grid.minor=element_blank(),
+    plot.background=element_blank()) +
+  labs(x="V_osc/V_comp", y="Error (ms)") -> p4
+
+# plot_grid <- rbind(
+#   c(1, 1, 2, 2, 2, 4, 4, 4), 
+#   c(3, 3, 2, 2, 2, 4, 4, 4))
+plot_grid <- rbind(
+  c(1, 1, 2, 2, 2), 
+  c(1, 1, 2, 2, 2), 
+  c(3, 3, 2, 2, 2),
+  c(3, 3, 2, 2, 2),
+  c(4, 4, 4, 4, 4),
+  c(4, 4, 4, 4, 4))
+grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
+rm(p1, p2, p3, p4, plot_grid, max_N)
 ```
+
+# Bound 2 - n_spikes < (0, 1)
+
+```{r}
+max_N <- max(fig1$N)
+
+fig1 %>% 
+  filter(freq==20) %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors, color=factor(delta_spikes))) +
+  geom_point(size=1, alpha=0.9) + 
+  geom_vline(xintercept = 1, alpha=0.8) +
+  geom_vline(xintercept = 0.5, alpha=0.4) +
+  facet_wrap(~rank) +
+  theme_classic() + 
+  theme(
+    legend.position="bottom", 
+    strip.text.x = element_text(size=0),
+    strip.background = element_blank()) +
+  scale_colour_brewer(palette = "Accent") +
+  xlab("V_osc/V_comp") 
+```

### 2018-03-11 voltagebudget/analysis/paper_figures.Rmd
tweaks to bound 1 fig

@@
             aes(x=V_osc/V_comp, y=errors*1e3), 
-            color="black", size=0.5) +
+            color="black", size=0.8) +
   labs(x="V_osc/V_comp", y="Error (ms)") -> p2

### 2018-03-12 voltagebudget/analysis/paper_figures.Rmd
stopping point - first 4 figures complete

--- 2018-03-11 voltagebudget/analysis/paper_figures.Rmd
@@
 }
+
+data_summary <- function(x) {
+   m <- mean(x)
+   ymin <- m-mad(x)
+   ymax <- m+mad(x)
+   return(c(y=m, ymin=ymin, ymax=ymax))
+}
+
+mean_summary <- function(x) {
+   m <- mean(x)
+   return(c(y=m))
+}
 ```
@@
   # Re-norm V_osc
-  mutate(V_osc = V_osc - V_osc_ref) -> results1
+  mutate(V_osc = V_osc - V_osc_ref) -> fig1
+
+# --------------------------------------------------------------------
+# Summarize over As 
+fig1 %>% 
+  group_by(As, freq) %>% 
+  summarise(
+    V_osc = mean(V_osc), 
+    V_comp = mean(V_comp), 
+    errors = mean(errors), 
+    variances = mean(variances)) -> fig2
 
@@
 ```{r, fig.width=1.5, fig.height=1.3}
-results0 %>% 
+fig0 %>% 
   filter(t > 0.15, t < 0.35) %>%
-  ggplot(aes(x=t, ymin=-70e-3, ymax=vm)) +
+  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=vm*1e3)) +
   geom_ribbon(fill="blue", alpha=0.5) +
-  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
-  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
-  labs(x="", y="Vm") +
+  geom_hline(yintercept=-50e-3*1e3, color="black", linetype="dotted", size=0.5) +
+  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
+  labs(x="", y=expression(V[m] (mvolt))) +
   theme_classic() -> p1
 
-results0 %>% 
+fig0 %>% 
   filter(t > 0.15, t < 0.35) %>%
-  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
+  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
   geom_ribbon(fill="red", alpha=0.5) +
-  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
-  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
-  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
-  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
+  geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
+  geom_hline(yintercept=-50e-3*1e3, color="black", linetype="dotted", size=0.5) +
+  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
+  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3*1e3, ymax=-50e-3*1e3),  fill=NA, color="black", alpha=0.01, size=.2) +
   # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
@@
   # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
-  labs(x="Times (s)", y="") +
+  labs(x="Time (s)", y="") +
   theme_classic() -> p2
 
-results0 %>% 
+fig0 %>% 
   filter(t > 0.23652 - 8e-3, t < 0.23652 + 2e-3 + 0.03333333 + 8e-3) %>%
-  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
+  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
   geom_ribbon(fill="red", alpha=0.5) +
-  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
+  geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
   # geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
   # geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
-  geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), fill="grey", alpha=0.01) +
-  geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3),  fill="grey", alpha=0.01) +
-  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
+  geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3*1e3, ymax=-50e-3*1e3), fill="grey", alpha=0.01) +
+  geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3*1e3, ymax=-50e-3*1e3),  fill="grey", alpha=0.01) +
+  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3*1e3, ymax=-50e-3*1e3),  fill=NA, color="black", alpha=0.01, size=.2) +
   labs(x="", y="") +
@@
 
-```{r, fig.width=1.3, fig.height=1.9}
-results1 %>% 
-  filter(rank == 0) %>% 
-  ggplot(aes(x=As*1e9, y=errors_pop*1e3, color=freq)) +
-  geom_point(size=0.05, alpha=0.6) + 
-  labs(x="A (namp)", y="Error (ms)") +
+```{r, fig.width=1.7, fig.height=1.8}
+fig2 %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=errors*1e3, y=variances*1e3, color=V_osc*1e3)) +
+  geom_point(size=0.05, alpha=.1) +
+  scale_color_gradient(low="purple", high="red", name=expression(V[o] (mvolt))) +
+  labs(x="Error (ms)", y="Variance (ms)") +
   theme_classic() +
-  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
-  theme(legend.position="none") -> p1
+  theme(
+    legend.position="bottom", 
+    legend.key.size = unit(.5, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) -> p1
 
-results1 %>% 
-  filter(rank == 0) %>% 
-  ggplot(aes(x=As*1e9, y=variances_pop*1e3, color=freq)) +
-  geom_point(size=0.05, alpha=0.6) + 
-  labs(x="A (namp)", y="Variance (ms)") +
-  lims(y=c(0, 12)) +
+fig2 %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=V_osc*1e3, y=errors*1e3)) +
+  geom_point(size=0.05, alpha=1, color="black") + 
+  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
+  lims(y=c(0, 10)) +
+  theme_classic() -> p2
+
+fig2 %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=V_osc*1e3, y=variances*1e3)) +
+  geom_point(size=0.05, alpha=1, color="black") + 
+  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
+  # lims(y=c(0, 10)) +
+  theme_classic() -> p3
+
+fig1 %>% 
+  filter(rank == 0, freq == 20) %>% 
+  ggplot(aes(x=As*1e9, y=V_osc*1e3)) +
+  geom_point(size=0.1, alpha=0.6, color="black") + 
+  labs(x="A (namp)", y=expression(V[o] (mvolt))) +
+  theme_classic() -> p4
+
+plot_grid <- rbind(
+  c(NA, NA, NA, 4, 4,   4),
+  c(NA, NA, NA, 4, 4,   4),
+  c(NA, NA, NA, 2, 2,   2),
+  c(1,  1,  1,  2, 2,   2),
+  c(1,  1,  1,  3, 3,   3),
+  c(1,  1,  1,  3, 3,   3),
+  c(1,  1,  1,  NA, NA, NA))
+grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
+rm(p1, p2, p3, plot_grid)
+```
+
+# Bound 1 - V_osc/V_comp (f = 20)
+
+```{r, fig.width=2.7, fig.height=2.2}
+fig1 %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
+  geom_point(size=0.01, alpha=0.01, color="grey") + 
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
   theme_classic() +
-  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
-  theme(legend.position="right") -> p2
+  geom_line(data=filter(fig2, freq==20), 
+            aes(x=V_osc/V_comp, y=errors*1e3), 
+            color="black", size=0.8) +
+  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1
 
-results1 %>% 
+fig1 %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
+  geom_point(size=0.01, alpha=0.01, color="grey") + 
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  theme_classic() +
+  geom_line(data=filter(fig2, freq==20), 
+            aes(x=V_osc/V_comp, y=variances*1e3), 
+            color="black", size=0.7, alpha=1) +
+  labs(x=expression(V[o]/V[c]), y="Variance (ms)") -> p2
+
+max_N <- max(fig1$N)
+
+fig1 %>% 
+  filter(freq==20) %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  filter(N %in% sample(1:max_N, 16, replace = FALSE)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
+  geom_point(size=.1, alpha=0.1, color="grey") + 
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  facet_wrap(~rank, nrow=2) +
+  theme_classic() + 
+  scale_x_continuous(breaks=c(0, 1, 2)) +
+  scale_y_continuous(breaks=c(0, 10)) +
+  theme(
+    strip.text.x = element_text(size=0),
+    strip.background = element_blank(),
+    # axis.line=element_blank(),
+    # axis.text.x=element_blank(),
+    # axis.text.y=element_blank(),
+    # axis.ticks=element_blank(),
+    # axis.title.x=element_blank(),
+    # axis.title.y=element_blank(),
+    panel.background=element_blank(),
+    # panel.border=element_blank(),
+    # panel.grid.major=element_blank(),
+    # panel.grid.minor=element_blank(),
+    plot.background=element_blank()) +
+  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3
+
+plot_grid <- rbind(
+  c(1, 1, 1, 2, 2), 
+  c(1, 1, 1, 2, 2), 
+  c(1, 1, 1, 2, 2),
+  c(1, 1, 1, NA, NA),
+  c(3, 3, 3, 3, 3),
+  c(3, 3, 3, 3, 3))
+grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+rm(p1, p2, p3, plot_grid, max_N)
+```
+
+# Bound 2 - n_spikes < (0, 1)
+
+```{r, fig.width=2.6, fig.height=2}
+max_N <- max(fig1$N)
+
+fig1 %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=V_osc*1e3, y=variances*1e3)) +
+  geom_point(size=0.1, alpha=0.1, color="grey") + 
+  theme_classic() +
+  geom_line(data=filter(fig2, freq==20), 
+            aes(x=V_osc*1e3, y=variances*1e3), 
+            color="black", size=0.7, alpha=1) +
+  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") -> p1
+
+fig1 %>% 
+  filter(freq==20) %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
+  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=factor(delta_spikes))) +
+  geom_point(size=1, alpha=1) + 
+  facet_wrap(~rank, ncol=2) +
+  geom_line(data=filter(fig2, freq==20), 
+            aes(x=V_osc*1e3, y=variances*1e3), 
+            color="black", size=0.7, alpha=1) +
+  scale_colour_brewer(palette = "Accent", name="N spikes") +
+  scale_x_continuous(breaks=c(0, 3, 6)) +
+  scale_y_continuous(breaks=c(6, 8)) +
+  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
+  theme_classic() + theme(
+    # legend.position="bottom",
+    strip.text.x = element_text(size=0),
+    strip.background = element_blank(),
+    legend.position="none", 
+    legend.key.size = unit(.5, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8),
+    # axis.line=element_blank(),
+    # axis.text.x=element_blank(),
+    # axis.text.y=element_blank(),
+    # axis.ticks=element_blank(),
+    # axis.title.x=element_blank(),
+    # axis.title.y=element_blank(),
+    panel.background=element_blank(),
+    # panel.border=element_blank(),
+    # panel.grid.major=element_blank(),
+    # panel.grid.minor=element_blank(),
+    plot.background=element_blank()) -> p2
+
+fig1 %>% 
+  filter(freq==20) %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
+  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=factor(delta_spikes))) +
+  geom_point(size=1, alpha=1) + 
+  facet_wrap(~rank, ncol=1) +
+  geom_line(data=filter(fig2, freq==20), 
+            aes(x=V_osc*1e3, y=errors*1e3), 
+            color="black", size=0.7, alpha=1) +
+  scale_colour_brewer(palette = "Accent", name="N spikes") +
+  scale_x_continuous(breaks=c(0, 3, 6)) +
+  scale_y_continuous(breaks=c(2, 8)) +
+  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
+  theme_classic() + theme(
+    # legend.position="bottom",
+    strip.text.x = element_text(size=0),
+    strip.background = element_blank(),
+    legend.position="right", 
+    legend.key.size = unit(.5, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8),
+    # axis.line=element_blank(),
+    # axis.text.x=element_blank(),
+    # axis.text.y=element_blank(),
+    # axis.ticks=element_blank(),
+    # axis.title.x=element_blank(),
+    # axis.title.y=element_blank(),
+    panel.background=element_blank(),
+    # panel.border=element_blank(),
+    # panel.grid.major=element_blank(),
+    # panel.grid.minor=element_blank(),
+    plot.background=element_blank()) -> p3
+
+plot_grid <- rbind(
+  c(1,  1,  1,  2, 2, 2, 2, 3, 3, 3, 3),
+  c(1,  1,  1,  2, 2, 2, 2, 3, 3, 3, 3),
+  c(NA, NA, NA, 2, 2, 2, 2, 3, 3, 3, 3),
+  c(NA, NA, NA, 2, 2, 2, 2, 3, 3, 3, 3),
+  c(NA, NA, NA, 2, 2, 2, 2, 3, 3, 3, 3))
+grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+rm(p1, p2, plot_grid, max_N)
+```
+
+# Freq effects - var reduction versus additional 'sampling'?
+
+```{r, fig.width=2.2, fig.height=1.5}
+fig1 %>%
   filter(rank == 0) %>% 
@@
   theme_classic() +
-  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
-  theme(legend.position="none") +
-  labs(x="Error (ms)", y="Variance (ms)") -> p3
+  scale_color_gradient(low="grey", high="black") +
+  theme(legend.position="right") +
+  labs(x="Error (ms)", y="Variance (ms)") -> p1
 
-plot_grid <- rbind(c(1, 1, NA), c(2, 2, 2), c(3, 3, NA))
-grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+plot_grid <- rbind(
+  c(1))
+
+grid.arrange(p1, layout_matrix=plot_grid)
+rm(p1, plot_grid)
 ```
 
-# Bound 1 - V_osc/V_comp (f = 20)
-
-```{r, fig.width=1.25, fig.height=1.15}
-results1 %>% 
-  filter(freq == 20) %>% 
-  ggplot(aes(x=As*1e9, y=1e3*V_osc)) +
-  geom_point(size=0.1, alpha=0.01) + 
-  labs(x="A (namp)", y="V_osc (mvolt)") +
-  theme_classic() -> p1
-
-plot_grid <- rbind(c(1))
-grid.arrange(p1, layout_matrix=plot_grid)
-```
+# Homeostatis - bigger budgets for more granular control.

### 2018-03-12 voltagebudget/analysis/paper_figures.Rmd
Tweaks to paper figs

@@
 
-```{r, fig.width=1.7, fig.height=1.8}
+```{r, fig.width=1.9, fig.height=1.8}
 fig2 %>% 
@@
     legend.position="bottom", 
-    legend.key.size = unit(.5, "cm"),
+    legend.key.size = unit(.4, "cm"),
     legend.title = element_text(size=8),
@@
   c(NA, NA, NA, 4, 4,   4),
-  c(NA, NA, NA, 2, 2,   2),
+  c(1, 1, 1, 2, 2,   2),
   c(1,  1,  1,  2, 2,   2),
   c(1,  1,  1,  3, 3,   3),
-  c(1,  1,  1,  3, 3,   3),
-  c(1,  1,  1,  NA, NA, NA))
+  c(1,  1,  1,  3, 3,   3))#,
+  # c(1,  1,  1,  NA, NA, NA))
 grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
@@
   theme_classic() +
-  geom_line(data=filter(fig2, freq==20), 
-            aes(x=V_osc*1e3, y=variances*1e3), 
+  geom_line(aes(x=V_osc*1e3, y=variances_pop*1e3), 
             color="black", size=0.7, alpha=1) +
@@
   facet_wrap(~rank, ncol=2) +
-  geom_line(data=filter(fig2, freq==20), 
-            aes(x=V_osc*1e3, y=variances*1e3), 
+  geom_line(aes(x=V_osc*1e3, y=variances_pop*1e3), 
             color="black", size=0.7, alpha=1) +
@@
   facet_wrap(~rank, ncol=1) +
-  geom_line(data=filter(fig2, freq==20), 
-            aes(x=V_osc*1e3, y=errors*1e3), 
+  geom_line(aes(x=V_osc*1e3, y=errors_pop*1e3), 
             color="black", size=0.7, alpha=1) +

### 2018-03-13 voltagebudget/analysis/freq_analysis.Rmd
Added freq analysis

---
title: "Sweep A - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

# Load and process

```{r, message=FALSE}
exp <- "72"
freqs <- c(8, 12, 20, 24, 30)

results <- NULL
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

  df$freq <- rep(freq, nrow(df))
  results <- rbind(results, df)
}

# Process
results %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results

results %>% 
  group_by(As, freq) %>% 
  summarise(
    V_osc = mean(V_osc),
    delta_spikes = mean(delta_spikes),
    V_comp = mean(V_comp), 
    errors = mean(errors), 
    variances = mean(variances)) -> avg_results

rm(df, exp, freq, freqs, name)
```

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>%
  ggplot(aes(x=As*1e9, y=V_osc*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.2) + 
  labs(x="As (namp)", y="Vo (mvolt)") +
  theme_classic() +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) 
```

- WTF? Vo is gettin way to big here...

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  ggplot(aes(x=As*1e9, y=delta_spikes, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x="As (namp)", y="Avg. spike count") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  ggplot(aes(x=As*1e9, y=errors*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x="As (namp)", y="Error (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

```{r, fig.width=1.2, fig.height=0.8}
avg_results %>% 
  ggplot(aes(x=As*1e9, y=variances, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x="As (namp)", y="Variance (ms") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

```{r, fig.width=1.2, fig.height=0.8}
results %>%
  filter(rank == 0) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.2) + 
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) 
```

### 2018-03-13 voltagebudget/exp/homeostasis.py
bugfix - missing kwarg in homeostasis

@@ -10,6 +10,7 @@ def homeostasis(name,
                 E_0=0,
                 N=250,
                 d=-2e-3,
+                w=-2e-3,
                 t=0.4,
                 A=0.05e-9,
                 Z_0=1e-6,

### 2018-03-13 voltagebudget/exp/autotune.py
Tweaking PSO hyper-params and docs

@@ -152,13 +152,16 @@ def autotune_homeostasis(stim,
     #
     # Hyper-params taken from
     # http://hvass-labs.org/people/magnus/publications/pedersen10good-pso.pdf
-    xopt, _ = pso(Z_problem, [bounds[0]], [bounds[1]],
-                  swarmsize=25,
-                  omega=0.39,
-                  phip=2.5,
-                  phig=1.33,
-                  minfunc=1e-2,
-                  processes=n_jobs)
+    xopt, _ = pso(
+        Z_problem,
+        [bounds[0]],
+        [bounds[1]],
+        swarmsize=25,
+        omega=0.39,
+        phip=2.5,
+        phig=1.33,
+        minfunc=1e-3,  # ...no need to be that precise
+        processes=n_jobs)
     Z_hat = xopt[0]
 
     return Z_hat

### 2018-03-13 voltagebudget/analysis/freq_analysis.Rmd
Rmd tweaks

@@
 
+```{r, fig.width=2.2, fig.height=1.8}
+results %>%
+  ggplot(aes(x=As*1e9, y=V_osc*1e3, color=freq)) +
+  geom_point(size=0.05, alpha=0.2) + 
+  labs(x="As (namp)", y="Vo (mvolt)") +
+  theme_classic() +
+  facet_wrap(~freq) +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) 
+```
+
 - WTF? Vo is gettin way to big here...

### 2018-03-13 voltagebudget/analysis/paper_figures.Rmd
Rmd tweaks

@@
     V_comp = mean(V_comp), 
+    V_comp_ref = mean(V_comp_ref), 
     errors = mean(errors), 
@@
 fig1 %>% 
-  filter(V_osc/V_comp <= 3) %>% 
+  filter(V_osc/V_comp_ref <= 3) %>% 
   filter(freq == 20) %>% 
@@
     # axis.text.y=element_blank(),
-    # axis.ticks=element_blank(),
+    # axis.ticks=element_blank(),s
     # axis.title.x=element_blank(),

### 2018-03-13 voltagebudget/analysis/paper_figures.Rmd
First complete fig draft

--- 2018-03-12 voltagebudget/analysis/paper_figures.Rmd
@@
 # Sweep A
-exp <- "72"
+exp <- "77"
 freqs <- c(8, 12, 20, 30)
@@
   summarise(
+    delta_spikes = mean(delta_spikes), 
     V_osc = mean(V_osc), 
     V_comp = mean(V_comp), 
+    V_comp_ref = mean(V_comp_ref), 
     errors = mean(errors), 
+    errors_pop = mean(errors_pop), 
+    variances_pop = mean(variances_pop), 
     variances = mean(variances)) -> fig2
@@
 
-```{r, fig.width=1.9, fig.height=1.8}
+```{r, fig.width=2.1, fig.height=1.8}
 fig2 %>% 
   filter(freq == 20) %>% 
-  ggplot(aes(x=errors*1e3, y=variances*1e3, color=V_osc*1e3)) +
-  geom_point(size=0.05, alpha=.1) +
-  scale_color_gradient(low="purple", high="red", name=expression(V[o] (mvolt))) +
+  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=V_osc*1e3)) +
+  geom_point(size=0.05, alpha=.4) +
+  scale_color_gradient(low="white", high="red", name=expression(V[o] (mvolt))) +
   labs(x="Error (ms)", y="Variance (ms)") +
@@
   filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc*1e3, y=errors*1e3)) +
+  ggplot(aes(x=V_osc*1e3, y=errors_pop*1e3)) +
   geom_point(size=0.05, alpha=1, color="black") + 
@@
   filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc*1e3, y=variances*1e3)) +
+  ggplot(aes(x=V_osc*1e3, y=variances_pop*1e3)) +
   geom_point(size=0.05, alpha=1, color="black") + 
@@
 plot_grid <- rbind(
-  c(NA, NA, NA, 4, 4,   4),
-  c(NA, NA, NA, 4, 4,   4),
-  c(1, 1, 1, 2, 2,   2),
-  c(1,  1,  1,  2, 2,   2),
-  c(1,  1,  1,  3, 3,   3),
-  c(1,  1,  1,  3, 3,   3))#,
+  c(NA, NA, NA, NA, 4, 4,   4),
+  c(NA, NA, NA, NA, 4, 4,   4),
+  c(1,  1,  1,  1, 2, 2,   2),
+  c(1,  1,  1,  1, 2, 2,   2),
+  c(1,  1,  1,  1, 3, 3,   3),
+  c(1,  1,  1,  1, 3, 3,   3))#,
   # c(1,  1,  1,  NA, NA, NA))
@@
   theme_classic() +
-  geom_line(data=filter(fig2, freq==20), 
+  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
             aes(x=V_osc/V_comp, y=errors*1e3), 
@@
   theme_classic() +
-  geom_line(data=filter(fig2, freq==20), 
+  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
             aes(x=V_osc/V_comp, y=variances*1e3), 
@@
 fig1 %>% 
+  filter(V_osc/V_comp <= 3) %>% 
   filter(freq==20) %>% 
   filter(V_osc/V_comp <= 3) %>% 
-  filter(N %in% sample(1:max_N, 16, replace = FALSE)) %>% 
+  filter(N %in% sample(1:max_N, 18, replace = FALSE)) %>% 
   ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
@@
   geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
-  facet_wrap(~rank, nrow=2) +
+  facet_wrap(~rank, nrow=3) +
   theme_classic() + 
@@
 
+fig1 %>% 
+  filter(freq==20) %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(y=V_osc/V_comp, x=delta_spikes)) +
+  geom_jitter(size=0.1, alpha=0.01) + 
+  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  theme_classic() +
+  labs(y=expression(V[o]/V[c]), x="Spike count") -> p4
+
 plot_grid <- rbind(
@@
   c(1, 1, 1, NA, NA),
-  c(3, 3, 3, 3, 3),
-  c(3, 3, 3, 3, 3))
-grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
-rm(p1, p2, p3, plot_grid, max_N)
+  c(3, 3, 3, 4, 4),
+  c(3, 3, 3, 4, 4),
+  c(3, 3, 3, 4, 4))
+grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
+rm(p1, p2, p3, p4, plot_grid, max_N)
 ```
@@
 
-```{r, fig.width=2.6, fig.height=2}
+```{r, fig.width=3, fig.height=3}
 max_N <- max(fig1$N)
@@
   filter(freq==20) %>% 
-  filter(V_osc/V_comp <= 3) %>% 
+  # filter(V_osc/V_comp <= 3) %>% 
   filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
@@
             color="black", size=0.7, alpha=1) +
-  scale_colour_brewer(palette = "Accent", name="N spikes") +
-  scale_x_continuous(breaks=c(0, 3, 6)) +
-  scale_y_continuous(breaks=c(6, 8)) +
+  scale_colour_brewer(palette = "Accent", name="Spike count") +
+  scale_x_continuous(breaks=c(0, 4, 8)) +
+  scale_y_continuous(breaks=c(8, 12)) +
   labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
@@
   filter(freq==20) %>% 
-  filter(V_osc/V_comp <= 3) %>% 
+  # filter(V_osc/V_comp <= 3) %>% 
   filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
@@
             color="black", size=0.7, alpha=1) +
-  scale_colour_brewer(palette = "Accent", name="N spikes") +
-  scale_x_continuous(breaks=c(0, 3, 6)) +
+  scale_colour_brewer(palette = "Accent", name="Spike count") +
+  scale_x_continuous(breaks=c(0, 4, 8)) +
   scale_y_continuous(breaks=c(2, 8)) +
@@
 
+# -
+M = min(fig1$variances_pop)
+
+fig1 %>% 
+  filter(freq==20) %>% 
+  mutate(quantile = ntile(V_osc, 10)) %>%
+  filter(quantile %in% c(1, 10)) %>% 
+  ggplot(aes(x=variances, fill=factor(quantile), group=quantile)) +
+  geom_density(alpha=0.6, size=0.2, color="black") +
+  geom_vline(xintercept = M, color="black") +
+  labs(x="Variance (ms)", y="Density (AU)") +
+  scale_fill_manual(
+    # values=c("#FFDED3", "#FD0D11"), 
+    values=c("grey", "black"),
+    name=expression("Deciles V"[o]), 
+    labels=c("0 - 10%", "90 - 100%")) +
+  theme_classic() +
+  theme(
+    legend.position="bottom", 
+    legend.key.size = unit(.3, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8) ) -> p4
+
+fig1 %>% 
+  filter(freq==20) %>% 
+  ggplot(aes(x=delta_spikes, y=variances*1e3, color=factor(delta_spikes))) +
+  geom_boxplot(outlier.size = NA, size=0.8, show.legend=FALSE)+
+  labs(x="Spike count", y="Variance (ms)") +
+  scale_colour_brewer(palette = "Accent", name="Spike count") +
+  theme_classic() +
+  theme(legend.position="none") -> p5
+
 plot_grid <- rbind(
-  c(1,  1,  1,  2, 2, 2, 2, 3, 3, 3, 3),
-  c(1,  1,  1,  2, 2, 2, 2, 3, 3, 3, 3),
-  c(NA, NA, NA, 2, 2, 2, 2, 3, 3, 3, 3),
-  c(NA, NA, NA, 2, 2, 2, 2, 3, 3, 3, 3),
-  c(NA, NA, NA, 2, 2, 2, 2, 3, 3, 3, 3))
-grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
-rm(p1, p2, plot_grid, max_N)
+  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,   3, 3),
+  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,   3, 3),
+  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,   3, 3),
+  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,   3, 3),
+  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,   3, 3),
+  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,   3, 3),
+  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA),
+  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA),
+  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA))
+
+grid.arrange(p1, p2, p3, p4, p5, layout_matrix=plot_grid)
+rm(p1, p2, p3, p4, plot_grid, max_N, M)
 ```
@@
 
-```{r, fig.width=2.2, fig.height=1.5}
-fig1 %>%
-  filter(rank == 0) %>% 
-  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=freq)) +
-  geom_point(size=0.05, alpha=0.6) + 
-  labs(x="Error (ms)", y="Variance (ms)") +
+```{r, fig.width=2, fig.height=1.7}
+fig2 %>% 
+  ggplot(aes(x=V_osc*1e3, y=delta_spikes, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) + 
+  labs(x=expression(V[o] (mvolt)), y="Spike count") +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
   theme_classic() +
-  scale_color_gradient(low="grey", high="black") +
-  theme(legend.position="right") +
-  labs(x="Error (ms)", y="Variance (ms)") -> p1
+  theme(legend.position="right", 
+    legend.key.size = unit(.3, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) -> p1
+
+fig2 %>% 
+  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) + 
+  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  theme_classic() +
+  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
+  theme(legend.position="none", 
+    legend.key.size = unit(.5, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) -> p2
+
+fig2 %>% 
+  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) + 
+  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
+  theme_classic() +
+  theme(legend.position="none", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) -> p3
 
 plot_grid <- rbind(
-  c(1))
+  c(1, 1, 1, 1, NA, NA),
+  c(1, 1, 1, 1, NA, NA),
+  c(1, 1, 1, 1, NA, NA),
+  c(2, 2, 2, 3, 3, 3),
+  c(2, 2, 2, 3, 3, 3),
+  c(2, 2, 2, 3, 3, 3))
 
-grid.arrange(p1, layout_matrix=plot_grid)
-rm(p1, plot_grid)
+grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+rm(p1, p2, p3, plot_grid)
 ```

### 2018-03-13 voltagebudget/analysis/freq_analysis.Rmd
freq analysis tweaks

--- 2018-03-13 voltagebudget/analysis/freq_analysis.Rmd
@@
 ```{r, message=FALSE}
-exp <- "72"
+exp <- "77"
 freqs <- c(8, 12, 20, 24, 30)
@@
 avg_results %>% 
-  ggplot(aes(x=As*1e9, y=delta_spikes, color=freq, group=freq)) +
+  ggplot(aes(x=V_osc*1e3, y=delta_spikes, color=freq, group=freq)) +
   geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x="As (namp)", y="Avg. spike count") +
+  labs(x="V_osc (mvolt)", y="Spike count") +
   scale_color_gradient(low="gold", high="darkgreen") +
@@
 avg_results %>% 
-  ggplot(aes(x=As*1e9, y=errors*1e3, color=freq, group=freq)) +
+  ggplot(aes(x=V_osc*1e3, y=errors, color=freq, group=freq)) +
   geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x="As (namp)", y="Error (ms)") +
+  labs(x="V_osc (mvolt)", y="Error (ms)") +
   scale_color_gradient(low="gold", high="darkgreen") +
@@
 avg_results %>% 
-  ggplot(aes(x=As*1e9, y=variances, color=freq, group=freq)) +
+  ggplot(aes(x=V_osc*1e3, y=variances, color=freq, group=freq)) +
   geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x="As (namp)", y="Variance (ms") +
+  labs(x="V_osc (mvolt)", y="Variance (ms)") +
   scale_color_gradient(low="gold", high="darkgreen") +

### 2018-03-15 voltagebudget/analysis/freq_analysis.Rmd
Added exp79 (slow frew) to figures

@@
 ```{r, message=FALSE}
+results <- NULL
+
+# --------------------------
 exp <- "77"
-freqs <- c(8, 12, 20, 24, 30)
+freqs <- c(24, 30)
 
-results <- NULL
 for(freq in freqs){
@@
 
+# --------------------------
+exp <- "79"
+freqs <- c(6, 8, 10, 12, 14, 16, 18, 20)
+
+for(freq in freqs){
+  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
+  df <- read_csv(paste(name, sep=","))
+  df %>%
+    filter(n_spikes > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  results <- rbind(results, df)
+}
+
+# --------------------------
 # Process
@@
 
-```{r, fig.width=1.2, fig.height=0.8}
+```{r, fig.width=1.3, fig.height=0.8}
 avg_results %>% 

### 2018-03-15 voltagebudget/analysis/paper_figures.Rmd
Added exp79 (slow frew) to figures

@@
 # --------------------------------------------------------------------
-# Sweep A
+fig1 <- NULL
+
+# --------------------------
 exp <- "77"
-freqs <- c(8, 12, 20, 30)
+freqs <- c(24, 30)
 
-# Load
-fig1 <- NULL
 for(freq in freqs){
-  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
+  df <- read_csv(paste(name, sep=","))
+  df %>%
+    filter(n_spikes > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  fig1 <- rbind(fig1, df)
+}
+
+# --------------------------
+exp <- "79"
+freqs <- c(6, 8, 10, 12, 14, 16, 18, 20)
+
+for(freq in freqs){
+  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
   df <- read_csv(paste(name, sep=","))
@@
 
-```{r, fig.width=2, fig.height=1.7}
+```{r, fig.width=1.8, fig.height=1.5}
 fig2 %>% 
-  ggplot(aes(x=V_osc*1e3, y=delta_spikes, color=freq, group=freq)) +
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
   geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o] (mvolt)), y="Spike count") +
+  labs(x=expression(V[o]/V[c]), y="Spike count") +
   scale_color_gradient(low="gold", high="darkgreen") +
-  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
+  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
   theme_classic() +
@@
 fig2 %>% 
-  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=freq, group=freq)) +
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
   geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
+  labs(x=expression(V[o]/V[c]), y="Error (ms)") +
   scale_color_gradient(low="gold", high="darkgreen") +
   theme_classic() +
-  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
+  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
   theme(legend.position="none", 
@@
     legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p2
+    legend.text = element_text(size=8)) -> p3
 
 fig2 %>% 
-  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=freq, group=freq)) +
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
   geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
+  labs(x=expression(V[o]/V[c]), y="Variance (ms)") +
   scale_color_gradient(low="gold", high="darkgreen") +
-  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
+  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
   theme_classic() +
@@
     legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p3
+    legend.text = element_text(size=8)) -> p2
 
@@
 ```
-
-# Homeostatis - bigger budgets for more granular control.

### 2018-03-15 voltagebudget/analysis/sweep_Z_analysis.Rmd
Improvements to sweep_Z vis. (many).

@@
 # Osc
-freq <- "40"
+freq <- "8"
 
 # Zs scan
-exp <- "74"
+exp <- "78"
 Zs <- c("0.1", "0.2", "0.3")
@@
 # Ref (Z=0)
-exp <- "72"
+exp <- "77"
 name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
@@
 
+# As
+
 ```{r, fig.width=1.5, fig.height=1.5}
@@
   ggplot(aes(x=As, y=n_spikes_pop, color=factor(Zs))) +
-  geom_line() + 
-  theme_classic() +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
-```{r, fig.width=1.5, fig.height=1.5}
-results %>% 
-  filter(rank == 0) %>% 
-  ggplot(aes(x=As, y=errors_pop, color=factor(Zs))) +
   geom_line() + 
@@
   filter(rank == 0) %>% 
+  ggplot(aes(x=As, y=errors_pop, color=factor(Zs))) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+# V_osc/V_b
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(rank == 0) %>% 
+  ggplot(aes(x=V_osc/V_b, y=n_spikes_pop, color=factor(Zs))) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+### Errors
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(rank == 0) %>% 
+  ggplot(aes(x=V_osc/V_b, y=errors_pop, color=factor(Zs))) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=1.9, fig.height=1}
+results %>% 
+  ggplot(aes(x=V_osc/V_b, y=errors*1e3)) +
+  geom_point(size=0.01, alpha=0.01) + 
+  theme_classic() +
+  facet_grid(.~Zs) +
+  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=1.9, fig.height=1}
+results %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
+  geom_point(size=0.01, alpha=0.01) + 
+  theme_classic() +
+  facet_grid(.~Zs) +
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=5.5, fig.height=2.5}
+M1 <- mean(filter(results, Zs == 0)$errors*1e3)
+max_N <- max(results$N)
+
+results %>% 
+  filter(V_osc/V_comp <= 3) %>%
+  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
+  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
+  geom_point(size=1, alpha=1) + 
+  facet_grid(Zs~rank) +
+  scale_colour_brewer(palette = "Accent", name="Spike count") +
+  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
+  geom_hline(yintercept = M1, alpha=0.7, color="black") +
+  theme_classic() + theme(
+    # legend.position="bottom",
+    strip.text.x = element_text(size=0),
+    strip.background = element_blank(),
+    legend.position="right", 
+    legend.key.size = unit(.5, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8),
+    # axis.line=element_blank(),
+    # axis.text.x=element_blank(),
+    # axis.text.y=element_blank(),
+    # axis.ticks=element_blank(),
+    # axis.title.x=element_blank(),
+    # axis.title.y=element_blank(),
+    panel.background=element_blank(),
+    # panel.border=element_blank(),
+    # panel.grid.major=element_blank(),
+    # panel.grid.minor=element_blank(),
+    plot.background=element_blank())
+
+rm(max_N, M1)
+```
+
+### Variances
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(rank == 0) %>% 
+  ggplot(aes(x=V_osc/V_b, y=variances_pop, color=factor(Zs))) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(rank == 0, V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances_pop, color=factor(Zs))) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=1.9, fig.height=1}
+results %>% 
+  # filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_b, y=variances*1e3)) +
+  geom_point(size=0.01, alpha=0.01) + 
+  theme_classic() +
+  facet_grid(.~Zs) +
+  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom")
+```
+
+```{r, fig.width=1.9, fig.height=1}
+results %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
+  geom_point(size=0.01, alpha=0.01) + 
+  theme_classic() +
+  facet_grid(.~Zs) +
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=5.5, fig.height=2.5}
+max_N <- max(results$N)
+
+results %>% 
+  filter(V_osc/V_comp <= 3) %>%
+  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
+  ggplot(aes(x=V_osc/V_b, y=variances*1e3, color=factor(delta_spikes))) +
+  geom_point(size=1, alpha=1) + 
+  facet_grid(Zs~rank) +
+  scale_colour_brewer(palette = "Accent", name="Spike count") +
+  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
+  theme_classic() + theme(
+    # legend.position="bottom",
+    strip.text.x = element_text(size=0),
+    strip.background = element_blank(),
+    legend.position="right", 
+    legend.key.size = unit(.5, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8),
+    # axis.line=element_blank(),
+    # axis.text.x=element_blank(),
+    # axis.text.y=element_blank(),
+    # axis.ticks=element_blank(),
+    # axis.title.x=element_blank(),
+    # axis.title.y=element_blank(),
+    panel.background=element_blank(),
+    # panel.border=element_blank(),
+    # panel.grid.major=element_blank(),
+    # panel.grid.minor=element_blank(),
+    plot.background=element_blank())
+
+rm(max_N)
+```
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(rank == 0) %>% 
   ggplot(aes(x=errors_pop, y=variances_pop, color=factor(Zs))) +
@@
 ```
+
+```{r, fig.width=1.9, fig.height=1}
+M1 = mean(filter(results, Zs == 0)$errors*1e3)
+M2 = mean(filter(results, Zs == 0)$variances*1e3)
+
+results %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=errors*1e3, y=variances*1e3)) +
+  geom_point(size=0.01, alpha=0.01, color="grey") + 
+  theme_classic() +
+  facet_grid(.~Zs) +
+  geom_vline(xintercept = M1, alpha=0.7, color="black") +
+  geom_hline(yintercept = M2, alpha=0.7, color="black") +
+  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom")
+
+rm(M1, M2)
+```
+
+```{r, fig.width=6.5, fig.height=2.5}
+M1 <- mean(filter(results, Zs == 0)$errors*1e3)
+M2 <- mean(filter(results, Zs == 0)$variances*1e3)
+max_N <- max(results$N)
+
+results %>% 
+  filter(V_osc/V_comp <= 3) %>%
+  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
+  ggplot(aes(x=errors*1e3, y=variances*1e3, color=factor(delta_spikes))) +
+  geom_point(size=1, alpha=1) + 
+  facet_grid(Zs~rank) +
+  scale_colour_brewer(palette = "Accent", name="Spike count") +
+  labs(x="Error (ms)", y="Variance (ms)") +
+  geom_vline(xintercept = M1, alpha=0.7, color="black") +
+  geom_hline(yintercept = M2, alpha=0.7, color="black") +
+  theme_classic() + theme(
+    # legend.position="bottom",
+    strip.text.x = element_text(size=0),
+    strip.background = element_blank(),
+    legend.position="right", 
+    legend.key.size = unit(.5, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8),
+    # axis.line=element_blank(),
+    # axis.text.x=element_blank(),
+    # axis.text.y=element_blank(),
+    # axis.ticks=element_blank(),
+    # axis.title.x=element_blank(),
+    # axis.title.y=element_blank(),
+    panel.background=element_blank(),
+    # panel.border=element_blank(),
+    # panel.grid.major=element_blank(),
+    # panel.grid.minor=element_blank(),
+    plot.background=element_blank())
+
+rm(max_N, M1)
+```
+
+## n_spikes v rest
 

### 2018-03-15 voltagebudget/analysis/freq_analysis.Rmd
Added more 'fast' freqs to freq_analysis - will need to do fast and slow subfigs  to take it all in.

@@
 exp <- "77"
-freqs <- c(24, 30)
+freqs <- c(24, 30, 40)
 
@@
 
+exp <- "80"
+freqs <- c(22, 24, 26, 28, 32, 34 ,36, 38)
+for(freq in freqs){
+  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
+  df <- read_csv(paste(name, sep=","))
+  df %>%
+    filter(n_spikes > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  results <- rbind(results, df)
+}
+
 # --------------------------
@@
   summarise(
+    V_b = mean(V_b),
     V_osc = mean(V_osc),
@@
 
-- WTF? Vo is gettin way to big here...
+```{r, fig.width=1.2, fig.height=0.8}
+avg_results %>%
+  ggplot(aes(x=As*1e9, y=errors*1e3, color=freq)) +
+  geom_point(size=0.05, alpha=0.2) + 
+  labs(x="As (namp)", y="Error (ms)") +
+  theme_classic() +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) 
+```
 
@@
 avg_results %>%
-  ggplot(aes(x=V_osc*1e3, y=delta_spikes, color=freq, group=freq)) +
+  ggplot(aes(x=As*1e9, y=variances*1e3, color=freq)) +
+  geom_point(size=0.05, alpha=0.2) + 
+  labs(x="As (namp)", y="Variance (ms)") +
+  theme_classic() +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) 
+```
+
+### V_osc/V_b
+
+```{r, fig.width=1.2, fig.height=0.8}
+avg_results %>% 
+  ggplot(aes(x=V_osc/V_b, y=delta_spikes, color=freq, group=freq)) +
   geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x="V_osc (mvolt)", y="Spike count") +
+  labs(x="V_osc/V_b", y="Spike count") +
   scale_color_gradient(low="gold", high="darkgreen") +
@@
 avg_results %>% 
-  ggplot(aes(x=V_osc*1e3, y=errors, color=freq, group=freq)) +
+  ggplot(aes(x=V_osc/V_b, y=errors, color=freq, group=freq)) +
   geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x="V_osc (mvolt)", y="Error (ms)") +
+  labs(x="V_osc/V_b", y="Error (ms)") +
   scale_color_gradient(low="gold", high="darkgreen") +
@@
 ```
+
+```{r, fig.width=1.2, fig.height=0.8}
+avg_results %>% 
+  ggplot(aes(x=V_osc/V_b, y=variances, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) + 
+  labs(x="V_osc/V_b", y="Variance (ms)") +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  theme_classic() +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8))
+```
+
+### V_osc/V_comp
+
+```{r, fig.width=1.2, fig.height=0.8}
+avg_results %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) + 
+  labs(x="V_osc/V_comp", y="Error (ms)") +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  theme_classic() +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8))
+```
+
+```{r, fig.width=1.2, fig.height=0.8}
+avg_results %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) + 
+  labs(x="V_osc/V_comp", y="Variance (ms)") +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  theme_classic() +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8))
+```
+
+```{r, fig.width=2.9, fig.height=2}
+avg_results %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  filter(errors*1e3 < 30) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
+  geom_point(size=0.01, alpha=0.9, color="black") + 
+  theme_classic() +
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  facet_wrap(~freq) +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=2.9, fig.height=2}
+results %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  filter(errors*1e3 < 30) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
+  geom_point(size=0.01, alpha=0.01, color="grey") + 
+  theme_classic() +
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  facet_wrap(~freq) +
+  theme(legend.position="bottom") 
+```
+
+### Var
 

### 2018-03-16 voltagebudget/exp/autotune.py
bugfix - homeostatis. int -> float issue.

@@ -130,8 +130,9 @@ def autotune_homeostasis(stim,
         loss = abs(target - delta)
 
         if verbose:
-            print("(Z {:0.18f}, bias_adj/bias {:0.18f}) -> (loss {:0.6f})".
-                  format(Z, bias / bias_in, loss))
+            print(
+                "(Z {:0.4f}, bias_adj/bias {:0.4f}) -> (ref size {}, y size {}, loss {:0.6f})".
+                format(Z, bias / bias_in, ts_ref.size, ts_y.size, loss))
 
         # return np.sqrt(np.sum(loss**2))
         return loss

### 2018-03-16 voltagebudget/exp/homeostasis.py

@@ -58,7 +58,7 @@ def homeostasis(name,
         n_samples=1,
         d=d,
         w=w,
-        T=1 / f,
+        T=1 / float(f),
         f=f,
         N=N,
         mode=mode,

### 2018-03-16 voltagebudget/analysis/paper_figures.Rmd
In paper figures, now norming all V_osc terms by V_b. Unitless is good.

@@
     delta_spikes = mean(delta_spikes), 
+    V_b = mean(V_b), 
     V_osc = mean(V_osc), 
@@
 
-# Trade-off
-
-```{r, fig.width=2.1, fig.height=1.8}
-fig2 %>% 
-  filter(freq == 20) %>% 
-  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=V_osc*1e3)) +
-  geom_point(size=0.05, alpha=.4) +
-  scale_color_gradient(low="white", high="red", name=expression(V[o] (mvolt))) +
-  labs(x="Error (ms)", y="Variance (ms)") +
-  theme_classic() +
-  theme(
-    legend.position="bottom", 
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p1
-
-fig2 %>% 
-  filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc*1e3, y=errors_pop*1e3)) +
-  geom_point(size=0.05, alpha=1, color="black") + 
-  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
-  lims(y=c(0, 10)) +
-  theme_classic() -> p2
-
-fig2 %>% 
-  filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc*1e3, y=variances_pop*1e3)) +
-  geom_point(size=0.05, alpha=1, color="black") + 
-  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
-  # lims(y=c(0, 10)) +
-  theme_classic() -> p3
-
+```{r, fig.width=1, fig.height=0.8}
 fig1 %>%
@@
   labs(x="A (namp)", y=expression(V[o] (mvolt))) +
-  theme_classic() -> p4
+  theme_classic() 
+```
+# Trade-off
+
+```{r, fig.width=1.5, fig.height=1.9}
+fig2 %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=V_osc/V_b, y=errors_pop*1e3, color=V_osc/V_b)) +
+  geom_point(size=0.05, alpha=1) + 
+  labs(x=expression(V[o]/V[b]), y="Avg. error (ms)") +
+  lims(y=c(0, 10)) +
+  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
+  scale_color_gradient(low="lightgrey", high="red") +
+  theme_classic() +
+  theme(
+    legend.position="none") -> p1
+
+fig2 %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=V_osc/V_b, y=variances_pop*1e3, color=V_osc/V_b)) +
+  geom_point(size=0.05, alpha=1) + 
+  labs(x=expression(V[o]/V[b]), y="Pop. variance (ms)") +
+  scale_color_gradient(low="lightgrey", high="red") +
+  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
+  theme_classic() +
+  theme(
+    legend.position="none") -> p2
+
+fig2 %>% 
+  filter(freq == 20) %>% 
+  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=V_osc/V_b)) +
+  geom_point(size=0.05, alpha=.6) +
+  scale_color_gradient(low="lightgrey", high="red", name=expression(V[o]/V[b])) +
+  # scale_color_gradient(low="lightgrey", high="red", name="A (namp)") +
+  geom_smooth(color="black", method=lm, alpha=0.2, size=.8, linetype='dotted') +
+  labs(x="Avg. error (ms)", y="Pop. variance (ms)") +
+  theme_classic() +
+  theme(
+    legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) -> p3
+
+# plot_grid <- rbind(
+#   c(NA, NA, NA, NA, 4, 4,   4),
+#   c(NA, NA, NA, NA, 4, 4,   4),
+#   c(1,  1,  1,  1, 2, 2,   2),
+#   c(1,  1,  1,  1, 2, 2,   2),
+#   c(1,  1,  1,  1, 3, 3,   3),
+#   c(1,  1,  1,  1, 3, 3,   3))#,
+  # c(1,  1,  1,  NA, NA, NA))
 
 plot_grid <- rbind(
-  c(NA, NA, NA, NA, 4, 4,   4),
-  c(NA, NA, NA, NA, 4, 4,   4),
-  c(1,  1,  1,  1, 2, 2,   2),
-  c(1,  1,  1,  1, 2, 2,   2),
-  c(1,  1,  1,  1, 3, 3,   3),
-  c(1,  1,  1,  1, 3, 3,   3))#,
-  # c(1,  1,  1,  NA, NA, NA))
-grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
+  c(NA),
+  c(1, 2),
+  c(1, 2),
+  c(3, 3),
+  c(3, 3),
+  c(3, 3))
+
+grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
 rm(p1, p2, p3, plot_grid)
@@
 
-```{r, fig.width=3, fig.height=3}
+```{r, fig.width=3.7, fig.height=3.1}
 max_N <- max(fig1$N)
@@
   filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc*1e3, y=variances*1e3)) +
+  ggplot(aes(x=V_osc/V_b, y=variances*1e3)) +
   geom_point(size=0.1, alpha=0.1, color="grey") + 
   theme_classic() +
-  geom_line(aes(x=V_osc*1e3, y=variances_pop*1e3), 
+  geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3), 
             color="black", size=0.7, alpha=1) +
-  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") -> p1
+  labs(x=expression(V[o]/V[b]), y="Variance (ms)") -> p1
 
@@
   filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
-  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=factor(delta_spikes))) +
+  ggplot(aes(x=V_osc/V_b, y=variances*1e3, color=factor(delta_spikes))) +
   geom_point(size=1, alpha=1) + 
   facet_wrap(~rank, ncol=2) +
-  geom_line(aes(x=V_osc*1e3, y=variances_pop*1e3), 
+  geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3), 
             color="black", size=0.7, alpha=1) +
   scale_colour_brewer(palette = "Accent", name="Spike count") +
-  scale_x_continuous(breaks=c(0, 4, 8)) +
+  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
   scale_y_continuous(breaks=c(8, 12)) +
-  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
+  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
   theme_classic() + theme(
@@
   filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
-  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=factor(delta_spikes))) +
+  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
   geom_point(size=1, alpha=1) + 
   facet_wrap(~rank, ncol=1) +
-  geom_line(aes(x=V_osc*1e3, y=errors_pop*1e3), 
+  geom_line(aes(x=V_osc/V_b, y=errors_pop*1e3), 
             color="black", size=0.7, alpha=1) +
   scale_colour_brewer(palette = "Accent", name="Spike count") +
-  scale_x_continuous(breaks=c(0, 4, 8)) +
+  scale_x_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
   scale_y_continuous(breaks=c(2, 8)) +
-  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
+  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
   theme_classic() + theme(

### 2018-03-23 voltagebudget/exp/optimal.py
debug max_dev

@@ -14,22 +14,19 @@ from voltagebudget.util import mae
 
 
 # -
-def _run(ts, changes, fn, save_ts=False, verbose=False):
+def _run(ts, changes, fn, verbose=False):
     # init
     initial_variances = []
     target_variances = []
     obs_variances = []
     errors = []
 
-    if save_ts:
-        ts_opts = []
-
     # run of changes
     for c in changes:
         if verbose:
             print(">>> Running c {}".format(c))
 
-        initial, target, obs, ns_opt, ts_opt = fn(ts, c)
+        initial, target, obs, ts_opt = fn(ts, c)
         err = mae(ts, ts_opt)
 
         obs_variances.append(obs)
@@ -37,13 +34,7 @@ def _run(ts, changes, fn, save_ts=False, verbose=False):
         target_variances.append(target)
         errors.append(err)
 
-        if save_ts:
-            ts_opts.append(ts_opt)
-
-    # Build the result
     results = [obs_variances, initial_variances, target_variances, errors]
-    if save_ts:
-        results.append(ts_opts)
 
     return results
 
@@ -87,14 +78,8 @@ def optimal(name,
         print(">>> Running {}.".format(alg))
 
     changes = np.linspace(p_0, p_max, n_samples)
-
-    if save_spikes:
-        (obs_variances, initial_variances, target_variances, errors,
-         ts_cs) = _run(
-             ts, changes, fn, save_ts=save_spikes, verbose=verbose)
-    else:
-        (obs_variances, initial_variances, target_variances, errors) = _run(
-            ts, changes, fn, verbose=verbose)
+    (obs_variances, initial_variances, target_variances, errors) = _run(
+        ts, changes, fn, verbose=verbose)
 
     # --------------------------------------------------------------
     if verbose:
@@ -118,11 +103,13 @@ def optimal(name,
     # -
     if save_spikes:
         if verbose:
-            print("Saving spikes.")
+            print(">>> Saving spikes.")
 
-        for c, ns_c, ts_c in zip(changes, ns_cs, ts_cs):
-            ts_name = "{}_c{}".format(name, c)
-            write_spikes(ts_name, ns_c, ts_c)
+        for c in changes:
+            initial, target, obs, ts_save = fn(ts, c)
+
+            ts_name = "{}_c{}_spikes".format(name, c)
+            write_spikes(ts_name, ns, ts_save)
 
     # -
     # If running in a CL, returns are line noise?

### 2018-03-23 voltagebudget/plc.py

@@ -108,18 +108,19 @@ def max_deviant(ts,
     if ts.size == 0:
         return ts
 
-    ts = np.asarray(ts)
-    np.sort(ts)
-
     # -
+    ts = np.asarray(ts)
     initial, target = _create_target(ts, percent_change)
 
     # Init
     adjusted = initial
-    M = mode_fm(ts)
+
+    idx = np.argsort(ts)
+    ts_opt = ts.copy()[idx]
+
+    M = mode_fm(ts_opt)
 
     # Which side of ts too look at?
-    ts_opt = ts.copy()
     if side == 'both':
         mask = np.ones_like(ts_opt, dtype=np.bool)
     elif side == 'left':
@@ -158,4 +159,9 @@ def max_deviant(ts,
 
             break
 
-    return initial, target, adjusted, np.asarray(ts_opt)
+    # Re-sort ts_opt to match the order in intial ts
+    ts_re = np.zeros_like(ts_opt)
+    for n, i in enumerate(idx):
+        ts_re[i] = ts_opt[n]
+
+    return initial, target, adjusted, ts_re

### 2018-03-23 voltagebudget/analysis/paper_figures.Rmd
Update fig7 vis

@@
 # --------------------------
+# INITIAL
 exp <- "77"
-freqs <- c(24, 30)
+freqs <- c(20, 30)
 
@@
 # --------------------------
+# SLOW
 exp <- "79"
-freqs <- c(6, 8, 10, 12, 14, 16, 18, 20)
+freqs <- c(6, 8, 10, 12, 14, 16, 18)
 
+for(freq in freqs){
+  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
+  df <- read_csv(paste(name, sep=","))
+  df %>%
+    filter(n_spikes > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  fig1 <- rbind(fig1, df)
+}
+
+# --------------------------
+# FAST
+exp <- "80"
+freqs <- c(22, 24, 26, 28)#, 32, 34 ,36, 38)
 for(freq in freqs){
@@
 
-rm(df, exp, freq, freqs, name)
+# --------------------------------------------------------------------
+# Data
+algs <- c("max", "left", "uni", "cc")
+alg_names <- c("max", "left", "uniform", "coincidence")
+exps <- c(82, 83, 84, 85)
+
+fig3 <- NULL
+for (n in 1:4){
+  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], ".csv", sep=""))
+  df$alg <- rep(alg_names[n], nrow(df))
+
+  fig3 <- rbind(fig3, df)
+}
+
+# Spikes
+# Load ref spikes
+ref <- read_csv("../data/stim1.csv")
+ref$set <- rep("initial", nrow(ref))
+
+# Load exp spikes
+exps <- c(86, 87, 88, 89)
+fig4 <- NULL
+for (n in 1:4){
+  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], "_c0.1_spikes.csv", sep=""))
+  df$set <- rep("synchronized", nrow(df))
+
+  # Add ref
+  df <- rbind(df, ref)
+
+  df$alg <- rep(alg_names[n], nrow(df))
+  fig4 <- rbind(fig4, df)
+}
+
+rm(df, exp, freq, freqs, name, ref, n)
 ```
@@
   filter(V_osc/V_comp <= 3) %>% 
-  filter(N %in% sample(1:max_N, 18, replace = FALSE)) %>% 
+  filter(N %in% sample(1:max_N, 24, replace = FALSE)) %>% 
   ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
@@
 
-fig1 %>% 
-  filter(freq==20) %>% 
-  filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(y=V_osc/V_comp, x=delta_spikes)) +
-  geom_jitter(size=0.1, alpha=0.01) + 
-  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
-  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
-  theme_classic() +
-  labs(y=expression(V[o]/V[c]), x="Spike count") -> p4
-
 plot_grid <- rbind(
@@
   c(1, 1, 1, NA, NA),
-  c(3, 3, 3, 4, 4),
-  c(3, 3, 3, 4, 4),
-  c(3, 3, 3, 4, 4))
-grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
-rm(p1, p2, p3, p4, plot_grid, max_N)
+  c(3, 3, 3, 3, 3),
+  c(3, 3, 3, 3, 3),
+  c(3, 3, 3, 3, 3))
+  # c(3, 3, 3, 4, 4),
+  # c(3, 3, 3, 4, 4),
+  # c(3, 3, 3, 4, 4))
+grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+rm(p1, p2, p3, plot_grid, max_N)
 ```
@@
 
+fig1 %>% 
+  filter(freq==20) %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(y=V_osc/V_comp, x=delta_spikes)) +
+  geom_jitter(size=0.1, alpha=0.01) + 
+  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  theme_classic() +
+  labs(y=expression(V[o]/V[c]), x="Spike count") -> p6
+
 plot_grid <- rbind(
@@
   c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,  3, 3),
-  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA),
-  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA),
-  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA))
+  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6),
+  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6),
+  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6))
 
-grid.arrange(p1, p2, p3, p4, p5, layout_matrix=plot_grid)
+grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=plot_grid)
 rm(p1, p2, p3, p4, plot_grid, max_N, M)
@@
 
-```{r, fig.width=1.8, fig.height=1.5}
+```{r, fig.width=1.8, fig.height=2.25}
+# ------------------------------------------
+# SLOW
 fig2 %>% 
+  filter(freq <= 20) %>%
   filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
   geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o]/V[c]), y="Spike count") +
-  scale_color_gradient(low="gold", high="darkgreen") +
-  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
+  labs(x=expression(V[o]/V[c]), y="Avg. error (ms)") +
+  scale_color_gradient2(
+    low="gold", high="darkgreen", mid="darkgrey", 
+    midpoint=20, name="Freq (Hz)", breaks = c(5, 10, 15, 20), limits=c(5, 20)) +
   theme_classic() +
-  theme(legend.position="right", 
+  geom_vline(xintercept = 1, alpha=0.5, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.3, color="black", linetype="dashed") +
+  scale_y_continuous(breaks=c(0, 4.0, 8.0, 12.0), limits=c(0, 12)) +
+  theme(legend.position="top", 
     legend.key.size = unit(.3, "cm"),
@@
 fig2 %>% 
-  filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o]/V[c]), y="Error (ms)") +
-  scale_color_gradient(low="gold", high="darkgreen") +
-  theme_classic() +
-  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
-  theme(legend.position="none", 
-    legend.key.size = unit(.5, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p3
-
-fig2 %>% 
+  filter(freq <= 20) %>%
   filter(V_osc/V_comp <= 3) %>% 
@@
   geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o]/V[c]), y="Variance (ms)") +
-  scale_color_gradient(low="gold", high="darkgreen") +
-  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
+  labs(x=expression(V[o]/V[c]), y="Pop. variance (ms)") +
+  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
+  scale_y_continuous(breaks=c(8.0, 10, 12.0), limits=c(8, 12)) +
   theme_classic() +
@@
 
+fig2 %>% 
+  filter(freq <= 20) %>%
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) + 
+  # labs(x=expression(V[o]/V[c]), y="Variance (ms)") +
+  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
+  lims(y=c(9,11)) +
+  theme_classic() +
+  theme(axis.line=element_blank(),
+      axis.text.x=element_blank(),
+      # axis.text.y=element_blank(),
+      axis.ticks.x=element_blank(),
+      axis.title.x=element_blank(),
+      axis.title.y=element_blank(),
+      legend.position="none",
+      panel.background=element_blank(),
+      panel.border=element_blank(),
+      panel.grid.major=element_blank(),
+      panel.grid.minor=element_blank(),
+      plot.background=element_blank()) -> p2.sub
+
+fig2 %>% 
+  filter(freq <= 20) %>%
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) + 
+  labs(x=expression(V[o]/V[c]), y="Spike count") +
+  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
+  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
+  theme_classic() +
+  theme(legend.position="none", 
+    legend.key.size = unit(.3, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) -> p3
+
+# ------------------------------------------
+# FAST
+fig2 %>% 
+  filter(freq >= 20) %>%
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) + 
+  labs(x=expression(V[o]/V[c]), y="Avg. error (ms)") +
+  scale_color_gradient2(
+    low="gold", high="darkgreen", mid="darkgrey", 
+    midpoint=20, name="", breaks = c(20, 25, 30)) +
+  theme_classic() +
+  geom_vline(xintercept = 1, alpha=0.5, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.3, color="black", linetype="dashed") +
+  scale_y_continuous(breaks=c(0, 4.0, 8.0, 12.0), limits=c(0, 12)) +
+  theme(legend.position="top", 
+    legend.key.size = unit(.3, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) -> p4
+
+fig2 %>% 
+  filter(freq >= 20) %>%
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) + 
+  labs(x=expression(V[o]/V[c]), y="Pop. variance (ms)") +
+  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
+  scale_y_continuous(breaks=c(8.0, 10, 12.0), limits=c(8, 12)) +
+  theme_classic() +
+  theme(legend.position="none", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) -> p5
+
+fig2 %>%
+  filter(freq >= 20) %>%
+  filter(V_osc/V_comp <= 3) %>%
+  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
+  geom_jitter(alpha=0.2, size=0.1) +
+  labs(x=expression(V[o]/V[c]), y="Spike count") +
+  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
+  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
+  theme_classic() +
+  theme(legend.position="none",
+    legend.key.size = unit(.3, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) -> p6
+
 plot_grid <- rbind(
-  c(1, 1, 1, 1, NA, NA),
-  c(1, 1, 1, 1, NA, NA),
-  c(1, 1, 1, 1, NA, NA),
-  c(2, 2, 2, 3, 3, 3),
-  c(2, 2, 2, 3, 3, 3),
-  c(2, 2, 2, 3, 3, 3))
+  c(1, 4),
+  c(1, 4),
+  c(1, 4),
+  c(2, 5),
+  c(2, 5),
+  c(3, 6),
+  c(3, 6))
+grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=plot_grid)
+rm(p1, p2, p3, p4, p5, p6, plot_grid)
+```
 
-grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
-rm(p1, p2, p3, plot_grid)
+# Optimal
+
+```{r, fig.width=3, fig.height=1.4}
+fig4 %>% 
+  filter(alg != "coincidence") %>%
+  ggplot(aes(x=(ts - min(ts))*1e3, y=ns, color=set)) +
+  geom_point(size=0.5, alpha=0.7) +
+  facet_grid(alg~.) +
+  scale_color_manual(values=c("black", "darkgrey"), name="") +
+  theme_classic() +
+  labs(x="Time (ms)", y="Neuron") +
+  theme(
+    legend.position="top", 
+    legend.key.size = unit(.5, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    strip.background = element_blank(),
+    strip.text.y = element_text(angle = 0)) -> p1
+
+fig3 %>% 
+  filter(alg != "coincidence") %>%
+  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, linetype=alg)) +
+  geom_line(size=0.6, alpha=0.9) +
+  scale_linetype_manual(values=c("longdash", "solid", "dotdash"), name="Algorithm") +
+  theme_classic() +
+  labs(x="Error (ms)", y="Variance (ms)") -> p2
+
+plot_grid <- rbind(
+  c(1, 1, 1, NA, NA, NA, NA),
+  c(1, 1, 1, 2, 2, 2, 2),
+  c(1, 1, 1, 2, 2, 2, 2),
+  c(1, 1, 1, 2, 2, 2, 2))
+
+grid.arrange(p1, p2, layout_matrix=plot_grid)
+rm(p1, p2, plot_grid)
 ```

### 2018-03-23 voltagebudget/analysis/optimal_analysis.Rmd
Added optimal analysis Rmb

---
title: "Optimal coordination - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)
library(scales)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

# Load and process

```{r, message=FALSE}
# Data
algs <- c("max", "left", "uni", "cc")
alg_names <- c("max", "left", "uniform", "coincidence")
exps <- c(82, 83, 84, 85)

results <- NULL
for (n in 1:4){
  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], ".csv", sep=""))
  df$alg <- rep(alg_names[n], nrow(df))

  results <- rbind(results, df)
}

# Spikes
# Load ref spikes
ref <- read_csv("../data/stim1.csv")
ref$set <- rep("reference", nrow(ref))

# Load exp spikes
exps <- c(86, 87, 88, 89)
spikes <- NULL
for (n in 1:4){
  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], "_c0.2.csv", sep=""))
  df$set <- rep("experiment", nrow(df))

  # Add ref
  df <- rbind(df, ref)

  df$alg <- rep(alg_names[n], nrow(df))
  spikes <- rbind(spikes, df)
}

rm(df, n, ref)
```

```{r, fig.width=1.4, fig.height=0.8}
results %>% 
  filter(alg != "coincidence") %>%
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, linetype=alg)) +
  geom_line(size=0.6, alpha=0.9) +
  scale_linetype_manual(values=c("longdash", "solid", "dotdash"), name="Algorithm") +
  theme_classic() +
  labs(x="Error (ms)", y="Variance (ms)")
```

```{r, fig.width=1.0, fig.height=1.5}
spikes %>% 
  filter(alg != "coincidence") %>%
  ggplot(aes(x=ts, y=ns, color=set)) +
  geom_point(size=0.1) +
  facet_grid(alg~.) +
  scale_color_manual(values=c("black", "grey")) +
  theme_classic() +
  theme(
    legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8))
```

### 2018-03-30 voltagebudget/analysis/paper_figures.Rmd
Added shift figure

@@
 
+# Shift-add cartoon
+fig5 <- read_csv("vm_ref_timecourse.csv")
+fig6 <- read_csv("vm_shift_timecourse.csv")
+fig7 <- read_csv("vm_add_timecourse.csv")
+
 rm(df, exp, freq, freqs, name, ref, n)
+```
+
+# Shift-add cartoon
+
+```{r, fig.width=1.2, fig.height=0.5}
+t_start <- 0.2
+t_stop <- 0.3
+
+fig6 %>% 
+  filter(t > t_start, t < t_stop) %>%
+  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
+  geom_ribbon(fill="red", alpha=0.5) +
+  geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
+  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.5) +
+  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
+  labs(x="", y="") +
+  theme_classic() +
+  theme(axis.line=element_blank(),
+      axis.text.x=element_blank(),
+      axis.text.y=element_blank(),
+      axis.ticks=element_blank(),
+      # axis.title.x=element_blank(),
+      # axis.title.y=element_blank(),
+      legend.position="none",
+      panel.background=element_blank(),
+      panel.border=element_blank(),
+      panel.grid.major=element_blank(),
+      panel.grid.minor=element_blank(),
+      plot.background=element_blank()) -> p1
+
+fig7 %>% 
+  filter(t > t_start, t < t_stop) %>%
+  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
+  geom_ribbon(fill="red", alpha=0.5) +
+  geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
+  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.5) +
+  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
+  labs(x="", y="") +
+  theme_classic() +
+  theme(axis.line=element_blank(),
+      axis.text.x=element_blank(),
+      axis.text.y=element_blank(),
+      axis.ticks=element_blank(),
+      # axis.title.x=element_blank(),
+      # axis.title.y=element_blank(),
+      legend.position="none",
+      panel.background=element_blank(),
+      panel.border=element_blank(),
+      panel.grid.major=element_blank(),
+      panel.grid.minor=element_blank(),
+      plot.background=element_blank()) -> p2
+
+plot_grid <- rbind(c(1, 1, 1, 2, 2, 2))
+grid.arrange(p1, p2, layout_matrix=plot_grid)
+rm(p1, p2, plot_grid)
 ```
@@
   ggplot(aes(x=(ts - min(ts))*1e3, y=ns, color=set)) +
-  geom_point(size=0.5, alpha=0.7) +
+  geom_point(size=0.7, alpha=1) +
   facet_grid(alg~.) +
@@
   ggplot(aes(x=errors*1e3, y=obs_variances*1e3, linetype=alg)) +
-  geom_line(size=0.6, alpha=0.9) +
-  scale_linetype_manual(values=c("longdash", "solid", "dotdash"), name="Algorithm") +
+  geom_line(size=0.8, alpha=1, color="darkgrey") +
+  scale_linetype_manual(values=c("dashed", "solid", "dotted"), name="Algorithm") +
   theme_classic() +

### 2018-03-30 voltagebudget/exp/sweep_A.py
Added noise exp and updated sweep_A API to accomidate this exp.

@@ -43,7 +43,7 @@ def sweep_A(name,
             f=8,
             N=10,
             mode='regular',
-            noise=False,
+            sigma=0,
             no_lock=False,
             verbose=False,
             save_only=False,
@@ -61,9 +61,7 @@ def sweep_A(name,
     if verbose:
         print(">>> Setting mode.")
 
-    params, w_in, bias_in, sigma = read_modes(mode)
-    if not noise:
-        sigma = 0
+    params, w_in, bias_in, _ = read_modes(mode)
 
     # --------------------------------------------------------------
     if verbose:

### 2018-04-02 voltagebudget/analysis/sweep_sigma_analysis.Rmd
Added sweep_sigma_analysis Rmd

---
title: "Sweep Z - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
data_summary <- function(x) {
   m <- mean(x)
   ymin <- m-mad(x)
   ymax <- m+mad(x)
   return(c(y=m,ymin=ymin,ymax=ymax))
}
mean_summary <- function(x) {
   m <- mean(x)
   return(c(y=m))
}
```

# Load and process

```{r, message=FALSE}
# Osc
freq <- "20"

# sigma scan
exp <- "90"
sigmas <- c("1.0e-9", "5.0e-9", "10.0e-9")

results <- NULL
for(sigma in sigmas){
  name <- paste("../data/exp", exp, "_sigma", sigma, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))

  df$sigma <- rep(as.numeric(sigma), nrow(df))
  results <- rbind(results, df)
}

# Ref (Z=0)
exp <- "91"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$sigma <- rep(0, nrow(df))
results <- rbind(df, results)

# Process
results %>% 
  filter(n_spikes_ref > 0) %>% 
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  mutate(V_osc = V_osc - V_osc_ref) -> results

rm(df, exp, freq, sigmas, sigma, name)
```

# As

```{r, fig.width=1.9, fig.height=1.5}
results %>% 
  # filter(rank == 0) %>% 
  ggplot(aes(x=As, y=n_spikes_pop, color=factor(sigma))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  # filter(rank == 0) %>% 
  ggplot(aes(x=As, y=variances_pop, color=factor(sigma))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  # filter(rank == 0) %>% 
  ggplot(aes(x=As, y=errors_pop, color=factor(sigma))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

# V_osc/V_b

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=V_osc/V_b, y=n_spikes_pop, color=factor(sigma))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

### Errors

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors_pop, color=factor(sigma))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.9, fig.height=1}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~sigma) +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.9, fig.height=1}
results %>% 
  filter(V_osc/V_comp <= 1) %>% 
  filter(n_spikes >0) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~sigma) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.1, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=5.5, fig.height=2.5}
M1 <- mean(filter(results, sigma == 0)$errors*1e3)
max_N <- max(results$N)

results %>% 
  filter(V_osc/V_comp <= 3) %>%
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_grid(sigma~rank) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
  geom_hline(yintercept = M1, alpha=0.7, color="black") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank())

rm(max_N, M1)
```

### Variances

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances_pop, color=factor(sigma))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0, V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop, color=factor(sigma))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.9, fig.height=1}
results %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~sigma) +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom")
```

```{r, fig.width=1.9, fig.height=1}
results %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~sigma) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=5.5, fig.height=2.5}
max_N <- max(results$N)

results %>% 
  filter(V_osc/V_comp <= 3) %>%
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_grid(sigma~rank) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank())

rm(max_N)
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=errors_pop, y=variances_pop, color=factor(sigma))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.9, fig.height=1}
M1 = mean(filter(results, sigma == 0)$errors*1e3)
M2 = mean(filter(results, sigma == 0)$variances*1e3)

results %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=errors*1e3, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  theme_classic() +
  facet_grid(.~sigma) +
  geom_vline(xintercept = M1, alpha=0.7, color="black") +
  geom_hline(yintercept = M2, alpha=0.7, color="black") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom")

rm(M1, M2)
```

```{r, fig.width=6.5, fig.height=2.5}
M1 <- mean(filter(results, sigma == 0)$errors*1e3)
M2 <- mean(filter(results, sigma == 0)$variances*1e3)
max_N <- max(results$N)

results %>% 
  filter(V_osc/V_comp <= 3) %>%
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=errors*1e3, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_grid(sigma~rank) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  labs(x="Error (ms)", y="Variance (ms)") +
  geom_vline(xintercept = M1, alpha=0.7, color="black") +
  geom_hline(yintercept = M2, alpha=0.7, color="black") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank())

rm(max_N, M1)
```

## n_spikes v rest

```{r, fig.width=2.25, fig.height=1}
results %>% 
  ggplot(aes(x=delta_spikes, y=errors)) +
  facet_grid(.~sigma) +
  lims(y=c(0, 0.03)) +
  geom_jitter(size=0.1, alpha=0.01) +
  stat_summary(fun.data=data_summary, color="darkgrey", size=0.6, geom="linerange") +
  stat_summary(fun.data=mean_summary, color="darkgrey", size=0.4, geom="point") +
  theme_classic() 
```

```{r, fig.width=2.25, fig.height=1}
results %>% 
  ggplot(aes(x=delta_spikes, y=variances)) +
  facet_grid(.~sigma) +
  # lims(y=c(0, 0.03)) +
  geom_jitter(size=0.1, alpha=0.01) +
  stat_summary(fun.data=data_summary, color="darkgrey", size=0.6, geom="linerange") +
  stat_summary(fun.data=mean_summary, color="darkgrey", size=0.4, geom="point") +
  theme_classic() 
```

### 2018-04-03 voltagebudget/analysis/sweep_sigma_analysis.Rmd
Update/cleanup sigma vis Rmd

@@
 # sigma scan
-exp <- "90"
-sigmas <- c("1.0e-9", "5.0e-9", "10.0e-9")
+exp <- "97"
+# sigmas <- c("1.0e-9", "5.0e-9", "10.0e-9")
+sigmas <- c("1.0e-9", "2.0e-9", "3.0e-9", "4.0e-9", "5.0e-9")
 
@@
 # Ref (Z=0)
-exp <- "91"
+exp <- "96"
 name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
@@
   theme_classic() +
-  facet_grid(.~sigma) +
+  facet_wrap(~sigma) +
   # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
@@
 
-```{r, fig.width=1.9, fig.height=1}
+```{r, fig.width=1.9, fig.height=1.3}
 results %>% 
-  filter(V_osc/V_comp <= 1) %>% 
-  filter(n_spikes >0) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
+  filter(V_osc/V_comp <= 3) %>% 
+  group_by(N, sigma) %>% 
+  mutate(norm_errors = errors/max(errors)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_errors)) +
   geom_point(size=0.01, alpha=0.01) + 
   theme_classic() +
-  facet_grid(.~sigma) +
+  facet_wrap(~sigma) +
   geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
-  geom_vline(xintercept = 0.1, alpha=0.5, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
   # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
   theme(legend.position="bottom") 
-```
-
-```{r, fig.width=5.5, fig.height=2.5}
-M1 <- mean(filter(results, sigma == 0)$errors*1e3)
-max_N <- max(results$N)
-
-results %>% 
-  filter(V_osc/V_comp <= 3) %>%
-  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
-  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
-  geom_point(size=1, alpha=1) + 
-  facet_grid(sigma~rank) +
-  scale_colour_brewer(palette = "Accent", name="Spike count") +
-  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
-  geom_hline(yintercept = M1, alpha=0.7, color="black") +
-  theme_classic() + theme(
-    # legend.position="bottom",
-    strip.text.x = element_text(size=0),
-    strip.background = element_blank(),
-    legend.position="right", 
-    legend.key.size = unit(.5, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8),
-    # axis.line=element_blank(),
-    # axis.text.x=element_blank(),
-    # axis.text.y=element_blank(),
-    # axis.ticks=element_blank(),
-    # axis.title.x=element_blank(),
-    # axis.title.y=element_blank(),
-    panel.background=element_blank(),
-    # panel.border=element_blank(),
-    # panel.grid.major=element_blank(),
-    # panel.grid.minor=element_blank(),
-    plot.background=element_blank())
-
-rm(max_N, M1)
 ```
@@
 
-```{r, fig.width=1.9, fig.height=1}
-results %>% 
-  # filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(x=V_osc/V_b, y=variances*1e3)) +
-  geom_point(size=0.01, alpha=0.01) + 
-  theme_classic() +
-  facet_grid(.~sigma) +
-  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom")
-```
-
-```{r, fig.width=1.9, fig.height=1}
+```{r, fig.width=1.9, fig.height=1.4}
 results %>% 
@@
   theme_classic() +
-  facet_grid(.~sigma) +
+  facet_wrap(~sigma) +
   geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
@@
   theme(legend.position="bottom") 
-```
-
-```{r, fig.width=5.5, fig.height=2.5}
-max_N <- max(results$N)
-
-results %>% 
-  filter(V_osc/V_comp <= 3) %>%
-  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
-  ggplot(aes(x=V_osc/V_b, y=variances*1e3, color=factor(delta_spikes))) +
-  geom_point(size=1, alpha=1) + 
-  facet_grid(sigma~rank) +
-  scale_colour_brewer(palette = "Accent", name="Spike count") +
-  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
-  theme_classic() + theme(
-    # legend.position="bottom",
-    strip.text.x = element_text(size=0),
-    strip.background = element_blank(),
-    legend.position="right", 
-    legend.key.size = unit(.5, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8),
-    # axis.line=element_blank(),
-    # axis.text.x=element_blank(),
-    # axis.text.y=element_blank(),
-    # axis.ticks=element_blank(),
-    # axis.title.x=element_blank(),
-    # axis.title.y=element_blank(),
-    panel.background=element_blank(),
-    # panel.border=element_blank(),
-    # panel.grid.major=element_blank(),
-    # panel.grid.minor=element_blank(),
-    plot.background=element_blank())
-
-rm(max_N)
 ```
@@
 
-```{r, fig.width=1.9, fig.height=1}
+```{r, fig.width=3, fig.height=1}
 M1 = mean(filter(results, sigma == 0)$errors*1e3)
@@
 rm(M1, M2)
-```
-
-```{r, fig.width=6.5, fig.height=2.5}
-M1 <- mean(filter(results, sigma == 0)$errors*1e3)
-M2 <- mean(filter(results, sigma == 0)$variances*1e3)
-max_N <- max(results$N)
-
-results %>% 
-  filter(V_osc/V_comp <= 3) %>%
-  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
-  ggplot(aes(x=errors*1e3, y=variances*1e3, color=factor(delta_spikes))) +
-  geom_point(size=1, alpha=1) + 
-  facet_grid(sigma~rank) +
-  scale_colour_brewer(palette = "Accent", name="Spike count") +
-  labs(x="Error (ms)", y="Variance (ms)") +
-  geom_vline(xintercept = M1, alpha=0.7, color="black") +
-  geom_hline(yintercept = M2, alpha=0.7, color="black") +
-  theme_classic() + theme(
-    # legend.position="bottom",
-    strip.text.x = element_text(size=0),
-    strip.background = element_blank(),
-    legend.position="right", 
-    legend.key.size = unit(.5, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8),
-    # axis.line=element_blank(),
-    # axis.text.x=element_blank(),
-    # axis.text.y=element_blank(),
-    # axis.ticks=element_blank(),
-    # axis.title.x=element_blank(),
-    # axis.title.y=element_blank(),
-    panel.background=element_blank(),
-    # panel.border=element_blank(),
-    # panel.grid.major=element_blank(),
-    # panel.grid.minor=element_blank(),
-    plot.background=element_blank())
-
-rm(max_N, M1)
 ```

### 2018-04-03 voltagebudget/analysis/sweep_Z_analysis.Rmd
Update Z vis Rmd

@@
 # Osc
-freq <- "8"
+freq <- "20"
 
 # Zs scan
-exp <- "78"
+exp <- "92"
 Zs <- c("0.1", "0.2", "0.3")
@@
 for(Z in Zs){
-  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, "_Z", Z, ".csv", sep="")
+  name <- paste("../data/exp", exp, "_Z", Z, ".csv", sep="")
   df <- read_csv(paste(name, sep=","))
@@
 # Ref (Z=0)
-exp <- "77"
+exp <- "91"
 name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
@@
 results %>% 
+  filter(n_spikes_ref > 0) %>% 
   mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
@@
 results %>% 
-  filter(V_osc/V_comp <= 3) %>% 
+  filter(V_osc/V_comp <= 1) %>% 
+  filter(n_spikes >0) %>% 
   ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
@@
   geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.1, alpha=0.5, color="purple", linetype="dashed") +
   # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +

### 2018-04-03 voltagebudget/analysis/sweep_Z_analysis.Rmd
Update Z vis Rmd

--- 2018-03-11 voltagebudget/analysis/sweep_Z_analysis.Rmd
@@
 # Osc
-freq <- "40"
+freq <- "20"
 
 # Zs scan
-exp <- "74"
+exp <- "98"
 Zs <- c("0.1", "0.2", "0.3")
@@
 # Ref (Z=0)
-exp <- "72"
+exp <- "96"
 name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
@@
   filter(rank == 0) %>% 
+  ggplot(aes(x=As, y=errors_pop, color=factor(Zs))) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+# V_osc/V_b
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(rank == 0) %>% 
+  ggplot(aes(x=V_osc/V_b, y=n_spikes_pop, color=factor(Zs))) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+### Errors
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(rank == 0) %>% 
+  ggplot(aes(x=V_osc/V_b, y=errors_pop, color=factor(Zs))) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=1.9, fig.height=1}
+results %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  filter(errors < 0.1) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
+  geom_point(size=0.01, alpha=0.01) + 
+  theme_classic() +
+  facet_grid(.~Zs) +
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=1.9, fig.height=1}
+results %>% 
+  filter(errors < 0.1) %>%
+  filter(V_osc/V_comp <= 3) %>% 
+  group_by(N, Zs) %>% 
+  mutate(norm_errors = errors/max(errors)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_errors)) +
+  geom_point(size=0.01, alpha=0.01) + 
+  theme_classic() +
+  facet_grid(.~Zs) +
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+### Variances
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(rank == 0) %>% 
+  ggplot(aes(x=V_osc/V_b, y=variances_pop, color=factor(Zs))) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(rank == 0, V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances_pop, color=factor(Zs))) +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  theme(legend.position="bottom") 
+```
+
+```{r, fig.width=1.9, fig.height=1}
+results %>% 
+  # filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_b, y=variances*1e3)) +
+  geom_point(size=0.01, alpha=0.01) + 
+  theme_classic() +
+  facet_grid(.~Zs) +
+  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom")
+```
+
+```{r, fig.width=1.9, fig.height=1}
+results %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
+  geom_point(size=0.01, alpha=0.01) + 
+  theme_classic() +
+  facet_grid(.~Zs) +
+  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+## Metrics
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(rank == 0) %>% 
   ggplot(aes(x=errors_pop, y=variances_pop, color=factor(Zs))) +
@@
 ```
+
+## n_spikes v rest
 

### 2018-04-03 voltagebudget/analysis/freq_analysis.Rmd
Improved freq vis

--- 2018-03-15 voltagebudget/analysis/freq_analysis.Rmd
@@
 # --------------------------
-exp <- "77"
-freqs <- c(24, 30)
+# exp <- "77"
+exp <- "96"
+freqs <- c(24, 30, 40)
 
@@
 # --------------------------
-exp <- "79"
+# exp <- "79"
+exp <- "94"
 freqs <- c(6, 8, 10, 12, 14, 16, 18, 20)
 
+for(freq in freqs){
+  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
+  df <- read_csv(paste(name, sep=","))
+  df %>%
+    filter(n_spikes > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  results <- rbind(results, df)
+}
+
+# exp <- "80"
+exp <- "95"
+freqs <- c(22, 24, 26, 28, 32, 34 ,36, 38)
 for(freq in freqs){
@@
   summarise(
+    N = 0,
+    V_b = mean(V_b),
     V_osc = mean(V_osc),
     delta_spikes = mean(delta_spikes),
+    errors = mean(errors), 
+    errors_pop = mean(errors_pop), 
     V_comp = mean(V_comp), 
     errors = mean(errors), 
+    variances_pop = mean(variances_pop),
     variances = mean(variances)) -> avg_results
@@
 
-- WTF? Vo is gettin way to big here...
+```{r, fig.width=1.2, fig.height=0.8}
+results %>%
+  filter(N == 0) %>% 
+  filter(freq <= 30) %>% 
+  ggplot(aes(x=As*1e9, y=errors_pop*1e3, color=freq, group=interaction(N, freq))) +
+  # geom_point(size=0.4, alpha=0.5) + 
+  geom_line(size=0.5, alpha=0.5) + 
+  labs(x="As (namp)", y="Error (ms)") +
+  theme_classic() +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) 
+```
 
@@
 avg_results %>%
-  ggplot(aes(x=V_osc*1e3, y=delta_spikes, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x="V_osc (mvolt)", y="Spike count") +
+  filter(As < 0.05e-9) %>% 
+  filter(freq <= 30) %>% 
+  ggplot(aes(x=As*1e9, y=variances_pop*1e3, color=freq, group=interaction(N, freq))) +
+  geom_line(size=0.5, alpha=0.5) + 
+  labs(x="As (namp)", y="Variance (ms)") +
+  theme_classic() +
   scale_color_gradient(low="gold", high="darkgreen") +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) 
+```
+
+### V_osc/V_comp
+
+```{r, fig.width=1.2, fig.height=0.8}
+avg_results %>% 
+  filter(V_osc/V_comp < 3) %>% 
+  filter(freq <= 30) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors_pop*1e3, color=freq, group=interaction(N, freq))) +
+  geom_line(size=0.3, alpha=1) + 
+  labs(x="V_osc/V_comp", y="Error (ms)") +
+  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
   theme_classic() +
@@
 avg_results %>% 
-  ggplot(aes(x=V_osc*1e3, y=errors, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x="V_osc (mvolt)", y="Error (ms)") +
+  filter(V_osc/V_comp < 3) %>% 
+  filter(freq <= 30) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances_pop*1e3, color=freq, group=interaction(N, freq))) +
+  geom_line(size=0.3, alpha=1) + 
+  labs(x="V_osc/V_comp", y="Variance (ms)") +
+  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
+  theme_classic() +
+  lims(y=c(5, 10)) +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8))
+```
+
+```{r, fig.width=1.2, fig.height=0.8}
+avg_results %>% 
+  filter(V_osc/V_comp < 3) %>% 
+  filter(freq <= 30) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=interaction(N, freq))) +
+  geom_line(size=0.5, alpha=0.5) + 
+  labs(x="V_osc/V_comp", y="Avg. count") +
   scale_color_gradient(low="gold", high="darkgreen") +
@@
 ```
-
-```{r, fig.width=1.3, fig.height=0.8}
-avg_results %>% 
-  ggplot(aes(x=V_osc*1e3, y=variances, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x="V_osc (mvolt)", y="Variance (ms)") +
-  scale_color_gradient(low="gold", high="darkgreen") +
-  theme_classic() +
-  theme(legend.position="right", 
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8))
-```
-
-```{r, fig.width=1.2, fig.height=0.8}
-results %>%
-  filter(rank == 0) %>% 
-  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=freq)) +
-  geom_point(size=0.05, alpha=0.2) + 
-  labs(x="Error (ms)", y="Variance (ms)") +
-  theme_classic() +
-  scale_color_gradient(low="gold", high="darkgreen") +
-  theme(legend.position="right", 
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) 
-```

### 2018-04-03 voltagebudget/analysis/paper_figures.Rmd
Update first 4 figs

@@
 }
+sample_n_groups = function(tbl, size, replace = FALSE, weight = NULL) {
+  # regroup when done
+  grps = tbl %>% groups %>% lapply(as.character) %>% unlist
+  # check length of groups non-zero
+  keep = tbl %>% summarise() %>% ungroup() %>% sample_n(size, replace, weight)
+  # keep only selected groups, regroup because joins change count.
+  # regrouping may be unnecessary but joins do something funky to grouping variable
+  tbl %>% right_join(keep, by=grps) %>% group_by_(.dots = grps)
+}
 ```
@@
 # INITIAL
-exp <- "77"
+exp <- "96"
 freqs <- c(20, 30)
@@
 # SLOW
-exp <- "79"
+exp <- "94"
 freqs <- c(6, 8, 10, 12, 14, 16, 18)
@@
 # FAST
-exp <- "80"
+exp <- "95"
 freqs <- c(22, 24, 26, 28)#, 32, 34 ,36, 38)
@@
 fig1 %>% 
+  filter(n_spikes_ref > 0) %>% 
   # Add delta_spikes
@@
   summarise(
+    N = 0,
     delta_spikes = mean(delta_spikes), 
@@
   labs(x=expression(V[o]/V[b]), y="Avg. error (ms)") +
-  lims(y=c(0, 10)) +
+  # lims(y=c(0, 10)) +
   scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
-  scale_color_gradient(low="lightgrey", high="red") +
+  scale_color_gradient(low="darkgrey", high="red") +
   theme_classic() +
@@
   labs(x=expression(V[o]/V[b]), y="Pop. variance (ms)") +
-  scale_color_gradient(low="lightgrey", high="red") +
+  scale_color_gradient(low="darkgrey", high="red") +
   scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
@@
   geom_point(size=0.05, alpha=.6) +
-  scale_color_gradient(low="lightgrey", high="red", name=expression(V[o]/V[b])) +
-  # scale_color_gradient(low="lightgrey", high="red", name="A (namp)") +
-  geom_smooth(color="black", method=lm, alpha=0.2, size=.8, linetype='dotted') +
+  scale_color_gradient(low="darkgrey", high="red", name=expression(V[o]/V[b])) +
+  # scale_color_gradient(low="darkgrey", high="red", name="A (namp)") +
+  geom_smooth(color="red", method=lm, alpha=0.2, size=.15, se=FALSE, linetype='solid') +
   labs(x="Avg. error (ms)", y="Pop. variance (ms)") +
@@
     legend.position="right", 
+    legend.background = element_rect(colour ="black"),
     legend.key.size = unit(.4, "cm"),
@@
 fig1 %>% 
+  group_by(N) %>% 
   filter(V_osc/V_comp <= 3) %>% 
   filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
-  geom_point(size=0.01, alpha=0.01, color="grey") + 
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
+  geom_line(size=0.5, alpha=0.2, color="grey") + 
   geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
@@
   filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
-  geom_point(size=0.01, alpha=0.01, color="grey") + 
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, group=N)) +
+  geom_line(size=0.5, alpha=0.2, color="grey") + 
   geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
@@
   theme_classic() +
-  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
-            aes(x=V_osc/V_comp, y=variances*1e3), 
+  geom_line(data=filter(fig1, freq==20, V_osc/V_comp <= 3), 
+            aes(x=V_osc/V_comp, y=variances_pop*1e3), 
             color="black", size=0.7, alpha=1) +
@@
 fig1 %>% 
-  filter(V_osc/V_comp <= 3) %>% 
   filter(freq==20) %>% 
@@
   filter(N %in% sample(1:max_N, 24, replace = FALSE)) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
-  geom_point(size=.1, alpha=0.1, color="grey") + 
+  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
+  geom_line(size=.5, alpha=0.9, color="grey") + 
   geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
@@
 
-```{r, fig.width=3.7, fig.height=3.1}
+```{r, fig.width=2.6, fig.height=3.2}
 max_N <- max(fig1$N)
@@
   filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc/V_b, y=variances*1e3)) +
-  geom_point(size=0.1, alpha=0.1, color="grey") + 
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  ggplot(aes(x=V_osc/V_b, y=variances*1e3, group=N)) +
+  geom_line(size=0.5, alpha=0.2, color="grey") + 
   theme_classic() +
@@
 fig1 %>% 
+  filter(freq == 20) %>% 
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  ggplot(aes(x=V_osc/V_b, y=variances*1e3, group=N, color=factor(delta_spikes))) +
+  geom_line(size=0.4, alpha=0.6) + 
+  scale_colour_brewer(
+    palette = "Reds", guide=guide_legend(title="Spike count", nrow=3)) +
+  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
+  theme_classic() + theme(legend.position="none") -> p2
+
+# -
+M = min(fig1$variances_pop)
+fig1 %>% 
+  filter(freq == 20) %>% 
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  ggplot(aes(x=variances*1e3, fill=factor(delta_spikes))) +
+  geom_density(alpha=0.6, size=0, color="black") +
+  scale_fill_brewer(palette = "Reds", name="Spike\ncount") +
+  geom_vline(xintercept = M*1e3, color="black", linetype="dotted") +
+  labs(x="Variance (ms)", y="Density (AU)") +
+  theme_classic() + 
+  theme(legend.position = c(1.25, 1.55), 
+        legend.background = element_rect(colour ="black"),
+        legend.key.size = unit(.5, "cm"),
+        legend.title = element_text(size=10),
+        legend.text = element_text(size=10)) -> p3
+
+fig1 %>% 
   filter(freq==20) %>% 
-  # filter(V_osc/V_comp <= 3) %>% 
-  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
+  filter(V_osc/V_comp <= 3) %>% 
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  ggplot(aes(y=V_osc/V_comp, x=factor(delta_spikes), group=delta_spikes)) +
+  geom_jitter(aes(color=factor(delta_spikes)), size=0.01, alpha=0.1, width=0.2) +
+  geom_boxplot(outlier.colour = NA, alpha=0.9, width=0.2) +
+  scale_colour_brewer(palette = "Reds", name="Spike count") +
+  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
+  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  theme_classic() +
+  theme(legend.position = "none") +
+  labs(y=expression(V[o]/V[c]), x="Spike count") + 
+  coord_flip()  -> p4
+
+fig1 %>%
+  filter(freq==20) %>%
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  ungroup() %>% 
+  group_by(N) %>% 
+  sample_n_groups(8) %>% 
   ggplot(aes(x=V_osc/V_b, y=variances*1e3, color=factor(delta_spikes))) +
   geom_point(size=1, alpha=1) +
-  facet_wrap(~rank, ncol=2) +
+  facet_wrap(~N, nrow=8) +
   geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3),
             color="black", size=0.7, alpha=1) +
-  scale_colour_brewer(palette = "Accent", name="Spike count") +
+  scale_colour_brewer(palette = "Reds", name="Spike count") +
   scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
-  scale_y_continuous(breaks=c(8, 12)) +
+  scale_y_continuous(breaks=c(6, 12)) +
   labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
@@
     # panel.grid.minor=element_blank(),
-    plot.background=element_blank()) -> p2
+    plot.background=element_blank()) -> p5
 
@@
   filter(freq==20) %>%
-  # filter(V_osc/V_comp <= 3) %>% 
-  filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
+  filter(V_osc/V_comp <= 3) %>%
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  sample_n_groups(8) %>% 
   ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
   geom_point(size=1, alpha=1) +
-  facet_wrap(~rank, ncol=1) +
-  geom_line(aes(x=V_osc/V_b, y=errors_pop*1e3), 
-            color="black", size=0.7, alpha=1) +
-  scale_colour_brewer(palette = "Accent", name="Spike count") +
+  facet_wrap(~N, nrow=8) +
+  # geom_line(aes(x=V_osc/V_b, y=errors_pop*1e3),
+  #           color="black", size=0.7, alpha=1) +
+  scale_colour_brewer(palette = "Reds", name="Spike count") +
   scale_x_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
@@
     strip.background = element_blank(),
-    legend.position="right", 
+    legend.position="none",
     legend.key.size = unit(.5, "cm"),
@@
     # panel.grid.minor=element_blank(),
-    plot.background=element_blank()) -> p3
-
-# -
-M = min(fig1$variances_pop)
-
-fig1 %>% 
-  filter(freq==20) %>% 
-  mutate(quantile = ntile(V_osc, 10)) %>%
-  filter(quantile %in% c(1, 10)) %>% 
-  ggplot(aes(x=variances, fill=factor(quantile), group=quantile)) +
-  geom_density(alpha=0.6, size=0.2, color="black") +
-  geom_vline(xintercept = M, color="black") +
-  labs(x="Variance (ms)", y="Density (AU)") +
-  scale_fill_manual(
-    # values=c("#FFDED3", "#FD0D11"), 
-    values=c("grey", "black"),
-    name=expression("Deciles V"[o]), 
-    labels=c("0 - 10%", "90 - 100%")) +
-  theme_classic() +
-  theme(
-    legend.position="bottom", 
-    legend.key.size = unit(.3, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8) ) -> p4
-
-fig1 %>% 
-  filter(freq==20) %>% 
-  ggplot(aes(x=delta_spikes, y=variances*1e3, color=factor(delta_spikes))) +
-  geom_boxplot(outlier.size = NA, size=0.8, show.legend=FALSE)+
-  labs(x="Spike count", y="Variance (ms)") +
-  scale_colour_brewer(palette = "Accent", name="Spike count") +
-  theme_classic() +
-  theme(legend.position="none") -> p5
-
-fig1 %>% 
-  filter(freq==20) %>% 
-  filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(y=V_osc/V_comp, x=delta_spikes)) +
-  geom_jitter(size=0.1, alpha=0.01) + 
-  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
-  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
-  theme_classic() +
-  labs(y=expression(V[o]/V[c]), x="Spike count") -> p6
+    plot.background=element_blank()) -> p6
 
 plot_grid <- rbind(
-  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,  3, 3),
-  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,  3, 3),
-  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,  3, 3),
-  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,  3, 3),
-  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,  3, 3),
-  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,  3, 3),
-  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6),
-  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6),
-  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6))
+  c(1, 1, 1, NA, 5, 5, 6, 6),
+  c(1, 1, 1, NA, 5, 5, 6, 6),
+  c(1, 1, 1, NA, 5, 5, 6, 6),
+  c(2, 2, 2, NA, 5, 5, 6, 6),
+  c(2, 2, 2, NA, 5, 5, 6, 6),
+  c(2, 2, 2, NA, 5, 5, 6, 6),
+  c(3, 3, 3, NA, 5, 5, 6, 6),
+  c(3, 3, 3, NA, 5, 5, 6, 6),
+  c(3, 3, 3, NA, 5, 5, 6, 6),
+  c(4, 4, 4, NA, NA, NA, NA, NA),
+  c(4, 4, 4, NA, NA, NA, NA, NA),
+  c(4, 4, 4, NA, NA, NA, NA, NA))
 

### 2018-04-04 voltagebudget/analysis/weight_analysis.Rmd
Added weight analysis Rmd

---
title: "Sweep Z - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
data_summary <- function(x) {
   m <- mean(x)
   ymin <- m-mad(x)
   ymax <- m+mad(x)
   return(c(y=m,ymin=ymin,ymax=ymax))
}
mean_summary <- function(x) {
   m <- mean(x)
   return(c(y=m))
}
```

# Load and process

```{r, message=FALSE}
# Osc
freq <- "20"

# Init
results <- NULL

# high w
exp <- "100"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$weight <- rep(2.48e-08, nrow(df))
results <- rbind(df, results)

# Ref (Z=0)
exp <- "96"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$weight <- rep(8.25e-09, nrow(df))
results <- rbind(df, results)

# low w
exp <- "99"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$weight <- rep(1.65e-09, nrow(df))
results <- rbind(df, results)

# Process
results %>% 
  filter(n_spikes_ref > 0) %>% 
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  mutate(V_osc = V_osc - V_osc_ref) -> results

rm(df, exp, freq, name)
```

# As

```{r, fig.width=1.9, fig.height=1.5}
results %>% 
  # filter(rank == 0) %>% 
  ggplot(aes(x=As, y=n_spikes_pop, color=factor(weight))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  # filter(rank == 0) %>% 
  ggplot(aes(x=As, y=variances_pop, color=factor(weight))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  # filter(rank == 0) %>% 
  ggplot(aes(x=As, y=errors_pop, color=factor(weight))) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

# V_osc/V_comp

```{r, fig.width=1.9, fig.height=1.3}
results %>% 
  filter(V_osc/V_comp <= 3) %>% 
  group_by(N, weight) %>% 
  mutate(norm_errors = errors/max(errors)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=interaction(N, weight), color=factor(weight*1e9))) +
  geom_line(size=0.3, alpha=0.4) + 
  theme_classic() +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

### 2018-04-04 voltagebudget/analysis/paper_figures.Rmd
Added control exps
Hetero vis still in progress

@@
 
-# --------------------------------------------------------------------
 # Summarize over As 
@@
 
-rm(df, exp, freq, freqs, name, ref, n)
+# --------------------------------------------------------------------
+# Load noise exp data...
+# Osc
+freq <- "20"
+
+# sigma scan
+exp <- "97"
+
+sigmas <- c("1.0e-9", "2.0e-9", "3.0e-9", "4.0e-9", "5.0e-9")
+
+fig8 <- NULL
+for(sigma in sigmas){
+  name <- paste("../data/exp", exp, "_sigma", sigma, ".csv", sep="")
+  df <- read_csv(paste(name, sep=","))
+
+  df$sigma <- rep(as.numeric(sigma), nrow(df))
+  fig8 <- rbind(fig8, df)
+}
+
+exp <- "96"
+name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+df <- read_csv(paste(name, sep=","))
+df$sigma <- rep(0, nrow(df))
+fig8 <- rbind(df, fig8)
+
+# Process
+fig8 %>% 
+  filter(n_spikes_ref > 0) %>% 
+  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
+  mutate(V_osc = V_osc - V_osc_ref) -> fig8
+
+# Summarize over As 
+fig8 %>% 
+  group_by(As, sigma) %>% 
+  summarise(
+    N = 0,
+    delta_spikes = mean(delta_spikes), 
+    V_b = mean(V_b), 
+    V_osc = mean(V_osc), 
+    V_comp = mean(V_comp), 
+    V_comp_ref = mean(V_comp_ref), 
+    errors = mean(errors), 
+    errors_pop = mean(errors_pop), 
+    variances_pop = mean(variances_pop), 
+    variances = mean(variances)) -> fig9
+
+# --------------------------------------------------------------------
+# Load weight exps
+# Osc
+freq <- "20"
+
+# Init
+fig10 <- NULL
+
+# high w
+exp <- "100"
+name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+df <- read_csv(paste(name, sep=","))
+df$weight <- rep(2.48e-08, nrow(df))
+fig10 <- rbind(df, fig10)
+
+# Ref (Z=0)
+exp <- "96"
+name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+df <- read_csv(paste(name, sep=","))
+df$weight <- rep(8.25e-09, nrow(df))
+fig10 <- rbind(df, fig10)
+
+# low w
+exp <- "99"
+name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+df <- read_csv(paste(name, sep=","))
+df$weight <- rep(1.65e-09, nrow(df))
+fig10 <- rbind(df, fig10)
+
+# Process
+fig10 %>% 
+  filter(n_spikes_ref > 0) %>% 
+  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
+  mutate(V_osc = V_osc - V_osc_ref) -> fig10
+
+# Summarize over As 
+fig10 %>% 
+  group_by(As, weight) %>% 
+  summarise(
+    N = 0,
+    delta_spikes = mean(delta_spikes), 
+    V_b = mean(V_b), 
+    V_osc = mean(V_osc), 
+    V_comp = mean(V_comp), 
+    V_comp_ref = mean(V_comp_ref), 
+    errors = mean(errors), 
+    errors_pop = mean(errors_pop), 
+    variances_pop = mean(variances_pop), 
+    variances = mean(variances)) -> fig11
+
+# --------------------------------------------------------------------
+# Hetero cells
+# Osc
+freq <- "20"
+
+# Init
+fig12 <- NULL
+
+# high w
+exp <- "101"
+name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+df <- read_csv(paste(name, sep=","))
+df$weight <- rep(2.48e-08, nrow(df))
+fig12 <- rbind(df, fig12)
+
+# Process
+fig12 %>% 
+  filter(n_spikes_ref > 0) %>% 
+  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
+  mutate(V_osc = V_osc - V_osc_ref) -> fig12
+
+# Summarize over As 
+fig12 %>% 
+  group_by(As, weight) %>% 
+  summarise(
+    N = 0,
+    delta_spikes = mean(delta_spikes), 
+    V_b = mean(V_b), 
+    V_osc = mean(V_osc), 
+    V_comp = mean(V_comp), 
+    V_comp_ref = mean(V_comp_ref), 
+    errors = mean(errors), 
+    errors_pop = mean(errors_pop), 
+    variances_pop = mean(variances_pop), 
+    variances = mean(variances)) -> fig13
+
+# --------------------------------------------------------------------
+rm(df, exp, freq, freqs, name, ref, n, sigmas, sigma, exps, alg_names, algs)
 ```
@@
   geom_line(size=0.5, alpha=0.2, color="grey") + 
-  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
   theme_classic() +
@@
   geom_line(size=.5, alpha=0.9, color="grey") + 
-  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
   facet_wrap(~rank, nrow=3) +
@@
   scale_colour_brewer(palette = "Reds", name="Spike count") +
-  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
-  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
+  geom_hline(yintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_hline(yintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
   theme_classic() +
@@
 
-# Freq effects - var reduction versus additional 'sampling'?
+# Control exps
+## Freqs, noise, weight
 
-```{r, fig.width=1.8, fig.height=2.25}
-# ------------------------------------------
-# SLOW
+```{r, fig.width=2.1, fig.height=2.4}
+# --------------------------------------------------------------
+# Freq
 fig2 %>% 
-  filter(freq <= 20) %>%
-  filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o]/V[c]), y="Avg. error (ms)") +
-  scale_color_gradient2(
-    low="gold", high="darkgreen", mid="darkgrey", 
-    midpoint=20, name="Freq (Hz)", breaks = c(5, 10, 15, 20), limits=c(5, 20)) +
+  filter(V_osc/V_comp < 3) %>% 
+  filter(freq <= 30) %>% 
+  group_by(N, freq) %>% 
+  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
+  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=freq, group=interaction(N, freq))) +
+  geom_line(size=0.3, alpha=1) + 
+  labs(x=expression(V[o]/V[b]), y="Norm. error") +
+  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
+  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
   theme_classic() +
-  geom_vline(xintercept = 1, alpha=0.5, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.3, color="black", linetype="dashed") +
-  scale_y_continuous(breaks=c(0, 4.0, 8.0, 12.0), limits=c(0, 12)) +
-  theme(legend.position="top", 
-    legend.key.size = unit(.3, "cm"),
+  theme(legend.position="none", 
+    legend.key.size = unit(.4, "cm"),
     legend.title = element_text(size=8),
@@
 fig2 %>% 
-  filter(freq <= 20) %>%
-  filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o]/V[c]), y="Pop. variance (ms)") +
-  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
-  scale_y_continuous(breaks=c(8.0, 10, 12.0), limits=c(8, 12)) +
+  filter(V_osc/V_comp < 3) %>% 
+  filter(freq <= 30) %>% 
+  group_by(N, freq) %>% 
+  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
+  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=freq, group=interaction(N, freq))) +
+  geom_line(size=0.3, alpha=1) + 
+  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
+  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
+  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
+  theme_classic() +
+  # lims(y=c(5, 10)) +
+  theme(legend.position="right", 
+    legend.background = element_rect(colour ="black"),
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) -> p2
+
+# --------------------------------------------------------------
+# Noise
+fig9 %>% 
+  filter(V_osc/V_comp < 3) %>% 
+  group_by(N, sigma) %>% 
+  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
+  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=10e-3*(sigma/10e-9) * 1e3/2, group=interaction(N, sigma))) +
+  geom_line(size=0.3, alpha=1) + 
+  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
+  labs(x=expression(V[o]/V[b]), y="Norm. error") +
+  scale_color_gradient(low="grey", high="orange") +
   theme_classic() +
@@
     legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p2
-
-fig2 %>% 
-  filter(freq <= 20) %>%
-  filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) + 
-  # labs(x=expression(V[o]/V[c]), y="Variance (ms)") +
-  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
-  lims(y=c(9,11)) +
-  theme_classic() +
-  theme(axis.line=element_blank(),
-      axis.text.x=element_blank(),
-      # axis.text.y=element_blank(),
-      axis.ticks.x=element_blank(),
-      axis.title.x=element_blank(),
-      axis.title.y=element_blank(),
-      legend.position="none",
-      panel.background=element_blank(),
-      panel.border=element_blank(),
-      panel.grid.major=element_blank(),
-      panel.grid.minor=element_blank(),
-      plot.background=element_blank()) -> p2.sub
-
-fig2 %>% 
-  filter(freq <= 20) %>%
-  filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o]/V[c]), y="Spike count") +
-  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
-  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
-  theme_classic() +
-  theme(legend.position="none", 
-    legend.key.size = unit(.3, "cm"),
-    legend.title = element_text(size=8),
     legend.text = element_text(size=8)) -> p3
 
-# ------------------------------------------
-# FAST
-fig2 %>% 
-  filter(freq >= 20) %>%
-  filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o]/V[c]), y="Avg. error (ms)") +
-  scale_color_gradient2(
-    low="gold", high="darkgreen", mid="darkgrey", 
-    midpoint=20, name="", breaks = c(20, 25, 30)) +
+fig9 %>% 
+  filter(V_osc/V_comp < 3) %>% 
+  group_by(N, sigma) %>% 
+  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
+  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=10e-3*(sigma/10e-9) * 1e3 /2, group=interaction(N, sigma))) +
+  geom_line(size=0.3, alpha=1) + 
+  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
+  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
+  scale_color_gradient(low="grey", high="orange", name="Noise (mV)") +
   theme_classic() +
-  geom_vline(xintercept = 1, alpha=0.5, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.3, color="black", linetype="dashed") +
-  scale_y_continuous(breaks=c(0, 4.0, 8.0, 12.0), limits=c(0, 12)) +
-  theme(legend.position="top", 
-    legend.key.size = unit(.3, "cm"),
+  # lims(y=c(5, 10)) +
+  theme(legend.position="right", 
+    legend.background = element_rect(colour ="black"),
+    legend.key.size = unit(.4, "cm"),
     legend.title = element_text(size=8),
@@
 
-fig2 %>% 
-  filter(freq >= 20) %>%
-  filter(V_osc/V_comp <= 3) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) + 
-  labs(x=expression(V[o]/V[c]), y="Pop. variance (ms)") +
-  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
-  scale_y_continuous(breaks=c(8.0, 10, 12.0), limits=c(8, 12)) +
+# --------------------------------------------------------------
+# Weight
+fig11 %>% 
+  filter(V_osc/V_comp < 3) %>% 
+  group_by(N, weight) %>% 
+  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
+  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=weight*1e9, group=interaction(N, weight))) +
+  geom_line(size=0.3, alpha=1) + 
+  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
+  labs(x=expression(V[o]/V[b]), y="Norm. error") +
+  scale_color_gradient2(
+    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9) +
   theme_classic() +
@@
 
-fig2 %>%
-  filter(freq >= 20) %>%
-  filter(V_osc/V_comp <= 3) %>%
-  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
-  geom_jitter(alpha=0.2, size=0.1) +
-  labs(x=expression(V[o]/V[c]), y="Spike count") +
-  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
-  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
+fig11 %>% 
+  filter(V_osc/V_comp < 3) %>% 
+  group_by(N, weight) %>% 
+  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
+  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=weight*1e9, group=interaction(N, weight))) +
+  geom_line(size=0.3, alpha=1) + 
+  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
+  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
+  scale_color_gradient2(
+    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9, name="Weight (nS)") +
   theme_classic() +
-  theme(legend.position="none",
-    legend.key.size = unit(.3, "cm"),
+  # lims(y=c(5, 10)) +
+  theme(legend.position="right", 
+    legend.background = element_rect(colour ="black"),
+    legend.key.size = unit(.4, "cm"),
     legend.title = element_text(size=8),
@@
 plot_grid <- rbind(
-  c(1, 4),
-  c(1, 4),
-  c(1, 4),
-  c(2, 5),
-  c(2, 5),
-  c(3, 6),
-  c(3, 6))
+  c(1, 1, 1, 2, 2, 2, 2, 2),
+  c(3, 3, 3, 4, 4, 4, 4, 4),
+  c(5, 5, 5, 6, 6, 6, 6, 6))
+
 grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=plot_grid)
-rm(p1, p2, p3, p4, p5, p6, plot_grid)
+rm(p1, p2, p3, p4, plot_grid)
+```
+## Heterocells
+```{r, fig.width=1.1, fig.height=1.5}
+fig12 %>%
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  filter(V_osc/V_comp <= 3) %>% 
+  mutate(norm_errors = errors/max(errors)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
+  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
+  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
+            aes(x=V_osc/V_comp, y=errors/max(errors)), 
+            color="black", size=0.8) +
+  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
+  theme_classic() +
+  lims(x=c(0, 3)) +
+  labs(x=expression(V[o]/V[b]), y="Norm. error") -> p1
+
+fig12 %>%
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  filter(V_osc/V_comp <= 3) %>% 
+  mutate(norm_variances = variances/max(variances)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_variances, group=N)) +
+  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
+  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
+            aes(x=V_osc/V_comp, y=variances/max(variances)), 
+            color="black", size=0.8) +
+  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
+  theme_classic() +
+  lims(x=c(0, 3)) +
+  labs(x=expression(V[o]/V[b]), y="Norm. variance") -> p2
+
+plot_grid <- rbind(
+  c(1),
+  c(2))
+
+grid.arrange(p1, p2, layout_matrix=plot_grid)
+rm(p1, p2, plot_grid)
 ```

### 2018-04-04 voltagebudget/analysis/paper_figures.Rmd
Figure update - added draft 1 hetero control

@@
     variances = mean(variances)) -> fig13
+
+# Load exmample timecourses for hetero
+fig14 <- read_csv("vm_hetero_timecourse.csv")
 
@@
 ## Heterocells
-```{r, fig.width=1.1, fig.height=1.5}
+
+```{r, fig.width=0.4, fig.height=1.2}
+fig14 %>% 
+  ggplot(aes(x=t, y=vm*1e3, group=cell)) +
+  geom_line(size=0.3, color="darkgrey") +
+  facet_grid(cell~.) +
+  theme_classic() +
+  labs(x="Time (s)", y="V (mV)") +
+  theme(
+    strip.text = element_blank(),
+    strip.background = element_blank(),
+    legend.position="none",
+    axis.line=element_blank(),
+    axis.text.x=element_blank(),
+    axis.text.y=element_blank(),
+    axis.ticks=element_blank(),
+    axis.title.x=element_blank(),
+    axis.title.y=element_blank(),
+    panel.background=element_blank(),
+    panel.border=element_blank(),
+    panel.grid.major=element_blank(),
+    panel.grid.minor=element_blank(),
+    plot.background=element_blank())
+```
+
+```{r, fig.width=0.9, fig.height=1.5}
 fig12 %>%

### 2018-04-04 voltagebudget/analysis/paper_figures.Rmd
Tweakf to opt PLC fig

@@
 
-```{r, fig.width=3, fig.height=1.4}
+```{r, fig.width=3, fig.height=1.6}
+min_t <- min(fig4$ts)
+
 fig4 %>% 
   filter(alg != "coincidence") %>% 
-  ggplot(aes(x=(ts - min(ts))*1e3, y=ns, color=set)) +
-  geom_point(size=0.7, alpha=1) +
+  group_by(set, alg) %>% 
+  mutate(ts = ts - min_t) -> tmp
+
+tmp %>% 
+  filter(set == "synchronized") %>%
+  ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
+  geom_point(size=1.6, alpha=.9, shape=4) +
+  geom_point(
+    data=filter(tmp, set == "initial"), 
+    mapping=aes(x=ts*1e3, y=ns), color="black", shape=16, alpha=0.7, size=0.5) +
   facet_grid(alg~.) +
-  scale_color_manual(values=c("black", "darkgrey"), name="") +
+  scale_color_brewer(palette = "Set1", guide=FALSE) +
   theme_classic() +
@@
   theme(
-    legend.position="top", 
-    legend.key.size = unit(.5, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8),
+    legend.position="none", 
     panel.grid.major = element_blank(),
@@
   filter(alg != "coincidence") %>%
-  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, linetype=alg)) +
-  geom_line(size=0.8, alpha=1, color="darkgrey") +
-  scale_linetype_manual(values=c("dashed", "solid", "dotted"), name="Algorithm") +
+  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
+  geom_line(size=0.8, alpha=0.8) +
+  scale_color_brewer(palette = "Set1", name="Algorithm:") +
   theme_classic() +
+  labs(x="Time (ms)", y="Neuron") +
+  theme(legend.position="top",
+    legend.key.size = unit(.5, "cm"),
+    legend.title = element_text(size=10),
+    legend.text = element_text(size=10),
+    legend.background = element_rect(colour ="black")) +
   labs(x="Error (ms)", y="Variance (ms)") -> p2
@@
 plot_grid <- rbind(
-  c(1, 1, 1, NA, NA, NA, NA),
+  # c(1, 1, 1, NA, NA, NA, NA),
   c(1, 1, 1, 2, 2, 2, 2),

### 2018-04-04 voltagebudget/analysis/paper_figures.Rmd
Fix typos in fig axes

@@
   geom_line(size=0.3, alpha=1) + 
-  labs(x=expression(V[o]/V[b]), y="Norm. error") +
+  labs(x=expression(V[o]/V[c]), y="Norm. error") +
   scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
@@
   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
+  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
   scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
@@
   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  labs(x=expression(V[o]/V[b]), y="Norm. error") +
+  labs(x=expression(V[o]/V[c]), y="Norm. error") +
   scale_color_gradient(low="grey", high="orange") +
@@
   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
+  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
   scale_color_gradient(low="grey", high="orange", name="Noise (mV)") +
@@
   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  labs(x=expression(V[o]/V[b]), y="Norm. error") +
+  labs(x=expression(V[o]/V[c]), y="Norm. error") +
   scale_color_gradient2(
@@
   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
+  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
   scale_color_gradient2(
@@
   lims(x=c(0, 3)) +
-  labs(x=expression(V[o]/V[b]), y="Norm. error") -> p1
+  labs(x=expression(V[o]/V[c]), y="Norm. error") -> p1
 
@@
   lims(x=c(0, 3)) +
-  labs(x=expression(V[o]/V[b]), y="Norm. variance") -> p2
+  labs(x=expression(V[o]/V[c]), y="Norm. variance") -> p2
 

### 2018-04-04 voltagebudget/analysis/paper_figures.Rmd
More tweaks to paper figs

@@
     V_comp_ref = mean(V_comp_ref), 
+    n_spikes_pop = mean(n_spikes), 
     errors = mean(errors), 
@@
   filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc/V_b, y=variances_pop*1e3, color=V_osc/V_b)) +
+  ggplot(aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3, color=V_osc/V_b)) +
   geom_point(size=0.05, alpha=1) + 
@@
   filter(freq == 20) %>% 
-  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=V_osc/V_b)) +
+  ggplot(aes(x=errors_pop*1e3, y=(variances_pop/n_spikes_pop)*1e3, color=V_osc/V_b)) +
   geom_point(size=0.05, alpha=.6) +
@@
   filter(V_free_initial > 0) %>%
-  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, group=N)) +
+  ggplot(aes(x=V_osc/V_comp, y=(variances/n_spikes)*1e3, group=N)) +
   geom_line(size=0.5, alpha=0.2, color="grey") + 
@@
   theme_classic() +
-  geom_line(data=filter(fig1, freq==20, V_osc/V_comp <= 3), 
-            aes(x=V_osc/V_comp, y=variances_pop*1e3), 
+  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
+            aes(x=V_osc/V_comp, y=(variances_pop/n_spikes_pop)*1e3), 
             color="black", size=0.7, alpha=1) +
@@
   filter(V_free_initial > 0) %>%
-  ggplot(aes(x=V_osc/V_b, y=variances*1e3, group=N)) +
+  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, group=N)) +
   geom_line(size=0.5, alpha=0.2, color="grey") + 
   theme_classic() +
-  geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3), 
+  geom_line(data=filter(fig2, freq == 20), aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3), 
             color="black", size=0.7, alpha=1) +
@@
   filter(V_free_initial > 0) %>%
-  ggplot(aes(x=V_osc/V_b, y=variances*1e3, group=N, color=factor(delta_spikes))) +
+  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, group=N, color=factor(delta_spikes))) +
   geom_line(size=0.4, alpha=0.6) + 
   scale_colour_brewer(
-    palette = "Reds", guide=guide_legend(title="Spike count", nrow=3)) +
+    palette = "Reds", guide=guide_legend(title="Spike\ncount", nrow=3)) +
   labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
-  theme_classic() + theme(legend.position="none") -> p2
-
-# -
-M = min(fig1$variances_pop)
-fig1 %>% 
-  filter(freq == 20) %>% 
-  group_by(N) %>%
-  mutate(V_free_initial = round(max(V_free), 3)) %>%
-  filter(V_free_initial > 0) %>%
-  ggplot(aes(x=variances*1e3, fill=factor(delta_spikes))) +
-  geom_density(alpha=0.6, size=0, color="black") +
-  scale_fill_brewer(palette = "Reds", name="Spike\ncount") +
-  geom_vline(xintercept = M*1e3, color="black", linetype="dotted") +
-  labs(x="Variance (ms)", y="Density (AU)") +
-  theme_classic() + 
-  theme(legend.position = c(1.25, 1.55), 
+  theme_classic() + theme(legend.position = c(1.25, 0.8), 
         legend.background = element_rect(colour ="black"),
@@
         legend.title = element_text(size=10),
-        legend.text = element_text(size=10)) -> p3
+        legend.text = element_text(size=10)) -> p2
 
@@
   labs(y=expression(V[o]/V[c]), x="Spike count") + 
-  coord_flip()  -> p4
+  coord_flip()  -> p3
+
+# -
+M = min(fig2$variances_pop/fig2$n_spikes_pop)
+fig1 %>% 
+  filter(freq==20) %>% 
+  mutate(quantile = ntile(V_osc, 10)) %>%
+  filter(quantile %in% c(1, 10)) %>% 
+  ggplot(aes(x=(variances/n_spikes)*1e3, fill=factor(quantile), group=quantile)) +
+  geom_density(alpha=0.6, size=0.2, color="black") +
+  geom_vline(xintercept = M*1e3, color="black") +
+  labs(x="Variance (ms)", y="Density (AU)") +
+  scale_fill_manual(
+    # values=c("#FFDED3", "#FD0D11"), 
+    values=c("grey", "black"),
+    name=expression("Deciles V"[o]), 
+    labels=c("0 - 10%", "90 - 100%")) +
+  theme_classic() +
+  theme(
+    legend.position="bottom", 
+    legend.key.size = unit(.3, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8) ) -> p4
+
+# fig1 %>% 
+#   filter(freq == 20) %>% 
+#   group_by(N) %>%
+#   mutate(V_free_initial = round(max(V_free), 3)) %>%
+#   filter(V_free_initial > 0) %>%
+#   ggplot(aes(x=(variances/n_spikes)*1e3, fill=factor(delta_spikes))) +
+#   geom_density(alpha=0.6, size=0, color="black") +
+#   scale_fill_brewer(palette = "Reds", name="Spike\ncount") +
+#   geom_vline(xintercept = M*1e3, color="black", linetype="dotted") +
+#   labs(x="Variance (ms)", y="Density (AU)") +
+#   theme_classic() + 
+#   theme(legend.position = c(1.25, 1.55), 
+#         legend.background = element_rect(colour ="black"),
+#         legend.key.size = unit(.5, "cm"),
+#         legend.title = element_text(size=10),
+#         legend.text = element_text(size=10)) -> p3
 
@@
   sample_n_groups(8) %>% 
-  ggplot(aes(x=V_osc/V_b, y=variances*1e3, color=factor(delta_spikes))) +
+  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, color=factor(delta_spikes))) +
   geom_point(size=1, alpha=1) +
   facet_wrap(~N, nrow=8) +
-  geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3),
-            color="black", size=0.7, alpha=1) +
+  # geom_line(aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3),
+  #           color="black", size=0.7, alpha=1) +
   scale_colour_brewer(palette = "Reds", name="Spike count") +
@@
   mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
-  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
+  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
   ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=freq, group=interaction(N, freq))) +
@@
   mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
-  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
+  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
   ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=freq, group=interaction(N, freq))) +
@@
   mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
-  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
+  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
   ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=10e-3*(sigma/10e-9) * 1e3 /2, group=interaction(N, sigma))) +
@@
   mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
-  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
+  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
   ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=weight*1e9, group=interaction(N, weight))) +
@@
             aes(x=V_osc/V_comp, y=errors/max(errors)), 
-            color="black", size=0.8) +
+            color="black", size=0.7) +
+  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
+            aes(x=V_osc/V_comp, y=errors/max(errors)), 
+            color="tan4", size=0.7, ) +
   geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
@@
   labs(x=expression(V[o]/V[c]), y="Norm. error") -> p1
+
+# fig1 %>% 
+#   group_by(N) %>% 
+#   filter(V_osc/V_comp <= 3) %>% 
+#   filter(freq == 20) %>% 
+#   group_by(N) %>%
+#   mutate(V_free_initial = round(max(V_free), 3)) %>%
+#   filter(V_free_initial > 0) %>%
+#   ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
+#   geom_line(size=0.5, alpha=0.2, color="grey") + 
+#   geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+#   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
+#   theme_classic() +
+#   geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
+#             aes(x=V_osc/V_comp, y=errors*1e3), 
+#             color="black", size=0.8) +
+#   labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1
 
@@
   mutate(norm_variances = variances/max(variances)) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=norm_variances, group=N)) +
+  ggplot(aes(x=V_osc/V_comp, y=norm_variances/n_spikes, group=N)) +
   geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
   geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
-            aes(x=V_osc/V_comp, y=variances/max(variances)), 
+            aes(x=V_osc/V_comp, y=(variances_pop/max(variances_pop))/n_spikes_pop), 
             color="black", size=0.8) +
+  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
+            aes(x=V_osc/V_comp, y=(variances_pop/max(variances_pop))/n_spikes_pop), 
+            color="tan4", size=0.7, ) +
   geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +

### 2018-04-04 voltagebudget/analysis/freq_analysis.Rmd
Cleanup freq analysis more

@@
     V_osc = mean(V_osc),
+    n_spikes = mean(n_spikes),
     delta_spikes = mean(delta_spikes),
@@
   geom_line(size=0.5, alpha=0.5) + 
+  labs(x="As (namp)", y="Deviation (ms)") +
+  theme_classic() +
+  scale_color_gradient(low="gold", high="darkgreen") +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8)) 
+```
+
+```{r, fig.width=1.2, fig.height=0.8}
+avg_results %>%
+  filter(As < 0.05e-9) %>% 
+  filter(freq <= 30) %>% 
+  ggplot(aes(x=As*1e9, y=(variances_pop/n_spikes)*1e3, color=freq, group=interaction(N, freq))) +
+  geom_line(size=0.5, alpha=0.5) + 
   labs(x="As (namp)", y="Variance (ms)") +
@@
   geom_line(size=0.3, alpha=1) + 
+  labs(x="V_osc/V_comp", y="Deviance (ms)") +
+  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
+  theme_classic() +
+  lims(y=c(5, 10)) +
+  theme(legend.position="right", 
+    legend.key.size = unit(.4, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8))
+```
+
+```{r, fig.width=1.2, fig.height=0.8}
+avg_results %>% 
+  filter(V_osc/V_comp < 3) %>% 
+  filter(freq <= 30) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=(variances_pop/n_spikes)*1e3, color=freq, group=interaction(N, freq))) +
+  geom_line(size=0.3, alpha=1) + 
   labs(x="V_osc/V_comp", y="Variance (ms)") +
@@
   theme_classic() +
-  lims(y=c(5, 10)) +
+  # lims(y=c(5, 10)) +
   theme(legend.position="right", 

### 2018-04-04 voltagebudget/exp/sweep_A.py
Exposed `n_cycles` in sweep_A

@@ -42,6 +42,7 @@ def sweep_A(name,
             T=0.0625,
             f=8,
             N=10,
+            n_cycles=2,
             mode='regular',
             sigma=0,
             w_in_0=None,
@@ -176,7 +177,7 @@ def sweep_A(name,
             A=A_i,
             phi=phi_E,
             E=E,
-            n_cycles=2,
+            n_cycles=n_cycles,
             sigma=sigma,
             budget=True,
             seed_value=seed_value,

### 2018-04-06 voltagebudget/analysis/paper_figures.Rmd
Update Fig 3

@@
   ggplot(aes(x=errors_pop*1e3, y=(variances_pop/n_spikes_pop)*1e3, color=V_osc/V_b)) +
-  geom_point(size=0.05, alpha=.6) +
+  geom_point(size=0.2, alpha=.6) +
   scale_color_gradient(low="darkgrey", high="red", name=expression(V[o]/V[b])) +
@@
   c(NA),
-  c(1, 2),
-  c(1, 2),
-  c(3, 3),
-  c(3, 3),
   c(3, 3))
 
-grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+grid.arrange(p3, layout_matrix=plot_grid)
 rm(p1, p2, p3, plot_grid)
@@
   ggplot(aes(x=t, y=vm*1e3, group=cell)) +
-  geom_line(size=0.3, color="darkgrey") +
+  geom_line(size=0.2, color="black") +
   facet_grid(cell~.) +

### 2018-04-06 voltagebudget/analysis/paper_figures.Rmd
Update fig3

@@
   # scale_color_gradient(low="darkgrey", high="red", name="A (namp)") +
-  geom_smooth(color="red", method=lm, alpha=0.2, size=.15, se=FALSE, linetype='solid') +
+  # geom_smooth(color="red", method=lm, alpha=0.2, size=.15, se=FALSE, linetype='solid') +
   labs(x="Avg. error (ms)", y="Pop. variance (ms)") +

### 2018-04-06 voltagebudget/analysis/fixed_run_time_analysis.Rmd
Added fixed_time analysis Rmb

---
title: "Sweep A - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

# Load and process

```{r, message=FALSE}
results <- NULL

# --------------------------"
exp <- "102"
freqs <- c(10, 20, 30)
run_times <-  c("0.25", "0.5", "1", "1.5", "2", "2.5", "3.0")
for(freq in freqs){
  for(t in run_times) {
    # exp102_f10_t1.5.csv
    name <- paste("../data/exp", exp, "_f", freq, "_t", t, ".csv", sep="")
    df <- read_csv(paste(name, sep=","))
    df %>%
      filter(n_spikes > 0) -> df

    df$freq <- rep(as.numeric(freq), nrow(df))
    df$run_time <- rep(as.numeric(t), nrow(df))
    results <- rbind(results, df)  
  }
}

# --------------------------
# Process
results %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results

# --------------------------
# Est avg pop responses
results %>% 
  group_by(freq, run_time) %>% 
  summarise(
    N = 0,
    V_b = mean(V_b),
    V_osc = mean(V_osc),
    n_spikes = mean(n_spikes),
    n_spikes_pop = mean(n_spikes_pop),
    delta_spikes = mean(delta_spikes),
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    V_comp = mean(V_comp), 
    errors = mean(errors), 
    variances_pop = mean(variances_pop),
    variances = mean(variances)) -> avg_results

rm(df, exp, freq, freqs, t, run_times, name)
```

# Population

```{r, fig.width=1.5, fig.height=0.7}
avg_results %>%
  ggplot(aes(x=run_time, y=(variances_pop/n_spikes_pop)*1e3, color=freq, group=interaction(freq, run_time))) +
  geom_point(size=1, alpha=0.8) +
  labs(x="Run time (s)", y="Variance (ms)") +
  theme_classic() +
  facet_grid(.~freq) +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank()) 
```

# Individual cells
## Error

```{r, fig.width=1.5, fig.height=0.7}
results %>%
  ggplot(aes(x=run_time, y=(errors/n_spikes)*1e3, color=freq, group=interaction(freq, run_time))) +
  # geom_point(size=0.05, alpha=0.2) + 
  geom_boxplot(outlier.size = NA) +
  labs(x="Run time (s)", y="Variance (ms)") +
  theme_classic() +
  facet_grid(.~freq) +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank()) 
```

## Var

```{r, fig.width=1.5, fig.height=0.7}
results %>%
  ggplot(aes(x=run_time, y=(variances/n_spikes)*1e3, color=freq, group=interaction(freq, run_time))) +
  # geom_point(size=0.05, alpha=0.2) + 
  geom_boxplot(outlier.size = NA) +
  labs(x="Run time (s)", y="Variance (ms)") +
  theme_classic() +
  facet_grid(.~freq) +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank()) 
```

### 2018-04-07 voltagebudget/analysis/paper_figures.Rmd
Figure simplification after v2 BV comments

@@
   geom_ribbon(fill="red", alpha=0.5) +
-  geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
+  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.2) +
   geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.5) +
@@
 
-```{r, fig.width=1.5, fig.height=1.3}
+```{r, fig.width=1.5, fig.height=0.7}
+t_on = 0.23852
+t_off = t_on + 2e-3
+
+v_min = -68e-3
+v_max = -50e-3
+box_buffer = .5e-3
+
 fig0 %>% 
-  filter(t > 0.15, t < 0.35) %>%
-  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=vm*1e3)) +
-  geom_ribbon(fill="blue", alpha=0.5) +
-  geom_hline(yintercept=-50e-3*1e3, color="black", linetype="dotted", size=0.5) +
-  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
-  labs(x="", y=expression(V[m] (mvolt))) +
+  filter(t > 0.1, t < 0.29) %>%
+  # ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=vm*1e3)) +
+  # geom_ribbon(fill="blue", alpha=0.5) +
+  ggplot(aes(x=t, y=vm*1e3)) +
+  geom_line(color="black", alpha=1, size=.2) +
+  geom_hline(yintercept=v_max*1e3, color="black", linetype="dotted", size=0.5) +
+  geom_hline(yintercept=v_min*1e3, color="black", linetype="dotted", size=0.5) +
+ geom_rect(
+    aes(
+      xmin=t_on, 
+      xmax=t_off, 
+      ymin=(v_min - box_buffer)*1e3, 
+      ymax=(v_max + box_buffer)*1e3),  
+    fill="grey", color=NA, alpha=0.01, size=.01) +
+  labs(x="Time (s)", y=expression(V[m] (mvolt))) +
+  scale_x_continuous(breaks=c(0, 0.1, 0.2, 0.3), limits = c(0.1, 0.3)) +
   theme_classic() -> p1
@@
 fig0 %>% 
-  filter(t > 0.15, t < 0.35) %>%
-  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
+  filter(t > t_on, t < t_off) %>%
+  ggplot(aes(x=t, ymin=v_min*1e3, ymax=osc*1e3)) +
   geom_ribbon(fill="red", alpha=0.5) +
@@
   geom_hline(yintercept=-50e-3*1e3, color="black", linetype="dotted", size=0.5) +
-  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
-  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3*1e3, ymax=-50e-3*1e3),  fill=NA, color="black", alpha=0.01, size=.2) +
-  # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
-  # geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), color="grey", alpha=0.5) +
-  # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
-  labs(x="Time (s)", y="") +
-  theme_classic() -> p2
-
-fig0 %>% 
-  filter(t > 0.23652 - 8e-3, t < 0.23652 + 2e-3 + 0.03333333 + 8e-3) %>%
-  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
-  geom_ribbon(fill="red", alpha=0.5) +
-  geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
-  # geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
-  # geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
-  geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3*1e3, ymax=-50e-3*1e3), fill="grey", alpha=0.01) +
-  geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3*1e3, ymax=-50e-3*1e3),  fill="grey", alpha=0.01) +
-  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3*1e3, ymax=-50e-3*1e3),  fill=NA, color="black", alpha=0.01, size=.2) +
+  geom_hline(yintercept=v_min*1e3, color="black", linetype="dotted", size=0.5) +
+  geom_rect(
+    aes(
+      xmin=t_on, 
+      xmax=t_off, 
+      ymin=(v_min - box_buffer)*1e3, 
+      ymax=(v_max + box_buffer)*1e3),  
+    fill=NA, color="grey", alpha=0.01, size=.6) +
   labs(x="", y="") +
@@
       panel.grid.minor=element_blank(),
-      plot.background=element_blank()) -> p3
-
-plot_grid <- rbind(c(1 , 1, NA), c(2, 2, 3))
-grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
-rm(p1, p2, p3, plot_grid)
+      plot.background=element_blank()) -> p2
+
+plot_grid <- rbind(c(1 , 1, 1, 1,1, 1, 1, NA, 2, 2, 2))
+grid.arrange(p1, p2, layout_matrix=plot_grid)
+rm(p1, p2, plot_grid)
+
+# fig0 %>% 
+#   filter(t > 0.15, t < 0.35) %>%
+#   ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
+#   geom_ribbon(fill="red", alpha=0.5) +
+#   geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
+#   geom_hline(yintercept=-50e-3*1e3, color="black", linetype="dotted", size=0.5) +
+#   geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
+#   geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3*1e3, ymax=-50e-3*1e3),  fill=NA, color="black", alpha=0.01, size=.2) +
+#   # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
+#   # geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), color="grey", alpha=0.5) +
+#   # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
+#   labs(x="Time (s)", y="") +
+#   theme_classic() -> p2
 ```
 
-```{r, fig.width=1, fig.height=0.8}
-fig1 %>%
-  filter(rank == 0, freq == 20) %>%
-  ggplot(aes(x=As*1e9, y=V_osc*1e3)) +
-  geom_point(size=0.1, alpha=0.6, color="black") +
-  labs(x="A (namp)", y=expression(V[o] (mvolt))) +
-  theme_classic() 
-```
 # Trade-off

### 2018-04-25 voltagebudget/analysis/paper_figures.Rmd
Update paper figs Rmd

@@
 rm(df, exp, freq, freqs, name, ref, n, sigmas, sigma, exps, alg_names, algs)
-```
-
-# Shift-add cartoon
-
-```{r, fig.width=1.2, fig.height=0.5}
-t_start <- 0.2
-t_stop <- 0.3
-
-fig6 %>% 
-  filter(t > t_start, t < t_stop) %>%
-  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
-  geom_ribbon(fill="red", alpha=0.5) +
-  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.2) +
-  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.5) +
-  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
-  labs(x="", y="") +
-  theme_classic() +
-  theme(axis.line=element_blank(),
-      axis.text.x=element_blank(),
-      axis.text.y=element_blank(),
-      axis.ticks=element_blank(),
-      # axis.title.x=element_blank(),
-      # axis.title.y=element_blank(),
-      legend.position="none",
-      panel.background=element_blank(),
-      panel.border=element_blank(),
-      panel.grid.major=element_blank(),
-      panel.grid.minor=element_blank(),
-      plot.background=element_blank()) -> p1
-
-fig7 %>% 
-  filter(t > t_start, t < t_stop) %>%
-  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
-  geom_ribbon(fill="red", alpha=0.5) +
-  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.2) +
-  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.5) +
-  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
-  labs(x="", y="") +
-  theme_classic() +
-  theme(axis.line=element_blank(),
-      axis.text.x=element_blank(),
-      axis.text.y=element_blank(),
-      axis.ticks=element_blank(),
-      # axis.title.x=element_blank(),
-      # axis.title.y=element_blank(),
-      legend.position="none",
-      panel.background=element_blank(),
-      panel.border=element_blank(),
-      panel.grid.major=element_blank(),
-      panel.grid.minor=element_blank(),
-      plot.background=element_blank()) -> p2
-
-plot_grid <- rbind(c(1, 1, 1, 2, 2, 2))
-grid.arrange(p1, p2, layout_matrix=plot_grid)
-rm(p1, p2, plot_grid)
 ```
@@
 
-# Bound 1 - V_osc/V_comp (f = 20)
+# V_o/V_c
 
 ```{r, fig.width=2.7, fig.height=2.2}
+
 fig1 %>% 
@@
   labs(x=expression(V[o]/V[c]), y="Variance (ms)") -> p2
+
+# # Norm error here
+# fig1 %>% 
+# filter(V_osc/V_comp < 3) %>% 
+#   filter(freq == 20) %>% 
+#   group_by(N, freq) %>% 
+#   mutate(norm_errors = errors/max(errors)) -> tmp1
+# 
+# tmp1 %>% 
+#   group_by(As) %>% 
+#   summarise(
+#     N = 0,
+#     norm_errors = mean(norm_errors),
+#     V_b = mean(V_b), 
+#     V_osc = mean(V_osc), 
+#     V_comp = mean(V_comp)) -> tmp2
+# 
+# tmp1 %>% 
+#   group_by(N) %>% 
+#   filter(V_osc/V_comp <= 3) %>% 
+#   filter(freq == 20) %>%
+#   group_by(N) %>%
+#   mutate(V_free_initial = round(max(V_free), 3)) %>%
+#   filter(V_free_initial > 0) %>%
+#   ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
+#   geom_line(size=0.5, alpha=0.2, color="grey") + 
+#   geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
+#   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
+#   theme_classic() +
+#   geom_line(data=tmp2, 
+#             aes(x=V_osc/V_comp, y=norm_errors), 
+#             color="black", size=0.8) +
+#   labs(x=expression(V[o]/V[c]), y="Norm. error") -> p2
 
@@
 
-# Bound 2 - n_spikes < (0, 1)
-
-```{r, fig.width=2.6, fig.height=3.2}
+$ V_o and variance
+
+```{r, fig.width=2.8, fig.height=3.2}
 max_N <- max(fig1$N)
-
-fig1 %>% 
-  filter(freq == 20) %>% 
-  group_by(N) %>%
-  mutate(V_free_initial = round(max(V_free), 3)) %>%
-  filter(V_free_initial > 0) %>%
-  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, group=N)) +
-  geom_line(size=0.5, alpha=0.2, color="grey") + 
-  theme_classic() +
-  geom_line(data=filter(fig2, freq == 20), aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3), 
-            color="black", size=0.7, alpha=1) +
-  labs(x=expression(V[o]/V[b]), y="Variance (ms)") -> p1
 
@@
   labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
-  theme_classic() + theme(legend.position = c(1.25, 0.8), 
+  theme_classic() + theme(legend.position = c(1.25, -0.8), 
         legend.background = element_rect(colour ="black"),
@@
         legend.title = element_text(size=10),
-        legend.text = element_text(size=10)) -> p2
+        legend.text = element_text(size=10)) -> p1
 
@@
   labs(y=expression(V[o]/V[c]), x="Spike count") + 
-  coord_flip()  -> p3
+  coord_flip()  -> p2
 
@@
     legend.title = element_text(size=8),
-    legend.text = element_text(size=8) ) -> p4
+    legend.text = element_text(size=8) ) -> p3
 
@@
     # panel.grid.minor=element_blank(),
-    plot.background=element_blank()) -> p5
+    plot.background=element_blank()) -> p4
 
@@
     # panel.grid.minor=element_blank(),
+    plot.background=element_blank()) -> p5
+
+# Shift-add cartoon
+t_start <- 0.2
+t_stop <- 0.3
+
+fig6 %>% 
+  filter(t > t_start, t < t_stop) %>%
+  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
+  geom_ribbon(fill="red", alpha=0.5) +
+  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.3) +
+  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.6) +
+  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.6) +
+  labs(x="", y="") +
+  theme_classic() +
+  theme(axis.line=element_blank(),
+      axis.text.x=element_blank(),
+      axis.text.y=element_blank(),
+      axis.ticks=element_blank(),
+      # axis.title.x=element_blank(),
+      # axis.title.y=element_blank(),
+      legend.position="none",
+      panel.background=element_blank(),
+      panel.border=element_blank(),
+      panel.grid.major=element_blank(),
+      panel.grid.minor=element_blank(),
       plot.background=element_blank()) -> p6
 
+fig7 %>% 
+  filter(t > t_start, t < t_stop) %>%
+  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
+  geom_ribbon(fill="red", alpha=0.5) +
+  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.3) +
+  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.6) +
+  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.6) +
+  labs(x="", y="") +
+  theme_classic() +
+  theme(axis.line=element_blank(),
+      axis.text.x=element_blank(),
+      axis.text.y=element_blank(),
+      axis.ticks=element_blank(),
+      # axis.title.x=element_blank(),
+      # axis.title.y=element_blank(),
+      legend.position="none",
+      panel.background=element_blank(),
+      panel.border=element_blank(),
+      panel.grid.major=element_blank(),
+      panel.grid.minor=element_blank(),
+      plot.background=element_blank()) -> p7
+
 plot_grid <- rbind(
-  c(1, 1, 1, NA, 5, 5, 6, 6),
-  c(1, 1, 1, NA, 5, 5, 6, 6),
-  c(1, 1, 1, NA, 5, 5, 6, 6),
-  c(2, 2, 2, NA, 5, 5, 6, 6),
-  c(2, 2, 2, NA, 5, 5, 6, 6),
-  c(2, 2, 2, NA, 5, 5, 6, 6),
-  c(3, 3, 3, NA, 5, 5, 6, 6),
-  c(3, 3, 3, NA, 5, 5, 6, 6),
-  c(3, 3, 3, NA, 5, 5, 6, 6),
-  c(4, 4, 4, NA, NA, NA, NA, NA),
-  c(4, 4, 4, NA, NA, NA, NA, NA),
-  c(4, 4, 4, NA, NA, NA, NA, NA))
-
-grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=plot_grid)
+  c(1, 1, 1, NA, 4, 4, 5, 5),
+  c(1, 1, 1, NA, 4, 4, 5, 5),
+  c(1, 1, 1, NA, 4, 4, 5, 5),
+  c(2, 2, 2, NA, 4, 4, 5, 5),
+  c(2, 2, 2, NA, 4, 4, 5, 5),
+  c(2, 2, 2, NA, 4, 4, 5, 5),
+  c(3, 3, 3, NA, 4, 4, 5, 5),
+  c(3, 3, 3, NA, NA, NA, NA, NA),
+  c(3, 3, 3, NA, 6, 6, 7, 7),
+  c(NA, NA, NA, NA, 6, 6, 7, 7))
+
+  # c(3, 3, 3, NA, 4, 4, 5, 5))
+  # c(3, 3, 3, NA, NA, NA, NA, NA))
+  # c(3, 3, 3, NA, NA, NA, NA, NA))
+
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix=plot_grid)
 rm(p1, p2, p3, p4, plot_grid, max_N, M)
@@
             aes(x=V_osc/V_comp, y=errors/max(errors)), 
-            color="tan4", size=0.7, ) +
+            color="black", size=0.7, linetype="dotdash") +
   geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
@@
             aes(x=V_osc/V_comp, y=(variances_pop/max(variances_pop))/n_spikes_pop), 
-            color="tan4", size=0.7, ) +
+            color="black", size=0.7, linetype="dotdash") +
   geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
@@
 fig4 %>% 
-  filter(alg != "coincidence") %>% 
+  filter(alg != "coincidence", alg != "left") %>% 
   group_by(set, alg) %>% 
@@
     legend.position="none", 
+    panel.border = element_rect(fill = NA, colour = "black"),
     panel.grid.major = element_blank(),
@@
 fig3 %>% 
-  filter(alg != "coincidence") %>%
+  filter(alg != "coincidence", alg != "left") %>%
   ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
@@
   labs(x="Time (ms)", y="Neuron") +
-  theme(legend.position="top",
+  theme(legend.position="bottom",
     legend.key.size = unit(.5, "cm"),
@@
   c(1, 1, 1, 2, 2, 2, 2),
-  c(1, 1, 1, 2, 2, 2, 2))
+  c(1, 1, 1, 2, 2, 2, 2),
+  c(1, 1, 1, 2, 2, 2, 2),
+    c(NA, NA, NA, 2, 2, 2, 2))
+  # c(1, 1, 1, 2, 2, 2, 2),
+  # c(NA, NA, NA, 2, 2, 2, 2))
 

### 2018-12-02 voltagebudget/analysis/fixed_run_time_analysis.Rmd
Update figs

@@
 
-```{r, fig.width=1.5, fig.height=0.7}
+```{r, fig.width=1.5, fig.height=0.9}
 avg_results %>%
   ggplot(aes(x=run_time, y=(variances_pop/n_spikes_pop)*1e3, color=freq, group=interaction(freq, run_time))) +
-  geom_point(size=1, alpha=0.8) +
-  labs(x="Run time (s)", y="Variance (ms)") +
+  geom_point(size=0.3, alpha=0.9) +
+  labs(x="Run time (s)", y="Avg. variance (ms)") +
   theme_classic() +
-  facet_grid(.~freq) +
   scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
@@
 # Individual cells
-## Error
 
-```{r, fig.width=1.5, fig.height=0.7}
+```{r, fig.width=2.5, fig.height=2.7}
 results %>%
-  ggplot(aes(x=run_time, y=(errors/n_spikes)*1e3, color=freq, group=interaction(freq, run_time))) +
-  # geom_point(size=0.05, alpha=0.2) + 
+  filter(As < 0.05e-9) %>% 
+  ggplot(aes(x=As, y=(variances/n_spikes)*1e3, color=run_time, group=interaction(As, run_time))) +
+  # geom_point(size=0.05, alpha=0.1) +
   geom_boxplot(outlier.size = NA) +
-  labs(x="Run time (s)", y="Variance (ms)") +
+  labs(x="A (namp)", y="Variance (ms)") +
   theme_classic() +
-  facet_grid(.~freq) +
-  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
-  theme(legend.position="right", 
+  facet_grid(freq~.) +
+  scale_color_gradient(low="blue", high="darkgreen") +
+  lims(y=c(0, 20)) +
+  theme(legend.position="bottom", 
     legend.key.size = unit(.4, "cm"),
@@
 ```
-
-## Var
-
-```{r, fig.width=1.5, fig.height=0.7}
-results %>%
-  ggplot(aes(x=run_time, y=(variances/n_spikes)*1e3, color=freq, group=interaction(freq, run_time))) +
-  # geom_point(size=0.05, alpha=0.2) + 
-  geom_boxplot(outlier.size = NA) +
-  labs(x="Run time (s)", y="Variance (ms)") +
-  theme_classic() +
-  facet_grid(.~freq) +
-  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
-  theme(legend.position="right", 
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8),
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    strip.background = element_blank(),
-    strip.text.x = element_blank()) 
-```

### 2018-12-02 voltagebudget/analysis/paper_figures.Rmd
Update figs

@@
 ---
-title: "Exp1 - Opt w_max and {A,phi)"
+title: "Paper figures"
 output: html_notebook
@@
 
-```{r, fig.width=3, fig.height=1.6}
+```{r, fig.width=1.2, fig.height=2}
 min_t <- min(fig4$ts)
@@
   theme(legend.position="bottom",
-    legend.key.size = unit(.5, "cm"),
+    legend.key.size = unit(.2, "cm"),
     legend.title = element_text(size=10),
@@
 plot_grid <- rbind(
-  # c(1, 1, 1, NA, NA, NA, NA),
-  c(1, 1, 1, 2, 2, 2, 2),
-  c(1, 1, 1, 2, 2, 2, 2),
-  c(1, 1, 1, 2, 2, 2, 2),
-  c(1, 1, 1, 2, 2, 2, 2),
-    c(NA, NA, NA, 2, 2, 2, 2))
-  # c(1, 1, 1, 2, 2, 2, 2),
-  # c(NA, NA, NA, 2, 2, 2, 2))
+  c(1),
+  c(1),
+  c(2),
+  c(2),
+  c(2))
 

### 2019-03-27 voltagebudget/exp/sweep_A.py
Cleanup

@@ -507,17 +507,12 @@ def optimal_sweep_A(name,
         # Filter spikes in E
         ns_i, ts_i = filter_spikes(ns_i, ts_i, (E, E + T))
 
-        # Pop var and error
+        # Pop var and error by oscillation
         var_pop = mad(ts_i)
         _, error_pop = score_by_n(N, ns_ref, ts_ref, ns_i, ts_i)
         n_spikes = ts_i.size
 
-        # Best possible pop error
-        # if (var_pop - var_ref) > 0:
-        #     ts_opt = -9999999
-        #     error_opt = -9999999
-        #     var_opt = -9999999
-        # else:
+        # Pop var and error by oscillation by optimal method
         _, _, var_opt, ts_opt = max_deviant(
             ts_ref, var_ref, var_pop, side='both', mode_fm=np.median, dt=dt)
         _, error_opt = score_by_n(N, ns_ref, ts_ref, ns_ref, ts_opt)
@@ -531,7 +526,7 @@ def optimal_sweep_A(name,
         errors_opt.append(error_opt)
         n_spikes_pop.append(n_spikes)
         phis.append(phi_E)
-        
+
         # -
         if verbose:
             print(

### 2019-03-27 voltagebudget/analysis/optimal_sweep_A_analysis.Rmd
Added opt_sweep_A notebook

---
title: "Optimal coordination - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(magrittr)
library(readr)
library(dplyr)
library(gridExtra)
library(readr)
library(scales)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

# Load and process

```{r, message=FALSE}
# Data
exp <- "103"
freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")

results <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  # df %>%
    # filter(n_spikes_pop > 0) -> df

  df$freq <- rep(freq, nrow(df))
  results <- rbind(results, df)
}

results$freq <- factor(results$freq, levels=freqs)
rm(df, exp, freq, freqs, name)
```

```{r, fig.width=1, fig.height=3}
ms <- 1e3
results %>% 
  filter(errors_pop > 0) %>% 
  ggplot(aes(x=errors_pop*ms, y=variances_pop*ms)) +
  geom_line(size=0.5) + 
  geom_line(mapping=aes(x=errors_opt*ms, y=variances_opt*ms), color="#e41a1c", alpha=0.8, size=.5) +
  scale_x_continuous(trans='log10') +
  annotation_logticks(sides = "b") +
  facet_grid(freq~.) +
  labs(x="Pop. error (ms)", y="Pop. variance (ms)") +
  theme_classic() +
  theme(strip.text.y = element_text(angle = 0), 
        panel.grid.minor = element_blank(),
         strip.background = element_blank())
```

### 2019-04-23 voltagebudget/exp/sweep_A.py
Add flag to opt_sweep_A to choose alt opt schemes

@@ -28,6 +28,7 @@ from voltagebudget.util import score_by_n
 from voltagebudget.util import find_E
 from voltagebudget.util import find_phis
 from voltagebudget.plc import max_deviant
+from voltagebudget.plc import uniform
 
 
 def sweep_A(name,
@@ -371,6 +372,7 @@ def optimal_sweep_A(name,
                     N=10,
                     n_cycles=2,
                     mode='regular',
+                    optimal_method='max_deviant',
                     sigma=0,
                     dt=0.01e-3,
                     w_in_0=None,
@@ -513,8 +515,20 @@ def optimal_sweep_A(name,
         n_spikes = ts_i.size
 
         # Pop var and error by oscillation by optimal method
-        _, _, var_opt, ts_opt = max_deviant(
-            ts_ref, var_ref, var_pop, side='both', mode_fm=np.median, dt=dt)
+        if optimal_method == 'max_deviant':
+            _, _, var_opt, ts_opt = max_deviant(
+                ts_ref,
+                var_ref,
+                var_pop,
+                side='both',
+                mode_fm=np.median,
+                dt=dt)
+        elif optimal_method == 'uniform':
+            _, _, var_opt, ts_opt = uniform(ts_ref, var_ref, var_pop)
+        else:
+            raise ValueError("Otimmal method not known")
+
+        # Est error for opt
         _, error_opt = score_by_n(N, ns_ref, ts_ref, ns_ref, ts_opt)
 
         # -

### 2019-04-23 voltagebudget/plc.py

@@ -14,6 +14,10 @@ from voltagebudget.util import mad
 
 
 def uniform(ts, initial, target):
+    """Shift each spike time a uniform amount
+
+    This is the min. max. or optimal policy for individual neuron errors"""
+
     # Init
     ts = np.asarray(ts)
     if ts.size == 0:
@@ -34,9 +38,9 @@ def uniform(ts, initial, target):
         ts_opt.append(t)
     ts_opt = np.asarray(ts_opt)
 
-    obs = mad(ts_opt)
+    adjusted = mad(ts_opt)
 
-    return initial, target, obs, ts_opt
+    return initial, target, adjusted, ts_opt
 
 
 def _delta(ts):
@@ -56,7 +60,10 @@ def _diffs(ts):
 
 
 def coincidence(ts, initial, target):
-    """Coordinate by increasing coincidences"""
+    """Coordinate by increasing coincidences.
+    
+    An approach inspired by neural oscillations.
+    """
 
     # Init
     ts = np.asarray(ts)
@@ -92,6 +99,11 @@ def max_deviant(ts,
                 mode_fm=np.mean,
                 dt=0.01e-3,
                 max_iterations=250000):
+    """Coordinate by adjusting the max variance neurons
+
+    This is the optimal policy for the network as a whole.
+    """
+
     # Init
     ts = np.asarray(ts)
     if ts.size == 0:

### 2019-04-23 voltagebudget/analysis/paper_figures.Rmd
Docs. Tweak Fig7/8

@@
 ```{r, message=FALSE}
-library(tidyverse)
+library(dplyr)
+library(ggplot2)
+library(reshape2)
+library(readr)
 library(gridExtra)
@@
 
+__NOTE__: to generate the needed 'vm_*.csv' files (which are voltage timecourses used in various figs) you have to 'run all' cells in the following:
+ 1. `../ipynb/figures_shit_add.ipynb`
+ 2. `../ipynb/figures_heterogenous.ipynb`
+ 3. `../ipynb/figures_SFN.ipynb`
+
 ```{r, message=FALSE}
@@
 for(freq in freqs){
-  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
+  name <- paste("../../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
   df <- read_csv(paste(name, sep=","))
@@
 for (n in 1:4){
-  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], ".csv", sep=""))
+  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], ".csv", sep=""))
   df$alg <- rep(alg_names[n], nrow(df))
@@
 # Load ref spikes
-ref <- read_csv("../data/stim1.csv")
+ref <- read_csv("../../data/stim1.csv")
 ref$set <- rep("initial", nrow(ref))
@@
 for (n in 1:4){
-  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], "_c0.1_spikes.csv", sep=""))
+  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_c0.1_spikes.csv", sep=""))
   df$set <- rep("synchronized", nrow(df))
@@
 for(sigma in sigmas){
-  name <- paste("../data/exp", exp, "_sigma", sigma, ".csv", sep="")
+  name <- paste("../../data/exp", exp, "_sigma", sigma, ".csv", sep="")
   df <- read_csv(paste(name, sep=","))
@@
 exp <- "96"
-name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
 df <- read_csv(paste(name, sep=","))
@@
 exp <- "100"
-name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
 df <- read_csv(paste(name, sep=","))
@@
 exp <- "99"
-name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
 df <- read_csv(paste(name, sep=","))
@@
 exp <- "101"
-name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
 df <- read_csv(paste(name, sep=","))
@@
 fig14 <- read_csv("vm_hetero_timecourse.csv")
+
+# -------------------------------------------------------------------
+# Optimal versus oscillation
+
+# Data
+exp <- "104"
+freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")
+
+fig15 <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  # df %>%
+    # filter(n_spikes_pop > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  fig15 <- rbind(fig15, df)
+}
+
+fig15$freq <- factor(fig15$freq, levels=freqs)
 
@@
 
-# Optimal
-
-```{r, fig.width=1.2, fig.height=2}
+# Optimal derivation
+
+```{r, fig.width=1.3, fig.height=2}
 min_t <- min(fig4$ts)
@@
   ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
-  geom_point(size=1.6, alpha=.9, shape=4) +
+  geom_point(size=1.4, alpha=.8, shape=4) +
   geom_point(
     data=filter(tmp, set == "initial"),
-    mapping=aes(x=ts*1e3, y=ns), color="black", shape=16, alpha=0.7, size=0.5) +
+    mapping=aes(x=ts*1e3, y=ns), color="black", shape=1, alpha=0.5, size=1.35) +
   facet_grid(alg~.) +
@@
 plot_grid <- rbind(
-  c(1),
-  c(1),
-  c(2),
-  c(2),
-  c(2))
+  c(1, 1),
+  c(1, 1),
+  c(2, 2),
+  c(2, 2),
+  c(2, 2))
 
@@
 ```
+
+# Optimal versus oscillation
+
+```{r, fig.width=1.2, fig.height=1}
+ms <- 1e3
+fig15 %>% 
+  filter(errors_pop > 0, freq == "8") %>% 
+  ggplot(aes(x=errors_pop*ms, y=variances_pop*ms)) +
+  geom_point(size=0.2, alpha=0.8) + 
+  geom_point(mapping=aes(x=errors_opt*ms, y=variances_opt*ms), color="#e41a1c", alpha=0.6, size=.2) +
+  scale_x_continuous(trans='log10') +
+  annotation_logticks(sides = "b") +
+  labs(x="Pop. error (ms)", y="Pop. variance (ms)") +
+  theme_classic() +
+  theme(strip.text.y = element_text(angle = 0), 
+        panel.grid.minor = element_blank(),
+         strip.background = element_blank())
+
+rm(ms)
+```

### 2019-04-23 voltagebudget/analysis/optimal_sweep_A_analysis.Rmd
WIP

@@
 # Data
-exp <- "103"
+exp <- "104"
 freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")
@@
 results <- NULL
+N <- 0
 for(freq in freqs){
@@
   df$freq <- rep(freq, nrow(df))
+  df$N <- rep(N, nrow(df))
+  N <- N + 1
+  df$i <- 1:nrow(df)
   results <- rbind(results, df)
@@
 
-```{r, fig.width=1, fig.height=3}
+```{r, fig.width=1.2, fig.height=4}
+# Make lof x look right, be more compact
+point <- format_format(big.mark = "", decimal.mark = ".", 
+                       scientific = FALSE, digits=1, drop0trailing=TRUE)
+
+# -
 ms <- 1e3
 results %>% 
-  filter(errors_pop > 0) %>% 
+  filter(errors_opt > 0, errors_pop > 0, variances_pop > 0) %>% 
   ggplot(aes(x=errors_pop*ms, y=variances_pop*ms)) +
-  geom_line(size=0.5) + 
-  geom_line(mapping=aes(x=errors_opt*ms, y=variances_opt*ms), color="#e41a1c", alpha=0.8, size=.5) +
-  scale_x_continuous(trans='log10') +
+  geom_point(size=0.1, alpha=0.6) + 
+  geom_point(
+    mapping=aes(x=errors_opt*ms, y=variances_opt*ms), 
+    color="#e41a1c", alpha=0.6, size=.1) +
+  scale_x_continuous(trans='log10', labels = point) +
   annotation_logticks(sides = "b") +

### 2019-04-23 voltagebudget/analysis/paper_figures.Rmd
Tweak figs

@@
 
+exp <- "105"
+freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")
+
+fig16 <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  # df %>%
+    # filter(n_spikes_pop > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  fig16 <- rbind(fig16, df)
+}
+
+fig16$freq <- factor(fig16$freq, levels=freqs)
+
+fig15$alg <- rep("max", nrow(fig15))
+fig16$alg <- rep("uniform", nrow(fig16))
+fig17 <- rbind(fig15, fig16)
 # --------------------------------------------------------------------
@@
   ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
-  geom_point(size=1.4, alpha=.8, shape=4) +
+  geom_point(size=1.4, alpha=1, shape=4) +
   geom_point(
     data=filter(tmp, set == "initial"),
-    mapping=aes(x=ts*1e3, y=ns), color="black", shape=1, alpha=0.5, size=1.35) +
+    mapping=aes(x=ts*1e3, y=ns), color="black", shape=1, alpha=1, size=1.35) +
   facet_grid(alg~.) +
-  scale_color_brewer(palette = "Set1", guide=FALSE) +
+  scale_color_brewer(palette = "Dark2", guide=FALSE) +
   theme_classic() +
@@
   ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
-  geom_line(size=0.8, alpha=0.8) +
-  scale_color_brewer(palette = "Set1", name="Algorithm:") +
+  geom_line(size=0.6, alpha=0.99) +
+  scale_color_brewer(palette = "Dark2", name="Algorithm:") +
   theme_classic() +
@@
 plot_grid <- rbind(
-  c(1, 1),
-  c(1, 1),
-  c(2, 2),
-  c(2, 2),
-  c(2, 2))
+  c(1, 1, 1, 1, 1),
+  c(1, 1, 1, 1, 1),
+  c(2, 2, 2, 2, NA),
+  c(2, 2, 2, 2, NA))
 
@@
 
-```{r, fig.width=1.2, fig.height=1}
+```{r, fig.width=1.2, fig.height=1.2}
 ms <- 1e3
-fig15 %>% 
+
+fig17 %>% 
   filter(errors_pop > 0, freq == "8") %>% 
   ggplot(aes(x=errors_pop*ms, y=variances_pop*ms)) +
-  geom_point(size=0.2, alpha=0.8) + 
-  geom_point(mapping=aes(x=errors_opt*ms, y=variances_opt*ms), color="#e41a1c", alpha=0.6, size=.2) +
+  geom_point(size=0.2, alpha=0.99) + 
+  geom_point(mapping=aes(x=errors_opt*ms, y=variances_opt*ms, color=alg), 
+             alpha=0.99, size=.2) +
   scale_x_continuous(trans='log10') +
   annotation_logticks(sides = "b") +
-  labs(x="Pop. error (ms)", y="Pop. variance (ms)") +
-  theme_classic() +
-  theme(strip.text.y = element_text(angle = 0), 
+  scale_color_brewer(palette = "Dark2", name="Algorithm:") +
+  labs(x="Error (ms)", y="Variance (ms)") +
+  theme_classic() +
+  theme(legend.position="bottom",
+    legend.key.size = unit(.2, "cm"),
+    legend.title = element_text(size=10),
+    legend.text = element_text(size=10),
+    legend.background = element_rect(colour ="black"),
+    strip.text.y = element_text(angle = 0), 
     panel.grid.minor = element_blank(),
     strip.background = element_blank())
-
 rm(ms)

### 2019-05-19 voltagebudget/analysis/paper_figures_redraft.Rmd
Added figure redraft
Revise ratio, story, and analysis.

Simplify everything!

--- 2019-04-23 voltagebudget/analysis/paper_figures.Rmd
@@
 }
+
+ms <- 1000
+mV <- 1000
 ```
@@
 fig1 %>% 
+  group_by(N, freq) %>% 
+  mutate(errors=normalize(errors),
+            variances=normalize(variances)) -> fig1
+
+fig1 %>% 
   group_by(As, freq) %>% 
@@
     V_osc = mean(V_osc), 
+    V_free = mean(V_free), 
     V_comp = mean(V_comp), 
@@
 
-# Budget intro
+# The trade off
 
-```{r, fig.width=1.5, fig.height=0.7}
-t_on = 0.23852
-t_off = t_on + 2e-3
+```{r, fig.width=1.7, fig.height=2.8}
+# Var
+fig2 %>% 
+  filter(V_osc/V_comp <= 5) %>%
+  ggplot(aes(x=V_osc*mV, variances_pop*ms, group=freq)) +
+  geom_point(size=.2, alpha=0.5) +
+  xlab(expression(paste(V[o], " (mV)"))) +
+  ylab("Variance (ms)") +
+  theme_classic() -> p1
+fig2 %>% 
+  filter(V_osc/V_comp <= 5) %>%
+  ggplot(aes(x=V_osc/V_comp, variances_pop*ms, group=freq)) +
+  geom_point(size=.2, alpha=0.5) +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="dashed") +
+  xlab(expression(V[o]/V[c])) +
+  ylab("Variance (ms)") +
+  theme_classic() -> p2
 
-v_min = -68e-3
-v_max = -50e-3
-box_buffer = .5e-3
+# Error
+fig2 %>% 
+  filter(V_osc/V_comp <= 5) %>%
+  ggplot(aes(x=V_osc*mV, errors_pop*ms, group=freq)) +
+  geom_point(size=.2, alpha=0.5) +
+  xlab(expression(paste(V[o], " (mV)"))) +
+  ylab("Error (ms)") +
+  theme_classic() -> p3
+fig2 %>% 
+  filter(V_osc/V_comp <= 5) %>%
+  ggplot(aes(x=V_osc/V_comp, errors_pop*ms, group=freq)) +
+  geom_point(size=.2, alpha=0.5) +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="dashed") +
+  xlab(expression(V[o]/V[c])) +
+  ylab("Error (ms)") +
+  theme_classic() -> p4
 
-fig0 %>% 
-  filter(t > 0.1, t < 0.29) %>%
-  # ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=vm*1e3)) +
-  # geom_ribbon(fill="blue", alpha=0.5) +
-  ggplot(aes(x=t, y=vm*1e3)) +
-  geom_line(color="black", alpha=1, size=.2) +
-  geom_hline(yintercept=v_max*1e3, color="black", linetype="dotted", size=0.5) +
-  geom_hline(yintercept=v_min*1e3, color="black", linetype="dotted", size=0.5) +
- geom_rect(
-    aes(
-      xmin=t_on, 
-      xmax=t_off, 
-      ymin=(v_min - box_buffer)*1e3, 
-      ymax=(v_max + box_buffer)*1e3),  
-    fill="grey", color=NA, alpha=0.01, size=.01) +
-  labs(x="Time (s)", y=expression(V[m] (mvolt))) +
-  scale_x_continuous(breaks=c(0, 0.1, 0.2, 0.3), limits = c(0.1, 0.3)) +
-  theme_classic() -> p1
+tmp <- fig2
+tmp$state <- rep("pathological", nrow(tmp))
+m <- tmp$V_osc/tmp$V_comp < 0.27
+tmp$state[m] <- "healthy"
 
-fig0 %>% 
-  filter(t > t_on, t < t_off) %>%
-  ggplot(aes(x=t, ymin=v_min*1e3, ymax=osc*1e3)) +
-  geom_ribbon(fill="red", alpha=0.5) +
-  geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
-  geom_hline(yintercept=-50e-3*1e3, color="black", linetype="dotted", size=0.5) +
-  geom_hline(yintercept=v_min*1e3, color="black", linetype="dotted", size=0.5) +
-  geom_rect(
-    aes(
-      xmin=t_on, 
-      xmax=t_off, 
-      ymin=(v_min - box_buffer)*1e3, 
-      ymax=(v_max + box_buffer)*1e3),  
-    fill=NA, color="grey", alpha=0.01, size=.6) +
-  labs(x="", y="") +
-  theme(axis.line=element_blank(),
-      axis.text.x=element_blank(),
-      axis.text.y=element_blank(),
-      axis.ticks=element_blank(),
-      # axis.title.x=element_blank(),
-      # axis.title.y=element_blank(),
-      legend.position="none",
-      panel.background=element_blank(),
-      panel.border=element_blank(),
-      panel.grid.major=element_blank(),
-      panel.grid.minor=element_blank(),
-      plot.background=element_blank()) -> p2
+tmp %>% 
+  filter(V_osc/V_comp <= 5) %>%
+  ggplot(aes(x=variances_pop*ms, errors_pop*ms, group=freq, color=state)) +
+  geom_point(size=.2, alpha=0.9) +
+  xlab("Variance (ms)") +
+  ylab("Error (ms)") +
+  scale_color_manual("", values=c("darkslategray3", "darkslategray")) +
+  theme_classic() -> p5
 
-plot_grid <- rbind(c(1 , 1, 1, 1,1, 1, 1, NA, 2, 2, 2))
-grid.arrange(p1, p2, layout_matrix=plot_grid)
-rm(p1, p2, plot_grid)
+plot_grid <- rbind(
+  c(NA, NA, NA, NA),
+  c(1, 1, 3, 3), 
+  c(1, 1, 3, 3),
+  c(1, 1, 3, 3),
+  c(1, 1, 3, 3),
+  c(NA, NA, NA, NA),
+  c(2, 2, 4, 4),
+  c(2, 2, 4, 4),
+  c(2, 2, 4, 4),
+  c(2, 2, 4, 4),
+  c(NA, NA, NA, NA),
+  c(5, 5, 5, 5),
+  c(5, 5, 5, 5),
+  c(5, 5, 5, 5),
+  c(5, 5, 5, 5),
+  c(5, 5, 5, 5),
+  c(5, 5, 5, 5))
 
-# fig0 %>% 
-#   filter(t > 0.15, t < 0.35) %>%
-#   ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
-#   geom_ribbon(fill="red", alpha=0.5) +
-#   geom_ribbon(aes(x=t, ymin=osc*1e3, ymax=comp*1e3), fill="purple", alpha=0.5) +
-#   geom_hline(yintercept=-50e-3*1e3, color="black", linetype="dotted", size=0.5) +
-#   geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.5) +
-#   geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3*1e3, ymax=-50e-3*1e3),  fill=NA, color="black", alpha=0.01, size=.2) +
-#   # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
-#   # geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), color="grey", alpha=0.5) +
-#   # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
-#   labs(x="Time (s)", y="") +
-#   theme_classic() -> p2
+grid.arrange(p1, p2, p3, p4, p5, layout_matrix=plot_grid)
 ```
 
-# Trade-off
+By looking at the ratio we identified a narrow region (V_o/V_c ~< 0.27) where the trade-off is approx linear across freq, and that accounts for approx.
+half the total change in both variance and error.
+We hypothesize that this narrow region can be considered a healthy range for modulation as it is maximially sensitive and linear -- representing the best possible trade-off irregardless of freq.
 
-```{r, fig.width=1.5, fig.height=1.9}
+Sync efficiency is strongly dependent on other osc input.
+Strong synapses need strong oscillations.
+Weak synapses need weak oscillations.
+To stay in healthy range, oscillation strength should be tuned on a compartment basis, either dendritically or somatically or both.
+
+# Vc and sync
+
+```{r, fig.width=1.4, fig.height=1}
 fig2 %>% 
-  filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc/V_b, y=errors_pop*1e3, color=V_osc/V_b)) +
-  geom_point(size=0.05, alpha=1) + 
-  labs(x=expression(V[o]/V[b]), y="Avg. error (ms)") +
-  # lims(y=c(0, 10)) +
-  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
-  scale_color_gradient(low="darkgrey", high="red") +
+  # filter(V_osc/V_comp <= ) %>%
+  ggplot(aes(x=V_comp*mV, variances_pop*ms, color=V_osc*mV)) +
+  geom_point(size=.2, alpha=0.5) +
+  xlab(expression(paste(V[c], " (mV)"))) +
+  ylab("Variance (ms)") +
+  scale_color_gradient(expression(paste(V[o], " (mV)")), low="goldenrod1", high="firebrick3") +
   theme_classic() +
-  theme(
-    legend.position="none") -> p1
-
-fig2 %>% 
-  filter(freq == 20) %>% 
-  ggplot(aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3, color=V_osc/V_b)) +
-  geom_point(size=0.05, alpha=1) + 
-  labs(x=expression(V[o]/V[b]), y="Pop. variance (ms)") +
-  scale_color_gradient(low="darkgrey", high="red") +
-  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
-  theme_classic() +
-  theme(
-    legend.position="none") -> p2
-
-fig2 %>% 
-  filter(freq == 20) %>% 
-  ggplot(aes(x=errors_pop*1e3, y=(variances_pop/n_spikes_pop)*1e3, color=V_osc/V_b)) +
-  geom_point(size=0.2, alpha=.6) +
-  scale_color_gradient(low="darkgrey", high="red", name=expression(V[o]/V[b])) +
-  # scale_color_gradient(low="darkgrey", high="red", name="A (namp)") +
-  # geom_smooth(color="red", method=lm, alpha=0.2, size=.15, se=FALSE, linetype='solid') +
-  labs(x="Avg. error (ms)", y="Pop. variance (ms)") +
-  theme_classic() +
-  theme(
-    legend.position="right", 
-    legend.background = element_rect(colour ="black"),
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p3
-
-# plot_grid <- rbind(
-#   c(NA, NA, NA, NA, 4, 4,   4),
-#   c(NA, NA, NA, NA, 4, 4,   4),
-#   c(1,  1,  1,  1, 2, 2,   2),
-#   c(1,  1,  1,  1, 2, 2,   2),
-#   c(1,  1,  1,  1, 3, 3,   3),
-#   c(1,  1,  1,  1, 3, 3,   3))#,
-  # c(1,  1,  1,  NA, NA, NA))
-
-plot_grid <- rbind(
-  c(NA),
-  c(3, 3))
-
-grid.arrange(p3, layout_matrix=plot_grid)
-rm(p1, p2, p3, plot_grid)
+  theme(legend.key.width=unit(0.3,"cm"),
+        legend.title=element_text(size=8),
+        legend.text=element_text(size=8))
 ```
 
-# V_o/V_c
+While the ratio determines the overall trade-off (above), again we see that about half the sync effect comes from weak oscillations (< 1 mV, orange) applied to strong inputs (i.e., V_c > 6 mV).
+However this story is complicated by the fact that the weaker Vc, the more sync is possible--though this sync is very high error.
 
-```{r, fig.width=2.7, fig.height=2.2}
+# Freq. dependence
 
-fig1 %>% 
-  group_by(N) %>% 
-  filter(V_osc/V_comp <= 3) %>% 
-  filter(freq == 20) %>% 
-  group_by(N) %>%
-  mutate(V_free_initial = round(max(V_free), 3)) %>%
-  filter(V_free_initial > 0) %>%
-  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
-  geom_line(size=0.5, alpha=0.2, color="grey") + 
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
+```{r, fig.width=1, fig.height=6}
+fig2 %>% 
+  filter(V_osc/V_comp <= 0.8) %>%
+  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms)) +
+  geom_point(size=.2, alpha=0.5) +
+  facet_grid(freq~.) +
+  xlab(expression(V[o]/V[c])) +
+  ylab("Variance (ms)") +
+  # geom_rect(
+  #   mapping=aes(xmin=0.15, xmax=0.4, ymin=min(variances_pop*ms), ymax=max(variances_pop*ms)),
+  #   color="darkslategray4", fill="darkslategray4", alpha=0.02) +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="dashed") +
   theme_classic() +
-  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
-            aes(x=V_osc/V_comp, y=errors*1e3), 
-            color="black", size=0.8) +
-  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1
-
-fig1 %>% 
-  filter(V_osc/V_comp <= 3) %>% 
-  filter(freq == 20) %>% 
-  group_by(N) %>%
-  mutate(V_free_initial = round(max(V_free), 3)) %>%
-  filter(V_free_initial > 0) %>%
-  ggplot(aes(x=V_osc/V_comp, y=(variances/n_spikes)*1e3, group=N)) +
-  geom_line(size=0.5, alpha=0.2, color="grey") + 
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  theme_classic() +
-  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
-            aes(x=V_osc/V_comp, y=(variances_pop/n_spikes_pop)*1e3), 
-            color="black", size=0.7, alpha=1) +
-  labs(x=expression(V[o]/V[c]), y="Variance (ms)") -> p2
-
-# # Norm error here
-# fig1 %>% 
-# filter(V_osc/V_comp < 3) %>% 
-#   filter(freq == 20) %>% 
-#   group_by(N, freq) %>% 
-#   mutate(norm_errors = errors/max(errors)) -> tmp1
-# 
-# tmp1 %>% 
-#   group_by(As) %>% 
-#   summarise(
-#     N = 0,
-#     norm_errors = mean(norm_errors),
-#     V_b = mean(V_b), 
-#     V_osc = mean(V_osc), 
-#     V_comp = mean(V_comp)) -> tmp2
-# 
-# tmp1 %>% 
-#   group_by(N) %>% 
-#   filter(V_osc/V_comp <= 3) %>% 
-#   filter(freq == 20) %>%
-#   group_by(N) %>%
-#   mutate(V_free_initial = round(max(V_free), 3)) %>%
-#   filter(V_free_initial > 0) %>%
-#   ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
-#   geom_line(size=0.5, alpha=0.2, color="grey") + 
-#   geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-#   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-#   theme_classic() +
-#   geom_line(data=tmp2, 
-#             aes(x=V_osc/V_comp, y=norm_errors), 
-#             color="black", size=0.8) +
-#   labs(x=expression(V[o]/V[c]), y="Norm. error") -> p2
-
-max_N <- max(fig1$N)
-
-fig1 %>% 
-  filter(freq==20) %>%
-  filter(V_osc/V_comp <= 3) %>% 
-  filter(N %in% sample(1:max_N, 24, replace = FALSE)) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
-  geom_line(size=.5, alpha=0.9, color="grey") + 
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  facet_wrap(~rank, nrow=3) +
-  theme_classic() + 
-  scale_x_continuous(breaks=c(0, 1, 2)) +
-  scale_y_continuous(breaks=c(0, 10)) +
-  theme(
-    strip.text.x = element_text(size=0),
-    strip.background = element_blank(),
-    # axis.line=element_blank(),
-    # axis.text.x=element_blank(),
-    # axis.text.y=element_blank(),
-    # axis.ticks=element_blank(),s
-    # axis.title.x=element_blank(),
-    # axis.title.y=element_blank(),
-    panel.background=element_blank(),
-    # panel.border=element_blank(),
-    # panel.grid.major=element_blank(),
-    # panel.grid.minor=element_blank(),
-    plot.background=element_blank()) +
-  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3
-
-plot_grid <- rbind(
-  c(1, 1, 1, 2, 2), 
-  c(1, 1, 1, 2, 2), 
-  c(1, 1, 1, 2, 2),
-  c(1, 1, 1, NA, NA),
-  c(3, 3, 3, 3, 3),
-  c(3, 3, 3, 3, 3),
-  c(3, 3, 3, 3, 3))
-  # c(3, 3, 3, 4, 4),
-  # c(3, 3, 3, 4, 4),
-  # c(3, 3, 3, 4, 4))
-grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
-rm(p1, p2, p3, plot_grid, max_N)
+  theme(strip.text.y = element_text(angle=0), strip.background = element_blank())
 ```
 
-$ V_o and variance
+Fo far we've focused on error-variance relationships common between frequencies. There are also clearly frequency dependent effects
 
-```{r, fig.width=2.8, fig.height=3.2}
-max_N <- max(fig1$N)
+...
 
-fig1 %>% 
-  filter(freq == 20) %>% 
-  group_by(N) %>%
-  mutate(V_free_initial = round(max(V_free), 3)) %>%
-  filter(V_free_initial > 0) %>%
-  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, group=N, color=factor(delta_spikes))) +
-  geom_line(size=0.4, alpha=0.6) + 
-  scale_colour_brewer(
-    palette = "Reds", guide=guide_legend(title="Spike\ncount", nrow=3)) +
-  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
-  theme_classic() + theme(legend.position = c(1.25, -0.8), 
-        legend.background = element_rect(colour ="black"),
-        legend.key.size = unit(.5, "cm"),
-        legend.title = element_text(size=10),
-        legend.text = element_text(size=10)) -> p1
+Faster oscillations offer less sync overall, and therefore have a more limited var-error range than slower oscillations.
+If we use the curveture of the variance curve to fine tune the healthy ratio / frequency, we see that...
 
-fig1 %>% 
-  filter(freq==20) %>% 
-  filter(V_osc/V_comp <= 3) %>% 
-  group_by(N) %>%
-  mutate(V_free_initial = round(max(V_free), 3)) %>%
-  filter(V_free_initial > 0) %>%
-  ggplot(aes(y=V_osc/V_comp, x=factor(delta_spikes), group=delta_spikes)) +
-  geom_jitter(aes(color=factor(delta_spikes)), size=0.01, alpha=0.1, width=0.2) +
-  geom_boxplot(outlier.colour = NA, alpha=0.9, width=0.2) +
-  scale_colour_brewer(palette = "Reds", name="Spike count") +
-  geom_hline(yintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_hline(yintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  theme_classic() +
-  theme(legend.position = "none") +
-  labs(y=expression(V[o]/V[c]), x="Spike count") + 
-  coord_flip()  -> p2
+TODO: get max second deriv. Use that to find the change point?
 
-# -
-M = min(fig2$variances_pop/fig2$n_spikes_pop)
-fig1 %>% 
-  filter(freq==20) %>% 
-  mutate(quantile = ntile(V_osc, 10)) %>%
-  filter(quantile %in% c(1, 10)) %>% 
-  ggplot(aes(x=(variances/n_spikes)*1e3, fill=factor(quantile), group=quantile)) +
-  geom_density(alpha=0.6, size=0.2, color="black") +
-  geom_vline(xintercept = M*1e3, color="black") +
-  labs(x="Variance (ms)", y="Density (AU)") +
-  scale_fill_manual(
-    # values=c("#FFDED3", "#FD0D11"), 
-    values=c("grey", "black"),
-    name=expression("Deciles V"[o]), 
-    labels=c("0 - 10%", "90 - 100%")) +
-  theme_classic() +
-  theme(
-    legend.position="bottom", 
-    legend.key.size = unit(.3, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8) ) -> p3
-
-# fig1 %>% 
-#   filter(freq == 20) %>% 
-#   group_by(N) %>%
-#   mutate(V_free_initial = round(max(V_free), 3)) %>%
-#   filter(V_free_initial > 0) %>%
-#   ggplot(aes(x=(variances/n_spikes)*1e3, fill=factor(delta_spikes))) +
-#   geom_density(alpha=0.6, size=0, color="black") +
-#   scale_fill_brewer(palette = "Reds", name="Spike\ncount") +
-#   geom_vline(xintercept = M*1e3, color="black", linetype="dotted") +
-#   labs(x="Variance (ms)", y="Density (AU)") +
-#   theme_classic() + 
-#   theme(legend.position = c(1.25, 1.55), 
-#         legend.background = element_rect(colour ="black"),
-#         legend.key.size = unit(.5, "cm"),
-#         legend.title = element_text(size=10),
-#         legend.text = element_text(size=10)) -> p3
-
-fig1 %>%
-  filter(freq==20) %>%
-  group_by(N) %>%
-  mutate(V_free_initial = round(max(V_free), 3)) %>%
-  filter(V_free_initial > 0) %>%
-  ungroup() %>% 
-  group_by(N) %>% 
-  sample_n_groups(8) %>% 
-  ggplot(aes(x=V_osc/V_b, y=(variances/n_spikes)*1e3, color=factor(delta_spikes))) +
-  geom_point(size=1, alpha=1) +
-  facet_wrap(~N, nrow=8) +
-  # geom_line(aes(x=V_osc/V_b, y=(variances_pop/n_spikes_pop)*1e3),
-  #           color="black", size=0.7, alpha=1) +
-  scale_colour_brewer(palette = "Reds", name="Spike count") +
-  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
-  scale_y_continuous(breaks=c(6, 12)) +
-  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
-  theme_classic() + theme(
-    # legend.position="bottom",
-    strip.text.x = element_text(size=0),
-    strip.background = element_blank(),
-    legend.position="none",
-    legend.key.size = unit(.5, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8),
-    # axis.line=element_blank(),
-    # axis.text.x=element_blank(),
-    # axis.text.y=element_blank(),
-    # axis.ticks=element_blank(),
-    # axis.title.x=element_blank(),
-    # axis.title.y=element_blank(),
-    panel.background=element_blank(),
-    # panel.border=element_blank(),
-    # panel.grid.major=element_blank(),
-    # panel.grid.minor=element_blank(),
-    plot.background=element_blank()) -> p4
-
-fig1 %>%
-  filter(freq==20) %>%
-  filter(V_osc/V_comp <= 3) %>%
-  group_by(N) %>%
-  mutate(V_free_initial = round(max(V_free), 3)) %>%
-  filter(V_free_initial > 0) %>%
-  sample_n_groups(8) %>% 
-  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
-  geom_point(size=1, alpha=1) +
-  facet_wrap(~N, nrow=8) +
-  # geom_line(aes(x=V_osc/V_b, y=errors_pop*1e3),
-  #           color="black", size=0.7, alpha=1) +
-  scale_colour_brewer(palette = "Reds", name="Spike count") +
-  scale_x_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
-  scale_y_continuous(breaks=c(2, 8)) +
-  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
-  theme_classic() + theme(
-    # legend.position="bottom",
-    strip.text.x = element_text(size=0),
-    strip.background = element_blank(),
-    legend.position="none",
-    legend.key.size = unit(.5, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8),
-    # axis.line=element_blank(),
-    # axis.text.x=element_blank(),
-    # axis.text.y=element_blank(),
-    # axis.ticks=element_blank(),
-    # axis.title.x=element_blank(),
-    # axis.title.y=element_blank(),
-    panel.background=element_blank(),
-    # panel.border=element_blank(),
-    # panel.grid.major=element_blank(),
-    # panel.grid.minor=element_blank(),
-    plot.background=element_blank()) -> p5
-
-# Shift-add cartoon
-t_start <- 0.2
-t_stop <- 0.3
-
-fig6 %>% 
-  filter(t > t_start, t < t_stop) %>%
-  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
-  geom_ribbon(fill="red", alpha=0.5) +
-  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.3) +
-  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.6) +
-  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.6) +
-  labs(x="", y="") +
-  theme_classic() +
-  theme(axis.line=element_blank(),
-      axis.text.x=element_blank(),
-      axis.text.y=element_blank(),
-      axis.ticks=element_blank(),
-      # axis.title.x=element_blank(),
-      # axis.title.y=element_blank(),
-      legend.position="none",
-      panel.background=element_blank(),
-      panel.border=element_blank(),
-      panel.grid.major=element_blank(),
-      panel.grid.minor=element_blank(),
-      plot.background=element_blank()) -> p6
-
-fig7 %>% 
-  filter(t > t_start, t < t_stop) %>%
-  ggplot(aes(x=t, ymin=-70e-3*1e3, ymax=osc*1e3)) +
-  geom_ribbon(fill="red", alpha=0.5) +
-  geom_line(aes(x=t, y=vm*1e3),color="black", alpha=1, size=.3) +
-  geom_hline(yintercept=-55e-3*1e3, color="black", linetype="dotted", size=0.6) +
-  geom_hline(yintercept=-70e-3*1e3, color="black", linetype="dotted", size=0.6) +
-  labs(x="", y="") +
-  theme_classic() +
-  theme(axis.line=element_blank(),
-      axis.text.x=element_blank(),
-      axis.text.y=element_blank(),
-      axis.ticks=element_blank(),
-      # axis.title.x=element_blank(),
-      # axis.title.y=element_blank(),
-      legend.position="none",
-      panel.background=element_blank(),
-      panel.border=element_blank(),
-      panel.grid.major=element_blank(),
-      panel.grid.minor=element_blank(),
-      plot.background=element_blank()) -> p7
-
-plot_grid <- rbind(
-  c(1, 1, 1, NA, 4, 4, 5, 5),
-  c(1, 1, 1, NA, 4, 4, 5, 5),
-  c(1, 1, 1, NA, 4, 4, 5, 5),
-  c(2, 2, 2, NA, 4, 4, 5, 5),
-  c(2, 2, 2, NA, 4, 4, 5, 5),
-  c(2, 2, 2, NA, 4, 4, 5, 5),
-  c(3, 3, 3, NA, 4, 4, 5, 5),
-  c(3, 3, 3, NA, NA, NA, NA, NA),
-  c(3, 3, 3, NA, 6, 6, 7, 7),
-  c(NA, NA, NA, NA, 6, 6, 7, 7))
-
-  # c(3, 3, 3, NA, 4, 4, 5, 5))
-  # c(3, 3, 3, NA, NA, NA, NA, NA))
-  # c(3, 3, 3, NA, NA, NA, NA, NA))
-
-grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix=plot_grid)
-rm(p1, p2, p3, p4, plot_grid, max_N, M)
-```
-
-# Control exps
-## Freqs, noise, weight
-
-```{r, fig.width=2.1, fig.height=2.4}
-# --------------------------------------------------------------
-# Freq
-fig2 %>% 
-  filter(V_osc/V_comp < 3) %>% 
-  filter(freq <= 30) %>% 
-  group_by(N, freq) %>% 
-  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
-  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=freq, group=interaction(N, freq))) +
-  geom_line(size=0.3, alpha=1) + 
-  labs(x=expression(V[o]/V[c]), y="Norm. error") +
-  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  theme_classic() +
-  theme(legend.position="none", 
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p1
-
-fig2 %>% 
-  filter(V_osc/V_comp < 3) %>% 
-  filter(freq <= 30) %>% 
-  group_by(N, freq) %>% 
-  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
-  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=freq, group=interaction(N, freq))) +
-  geom_line(size=0.3, alpha=1) + 
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
-  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
-  theme_classic() +
-  # lims(y=c(5, 10)) +
-  theme(legend.position="right", 
-    legend.background = element_rect(colour ="black"),
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p2
-
-# --------------------------------------------------------------
-# Noise
-fig9 %>% 
-  filter(V_osc/V_comp < 3) %>% 
-  group_by(N, sigma) %>% 
-  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
-  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=10e-3*(sigma/10e-9) * 1e3/2, group=interaction(N, sigma))) +
-  geom_line(size=0.3, alpha=1) + 
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  labs(x=expression(V[o]/V[c]), y="Norm. error") +
-  scale_color_gradient(low="grey", high="orange") +
-  theme_classic() +
-  theme(legend.position="none", 
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p3
-
-fig9 %>% 
-  filter(V_osc/V_comp < 3) %>% 
-  group_by(N, sigma) %>% 
-  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
-  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=10e-3*(sigma/10e-9) * 1e3 /2, group=interaction(N, sigma))) +
-  geom_line(size=0.3, alpha=1) + 
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
-  scale_color_gradient(low="grey", high="orange", name="Noise (mV)") +
-  theme_classic() +
-  # lims(y=c(5, 10)) +
-  theme(legend.position="right", 
-    legend.background = element_rect(colour ="black"),
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p4
-
-# --------------------------------------------------------------
-# Weight
-fig11 %>% 
-  filter(V_osc/V_comp < 3) %>% 
-  group_by(N, weight) %>% 
-  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
-  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=weight*1e9, group=interaction(N, weight))) +
-  geom_line(size=0.3, alpha=1) + 
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  labs(x=expression(V[o]/V[c]), y="Norm. error") +
-  scale_color_gradient2(
-    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9) +
-  theme_classic() +
-  theme(legend.position="none", 
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p5
-
-fig11 %>% 
-  filter(V_osc/V_comp < 3) %>% 
-  group_by(N, weight) %>% 
-  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
-  mutate(norm_variances_pop = (variances_pop/n_spikes_pop)/max((variances_pop/n_spikes_pop))) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=weight*1e9, group=interaction(N, weight))) +
-  geom_line(size=0.3, alpha=1) + 
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
-  scale_color_gradient2(
-    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9, name="Weight (nS)") +
-  theme_classic() +
-  # lims(y=c(5, 10)) +
-  theme(legend.position="right", 
-    legend.background = element_rect(colour ="black"),
-    legend.key.size = unit(.4, "cm"),
-    legend.title = element_text(size=8),
-    legend.text = element_text(size=8)) -> p6
-
-plot_grid <- rbind(
-  c(1, 1, 1, 2, 2, 2, 2, 2),
-  c(3, 3, 3, 4, 4, 4, 4, 4),
-  c(5, 5, 5, 6, 6, 6, 6, 6))
-
-grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=plot_grid)
-rm(p1, p2, p3, p4, plot_grid)
-```
-## Heterocells
-
-```{r, fig.width=0.4, fig.height=1.2}
-fig14 %>% 
-  ggplot(aes(x=t, y=vm*1e3, group=cell)) +
-  geom_line(size=0.2, color="black") +
-  facet_grid(cell~.) +
-  theme_classic() +
-  labs(x="Time (s)", y="V (mV)") +
-  theme(
-    strip.text = element_blank(),
-    strip.background = element_blank(),
-    legend.position="none",
-    axis.line=element_blank(),
-    axis.text.x=element_blank(),
-    axis.text.y=element_blank(),
-    axis.ticks=element_blank(),
-    axis.title.x=element_blank(),
-    axis.title.y=element_blank(),
-    panel.background=element_blank(),
-    panel.border=element_blank(),
-    panel.grid.major=element_blank(),
-    panel.grid.minor=element_blank(),
-    plot.background=element_blank())
-```
-
-```{r, fig.width=0.9, fig.height=1.5}
-fig12 %>%
-  group_by(N) %>%
-  mutate(V_free_initial = round(max(V_free), 3)) %>%
-  filter(V_free_initial > 0) %>%
-  filter(V_osc/V_comp <= 3) %>% 
-  mutate(norm_errors = errors/max(errors)) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
-  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
-  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
-            aes(x=V_osc/V_comp, y=errors/max(errors)), 
-            color="black", size=0.7) +
-  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
-            aes(x=V_osc/V_comp, y=errors/max(errors)), 
-            color="black", size=0.7, linetype="dotdash") +
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
-  theme_classic() +
-  lims(x=c(0, 3)) +
-  labs(x=expression(V[o]/V[c]), y="Norm. error") -> p1
-
-# fig1 %>% 
-#   group_by(N) %>% 
-#   filter(V_osc/V_comp <= 3) %>% 
-#   filter(freq == 20) %>% 
-#   group_by(N) %>%
-#   mutate(V_free_initial = round(max(V_free), 3)) %>%
-#   filter(V_free_initial > 0) %>%
-#   ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
-#   geom_line(size=0.5, alpha=0.2, color="grey") + 
-#   geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-#   geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
-#   theme_classic() +
-#   geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
-#             aes(x=V_osc/V_comp, y=errors*1e3), 
-#             color="black", size=0.8) +
-#   labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1
-
-fig12 %>%
-  group_by(N) %>%
-  mutate(V_free_initial = round(max(V_free), 3)) %>%
-  filter(V_free_initial > 0) %>%
-  filter(V_osc/V_comp <= 3) %>% 
-  mutate(norm_variances = variances/max(variances)) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=norm_variances/n_spikes, group=N)) +
-  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
-  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
-            aes(x=V_osc/V_comp, y=(variances_pop/max(variances_pop))/n_spikes_pop), 
-            color="black", size=0.8) +
-  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
-            aes(x=V_osc/V_comp, y=(variances_pop/max(variances_pop))/n_spikes_pop), 
-            color="black", size=0.7, linetype="dotdash") +
-  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
-  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
-  theme_classic() +
-  lims(x=c(0, 3)) +
-  labs(x=expression(V[o]/V[c]), y="Norm. variance") -> p2
-
-plot_grid <- rbind(
-  c(1),
-  c(2))
-
-grid.arrange(p1, p2, layout_matrix=plot_grid)
-rm(p1, p2, plot_grid)
-```
+# Controls - Ws, noise, cell type
+TODO
 
 # Optimal derivation
-
 ```{r, fig.width=1.3, fig.height=2}
@@
   ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
-  geom_point(size=1.4, alpha=1, shape=4) +
+  geom_point(size=2, alpha=1, shape=4) +
   geom_point(
     data=filter(tmp, set == "initial"),
-    mapping=aes(x=ts*1e3, y=ns), color="black", shape=1, alpha=1, size=1.35) +
+    mapping=aes(x=ts*1e3, y=ns), color="black", shape=1, alpha=1, size=1.2) +
   facet_grid(alg~.) +
-  scale_color_brewer(palette = "Dark2", guide=FALSE) +
+  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3")) +
   theme_classic() +
@@
   geom_line(size=0.6, alpha=0.99) +
-  scale_color_brewer(palette = "Dark2", name="Algorithm:") +
+  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3")) +
   theme_classic() +
+  coord_flip() +
   labs(x="Time (ms)", y="Neuron") +
@@
 
-# Optimal versus oscillation
+# Optimal vs. oscillation
 
-```{r, fig.width=1.2, fig.height=1.2}
+```{r, fig.width=1.3, fig.height=1.2}
 ms <- 1e3
@@
 fig17 %>% 
-  filter(errors_pop > 0, freq == "8") %>% 
-  ggplot(aes(x=errors_pop*ms, y=variances_pop*ms)) +
+  filter(errors_pop > 0, freq == "20") %>% 
+  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
   geom_point(size=0.2, alpha=0.99) + 
-  geom_point(mapping=aes(x=errors_opt*ms, y=variances_opt*ms, color=alg), 
+  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
              alpha=0.99, size=.2) +
-  scale_x_continuous(trans='log10') +
-  annotation_logticks(sides = "b") +
-  scale_color_brewer(palette = "Dark2", name="Algorithm:") +
-  labs(x="Error (ms)", y="Variance (ms)") +
+  scale_y_continuous(trans='log10') +
+  annotation_logticks(sides = "l") +
+  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3")) +
+  labs(x="Variance (ms)", y="Error (ms)") +
   theme_classic() +
@@
     panel.grid.minor = element_blank(),
+    legend.key.width=unit(0.1,"cm"),
     strip.background = element_blank()) 

### 2019-05-19 voltagebudget/analysis/paper_figures_redraft.Rmd
Update fig redraft

@@
   geom_point(size=.2, alpha=0.5) +
-  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="dashed") +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
   xlab(expression(V[o]/V[c])) +
@@
 While the ratio determines the overall trade-off (above), again we see that about half the sync effect comes from weak oscillations (< 1 mV, orange) applied to strong inputs (i.e., V_c > 6 mV).
-However this story is complicated by the fact that the weaker Vc, the more sync is possible--though this sync is very high error.
+We interpret this to mean that the optimal target for oscillatory modulation are strong synapses.
+However this interpretation is complicated by the fact that the weaker Vc, the more sync is possible--though this sync is very high error.
 
 # Freq. dependence
-
 ```{r, fig.width=1, fig.height=6}
@@
   #   color="darkslategray4", fill="darkslategray4", alpha=0.02) +
-  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="dashed") +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
   theme_classic() +
@@
 # Controls - Ws, noise, cell type
+TODO
+
+# MINST exp (BIND)
 TODO
@@
     strip.background = element_blank()) 
-rm(ms)
 ```

### 2019-05-19 voltagebudget/analysis/paper_figures_redraft.Rmd
WIP

@@
 half the total change in both variance and error.
-We hypothesize that this narrow region can be considered a healthy range for modulation as it is maximially sensitive and linear -- representing the best possible trade-off irregardless of freq.
+We hypothesize that this narrow region can be considered a healthy range for modulation as it is maximially sensitive (has the highest dirvative) and is approx.
+linear--representing the best possible trade-off irregardless of freq.
 
@@
 
+Our analysis suggests a simple biological scaling rule for oscillatory modulation.
+This is useful both in analyzing for patholigical acitivty, but also in desgining optogenetic and other stimulation experiments.
+You should scale your oscillatory manipulation be no more the 0.27 times as strong as the average membrane potential observed in vivo, without stimulation.
+
+If your observaing a excitatory interneuron, with weak sparse inputs, a good level of oscillatory stimulation will be much lower then if, for example, you were working with a layer 5 pyrimidal cell recieving strong thalmic drive.
+
 # Vc and sync
-
 ```{r, fig.width=1.4, fig.height=1}
@@
 However this interpretation is complicated by the fact that the weaker Vc, the more sync is possible--though this sync is very high error.
+That is, if very high syncrony is needed very high error unavoidably the cost--a cost we can predict based on measurable membrane potential Vc.
+
+A simple biological response to this is to have (weak, <1 mV) oscillatory modulation selectivly target strong synapses.
 
 # Freq. dependence
-```{r, fig.width=1, fig.height=6}
+```{r, fig.width=0.65, fig.height=2.5}
+fig2 %>% 
+filter(V_osc/V_comp <= 5) %>%
+  ggplot(aes(x=variances_pop*ms, errors_pop*ms, group=freq)) +
+  geom_point(size=.2, alpha=0.9) +
+  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
+  scale_y_continuous(breaks=c(0,30,60)) +
+  xlab("Variance (ms)") +
+  ylab("Error (ms)") +
+  facet_grid(freq~.) +
+  theme_classic() +
+  theme(strip.text.y = element_text(angle=0), strip.background = element_blank())
+```
+
+```{r, fig.width=0.65, fig.height=2.5}
 fig2 %>% 
@@
   ylab("Variance (ms)") +
+  scale_y_continuous(breaks=c(7.5,8,8.5,9)) +
+  scale_x_continuous(breaks=c(0,0.4,0.8)) +
   # geom_rect(
@@
 
-Fo far we've focused on error-variance relationships common between frequencies. There are also clearly frequency dependent effects
+Fo far we've focused on error-variance relationships common between frequencies. Frequency also effect error-variance trade off.
 
@@
 TODO: get max second deriv. Use that to find the change point?
+TODO: plot max second derive ration point by freq. How does the healthy boundry scale with freq?
+
+Slower oscillations have a wider working range, than faster oscillations. If doing stimulation experiments, once must also consider your freqeuncy carefully.
 

### 2019-05-19 voltagebudget/exp/sweep_A.py
Exposed g_l and V_l

@@ -48,6 +48,8 @@ def sweep_A(name,
             n_cycles=2,
             mode='regular',
             sigma=0,
+            g_l=10e-9,
+            V_l=-70e-3,
             w_in_0=None,
             w_in_max=None,
             no_lock=False,
@@ -103,6 +105,8 @@ def sweep_A(name,
         A=0,
         phi=0,
         sigma=sigma,
+        g_l=g_l,
+        V_l=V_l,
         budget=True,
         save_args=None,
         time_step=time_step,
@@ -188,6 +192,8 @@ def sweep_A(name,
             E=E,
             n_cycles=n_cycles,
             sigma=sigma,
+            g_l=g_l,
+            V_l=V_l,
             budget=True,
             seed_value=seed_value,
             time_step=time_step,
@@ -213,6 +219,8 @@ def sweep_A(name,
             A=0,
             phi=0,
             sigma=0,
+            g_l=g_l,
+            V_l=V_l,
             budget=True,
             save_args=None,
             time_step=time_step,

### 2019-05-19 voltagebudget/analysis/paper_figures_redraft.Rmd
WIP

@@
 
+## Heterocells
+
+```{r, fig.width=0.5, fig.height=1.4}
+fig14 %>% 
+  ggplot(aes(x=t, y=vm*1e3, group=cell)) +
+  geom_line(size=0.2, color="black") +
+  facet_grid(cell~.) +
+  theme_classic() +
+  labs(x="Time (s)", y="V (mV)") +
+  theme(
+    strip.text = element_blank(),
+    strip.background = element_blank(),
+    legend.position="none",
+    axis.line=element_blank(),
+    axis.text.x=element_blank(),
+    axis.text.y=element_blank(),
+    axis.ticks=element_blank(),
+    axis.title.x=element_blank(),
+    axis.title.y=element_blank(),
+    panel.background=element_blank(),
+    panel.border=element_blank(),
+    panel.grid.major=element_blank(),
+    panel.grid.minor=element_blank(),
+    plot.background=element_blank()) -> p1
+plot(p1)
+```
+
+```{r, fig.width=2.1, fig.height=1.5}
+# --------------------------------------------------
+# Cell type
+fig12 %>%
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  filter(V_osc/V_comp <= 5) %>% 
+  mutate(norm_errors = normalize(errors_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
+  geom_point(size=.1, alpha=0.4) +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  labs(x=expression(V[o]/V[c]), y="Norm. error", title="Cell type") +
+  theme_classic() +
+  theme(title = element_text(size=10)) +
+  lims(x=c(0, 5)) -> p2
+
+fig12 %>%
+  group_by(N) %>%
+  mutate(V_free_initial = round(max(V_free), 3)) %>%
+  filter(V_free_initial > 0) %>%
+  filter(V_osc/V_comp <= 5) %>% 
+  mutate(norm_variance = normalize(variances_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_variance, group=N)) +
+  geom_point(size=.1, alpha=0.4) +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  theme_classic() +
+  lims(x=c(0, 5)) +
+  labs(x=expression(V[o]/V[c]), y="Norm. variance") -> p3
+
+# --------------------------------------------------------------
+# Noise
+fig9 %>% 
+  filter(V_osc/V_comp < 5) %>% 
+  group_by(N, sigma) %>% 
+  mutate(norm_errors_pop = normalize(errors_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, 
+             color=10e-3*(sigma/10e-9) * 1e3/2, group=interaction(N, sigma))) +
+  geom_point(size=.1, alpha=0.4) +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  labs(x=expression(V[o]/V[c]), y="Norm. error") +
+  scale_color_gradient("Noise\n(mV)", low="grey", high="black") +
+  theme_classic() +
+  # theme(legend.position="top", 
+  theme(
+    # legend.position = c(.2, .9), 
+    # legend.direction = "horizontal",
+    legend.position="top", 
+    legend.margin=margin(t = 0, b=-.25, unit='cm'),
+    legend.key.size = unit(.3, "cm"),
+    legend.key.height=unit(0.15,"cm"),
+    legend.key.width=unit(0.3,"cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=4)) -> p4
+
+fig9 %>% 
+  filter(V_osc/V_comp < 5) %>% 
+  group_by(N, sigma) %>% 
+  mutate(norm_variances_pop = normalize(variances_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, 
+             color=10e-3*(sigma/10e-9) * 1e3/2, group=interaction(N, sigma))) +
+  geom_point(size=.1, alpha=0.4) +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
+  scale_color_gradient(low="grey", high="black") +
+  theme_classic() +
+  theme(legend.position="none") -> p5
+
+plot_grid <- rbind(
+  c(1, 1, 2, 2, 2, 2, 4, 4, 4, 4),
+  c(1, 1, 2, 2, 2, 2, 4, 4, 4, 4),
+  c(1, 1, 2, 2, 2, 2, 4, 4, 4, 4),
+  c(1, 1, 2, 2, 2, 2, 4, 4, 4, 4),
+  c(1, 1, 2, 2, 2, 2, 4, 4, 4, 4),
+  c(1, 1, 3, 3, 3, 3, 5, 5, 5, 5),
+  c(1, 1, 3, 3, 3, 3, 5, 5, 5, 5),
+  c(1, 1, 3, 3, 3, 3, 5, 5, 5, 5),
+  c(1, 1, 3, 3, 3, 3, 5, 5, 5, 5))
+
+grid.arrange(p1, p2, p3, p4, p5, layout_matrix=plot_grid)
+```
+
 # MINST exp (BIND)
@@
 
-```{r, fig.width=1.3, fig.height=1.2}
+```{r, fig.width=1.1, fig.height=2}
 ms <- 1e3
@@
 fig17 %>% 
-  filter(errors_pop > 0, freq == "20") %>% 
+  filter(errors_pop > 0, freq %in% c("8","12","20","30")) %>%
   ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
@@
   annotation_logticks(sides = "l") +
+  facet_grid(freq~.) +
   scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3")) +
   labs(x="Variance (ms)", y="Error (ms)") +
+  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
   theme_classic() +
@@
     panel.grid.minor = element_blank(),
-    legend.key.width=unit(0.1,"cm"),
+    legend.key.width=unit(0.05,"cm"),
     strip.background = element_blank()) 

### 2019-05-21 voltagebudget/analysis/exp106_analysis.Rmd
exp106/107 analysis notebooks

---
title: "Sweep A - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}

mV <- 1000
ms <- 1000
```

# Load and process

```{r, message=FALSE}
exp <- "106"
g_ls <- c("10e-9", "12e-9", "14e-9")

results <- NULL
for(g_l in g_ls){
  name <- paste("../../data/exp", exp, "_g_l", g_l, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df %>%
    filter(n_spikes > 0) -> df

  df$g_l <- rep(g_l, nrow(df))
  results <- rbind(results, df)
}
results$g_l <- factor(results$g_l, levels=g_ls)

results %>% 
  filter(n_spikes_ref > 0) %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results

# -
rm(df, exp, g_l, g_ls, name)
```

# Overall distributions

```{r, fig.width=2.75, fig.height=2}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=variances_pop*ms, fill=g_l)) +
  geom_histogram(bins=20, alpha=1) + 
  xlab("Variance") +
  theme_classic() -> p1

results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=errors_pop*ms, fill=g_l)) +
  geom_histogram(bins=20) + 
  xlab("Error") +
  theme_classic() -> p2

results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc*mV, fill=g_l)) +
  geom_histogram(bins=20) +
  xlab("Vc (volt)") +
  theme_classic() -> p3

results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_comp*mV, fill=g_l)) +
  geom_histogram(bins=20) +
  xlab("Vo (volt)") +
  theme_classic() -> p4

grid.arrange(p1, p2, p3, p4, nrow=2)
rm(p1, p2, p3, p4)
```

# As

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=As*1e9, y=V_osc*mV, color=g_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc*mV, y=n_spikes_pop - n_spikes_ref, color=g_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc * mV, y=variances_pop*ms, color=g_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```
```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms, color=g_l)) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc * mV, y=errors_pop*ms, color=g_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors_pop*ms, color=g_l)) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=g_l)) +
  geom_point(size=.05) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

### 2019-05-21 voltagebudget/analysis/exp107_analysis.Rmd
exp106/107 analysis notebooks

---
title: "Sweep A - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)
library(gridExtra)
library(readr)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}

mV <- 1000
ms <- 1000
```

# Load and process

```{r, message=FALSE}
exp <- "107"
V_ls <- c("-70e-3", "-72e-3", "-74e-3", "-76e-3", "-78e-3", "-80e-3")

results <- NULL
for(V_l in V_ls){
  name <- paste("../../data/exp", exp, "_V_l", V_l, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df %>%
    filter(n_spikes > 0) -> df

  df$V_l <- rep(V_l, nrow(df))
  results <- rbind(results, df)
}
results$V_l <- factor(results$V_l, levels=V_ls)

results %>% 
  filter(n_spikes_ref > 0) %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results

# -
rm(df, exp, V_l, V_ls, name)
```

# Overall distributions

```{r, fig.width=2.75, fig.height=2}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=variances_pop*ms, fill=V_l)) +
  geom_histogram(bins=20, alpha=1) + 
  xlab("Variance") +
  theme_classic() -> p1

results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=errors_pop*ms, fill=V_l)) +
  geom_histogram(bins=20) + 
  xlab("Error") +
  theme_classic() -> p2

results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc*mV, fill=V_l)) +
  geom_histogram(bins=20) +
  xlab("Vc (volt)") +
  theme_classic() -> p3

results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_comp*mV, fill=V_l)) +
  geom_histogram(bins=20) +
  xlab("Vo (volt)") +
  theme_classic() -> p4

grid.arrange(p1, p2, p3, p4, nrow=2)
rm(p1, p2, p3, p4)
```

# As

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=As*1e9, y=V_osc*mV, color=V_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc*mV, y=n_spikes_pop - n_spikes_ref, color=V_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc * mV, y=variances_pop*ms, color=V_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```
```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms, color=V_l)) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc * mV, y=errors_pop*ms, color=V_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors_pop*ms, color=V_l)) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=V_l)) +
  geom_point(size=.05) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

### 2019-05-21 voltagebudget/analysis/paper_figures_redraft.Rmd
redraft fig WIP

@@
     variances = mean(variances)) -> fig9
-
-# --------------------------------------------------------------------
-# Load weight exps
-# Osc
-freq <- "20"
-
-# Init
-fig10 <- NULL
-
-# high w
-exp <- "100"
-name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
-df <- read_csv(paste(name, sep=","))
-df$weight <- rep(2.48e-08, nrow(df))
-fig10 <- rbind(df, fig10)
-
-# Ref (Z=0)
-exp <- "96"
-name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
-df <- read_csv(paste(name, sep=","))
-df$weight <- rep(8.25e-09, nrow(df))
-fig10 <- rbind(df, fig10)
-
-# low w
-exp <- "99"
-name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
-df <- read_csv(paste(name, sep=","))
-df$weight <- rep(1.65e-09, nrow(df))
-fig10 <- rbind(df, fig10)
-
-# Process
-fig10 %>% 
-  filter(n_spikes_ref > 0) %>% 
-  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
-  mutate(V_osc = V_osc - V_osc_ref) -> fig10
-
-# Summarize over As 
-fig10 %>% 
-  group_by(As, weight) %>% 
-  summarise(
-    N = 0,
-    delta_spikes = mean(delta_spikes), 
-    V_b = mean(V_b), 
-    V_osc = mean(V_osc), 
-    V_comp = mean(V_comp), 
-    V_comp_ref = mean(V_comp_ref), 
-    n_spikes_pop = mean(n_spikes), 
-    errors = mean(errors), 
-    errors_pop = mean(errors_pop), 
-    variances_pop = mean(variances_pop), 
-    variances = mean(variances)) -> fig11
 

### 2019-05-21 voltagebudget/analysis/exp107_analysis.Rmd
Added E_50 detection (test)

@@
 library(readr)
+library(NNTbiomarker)
 
 normalize <- function(x) {
-    return ((x - min(x)) / (max(x) - min(x)))
+    return((x - min(x)) / (max(x) - min(x)))
+}
+
+find_point <- function(x, y, point){
+  i <- argmin(x, target = point)
+  return(c(x[i], y[i]))
 }
@@
 rm(df, exp, V_l, V_ls, name)
+```
+
+```{r}
+tmp <- filter(results, V_l == "-70e-3", N == 1, V_osc/V_comp < 5)
+pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)
 ```
@@
 # As
-
 ```{r, fig.width=1.5, fig.height=1.5}
@@
 
-```{r, fig.width=1.5, fig.height=1.5}
-results %>% 
-  filter(N == 1, V_osc/V_comp < 5) %>% 
-  ggplot(aes(x=V_osc*mV, y=n_spikes_pop - n_spikes_ref, color=V_l)) +
-  geom_line() + 
-  theme_classic() +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-
+# Variance
 ```{r, fig.width=1.5, fig.height=1.5}
@@
 ```
+
 ```{r, fig.width=1.5, fig.height=1.5}
 results %>% 
+  filter(V_l %in% c("-70e-3", "-72e-3", "-74e-3", "-76e-3")) %>% 
   filter(N == 1, V_osc/V_comp < 5) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms, color=V_l)) +
+  group_by(V_l) %>% 
+  mutate(variances_pop=normalize(variances_pop)) %>% 
+  mutate(errors_pop=normalize(errors_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances_pop, color=V_l)) +
   geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
@@
 
+# Error
 ```{r, fig.width=1.6, fig.height=1.6}
@@
 results %>% 
+  filter(V_l %in% c("-70e-3", "-72e-3", "-74e-3", "-76e-3")) %>% 
+  filter(N == 1, V_osc/V_comp < 5) %>% 
+  group_by(V_l) %>% 
+  mutate(variances_pop=normalize(variances_pop)) %>% 
+  mutate(errors_pop=normalize(errors_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors_pop, color=V_l)) +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+# Ratio ests
+```{r}
+ratios <- NULL
+for (V in c("-70e-3", "-72e-3", "-74e-3", "-76e-3")){
+  tmp <- filter(results, V_l == V, N == 1, V_osc/V_comp < 5)
+  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
+  row <- c(pnts, as.numeric(V))
+  ratios <- rbind(ratios, row)
+}
+ratios <- as.data.frame(ratios, stringsAsFactors=FALSE)
+colnames(ratios) <- c("error_50", "ratio", "V_l")
+# Get ratio
+
+ratios %>% 
+  ggplot(aes(x=V_l, ratio)) + 
+  geom_point() + 
+  theme_classic()
+```
+
+# Trade off
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
   filter(N == 1, V_osc/V_comp < 5) %>% 
@@
 ```
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(N == 1, V_osc/V_comp < 5) %>% 
+  group_by(V_l) %>% 
+  filter(V_l %in% c("-70e-3", "-72e-3", "-74e-3", "-76e-3")) %>% 
+  mutate(errors_pop = normalize(errors_pop)) %>%
+  mutate(variances_pop = normalize(variances_pop)) %>%
+  ggplot(aes(x=variances_pop, y=errors_pop, color=V_l)) +
+  geom_point(size=.05) + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```

### 2019-05-21 voltagebudget/analysis/paper_figures_redraft.Rmd
WIP

@@
 # The trade off
-
-```{r, fig.width=1.7, fig.height=2.8}
-# Var
+```{r, fig.width=2, fig.height=4}
+# By freq
 fig2 %>% 
   filter(V_osc/V_comp <= 5) %>%
-  ggplot(aes(x=V_osc*mV, variances_pop*ms, group=freq)) +
-  geom_point(size=.2, alpha=0.5) +
+  ggplot(aes(x=V_osc*mV, errors_pop*ms, group=freq, color=freq)) +
+  geom_line(size=.5, alpha=0.8) +
+  scale_colour_continuous("Freq.", low="lightsalmon1", high="orange4") +
+  xlab(expression(paste(V[o], " (mV)"))) +
+  ylab("Error (ms)") +
+  theme_classic() +
+  theme(legend.position="none") -> p1
+fig2 %>% 
+  filter(V_osc/V_comp <= 5) %>%
+  ggplot(aes(x=V_osc*mV, variances_pop*ms, group=freq, color=freq)) +
+  geom_line(size=.5, alpha=0.8) +
+  scale_colour_continuous("Freq.", low="lightsalmon1", high="orange4") +
   xlab(expression(paste(V[o], " (mV)"))) +
   ylab("Variance (ms)") +
-  theme_classic() -> p1
+  theme_classic() +
+  theme(
+    legend.position=c(0.4, 1.5),
+    legend.direction="horizontal",    
+    legend.key.size = unit(.5, "cm"),
+    legend.key.height=unit(0.3,"cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8),
+    legend.background = element_rect(colour ="black")) -> p2
+
+# Norm
 fig2 %>% 
   filter(V_osc/V_comp <= 5) %>%
-  ggplot(aes(x=V_osc/V_comp, variances_pop*ms, group=freq)) +
-  geom_point(size=.2, alpha=0.5) +
-  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  group_by(freq, N) %>%
+  mutate(errors_pop = normalize(errors_pop)) %>%
+  mutate(variances_pop = normalize(variances_pop)) %>%
+  ggplot(aes(x=V_osc/V_comp, errors_pop, group=freq)) +
+  geom_line(size=.5, alpha=0.5) +
+  geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
   xlab(expression(V[o]/V[c])) +
-  ylab("Variance (ms)") +
-  theme_classic() -> p2
-
-# Error
-fig2 %>% 
-  filter(V_osc/V_comp <= 5) %>%
-  ggplot(aes(x=V_osc*mV, errors_pop*ms, group=freq)) +
-  geom_point(size=.2, alpha=0.5) +
-  xlab(expression(paste(V[o], " (mV)"))) +
-  ylab("Error (ms)") +
+  ylab("Norm. error") +
   theme_classic() -> p3
@@
   filter(V_osc/V_comp <= 5) %>%
-  ggplot(aes(x=V_osc/V_comp, errors_pop*ms, group=freq)) +
-  geom_point(size=.2, alpha=0.5) +
-  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  group_by(freq, N) %>%
+  mutate(errors_pop = normalize(errors_pop)) %>%
+  mutate(variances_pop = normalize(variances_pop)) %>%
+  ggplot(aes(x=V_osc/V_comp, variances_pop, group=freq)) +
+  geom_line(size=.5, alpha=0.5) +
   xlab(expression(V[o]/V[c])) +
-  ylab("Error (ms)") +
+  ylab("Norm. variance") +
   theme_classic() -> p4
+
+# Budget
+fig2 %>% 
+  filter(V_osc/V_comp <= 5) %>%
+  group_by(freq, N) %>%
+  mutate(errors_pop = normalize(errors_pop)) %>%
+  mutate(variances_pop = normalize(variances_pop)) %>%
+  ggplot(aes(x=V_osc/V_comp, errors_pop, group=freq)) +
+  geom_line(size=.5, alpha=0.5) +
+
+  # Arrow
+  # geom_segment(aes(x = 0.27, y = 0.5, xend = -.1, yend = 0.5), 
+  #              color="darkslategray3", linetype="solid", size=.3,
+  #              lineend = "round", linejoin = "round",
+  #              arrow = arrow(length = unit(0.06, "npc"))) +
+  # geom_segment(aes(x = .27, y = .5, xend = 0.27, yend = 0), 
+  #              color="darkslategray3", linetype="solid", size=.3,
+  #              lineend = "round", linejoin = "round",
+  #              arrow = arrow(length = unit(0.06, "npc"))) +
+
+  # X
+  # geom_point((aes(x=0.27, y=0.5)), color="grey", size=3, shape=4, alpha=0.6) +
+
+  # Line
+  geom_vline(xintercept = 0.27, alpha=0.8, color="darkslategray3", linetype="solid") +
+  xlab(expression(V[o]/V[c])) +
+  ylab("Norm. error") +
+  theme_classic() -> p5
+fig2 %>% 
+  filter(V_osc/V_comp <= 5) %>%
+  group_by(freq, N) %>%
+  mutate(errors_pop = normalize(errors_pop)) %>%
+  mutate(variances_pop = normalize(variances_pop)) %>%
+  ggplot(aes(x=V_osc/V_comp, variances_pop, group=freq)) +
+  geom_line(size=.5, alpha=0.5) +
+
+  # Arrow
+  # geom_segment(aes(x = 0.28, y = 0.28, xend = -0.1, yend = 0.28), 
+  #              color="darkslategray3", linetype="solid", size=.3,
+  #              lineend = "round", linejoin = "round",
+  #              arrow = arrow(length = unit(0.06, "npc"))) +
+  # geom_segment(aes(x = .27, y = .28, xend = 0.27, yend = 0.0), 
+  #              color="darkslategray3", linetype="solid", size=.3,
+  #              lineend = "round", linejoin = "round",
+  #              arrow = arrow(length = unit(0.06, "npc"))) +
+
+  # Line
+  geom_vline(xintercept = 0.27, alpha=0.8, color="darkslategray3", linetype="solid") +
+  xlab(expression(V[o]/V[c])) +
+  ylab("Norm. variance") +
+  theme_classic() -> p6
 
@@
   filter(V_osc/V_comp <= 5) %>%
-  ggplot(aes(x=variances_pop*ms, errors_pop*ms, group=freq, color=state)) +
-  geom_point(size=.2, alpha=0.9) +
-  xlab("Variance (ms)") +
-  ylab("Error (ms)") +
+  group_by(freq, N) %>%
+  mutate(errors_pop = normalize(errors_pop)) %>%
+  mutate(variances_pop = normalize(variances_pop)) %>%
+  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
+  geom_point(size=.8, alpha=0.8) +
+  xlab("Norm. variance") +
+  ylab("Norm. error") +
   scale_color_manual("", values=c("darkslategray3", "darkslategray")) +
-  theme_classic() -> p5
+  theme_classic() -> p7
 
@@
   c(NA, NA, NA, NA),
-  c(1, 1, 3, 3), 
-  c(1, 1, 3, 3),
-  c(1, 1, 3, 3),
-  c(1, 1, 3, 3),
   c(NA, NA, NA, NA),
-  c(2, 2, 4, 4),
-  c(2, 2, 4, 4),
-  c(2, 2, 4, 4),
-  c(2, 2, 4, 4),
+  c(1, 1, 2, 2), 
+  c(1, 1, 2, 2),
+  c(1, 1, 2, 2),
+  c(1, 1, 2, 2),
   c(NA, NA, NA, NA),
-  c(5, 5, 5, 5),
-  c(5, 5, 5, 5),
-  c(5, 5, 5, 5),
-  c(5, 5, 5, 5),
-  c(5, 5, 5, 5),
-  c(5, 5, 5, 5))
+  c(3, 3, 4, 4),
+  c(3, 3, 4, 4),
+  c(3, 3, 4, 4),
+  c(3, 3, 4, 4),
+  c(NA, NA, NA, NA),
+  c(5, 5, 6, 6),
+  c(5, 5, 6, 6),
+  c(5, 5, 6, 6),
+  c(5, 5, 6, 6),
+  c(NA, NA, NA, NA),
+  c(7, 7, 7, 7),
+  c(7, 7, 7, 7),
+  c(7, 7, 7, 7),
+  c(7, 7, 7, 7),
+  c(7, 7, 7, 7),
+  c(7, 7, 7, 7),
+  c(7, 7, 7, 7))
 
-grid.arrange(p1, p2, p3, p4, p5, layout_matrix=plot_grid)
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix=plot_grid)
 ```
 
-By looking at the ratio we identified a narrow region (V_o/V_c ~< 0.27) where the trade-off is approx linear across freq, and that accounts for approx.
-half the total change in both variance and error.
-We hypothesize that this narrow region can be considered a healthy range for modulation as it is maximially sensitive (has the highest dirvative) and is approx.
-linear--representing the best possible trade-off irregardless of freq.
+Error below 0.5 implies the result contains a majority of the reference.
+Beyond 0.5, the modulator dominates spiking.
+This means 0.5 serves as natural boundry to seperate oscillations that modulate other activity, and oscillations that activity.
+The ratio at 0.5 error is V_o/V_c = 0.27.
+This point turns out to several interesting features.
+It is where the trade-off is approx linear across freq, and where the trade-off is most stable.
+
+We hypothesize that this narrow region of budget ratio can be considered a healthy range for modulation as it, let's comp dom, is maximially sensitive (has the highest dirvative) and is approx.
+linear is maximmally consistent--representing the best possible trade-off irregardless of freq.
 
@@
 # Vc and sync
-```{r, fig.width=1.4, fig.height=1}
+```{r, fig.width=1.4, fig.height=0.8}
 fig2 %>% 
-  # filter(V_osc/V_comp <= ) %>%
-  ggplot(aes(x=V_comp*mV, variances_pop*ms, color=V_osc*mV)) +
+  filter(V_osc/V_comp <= 5) %>%
+  group_by(freq, N) %>% 
+  mutate(errors_pop = normalize(errors_pop)) %>%
+  mutate(variances_pop = normalize(variances_pop)) %>%
+  ggplot(aes(x=V_comp*mV, variances_pop, color=V_osc*mV)) +
   geom_point(size=.2, alpha=0.5) +
   xlab(expression(paste(V[c], " (mV)"))) +
-  ylab("Variance (ms)") +
-  scale_color_gradient(expression(paste(V[o], " (mV)")), low="goldenrod1", high="firebrick3") +
+  ylab("Norm. variance") +
+  scale_color_gradient(expression(paste(V[o], " (mV)")), low="darkgrey", high="firebrick3") +
   theme_classic() +
-  theme(legend.key.width=unit(0.3,"cm"),
+  theme(legend.key.height=unit(0.3,"cm"),
+        legend.key.width=unit(0.3,"cm"),
+        legend.background = element_rect(colour ="black"),
         legend.title=element_text(size=8),
@@
 
-# Freq. dependence
-```{r, fig.width=0.65, fig.height=2.5}
-fig2 %>% 
-filter(V_osc/V_comp <= 5) %>%
-  ggplot(aes(x=variances_pop*ms, errors_pop*ms, group=freq)) +
-  geom_point(size=.2, alpha=0.9) +
-  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
-  scale_y_continuous(breaks=c(0,30,60)) +
-  xlab("Variance (ms)") +
-  ylab("Error (ms)") +
-  facet_grid(freq~.) +
-  theme_classic() +
-  theme(strip.text.y = element_text(angle=0), strip.background = element_blank())
-```
-
-```{r, fig.width=0.65, fig.height=2.5}
-fig2 %>% 
-  filter(V_osc/V_comp <= 0.8) %>%
-  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms)) +
-  geom_point(size=.2, alpha=0.5) +
-  facet_grid(freq~.) +
-  xlab(expression(V[o]/V[c])) +
-  ylab("Variance (ms)") +
-  scale_y_continuous(breaks=c(7.5,8,8.5,9)) +
-  scale_x_continuous(breaks=c(0,0.4,0.8)) +
-  # geom_rect(
-  #   mapping=aes(xmin=0.15, xmax=0.4, ymin=min(variances_pop*ms), ymax=max(variances_pop*ms)),
-  #   color="darkslategray4", fill="darkslategray4", alpha=0.02) +
-  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
-  theme_classic() +
-  theme(strip.text.y = element_text(angle=0), strip.background = element_blank())
-```
-
-Fo far we've focused on error-variance relationships common between frequencies. Frequency also effect error-variance trade off.
-
-...
-
-Faster oscillations offer less sync overall, and therefore have a more limited var-error range than slower oscillations.
-If we use the curveture of the variance curve to fine tune the healthy ratio / frequency, we see that...
-
-TODO: get max second deriv. Use that to find the change point?
-TODO: plot max second derive ration point by freq. How does the healthy boundry scale with freq?
-
-Slower oscillations have a wider working range, than faster oscillations. If doing stimulation experiments, once must also consider your freqeuncy carefully.
-
 # Controls - Ws, noise, cell type
-TODO
-
-## Heterocells
-
-```{r, fig.width=0.5, fig.height=1.4}
+```{r, fig.width=2.1, fig.height=1.5}
+# --------------------------------------------------
 fig14 %>% 
@@
     plot.background=element_blank()) -> p1
-plot(p1)
-```
 
-```{r, fig.width=2.1, fig.height=1.5}
-# --------------------------------------------------
 # Cell type
@@
 
-```{r, fig.width=1.1, fig.height=2}
+```{r, fig.width=1.1, fig.height=3}
 ms <- 1e3

### 2019-05-21 voltagebudget/analysis/exp106_analysis.Rmd
WIP

@@
 exp <- "106"
-g_ls <- c("10e-9", "12e-9", "14e-9")
+g_ls <- c("10e-9", "12e-9", "14e-9", "16e-9")
 
@@
 
+# Variance
 ```{r, fig.width=1.5, fig.height=1.5}
@@
   filter(N == 1, V_osc/V_comp < 5) %>% 
-  ggplot(aes(x=V_osc*mV, y=n_spikes_pop - n_spikes_ref, color=g_l)) +
+  ggplot(aes(x=V_osc * mV, y=variances_pop*ms, color=g_l)) +
   geom_line() + 
@@
   filter(N == 1, V_osc/V_comp < 5) %>% 
-  ggplot(aes(x=V_osc * mV, y=variances_pop*ms, color=g_l)) +
-  geom_line() + 
-  theme_classic() +
-  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
-  theme(legend.position="bottom") 
-```
-```{r, fig.width=1.5, fig.height=1.5}
-results %>% 
-  filter(N == 1, V_osc/V_comp < 5) %>% 
-  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms, color=g_l)) +
+  group_by(g_l) %>% 
+  mutate(variances_pop=normalize(variances_pop)) %>% 
+  mutate(errors_pop=normalize(errors_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances_pop, color=g_l)) +
   geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
@@
   filter(N == 1, V_osc/V_comp < 5) %>% 
+  group_by(g_l) %>% 
+  mutate(variances_pop=normalize(variances_pop)) %>% 
+  mutate(errors_pop=normalize(errors_pop)) %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors_pop, color=g_l)) +
+  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  geom_line() + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```
+
+# Ratio ests
+```{r, fig.width=1}
+ratios <- NULL
+for (V in c("10e-9", "12e-9", "14e-9")) {
+  tmp <- filter(results, g_l == V, N == 1, V_osc/V_comp < 5)
+  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
+  row <- c(pnts, as.numeric(V))
+  ratios <- rbind(ratios, row)
+}
+ratios <- as.data.frame(ratios, stringsAsFactors=FALSE)
+colnames(ratios) <- c("error_50", "ratio", "g_l")
+# Get ratio
+
+ratios %>% 
+  ggplot(aes(x=g_l*1e9, ratio)) + 
+  geom_point() + 
+  theme_classic()
+```
+
+# Trade off
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(N == 1, V_osc/V_comp < 5) %>% 
   ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=g_l)) +
@@
 ```
+
+```{r, fig.width=1.5, fig.height=1.5}
+results %>% 
+  filter(N == 1, V_osc/V_comp < 5) %>% 
+  group_by(g_l) %>% 
+  mutate(errors_pop = normalize(errors_pop)) %>%
+  mutate(variances_pop = normalize(variances_pop)) %>%
+  ggplot(aes(x=variances_pop, y=errors_pop, color=g_l)) +
+  geom_point(size=.05) + 
+  theme_classic() +
+  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
+  theme(legend.position="bottom") 
+```

### 2019-05-21 voltagebudget/analysis/exp107_analysis.Rmd
WIP

@@
 # Ratio ests
-```{r}
+```{r, fig.width=1}
 ratios <- NULL
@@
 ratios %>% 
-  ggplot(aes(x=V_l, ratio)) + 
+  ggplot(aes(x=V_l*mV, ratio)) + 
   geom_point() + 

### 2019-05-21 voltagebudget/analysis/paper_figures_redraft.Rmd
WIP

@@
     variances = mean(variances)) -> fig2
+
+# Ratio ests
+fig2_ratios <- NULL
+freqs <- unique(fig2$freq)
+for (f in freqs) {
+  tmp <- filter(fig2, f == freq, V_osc/V_comp < 5)
+  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
+  row <- c(pnts, f)
+  fig2_ratios <- rbind(fig2_ratios, row)
+}
+fig2_ratios <- as.data.frame(fig2_ratios, stringsAsFactors=FALSE)
+colnames(fig2_ratios) <- c("error_50", "ratio", "freq")
 
@@
 # The trade off
-```{r, fig.width=2, fig.height=4}
+```{r, fig.width=2, fig.height=5}
 # By freq
@@
   theme(
-    legend.position=c(0.4, 1.5),
+    legend.position=c(0.45, 1.5),
     legend.direction="horizontal",    
@@
   geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
+  annotate("text", x = 4, y = 0.65, label = expression(paste("E"[50]))) +
   xlab(expression(V[o]/V[c])) +
@@
 
-  # Arrow
-  # geom_segment(aes(x = 0.27, y = 0.5, xend = -.1, yend = 0.5), 
-  #              color="darkslategray3", linetype="solid", size=.3,
-  #              lineend = "round", linejoin = "round",
-  #              arrow = arrow(length = unit(0.06, "npc"))) +
-  # geom_segment(aes(x = .27, y = .5, xend = 0.27, yend = 0), 
-  #              color="darkslategray3", linetype="solid", size=.3,
-  #              lineend = "round", linejoin = "round",
-  #              arrow = arrow(length = unit(0.06, "npc"))) +
-
-  # X
-  # geom_point((aes(x=0.27, y=0.5)), color="grey", size=3, shape=4, alpha=0.6) +
-
   # Line
-  geom_vline(xintercept = 0.27, alpha=0.8, color="darkslategray3", linetype="solid") +
+  geom_vline(xintercept = 0.2858, alpha=0.8, color="darkslategray3", linetype="solid") +
   xlab(expression(V[o]/V[c])) +
@@
 
-  # Arrow
-  # geom_segment(aes(x = 0.28, y = 0.28, xend = -0.1, yend = 0.28), 
-  #              color="darkslategray3", linetype="solid", size=.3,
-  #              lineend = "round", linejoin = "round",
-  #              arrow = arrow(length = unit(0.06, "npc"))) +
-  # geom_segment(aes(x = .27, y = .28, xend = 0.27, yend = 0.0), 
-  #              color="darkslategray3", linetype="solid", size=.3,
-  #              lineend = "round", linejoin = "round",
-  #              arrow = arrow(length = unit(0.06, "npc"))) +
-
   # Line
-  geom_vline(xintercept = 0.27, alpha=0.8, color="darkslategray3", linetype="solid") +
+  geom_vline(xintercept = 0.2858, alpha=0.8, color="darkslategray3", linetype="solid") +
   xlab(expression(V[o]/V[c])) +
@@
 tmp$state <- rep("pathological", nrow(tmp))
-m <- tmp$V_osc/tmp$V_comp < 0.27
+m <- tmp$V_osc/tmp$V_comp < 0.2858
 tmp$state[m] <- "healthy"
@@
 
+print(summary(fig2_ratios$ratio))
+fig2_ratios %>% 
+  ggplot(aes(x=freq, y=ratio)) +
+  geom_point(color="darkslategray3", size=1.6) +
+  xlab("Freq (Hz)") +
+  geom_hline(yintercept = mean(fig2_ratios$ratio), alpha=0.8, color="darkslategray3", linetype="solid") +
+  ylab(expression(paste(V[o]/V[c], " at E"[50]))) +
+  theme_classic() +
+  ylim(0, 1) -> p8
+
 plot_grid <- rbind(
@@
   c(3, 3, 4, 4),
+  c(NA, NA, NA, NA),
+  c(8, 8, 8, NA),
+  c(8, 8, 8, NA),
+  c(8, 8, 8, NA),
+  c(8, 8, 8, NA),
   c(NA, NA, NA, NA),
@@
 
-grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix=plot_grid)
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=plot_grid)
 ```
@@
 This is useful both in analyzing for patholigical acitivty, but also in desgining optogenetic and other stimulation experiments.
-You should scale your oscillatory manipulation be no more the 0.27 times as strong as the average membrane potential observed in vivo, without stimulation.
+You should scale your oscillatory manipulation be no more the 0.2858 times as strong as the average membrane potential observed in vivo, without stimulation.
 
@@
   geom_point(size=.1, alpha=0.4) +
-  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  geom_vline(xintercept = 0.2858, alpha=1, color="darkslategray3", linetype="solid") +
   labs(x=expression(V[o]/V[c]), y="Norm. error", title="Cell type") +
@@
   geom_point(size=.1, alpha=0.4) +
-  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  geom_vline(xintercept = 0.2858, alpha=1, color="darkslategray3", linetype="solid") +
   theme_classic() +
@@
   geom_point(size=.1, alpha=0.4) +
-  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  geom_vline(xintercept = 0.2858, alpha=1, color="darkslategray3", linetype="solid") +
   labs(x=expression(V[o]/V[c]), y="Norm. error") +
@@
   geom_point(size=.1, alpha=0.4) +
-  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
+  geom_vline(xintercept = 0.2858, alpha=1, color="darkslategray3", linetype="solid") +
   labs(x=expression(V[o]/V[c]), y="Norm. variance") +

### 2019-06-19 voltagebudget/exp/optimal.py
FIX bug in opt. coincidence alg

@@ -11,38 +11,34 @@ from voltagebudget.plc import uniform
 from voltagebudget.plc import coincidence
 
 from voltagebudget.util import mae
+from voltagebudget.util import mad
 
+# # -
+# def _run(ts, target, fn, verbose=False):
+#     # init
+#     initial_variances = []
+#     target_variances = []
+#     obs_variances = []
+#     errors = []
 
-# -
-def _run(ts, changes, fn, verbose=False):
-    # init
-    initial_variances = []
-    target_variances = []
-    obs_variances = []
-    errors = []
+#     # run of changes
+#     for c in changes:
+#         if verbose:
+#             print(">>> Running c {}".format(c))
 
-    # run of changes
-    for c in changes:
-        if verbose:
-            print(">>> Running c {}".format(c))
+#         obs_variances.append(obs)
+#         initial_variances.append(initial)
+#         target_variances.append(target)
+#         errors.append(err)
 
-        initial, target, obs, ts_opt = fn(ts, c)
-        err = mae(ts, ts_opt)
+#     results = [obs_variances, initial_variances, target_variances, errors]
 
-        obs_variances.append(obs)
-        initial_variances.append(initial)
-        target_variances.append(target)
-        errors.append(err)
-
-    results = [obs_variances, initial_variances, target_variances, errors]
-
-    return results
+#     return results
 
 
 def optimal(name,
             stim,
-            p_0,
-            p_max,
+            var_target,
             alg='max_deviants',
             n_samples=100,
             verbose=False,
@@ -57,7 +53,7 @@ def optimal(name,
     if alg == 'max_deviants':
         fn = max_deviant
     elif alg == 'left_deviants':
-        fn = lambda x, p: max_deviant(x, p, side='left')
+        fn = lambda ts, intial, target: max_deviant(ts, intial, target, side='left')
     elif alg == 'uniform':
         fn = uniform
     elif alg == 'coincidence':
@@ -72,14 +68,30 @@ def optimal(name,
     ns = np.asarray(stim_data['ns'])
     ts = np.asarray(stim_data['ts'])
 
+    var_ref = mad(ts)
+
     # --------------------------------------------------------------
     # Run plc!
     if verbose:
         print(">>> Running {}.".format(alg))
 
-    changes = np.linspace(p_0, p_max, n_samples)
-    (obs_variances, initial_variances, target_variances, errors) = _run(
-        ts, changes, fn, verbose=verbose)
[…]

### 2019-06-19 voltagebudget/plc.py

@@ -59,11 +59,23 @@ def _diffs(ts):
     return np.asarray(ds)
 
 
-def coincidence(ts, initial, target):
+def _find_value(x, array):
+    array = np.asarray(array)
+    idx = (np.abs(array - x)).argmin()
+    return idx
+
+
+def coincidence(ts, initial, target, min_distance=1e-6, max_iterations=1000):
     """Coordinate by increasing coincidences.
     
-    An approach inspired by neural oscillations.
+    This is the optimal policy to minimize the minimum
+    description length (MDL). 
+    
+    https://en.wikipedia.org/wiki/Minimum_description_length
     """
+
+    if np.isclose(initial, target):
+        return initial, initial, initial, ts
 
     # Init
     ts = np.asarray(ts)
@@ -73,22 +85,37 @@ def coincidence(ts, initial, target):
     # Prelim...
     ts = np.sort(ts)
 
-    # Est the seq. differences between ts,
-    # and index their order.
-    i = np.argmin(_diffs(ts))
-
     # -
     # Shift closest spikes (smallest deltas)
     # to be the same until target MAD is achieved.
+    N = ts.size
     ts_opt = ts.copy()
     adjusted = initial
-    while adjusted > target:
+
+    n = 0
+    while (adjusted >= target) and (n < max_iterations):
+        # Find distances
+        deltas = _diffs(ts_opt)
+
+        # Must be not already a coincidence
+        deltas[deltas > min_distance] = np.nan
+        # print(deltas > min_distance)
+
+        # Find smallest distance
+        i = np.nanargmin(deltas)
+
+        # Shift
+        # Est the seq. differences between ts,
+        # and index their order.
+        # Note: nans are last in argsort.
         ts_opt[i + 1] = ts_opt[i]
 
+        # Update stats/counters
         adjusted = mad(ts_opt)
 
-        i = np.argmin(_diffs(ts_opt))
+        n += 1
 
+    print(initial, target, adjusted, np.asarray(ts_opt))
     return initial, target, adjusted, np.asarray(ts_opt)
 
 

### 2019-06-19 voltagebudget/exp/sweep_A.py
Expose coincidence alg to opt_sweep_A

@@ -29,6 +29,7 @@ from voltagebudget.util import find_E
 from voltagebudget.util import find_phis
 from voltagebudget.plc import max_deviant
 from voltagebudget.plc import uniform
+from voltagebudget.plc import coincidence
 
 
 def sweep_A(name,
@@ -532,6 +533,8 @@ def optimal_sweep_A(name,
                 dt=dt)
         elif optimal_method == 'uniform':
             _, _, var_opt, ts_opt = uniform(ts_ref, var_ref, var_pop)
+        elif optimal_method == 'coincidence':
+            _, _, var_opt, ts_opt = coincidence(ts_ref, var_ref, var_pop)
         else:
             raise ValueError("Otimmal method not known")
 

### 2019-06-19 voltagebudget/analysis/optimal_analysis.Rmd
Update imports
Update test vis for coincidence alg

@@
 ```{r, message=FALSE}
-library(tidyverse)
+library(ggplot2)
+library(magrittr)
+library(readr)
 library(gridExtra)
@@
 library(scales)
+library(dplyr)
+library(NNTbiomarker)
 
@@
 }
+find_point <- function(x, y, point){
+  i <- argmin(x, target = point)
+  return(c(x[i], y[i]))
+}
+
 ```
@@
 # Load ref spikes
-ref <- read_csv("../data/stim1.csv")
+ref <- read_csv("../../data/stim1.csv")
 ref$set <- rep("reference", nrow(ref))
@@
 # Load exp spikes
-exps <- c(86, 87, 88, 89)
+# exps <- c(86, 87, 88, 89)
+exps <- c(110, 111, 112, 113)
 spikes <- NULL
 for (n in 1:4){
-  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], "_c0.2.csv", sep=""))
+  # df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_c0.2.csv", sep=""))
+  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_target0.01_spikes.csv", sep=""))
   df$set <- rep("experiment", nrow(df))
@@
 results %>% 
-  filter(alg != "coincidence") %>%
+  filter(alg != "left") %>%
   ggplot(aes(x=errors*1e3, y=obs_variances*1e3, linetype=alg)) +
   geom_line(size=0.6, alpha=0.9) +
-  scale_linetype_manual(values=c("longdash", "solid", "dotdash"), name="Algorithm") +
+  # scale_linetype_manual(values=c("longdash", "solid", "dotdash", "dot"), name="Algorithm") +
   theme_classic() +
@@
 spikes %>% 
-  filter(alg != "coincidence") %>%
+  filter(alg != "left") %>%
   ggplot(aes(x=ts, y=ns, color=set)) +
@@
 ```
+
+```{r, fig.width=1.5, fig.height=1.5}
+ spikes %>% 
+  filter(alg != "left") %>% 
+  filter(set == "experiment") %>%
+  ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
+  geom_point(size=2.3, alpha=1, shape=4) +
+  geom_point(
+    data=filter(filter(spikes, alg != "left"), set == "reference"),
+    mapping=aes(x=ts*1e3, y=ns), color="black", shape=1, alpha=1, size=1.2) +
+  facet_grid(alg~.) +
+  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3", "chartreuse3")) +
+  theme_classic() +
+  labs(x="Time (ms)", y="Neuron") +
+  theme(
+    legend.position="none", 
+    panel.border = element_rect(fill = NA, colour = "black"),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    strip.background = element_blank(),
+    strip.text.y = element_text(angle = 0))
+```

### 2019-06-19 voltagebudget/analysis/exp108_analysis.Rmd
WIP

--- 2019-05-21 voltagebudget/analysis/exp106_analysis.Rmd
@@
 ---
-title: "Sweep A - general experiment analysis."
+title: "exp108 - g_l sensitivity analysis."
 output: html_notebook
@@
 ```{r, message=FALSE}
-exp <- "106"
-g_ls <- c("10e-9", "12e-9", "14e-9", "16e-9")
+exp <- "108"
+g_ls <- c("1.0e-08", "1.05e-08", "1.1e-08", "1.15e-08", "1.2e-08")
 
@@
 # -
-rm(df, exp, g_l, g_ls, name)
+# rm(df, exp, g_l, g_ls, name)
 ```
@@
 ratios <- NULL
-for (V in c("10e-9", "12e-9", "14e-9")) {
+for (V in g_ls) {
   tmp <- filter(results, g_l == V, N == 1, V_osc/V_comp < 5)
@@
   geom_point() + 
-  theme_classic()
+  theme_classic() +
+  ylim(0, 1)
 ```

### 2019-06-20 voltagebudget/analysis/paper_figures_redraft.Rmd
Add dianostic plots for opt exps

@@
 library(readr)
+library(NNTbiomarker)
 
@@
   tbl %>% right_join(keep, by=grps) %>% group_by_(.dots = grps)
+}
+
+find_point <- function(x, y, point){
+  i <- argmin(x, target = point)
+  return(c(x[i], y[i]))
 }
@@
 alg_names <- c("max", "left", "uniform", "coincidence")
-exps <- c(82, 83, 84, 85)
+exps <- c(114, 115, 116, 117)
 
@@
 # Load exp spikes
-exps <- c(86, 87, 88, 89)
+exps <- c(110, 111, 112, 113)
 fig4 <- NULL
 for (n in 1:4){
-  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_c0.1_spikes.csv", sep=""))
+  # df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_c0.1_spikes.csv", sep=""))
+  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_target0.01_spikes.csv", sep=""))
   df$set <- rep("synchronized", nrow(df))
@@
 # Data
-exp <- "104"
+exp <- "118"
 freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")
@@
 
-exp <- "105"
+exp <- "119"
 freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")
@@
 
+# -
+exp <- "109"
+freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")
+
+fig18 <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  # df %>%
+    # filter(n_spikes_pop > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  fig18 <- rbind(fig18, df)
+}
+
+fig16$freq <- factor(fig16$freq, levels=freqs)
+
+# -
 fig15$alg <- rep("max", nrow(fig15))
 fig16$alg <- rep("uniform", nrow(fig16))
-fig17 <- rbind(fig15, fig16)
+fig18$alg <- rep("coincidence", nrow(fig18))
+fig17 <- rbind(fig15, fig16, fig18)
 # --------------------------------------------------------------------
@@
   ylab("Norm. error") +
-  scale_color_manual("", values=c("darkslategray3", "darkslategray")) +
-  theme_classic() -> p7
+  scale_color_manual("State", values=c("darkslategray3", "darkslategray")) +
+  theme_classic() +
+  theme(legend.background = element_rect(colour ="black")) -> p7
 
@@
   geom_point(color="darkslategray3", size=1.6) +
-  xlab("Freq (Hz)") +
+  xlab("Freq. (Hz)") +
   geom_hline(yintercept = mean(fig2_ratios$ratio), alpha=0.8, color="darkslategray3", linetype="solid") +
@@
 # Optimal derivation
-```{r, fig.width=1.3, fig.height=2}
+```{r, fig.width=1.3, fig.height=2.2}
 min_t <- min(fig4$ts)
@@
 fig4 %>% 
-  filter(alg != "coincidence", alg != "left") %>% 
+  filter(alg != "left") %>% 
   group_by(set, alg) %>% 
@@
   ggplot(aes(x=ts*1e3, y=ns, color=alg)) +
-  geom_point(size=2, alpha=1, shape=4) +
+  geom_point(size=2.3, alpha=1, shape=4) +
   geom_point(
@@
   facet_grid(alg~.) +
-  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3")) +
+  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3", "chartreuse3")) +
   theme_classic() +
@@
 fig3 %>% 
-  filter(alg != "coincidence", alg != "left") %>%
+  filter(alg != "left") %>%
+  filter(obs_variances > 10e-3) %>% 
   ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
-  geom_line(size=0.6, alpha=0.99) +
-  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3")) +
+  # geom_line(size=0.1, alpha=0.99) +
+  geom_point(size=1, alpha=0.99) +
+  scale_color_manual("Algorithm:", 
+                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
+                     guide = guide_legend(nrow = 3)) +
   theme_classic() +
@@
 
-```{r, fig.width=1.1, fig.height=3}
+```{r, fig.width=3, fig.height=2.8}
+
+hospital_names <- list(
+  '8'="Freq.\n\n8 Hz",
+  '12'="12 Hz",
+  '20'="20 Hz",
+  '30'="30 Hz"
+)
+hospital_labeller <- function(variable,value){
+  return(hospital_names[as.character(value)])
+}
+
 ms <- 1e3
@@
   geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
-             alpha=0.99, size=.2) +
+             alpha=0.99, size=0.4) +
   scale_y_continuous(trans='log10') +
   annotation_logticks(sides = "l") +
-  facet_grid(freq~.) +
-  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3")) +
+  facet_grid(freq~., labeller=hospital_labeller) +
+  scale_color_manual("Algorithm", 
+                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
+                     guide = guide_legend(nrow = 3)) +
   labs(x="Variance (ms)", y="Error (ms)") +
@@
   theme_classic() +
-  theme(legend.position="bottom",
+  theme(legend.position="right",
     legend.key.size = unit(.2, "cm"),
@@
     legend.key.width=unit(0.05,"cm"),
-    strip.background = element_blank()) 
+    strip.background = element_blank()) -> p1
+
+fig17 %>% 
+  filter(errors_pop > 0, freq %in% c("8")) %>%
+  ggplot(aes(x=variances_pop*ms, y=variances_opt*ms, color=alg)) +
+  geom_point(size=0.8, alpha=0.3) +
+  geom_abline(intercept = 0, color="black", alpha=1) +
+  labs(x="Obs. variance (ms)", y="Opt. variance (ms)") +
+  scale_color_manual("Algorithm:", 
+                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
+                     guide = "none") +
+  ggtitle("Freq. 8 Hz") +
+  theme_classic() -> p2
+
+fig17 %>% 
+  filter(errors_pop > 0, freq %in% c("8")) %>%
+  ggplot(aes(x=errors_pop*ms, y=errors_opt*ms, color=alg)) +
+  geom_point(size=0.8, alpha=0.5) +
+  lims(x=c(0,25),y=c(0,25)) +
+  geom_abline(intercept = 0, color="black", alpha=1) +
+  labs(x="Obs. error (ms)", y="Opt. error (ms)") +
+  scale_color_manual("Algorithm:", 
+                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
+                     guide = "none") +
+  ggtitle(" ") +
+  theme_classic() -> p3
+
+plot_grid <- rbind(
+  c(1, 1, 1, 2, 2),
+  c(1, 1, 1, 2, 2),
+  c(1, 1, 1, 3, 3),
+  c(1, 1, 1, 3, 3),
+  c(1, 1, 1, NA, NA))
+
+grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
+rm(p1, p2, plot_grid)
 ```
+
+```{r, fig.width=1.6, fig.height=0.9}
+
+```
+
+```{r, fig.width=1.5, fig.height=0.8}
+
+```

### 2019-06-20 voltagebudget/analysis/optimal_analysis.Rmd
Tweak  general opt. analysis notebook

@@
 alg_names <- c("max", "left", "uniform", "coincidence")
-exps <- c(82, 83, 84, 85)
+# exps <- c(82, 83, 84, 85)
+exps <- c(120, 121, 122, 123)
 
@@
 
+```{r, fig.width=1.4, fig.height=0.8}
+results %>% 
+  filter(alg != "left") %>%
+  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
+  geom_point(size=0.6, alpha=0.9) +
+  # scale_linetype_manual(values=c("longdash", "solid", "dotdash", "dot"), name="Algorithm") +
+  theme_classic() +
+  labs(x="Error (ms)", y="Variance (ms)")
+```
+
 ```{r, fig.width=1.0, fig.height=1.5}

### 2019-06-20 voltagebudget/analysis/paper_figures_redraft.Rmd
Tweak paper figs

@@
   # geom_line(size=0.1, alpha=0.99) +
-  geom_point(size=1, alpha=0.99) +
-  scale_color_manual("Algorithm:", 
+  geom_line(size=1, alpha=0.99) +
+  scale_color_manual("Algorithm", 
                      values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
@@
   geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
-             alpha=0.99, size=0.4) +
+             alpha=0.99, size=0.6) +
   scale_y_continuous(trans='log10') +
@@
                      guide = "none") +
-  ggtitle("Freq. 8 Hz") +
-  theme_classic() -> p2
+  ggtitle("            Freq. 8 Hz") +
+  theme_classic() +
+  theme(plot.title = element_text(size = 10)) -> p2
 

### 2019-06-21 voltagebudget/analysis/paper_figures_redraft.Rmd
Removed redundant panel from trade-off fig

@@
 # The trade off
-```{r, fig.width=2, fig.height=5}
+```{r, fig.width=2.2, fig.height=4}
 # By freq
@@
   theme_classic() -> p3
-fig2 %>% 
-  filter(V_osc/V_comp <= 5) %>%
-  group_by(freq, N) %>%
-  mutate(errors_pop = normalize(errors_pop)) %>%
-  mutate(variances_pop = normalize(variances_pop)) %>%
-  ggplot(aes(x=V_osc/V_comp, variances_pop, group=freq)) +
-  geom_line(size=.5, alpha=0.5) +
-  xlab(expression(V[o]/V[c])) +
-  ylab("Norm. variance") +
-  theme_classic() -> p4
+
+print(summary(fig2_ratios$ratio))
+fig2_ratios %>% 
+  ggplot(aes(x=freq, y=ratio)) +
+  geom_point(color="darkslategray3", size=1.6) +
+  xlab("Freq. (Hz)") +
+  geom_hline(yintercept = mean(fig2_ratios$ratio), alpha=0.8, color="darkslategray3", linetype="solid") +
+  ylab(expression(paste(V[o]/V[c], " at E"[50]))) +
+  theme_classic() +
+  ylim(0, 1) -> p4
+
+# fig2 %>% 
+#   filter(V_osc/V_comp <= 5) %>%
+#   group_by(freq, N) %>%
+#   mutate(errors_pop = normalize(errors_pop)) %>%
+#   mutate(variances_pop = normalize(variances_pop)) %>%
+#   ggplot(aes(x=V_osc/V_comp, variances_pop, group=freq)) +
+#   geom_line(size=.5, alpha=0.5) +
+#   xlab(expression(V[o]/V[c])) +
+#   ylab("Norm. variance") +
+#   theme_classic() -> p4
 
@@
   ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
-  geom_point(size=.8, alpha=0.8) +
+  geom_point(size=1.2, alpha=0.8) +
   xlab("Norm. variance") +
@@
   theme(legend.background = element_rect(colour ="black")) -> p7
-
-print(summary(fig2_ratios$ratio))
-fig2_ratios %>% 
-  ggplot(aes(x=freq, y=ratio)) +
-  geom_point(color="darkslategray3", size=1.6) +
-  xlab("Freq. (Hz)") +
-  geom_hline(yintercept = mean(fig2_ratios$ratio), alpha=0.8, color="darkslategray3", linetype="solid") +
-  ylab(expression(paste(V[o]/V[c], " at E"[50]))) +
-  theme_classic() +
-  ylim(0, 1) -> p8
 
@@
   c(NA, NA, NA, NA),
-  c(8, 8, 8, NA),
-  c(8, 8, 8, NA),
-  c(8, 8, 8, NA),
-  c(8, 8, 8, NA),
-  c(NA, NA, NA, NA),
   c(5, 5, 6, 6),
@@
 
-grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=plot_grid)
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix=plot_grid)
 ```

### 2019-06-21 voltagebudget/analysis/paper_figures_redraft.Rmd
Clarify and unify plot labels for paper figs

@@
   xlab(expression(paste(V[o], " (mV)"))) +
-  ylab("Error (ms)") +
+  ylab("Pop. error (ms)") +
   theme_classic() +
@@
   xlab(expression(paste(V[o], " (mV)"))) +
-  ylab("Variance (ms)") +
+  ylab("Pop. variance (ms)") +
   theme_classic() +
@@
   group_by(freq, N) %>% 
-  mutate(errors_pop = normalize(errors_pop)) %>%
-  mutate(variances_pop = normalize(variances_pop)) %>%
-  ggplot(aes(x=V_comp*mV, variances_pop, color=V_osc*mV)) +
+  mutate(errors = normalize(errors)) %>%
+  mutate(variances = normalize(variances)) %>%
+  ggplot(aes(x=V_comp*mV, variances, color=V_osc*mV)) +
   geom_point(size=.2, alpha=0.5) +
   xlab(expression(paste(V[c], " (mV)"))) +
-  ylab("Norm. variance") +
+  ylab("Norm. indiv.\nvariance") +
   scale_color_gradient(expression(paste(V[o], " (mV)")), low="darkgrey", high="firebrick3") +
@@
   geom_abline(intercept = 0, color="black", alpha=1) +
-  labs(x="Obs. variance (ms)", y="Opt. variance (ms)") +
+  labs(x="Pop. variance (ms)", y="Opt. variance (ms)") +
   scale_color_manual("Algorithm:", 
@@
   geom_abline(intercept = 0, color="black", alpha=1) +
-  labs(x="Obs. error (ms)", y="Opt. error (ms)") +
+  labs(x="Pop. error (ms)", y="Opt. error (ms)") +
   scale_color_manual("Algorithm:", 
@@
 ```
-
-```{r, fig.width=1.6, fig.height=0.9}
-
-```
-
-```{r, fig.width=1.5, fig.height=0.8}
-
-```

### 2019-07-03 voltagebudget/analysis/sparse_analysis.Rmd
Added gen. testing notebook for sparse A

---
title: "Optimal coordination - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(magrittr)
library(readr)
library(gridExtra)
library(readr)
library(scales)
library(dplyr)
library(NNTbiomarker)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
find_point <- function(x, y, point){
  i <- argmin(x, target = point)
  return(c(x[i], y[i]))
}

```

# Load and process

```{r, message=FALSE}
# Sparse
exp <- "124"
freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")

results <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  results <- rbind(results, df)
}
results$freq <- factor(results$freq, levels=freqs)

results %>% 
  filter(n_spikes_ref > 0) %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results

rm(tmp, df)

# --------------------------
# Dense
ref <- NULL

exp <- "96"
freqs <- c(20, 30)

for(freq in freqs){
  name <- paste("../../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

  df$freq <- rep(freq, nrow(df))
  ref <- rbind(ref, df)
}

# --------------------------
# SLOW
exp <- "94"
freqs <- c(6, 8, 10, 12, 14, 16, 18)

for(freq in freqs){
  name <- paste("../../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

  df$freq <- rep(freq, nrow(df))
  ref <- rbind(ref, df)
}

# --------------------------
# FAST
exp <- "95"
freqs <- c(22, 24, 26, 28)#, 32, 34 ,36, 38)
for(freq in freqs){
  name <- paste("../../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

  df$freq <- rep(freq, nrow(df))
  ref <- rbind(ref, df)
}

# Process
ref %>% 
  filter(n_spikes_ref > 0) %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> ref

rm(tmp, df)
```
```{r}
results %>% 
  ggplot(aes(x=As, y=variances_pop, color=freq)) +
  geom_point(size=0.1) +
  theme_classic()
```

```{r}
results %>% 
  ggplot(aes(x=As, y=errors_pop, color=freq)) +
  geom_point(size=0.1) +
  theme_classic()
```

```{r}
tmp <- results
tmp$state <- rep("pathological", nrow(tmp))
m <- tmp$V_osc/tmp$V_comp < 0.2858
tmp$state[m] <- "healthy"

tmp %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  # mutate(errors_pop = normalize(errors_pop)) %>%
  # mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
  geom_point(size=1.2, alpha=0.8) +
  xlab("Norm. variance") +
  ylab("Norm. error") +
  scale_color_manual("State", values=c("darkslategray3", "darkslategray")) +
  theme_classic() +
  theme(legend.background = element_rect(colour ="black")) 
```

### 2019-07-14 voltagebudget/analysis/exp127_analysis.Rmd
Add exp127 analysis Rmd

---
title: "Optimal coordination - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(magrittr)
library(readr)
library(gridExtra)
library(readr)
library(scales)
library(dplyr)
library(NNTbiomarker)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
find_point <- function(x, y, point){
  i <- argmin(x, target = point)
  return(c(x[i], y[i]))
}
ms <- 1e3
```

# Load and process

```{r, message=FALSE}
# Sparse
freqs <- c("8")#, "40", "60")
results <- NULL

exp <- "127a_1"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_5"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127a_9"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "127b"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

# - 
results %>% 
  filter(n_spikes_ref > 0) %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results

# -
rm(tmp, df)
```

```{r}
results %>% 
  ggplot(aes(x=As, y=variances_pop*ms, color=exp, shape=exp)) +
  geom_line(size=2, alpha=0.2) +
  geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
results %>% 
  ggplot(aes(x=As, y=n_spikes_pop, color=exp, shape=exp)) +
  geom_line(size=2, alpha=0.2) +
  geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
results %>% 
  ggplot(aes(x=As, y=errors_pop*ms, color=exp, shape=exp)) +
  geom_line(size=2, alpha=0.2) +
  geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
tmp <- results
tmp$state <- rep("pathological", nrow(tmp))
m <- tmp$V_osc/tmp$V_comp < 0.2858
tmp$state[m] <- "healthy"

tmp %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  # mutate(errors_pop = normalize(errors_pop)) %>%
  # mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
  geom_point(size=1.2, alpha=0.8) +
  xlab("Norm. variance") +
  ylab("Norm. error") +
  scale_color_manual("State", values=c("darkslategray3", "darkslategray")) +
  theme_classic() +
  theme(legend.background = element_rect(colour ="black")) 
```

### 2019-07-15 voltagebudget/analysis/exp127_analysis.Rmd
Add analysis to match last exp change for 127

@@
 ```{r, message=FALSE}
-# Sparse
 freqs <- c("8")#, "40", "60")
@@
 
+# Sparse exps
 exp <- "127a_1"
+tmp <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  df$freq <- rep(freq, nrow(df))
+  tmp <- rbind(tmp, df)
+}
+tmp$exp <- rep(exp, nrow(tmp))
+results <- rbind(results, tmp)
+
+exp <- "127a_2"
+tmp <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  df$freq <- rep(freq, nrow(df))
+  tmp <- rbind(tmp, df)
+}
+tmp$exp <- rep(exp, nrow(tmp))
+results <- rbind(results, tmp)
+
+exp <- "127a_3"
+tmp <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  df$freq <- rep(freq, nrow(df))
+  tmp <- rbind(tmp, df)
+}
+tmp$exp <- rep(exp, nrow(tmp))
+results <- rbind(results, tmp)
+
+exp <- "127a_4"
 tmp <- NULL
@@
 
+exp <- "127a_6"
+tmp <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  df$freq <- rep(freq, nrow(df))
+  tmp <- rbind(tmp, df)
+}
+tmp$exp <- rep(exp, nrow(tmp))
+results <- rbind(results, tmp)
+
+exp <- "127a_7"
+tmp <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  df$freq <- rep(freq, nrow(df))
+  tmp <- rbind(tmp, df)
+}
+tmp$exp <- rep(exp, nrow(tmp))
+results <- rbind(results, tmp)
+
+exp <- "127a_8"
+tmp <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  df$freq <- rep(freq, nrow(df))
+  tmp <- rbind(tmp, df)
+}
+tmp$exp <- rep(exp, nrow(tmp))
+results <- rbind(results, tmp)
+
 exp <- "127a_9"
@@
 
+# -
+# Org dense code
 exp <- "127b"
@@
 rm(tmp, df)
+```
+
+```{r}
+results %>% 
+  ggplot(aes(x=(V_osc/V_comp), fill=exp)) +
+  geom_histogram(bins=12) +
+  facet_grid(exp~As, scale="free") +
+  theme_classic()
 ```
@@
 ```{r}
+results %>% 
+  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=exp, shape=exp)) +
+  geom_line(size=2, alpha=0.2) +
+  geom_point(size=2, alpha=0.8) +
+  # facet_grid(exp~.) +
+  theme_classic()
+```
+
+```{r}
 tmp <- results

### 2019-07-15 voltagebudget/analysis/exp127_analysis.Rmd
Add exp127 analysis

@@
 # Org dense code
-exp <- "127b"
-tmp <- NULL
-for(freq in freqs){
-  name <- paste("../../data/exp", exp, ".csv", sep="")
-  df <- read_csv(paste(name, sep=""))
-  df$freq <- rep(freq, nrow(df))
-  tmp <- rbind(tmp, df)
-}
-tmp$exp <- rep(exp, nrow(tmp))
-results <- rbind(results, tmp)
+# exp <- "127b"
+# tmp <- NULL
+# for(freq in freqs){
+#   name <- paste("../../data/exp", exp, ".csv", sep="")
+#   df <- read_csv(paste(name, sep=""))
+#   df$freq <- rep(freq, nrow(df))
+#   tmp <- rbind(tmp, df)
+# }
+# tmp$exp <- rep(exp, nrow(tmp))
+# results <- rbind(results, tmp)
+# 
+# # - 
+# results %>% 
+#   filter(n_spikes_ref > 0) %>% 
+#   # Add delta_spikes
+#   mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
+#   # Re-norm V_osc
+#   mutate(V_osc = V_osc - V_osc_ref) -> results
 
-# - 
+# Process
 results %>% 
@@
 
+results %>% 
+  group_by(As, freq, exp) %>% 
+  summarise(
+    N = 0,
+    delta_spikes = mean(delta_spikes), 
+    V_b = mean(V_b), 
+    V_osc = mean(V_osc), 
+    V_free = mean(V_free), 
+    V_comp = mean(V_comp), 
+    V_comp_ref = mean(V_comp_ref), 
+    n_spikes_pop = mean(n_spikes), 
+    errors = mean(errors), 
+    errors_pop = mean(errors_pop), 
+    variances_pop = mean(variances_pop), 
+    variances = mean(variances)) -> avg_results
+
 # -
@@
 
+# Plot
+## Variance and error
+### As
 ```{r}
-results %>% 
-  ggplot(aes(x=(V_osc/V_comp), fill=exp)) +
-  geom_histogram(bins=12) +
-  facet_grid(exp~As, scale="free") +
-  theme_classic()
-```
-
-```{r}
-results %>% 
+avg_results %>% 
   ggplot(aes(x=As, y=variances_pop*ms, color=exp, shape=exp)) +
-  geom_line(size=2, alpha=0.2) +
-  geom_point(size=2, alpha=0.8) +
+  geom_line(size=1, alpha=0.6) +
+  # geom_point(size=2, alpha=0.8) +
   # facet_grid(exp~.) +
@@
 ```{r}
-results %>% 
+avg_results %>% 
   ggplot(aes(x=As, y=n_spikes_pop, color=exp, shape=exp)) +
-  geom_line(size=2, alpha=0.2) +
-  geom_point(size=2, alpha=0.8) +
+  geom_line(size=1, alpha=0.6) +
+  # geom_point(size=2, alpha=0.8) +
   # facet_grid(exp~.) +
@@
 ```{r}
-results %>% 
+avg_results %>% 
   ggplot(aes(x=As, y=errors_pop*ms, color=exp, shape=exp)) +
-  geom_line(size=2, alpha=0.2) +
-  geom_point(size=2, alpha=0.8) +
+  geom_line(size=1, alpha=0.6) +
+  # geom_point(size=2, alpha=0.8) +
+  # facet_grid(exp~.) +
+  theme_classic()
+```
+
+### Ratio
+
+```{r}
+avg_results %>% 
+  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms, color=exp)) +
+  geom_line(size=1, alpha=0.6) +
+  # geom_point(size=2, alpha=0.8) +
   # facet_grid(exp~.) +
@@
 ```{r}
-results %>% 
-  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=exp, shape=exp)) +
-  geom_line(size=2, alpha=0.2) +
-  geom_point(size=2, alpha=0.8) +
+avg_results %>% 
+  ggplot(aes(x=V_osc/V_comp, y=n_spikes_pop, color=exp, shape=exp)) +
+  geom_line(size=1, alpha=0.6) +
+  # geom_point(size=2, alpha=0.8) +
   # facet_grid(exp~.) +
@@
 
+```{r}
+avg_results %>% 
+  ggplot(aes(x=V_osc/V_comp, y=errors_pop*ms, color=exp)) +
+  geom_line(size=1, alpha=0.6) +
+  # geom_point(size=2, alpha=0.8) +
+  # facet_grid(exp~.) +
+  theme_classic()
+```
+
+## Trade-off
+```{r}
+avg_results %>% 
+  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=exp, group=interaction(exp,As))) +
+  geom_line(size=1, alpha=0.6) +
+  geom_point(size=1, alpha=0.8) +
+  # geom_boxplot() +
+  # facet_grid(exp~.) +
+  theme_classic()
+```
+
+## Pathological boundary.
 ```{r}

### 2019-07-15 voltagebudget/analysis/exp128_analysis.Rmd
Add exp128 analysis

--- 2019-07-15 voltagebudget/analysis/exp127_analysis.Rmd
@@
 # Sparse exps
-exp <- "127a_1"
+exp <- "128a_1"
 tmp <- NULL
@@
 
-exp <- "127a_2"
+exp <- "128a_2"
 tmp <- NULL
@@
 
-exp <- "127a_3"
+exp <- "128a_3"
 tmp <- NULL
@@
 
-exp <- "127a_4"
+exp <- "128a_4"
 tmp <- NULL
@@
 
-exp <- "127a_5"
+exp <- "128a_5"
 tmp <- NULL
@@
 
-exp <- "127a_6"
+exp <- "128a_6"
 tmp <- NULL
@@
 
-exp <- "127a_7"
+exp <- "128a_7"
 tmp <- NULL
@@
 
-exp <- "127a_8"
+# Org dense code
+exp <- "128b"
 tmp <- NULL
@@
 results <- rbind(results, tmp)
-
-exp <- "127a_9"
-tmp <- NULL
-for(freq in freqs){
-  name <- paste("../../data/exp", exp, ".csv", sep="")
-  df <- read_csv(paste(name, sep=""))
-  df$freq <- rep(freq, nrow(df))
-  tmp <- rbind(tmp, df)
-}
-tmp$exp <- rep(exp, nrow(tmp))
-results <- rbind(results, tmp)
-
-# -
-# Org dense code
-# exp <- "127b"
-# tmp <- NULL
-# for(freq in freqs){
-#   name <- paste("../../data/exp", exp, ".csv", sep="")
-#   df <- read_csv(paste(name, sep=""))
-#   df$freq <- rep(freq, nrow(df))
-#   tmp <- rbind(tmp, df)
-# }
-# tmp$exp <- rep(exp, nrow(tmp))
-# results <- rbind(results, tmp)
 # 
@@
 avg_results %>% 
-  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=exp, group=interaction(exp,As))) +
+  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=exp, group=interaction(exp))) +
   geom_line(size=1, alpha=0.6) +
-  geom_point(size=1, alpha=0.8) +
+  # geom_point(size=1, alpha=0.8) +
+  # geom_boxplot() +
+  # facet_grid(exp~.) +
+  theme_classic()
+```
+
+```{r}
+avg_results %>% 
+  ggplot(aes(x=errors_pop*ms, y=variances_pop*ms, color=exp, group=interaction(exp))) +
+  geom_line(size=1, alpha=0.6) +
+  # geom_point(size=1, alpha=0.8) +
   # geom_boxplot() +

### 2019-07-16 voltagebudget/analysis/exp129_analysis.Rmd
Update exp analysis to use N_oscs

---
title: "Exp129: Sparse coordination - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(magrittr)
library(readr)
library(gridExtra)
library(readr)
library(scales)
library(dplyr)
library(NNTbiomarker)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
find_point <- function(x, y, point){
  i <- argmin(x, target = point)
  return(c(x[i], y[i]))
}
ms <- 1e3
```

# Load and process

```{r, message=FALSE}
freqs <- c("8")#, "40", "60")
results <- NULL

# Sparse exps
exp <- "129a_70"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "129a_71"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "129a_72"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "129a_73"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "129a_74"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "129a_75"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "129a_76"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "129a_77"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "129a_78"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

# Org dense code
exp <- "129b"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
tmp$N_oscs <- rep(250, nrow(tmp))

# -
results <- rbind(results, tmp)

# -
# Process
results %>% 
  filter(n_spikes_ref > 0) %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results

results %>% 
  group_by(As, freq, exp) %>% 
  summarise(
    N = 0,
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_free = mean(V_free), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    n_spikes_pop = mean(n_spikes), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop),
    N_oscs = mean(N_oscs),
    variances = mean(variances)) -> avg_results

# -
rm(tmp, df)
```

# Plot
## Variance and error
### As
```{r}
avg_results %>% 
  ggplot(aes(x=As, y=variances_pop*ms, color=as.factor(N_oscs), shape=as.factor(N_oscs))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  ggplot(aes(x=As, y=n_spikes_pop, color=as.factor(N_oscs), shape=as.factor(N_oscs))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  ggplot(aes(x=As, y=errors_pop*ms, color=as.factor(N_oscs), shape=as.factor(N_oscs))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

### Ratio

```{r}
avg_results %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms, color=as.factor(N_oscs), shape=as.factor(N_oscs))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  ggplot(aes(x=V_osc/V_comp, y=n_spikes_pop, color=as.factor(N_oscs), shape=as.factor(N_oscs))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors_pop*ms, color=as.factor(N_oscs), shape=as.factor(N_oscs))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

## Trade-off
```{r}
avg_results %>% 
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=as.factor(N_oscs), shape=as.factor(N_oscs))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=1, alpha=0.8) +
  # geom_boxplot() +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  ggplot(aes(x=errors_pop*ms, y=variances_pop*ms, color=as.factor(N_oscs))) +
  # geom_line(size=1, alpha=0.6) +
  geom_point(size=1, alpha=0.8) +
  # geom_boxplot() +
  # facet_grid(exp~.) +
  theme_classic()
```

### 2019-07-16 voltagebudget/analysis/exp130_analysis.Rmd
Add exp130 analysis notebook (skeleton)

--- 2019-07-16 voltagebudget/analysis/exp129_analysis.Rmd
@@
 ---
-title: "Exp129: Sparse coordination - general experiment analysis."
+title: "Exp130: Sparse coordination - general experiment analysis."
 output: html_notebook
@@
 # Sparse exps
-exp <- "129a_70"
+exp <- "130a_780"
 tmp <- NULL
@@
 
-exp <- "129a_71"
+exp <- "130a_781"
 tmp <- NULL
@@
 
-exp <- "129a_72"
+exp <- "130a_782"
 tmp <- NULL
@@
 
-exp <- "129a_73"
+exp <- "130a_783"
 tmp <- NULL
@@
 
-exp <- "129a_74"
+exp <- "130a_784"
 tmp <- NULL
@@
 
-exp <- "129a_75"
+exp <- "130a_785"
 tmp <- NULL
@@
 
-exp <- "129a_76"
-tmp <- NULL
-for(freq in freqs){
-  name <- paste("../../data/exp", exp, ".csv", sep="")
-  df <- read_csv(paste(name, sep=""))
-  df$freq <- rep(freq, nrow(df))
-  tmp <- rbind(tmp, df)
-}
-tmp$exp <- rep(exp, nrow(tmp))
-results <- rbind(results, tmp)
-
-exp <- "129a_77"
-tmp <- NULL
-for(freq in freqs){
-  name <- paste("../../data/exp", exp, ".csv", sep="")
-  df <- read_csv(paste(name, sep=""))
-  df$freq <- rep(freq, nrow(df))
-  tmp <- rbind(tmp, df)
-}
-tmp$exp <- rep(exp, nrow(tmp))
-results <- rbind(results, tmp)
-
-exp <- "129a_78"
+exp <- "130a_786"
 tmp <- NULL
@@
 # Org dense code
-exp <- "129b"
+exp <- "130b"
 tmp <- NULL

### 2019-07-17 voltagebudget/analysis/exp131_analysis.Rmd
exp131 analysis

--- 2019-07-16 voltagebudget/analysis/exp130_analysis.Rmd
@@
 # Sparse exps
-exp <- "130a_780"
+exp <- "131a_780"
 tmp <- NULL
@@
 
-exp <- "130a_781"
+exp <- "131a_781"
 tmp <- NULL
@@
 
-exp <- "130a_782"
+exp <- "131a_782"
 tmp <- NULL
@@
 
-exp <- "130a_783"
+exp <- "131a_783"
 tmp <- NULL
@@
 
-exp <- "130a_784"
+exp <- "131a_784"
 tmp <- NULL
@@
 
-exp <- "130a_785"
+exp <- "131a_785"
 tmp <- NULL
@@
 
-exp <- "130a_786"
+exp <- "131a_786"
 tmp <- NULL
@@
 # Org dense code
-exp <- "130b"
+exp <- "131b"
 tmp <- NULL
@@
 results %>% 
-  group_by(As, freq, exp) %>% 
+  group_by(As, freq, N_oscs) %>% 
   summarise(
@@
     variances_pop = mean(variances_pop),
-    N_oscs = mean(N_oscs),
+    # N_oscs = mean(N_oscs),
     variances = mean(variances)) -> avg_results

### 2019-07-18 voltagebudget/analysis/exp132_analysis.Rmd
exp132 analysis

--- 2019-07-17 voltagebudget/analysis/exp131_analysis.Rmd
@@
 # Sparse exps
-exp <- "131a_780"
+exp <- "132a_780"
 tmp <- NULL
@@
 
-exp <- "131a_781"
+exp <- "132a_781"
 tmp <- NULL
@@
 
-exp <- "131a_782"
+exp <- "132a_782"
 tmp <- NULL
@@
 
-exp <- "131a_783"
+exp <- "132a_783"
 tmp <- NULL
@@
 
-exp <- "131a_784"
+exp <- "132a_784"
 tmp <- NULL
@@
 
-exp <- "131a_785"
+exp <- "132a_785"
 tmp <- NULL
@@
 
-exp <- "131a_786"
+exp <- "132a_786"
 tmp <- NULL
@@
 # Org dense code
-exp <- "131b"
+exp <- "132b"
 tmp <- NULL
@@
 avg_results %>% 
+  filter(V_osc/V_comp < 1) %>% 
   ggplot(aes(x=errors_pop*ms, y=variances_pop*ms, color=as.factor(N_oscs))) +
   # geom_line(size=1, alpha=0.6) +
-  geom_point(size=1, alpha=0.8) +
+  geom_point(size=2, alpha=0.8) +
   # geom_boxplot() +

### 2019-07-22 voltagebudget/analysis/exp134_analysis.Rmd
Add exp134 analysis

---
title: "Exp134: Sparse coordination - general experiment analysis."
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(magrittr)
library(readr)
library(gridExtra)
library(readr)
library(scales)
library(dplyr)
library(NNTbiomarker)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
find_point <- function(x, y, point){
  i <- argmin(x, target = point)
  return(c(x[i], y[i]))
}
ms <- 1e3
```

# Load and process

```{r, message=FALSE}
freqs <- c("8")#, "40", "60")
results <- NULL

# Sparse exps
# exp <- "134_1"
# tmp <- NULL
# for(freq in freqs){
#   name <- paste("../../data/exp", exp, ".csv", sep="")
#   df <- read_csv(paste(name, sep=""))
#   df$freq <- rep(freq, nrow(df))
#   tmp <- rbind(tmp, df)
# }
# tmp$exp <- rep(exp, nrow(tmp))
# results <- rbind(results, tmp)
# 
# exp <- "134_2"
# tmp <- NULL
# for(freq in freqs){
#   name <- paste("../../data/exp", exp, ".csv", sep="")
#   df <- read_csv(paste(name, sep=""))
#   df$freq <- rep(freq, nrow(df))
#   tmp <- rbind(tmp, df)
# }
# tmp$exp <- rep(exp, nrow(tmp))
# results <- rbind(results, tmp)
# 
# exp <- "134_3"
# tmp <- NULL
# for(freq in freqs){
#   name <- paste("../../data/exp", exp, ".csv", sep="")
#   df <- read_csv(paste(name, sep=""))
#   df$freq <- rep(freq, nrow(df))
#   tmp <- rbind(tmp, df)
# }
# tmp$exp <- rep(exp, nrow(tmp))
# results <- rbind(results, tmp)
# 
# exp <- "134_4"
# tmp <- NULL
# for(freq in freqs){
#   name <- paste("../../data/exp", exp, ".csv", sep="")
#   df <- read_csv(paste(name, sep=""))
#   df$freq <- rep(freq, nrow(df))
#   tmp <- rbind(tmp, df)
# }
# tmp$exp <- rep(exp, nrow(tmp))
# results <- rbind(results, tmp)

exp <- "134_5"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "134_6"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "134_7"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

exp <- "134_8"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

# Org dense code
exp <- "132b"
tmp <- NULL
for(freq in freqs){
  name <- paste("../../data/exp", exp, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df$freq <- rep(freq, nrow(df))
  tmp <- rbind(tmp, df)
}
tmp$exp <- rep(exp, nrow(tmp))
results <- rbind(results, tmp)

# -
# Process
results %>% 
  filter(n_spikes_ref > 0) %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results

results %>% 
  group_by(As, freq, exp) %>% 
  summarise(
    N = 0,
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_free = mean(V_free), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    n_spikes_pop = mean(n_spikes), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop),
    # N_oscs = mean(N_oscs),
    variances = mean(variances)) -> avg_results

# -
rm(tmp, df)
```

# Plot
## Variance and error
### As
```{r}
avg_results %>% 
  ggplot(aes(x=As, y=variances_pop*ms, color=as.factor(exp), shape=as.factor(exp))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  ggplot(aes(x=As, y=n_spikes_pop, color=as.factor(exp), shape=as.factor(exp))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  ggplot(aes(x=As, y=errors_pop*ms, color=as.factor(exp), shape=as.factor(exp))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

### Ratio

```{r}
avg_results %>% 
  filter(V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms, color=as.factor(exp), shape=as.factor(exp))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  filter(V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc/V_comp, y=n_spikes_pop, color=as.factor(exp), shape=as.factor(exp))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  filter(V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors_pop*ms, color=as.factor(exp), shape=as.factor(exp))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # facet_grid(exp~.) +
  theme_classic()
```

## Trade-off
```{r}
avg_results %>% 
  filter(V_osc/V_comp < 1) %>% 
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=as.factor(exp), shape=as.factor(exp))) +
  geom_point(size=1, alpha=0.6) +
  # geom_point(size=1, alpha=0.8) +
  # geom_boxplot() +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  filter(V_osc/V_comp < 1) %>% 
  ggplot(aes(x=errors_pop*ms, y=variances_pop*ms, color=as.factor(exp))) +
  # geom_line(size=1, alpha=0.6) +
  geom_point(size=2, alpha=0.8) +
  # geom_boxplot() +
  # facet_grid(exp~.) +
  theme_classic()
```

```{r}
avg_results %>% 
  filter(V_osc/V_comp < 1) %>% 
  group_by(exp) %>% 
  mutate(errors_pop=normalize(errors_pop), variances_pop=normalize(variances_pop)) %>% 
  ggplot(aes(x=errors_pop, y=variances_pop, color=as.factor(exp))) +
  geom_line(size=1, alpha=0.6) +
  # geom_point(size=2, alpha=0.8) +
  # geom_boxplot() +
  # facet_grid(exp~.) +
  theme_classic()
```

### 2020-03-20 voltagebudget/exp/__init__.py
Removed dependecy on the playpus lib
NOTE: this breaks some very old experiments, but they don't matter

@@ -1,7 +1,7 @@
 from voltagebudget.exp.replay import replay
 from voltagebudget.exp.perturb import perturb
 from voltagebudget.exp.reverse import reverse
-from voltagebudget.exp.pareto import pareto
+# from voltagebudget.exp.pareto import pareto
 from voltagebudget.exp.forward import forward
 from voltagebudget.exp.population import population
 from voltagebudget.exp.single import single

### 2020-03-20 voltagebudget/exp/budget_experiments.py

@@ -30,7 +30,7 @@ from voltagebudget.exp import population
 from voltagebudget.exp import single
 from voltagebudget.exp import perturb
 from voltagebudget.exp import replay
-from voltagebudget.exp import pareto
+# from voltagebudget.exp import pareto
 from voltagebudget.exp import reverse
 from voltagebudget.exp import create_stim
 from voltagebudget.exp import autotune_membrane
@@ -52,6 +52,6 @@ if __name__ == "__main__":
         'homeostasis': homeostasis,
         'perturb': perturb,
         'reverse': reverse,
-        'pareto': pareto,
+        # 'pareto': pareto,
         'replay': replay
     })

### 2020-03-20 voltagebudget/analysis/paper_figures_lossy.Rmd
WIP - Figures for Lossy redraft of the results

---
title: "Paper figures"
output: html_notebook
---

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(reshape2)
library(readr)
library(gridExtra)
library(readr)
library(patchwork)
library(NNTbiomarker)

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}

data_summary <- function(x) {
   m <- mean(x)
   ymin <- m-mad(x)
   ymax <- m+mad(x)
   return(c(y=m, ymin=ymin, ymax=ymax))
}

mean_summary <- function(x) {
   m <- mean(x)
   return(c(y=m))
}
sample_n_groups = function(tbl, size, replace = FALSE, weight = NULL) {
  # regroup when done
  grps = tbl %>% groups %>% lapply(as.character) %>% unlist
  # check length of groups non-zero
  keep = tbl %>% summarise() %>% ungroup() %>% sample_n(size, replace, weight)
  # keep only selected groups, regroup because joins change count.
  # regrouping may be unnecessary but joins do something funky to grouping variable
  tbl %>% right_join(keep, by=grps) %>% group_by_(.dots = grps)
}

find_point <- function(x, y, point){
  i <- argmin(x, target = point)
  return(c(x[i], y[i]))
}

ms <- 1000
mV <- 1000
```

# Figure 1 - intro story
```{r, message=FALSE, fig.height=1, fig.width=3}
# Load a Poisson sampled stimulus
ref_times <- read_csv("../../data/stim1.csv")
ref_times %>% 
   mutate(ts = ts - min(ts)) -> ref_times

# Max compress the reference. Just pick a spike time
# and put it everywhere.
sync_times <- ref_times
sync_times$ts <- ref_times$ts[9] # I picked 9 for no reason.

# Plot em....
p1 <- ref_times %>% 
  ggplot(aes(x=ts*1e3, y=ns)) +
  geom_point(alpha=0.8) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  ggtitle("Original\nmessage")

p2 <- ref_times %>% 
  ggplot(aes(x=ts*1e3, y=ns)) +
  geom_blank() +
  annotate("text", x =25, y = 20, label = "?", size=20, alpha=0.8) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  ggtitle("Optimal\ncompression")

p3 <- sync_times %>% 
  ggplot(aes(x=ts*1e3, y=ns)) +
  geom_point(alpha=0.8) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  ggtitle("Maximum\ncompression")

# Join plots into the final figure
# and save the result
# (patchwork at work)
p1 + p2 + p3  
ggsave("figures/lossy_fig1.png", dpi=600)
```

# Figure 2 - random sync
```{r, message=FALSE, fig.height=2.4, fig.width=3.1}
# Load a Poisson sampled stimulus
ref_times <- read_csv("../../data/stim1.csv")
ref_times %>% 
   mutate(ts = ts - min(ts)) -> ref_times

# Examples 
monte_carlo_times <- NULL
exps <- 1:9z # Only load the first 12 as examples
for(i in exps) {
  df <- read_csv(paste("../../data/exp135_mc_", as.character(i), "_target0.011_spikes.csv", sep = ""))
  df$exp <- rep(i, nrow(df))
  df$ts <- df$ts - min(df$ts)
  df$delta <- ref_times$ts - df$ts
  monte_carlo_times <- bind_rows(monte_carlo_times, df)
}

# Drop tiny deltas to clean up the visualization
monte_carlo_times$delta[monte_carlo_times$delta < 1e-3] = NA

# Errors (avg)
monte_carlo_results <- NULL
exps <- 1:100
for(i in exps) {
  df <- read_csv(paste("../../data/exp135_mc_", as.character(i), ".csv", sep = ""))
  df$exp <- rep(i, nrow(df))
  monte_carlo_results <- bind_rows(monte_carlo_results, df)
}

# Plot
p1 <- monte_carlo_times %>% 
  ggplot(aes(x=ts*ms, y=ns)) +
  geom_point(alpha=0.8, shape=1) +
  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns), 
               size=.4,
               color="darkred",
               alpha=0.8,
               arrow=arrow(length = unit(.08, "npc")),
               lineend = 'round', 
               linejoin = 'round') +
  facet_wrap(~exp) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "grey"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    strip.text.y = element_text(angle = 0)) +
  ggtitle("Random\ncompression (10%)")

p2 <- monte_carlo_results %>% 
  ggplot(aes(x=(errors - mean(errors))*ms)) +
  geom_histogram(alpha=0.4, fill="darkred") +
  # geom_histogram(alpha=0.8, bins=30, binwidth = .01) +
  geom_density(alpha=0.8, color="darkred") +
  labs(y="Count", x="Error (ms)") +
  lims(x=c(-0.25, 0.25)) +
  theme_classic()

p3 <- monte_carlo_results %>% 
  ggplot(aes(x=(obs_variances - mean(obs_variances))*ms)) +
  geom_histogram(alpha=0.4) +
  geom_density(alpha=0.8) +
  labs(y="Count", x="Synchrony (ms)") +
  lims(x=c(-0.25, 0.25)) +
  theme_classic()

p1 / (p3 + p2 + plot_spacer()) + 
  plot_layout(heights = c(3, 1)) + 
  plot_annotation(tag_levels = 'a', tag_suffix = ".")

ggsave("figures/lossy_fig2.png", dpi=600)
```

### 2020-03-20 voltagebudget/analysis/paper_figures_lossy.Rmd
Tweak Fig 1 and 2

@@
 # Figure 1 - intro story
-```{r, message=FALSE, fig.height=1, fig.width=3}
+```{r, message=FALSE, fig.height=1, fig.width=4.2}
 # Load a Poisson sampled stimulus
@@
 sync_times$ts <- ref_times$ts[9] # I picked 9 for no reason.
+sync_times$delta <- ref_times$ts - sync_times$ts
 
@@
 
+p4 <- sync_times %>% 
+  ggplot(aes(x=ts*1e3, y=ns)) +
+  geom_point(alpha=0.8, size=1.2, shape=1) +
+  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns), 
+               size=.4,
+               color="darkred",
+               alpha=0.8,
+               arrow=arrow(length = unit(.08, "npc")),
+               lineend = 'round', 
+               linejoin = 'round') +
+  labs(x="Time (ms)", y="Neuron") +
+  lims(x=c(0, 50)) +
+  theme_classic() +
+  ggtitle("Compression\nerror")
+
 # Join plots into the final figure
@@
 # (patchwork at work)
-p1 + p2 + p3  
+p1 + p2 + p3 + p4 + 
+  plot_layout(ncol=4) +
+  plot_annotation(tag_levels = 'a', tag_suffix = ".")
 ggsave("figures/lossy_fig1.png", dpi=600)
@@
 # Figure 2 - random sync
-```{r, message=FALSE, fig.height=2.4, fig.width=3.1}
+```{r, message=FALSE, fig.height=2.4, fig.width=2.4}
 # Load a Poisson sampled stimulus
@@
 monte_carlo_times <- NULL
-exps <- 1:9z # Only load the first 12 as examples
+exps <- 1:9 # Only load the first 12 as examples
 for(i in exps) {

### 2020-03-20 voltagebudget/analysis/paper_figures_lossy.Rmd
- Split Fig 1 into Fig 1 and 2 - Misc other tweaks

--- 2020-03-20 voltagebudget/analysis/paper_figures_lossy.Rmd
@@
 # (patchwork at work)
-p1 + p2 + p3  
+p1 + p2 + p3 + 
+  plot_annotation(tag_levels = 'a', tag_suffix = ".")
 ggsave("figures/lossy_fig1.png", dpi=600)
@@
 
-# Figure 2 - random sync
-```{r, message=FALSE, fig.height=2.4, fig.width=3.1}
+# Figure 2 - error
+```{r, message=FALSE, fig.height=0.85, fig.width=1}
+p1 <- sync_times %>% 
+  ggplot(aes(x=ts*1e3, y=ns)) +
+  geom_point(alpha=0.8, size=1.2, shape=1) +
+  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns), 
+               size=.4,
+               color="darkred",
+               alpha=0.8,
+               arrow=arrow(length = unit(.08, "npc")),
+               lineend = 'round', 
+               linejoin = 'round') +
+  labs(x="Time (ms)", y="Neuron") +
+  lims(x=c(0, 50)) +
+  theme_classic() +
+  ggtitle("Compression\nerror")
+
+p1 
+ggsave("figures/lossy_fig2.png", dpi=600)
+```
+
+# Figure 3 - random sync
+```{r, message=FALSE, fig.height=2.4, fig.width=2.6}
 # Load a Poisson sampled stimulus
@@
 
-ggsave("figures/lossy_fig2.png", dpi=600)
+ggsave("figures/lossy_fig3.png", dpi=600)
 ```

### 2020-03-20 voltagebudget/analysis/paper_figures_lossy.Rmd
Added Lossy Figures 3-6

@@
 
-# Figure 1 - intro story
+# Figure 1 and 2 - intro story, definition of error
+## Figure 1 - intro
 ```{r, message=FALSE, fig.height=1, fig.width=3}
@@
 sync_times$delta <- ref_times$ts - sync_times$ts
+
+sync_times$delta[abs(sync_times$delta) < 1e-3] = NA
 
@@
 
-# Figure 2 - error
-```{r, message=FALSE, fig.height=0.85, fig.width=1}
+## Figure 2 - error
+```{r, message=FALSE, fig.height=0.95, fig.width=1}
 p1 <- sync_times %>% 
@@
                size=.4,
-               color="darkred",
-               alpha=0.8,
-               arrow=arrow(length = unit(.08, "npc")),
+               color="palegreen4",
+               alpha=0.99,
+               # arrow=arrow(length = unit(.08, "npc")),
                lineend = 'round', 
@@
   theme_classic() +
-  ggtitle("Compression\nerror")
+  ggtitle("Maximum\ncompression\nerror")
 
@@
 # Drop tiny deltas to clean up the visualization
-monte_carlo_times$delta[monte_carlo_times$delta < 1e-3] = NA
+monte_carlo_times$delta[abs(monte_carlo_times$delta) < 2e-3] = NA
 
@@
   geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns), 
-               size=.4,
-               color="darkred",
-               alpha=0.8,
-               arrow=arrow(length = unit(.08, "npc")),
+               size=.6,
+               color="palegreen4",
+               alpha=0.99,
+               # arrow=arrow(length = unit(.08, "npc")),
                lineend = 'round', 
@@
   ggplot(aes(x=(errors - mean(errors))*ms)) +
-  geom_histogram(alpha=0.4, fill="darkred") +
+  geom_histogram(alpha=0.4, fill="palegreen4") +
   # geom_histogram(alpha=0.8, bins=30, binwidth = .01) +
-  geom_density(alpha=0.8, color="darkred") +
+  geom_density(alpha=0.8, color="palegreen4") +
   labs(y="Count", x="Error (ms)") +
@@
 ```
+
+# Figure 4 - optimal algs
+```{r, fig.width=1.4, fig.height=2.4, message=FALSE}
+# Agls
+algs <- c("max", "left", "uni", "cc")
+alg_names <- c("Single cell", "left", "Population", "Information\ntheory")
+exps <- c(114, 115, 116, 117)
+
+# Load agg. results
+optimal_results <- NULL
+for (n in 1:4){
+  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], ".csv", sep=""))
+  df$alg <- rep(alg_names[n], nrow(df))
+  optimal_results <- rbind(optimal_results, df)
+}
+
+# Load exp spikes
+exps <- c(110, 111, 112, 113)
+optimal_times <- NULL
+for (n in 1:4){
+  # df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_c0.1_spikes.csv", sep=""))
+  df <- read_csv(paste("../../data/exp", as.character(exps[n]), "_", algs[n], "_target0.01_spikes.csv", sep=""))
+  df$ts <- df$ts - min(df$ts)
+  df$delta <- ref_times$ts - df$ts
+  df$alg <- rep(alg_names[n], nrow(df))
+  optimal_times <- rbind(optimal_times, df)
+}
+
+# Drop lext max dev.
+optimal_times %>% 
+  filter(alg != "left") -> optimal_times
+
+optimal_times$delta[abs(optimal_times$delta) < 2e-3] = NA
+
+# Plot....
+optimal_times %>% 
+  ggplot(aes(x=ts*ms, y=ns)) +
+  geom_point(size=1.2, alpha=0.8, shape=1) +
+  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns, color=alg), 
+               size=.6,
+               alpha=0.8,
+               # arrow=arrow(length = unit(.08, "npc")),
+               lineend = 'round', 
+               linejoin = 'round') +
+  facet_grid(alg~.) +
+  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3", "chartreuse3")) +
+  theme_classic() +
+  labs(x="Time (ms)", y="Neuron") +
+  ggtitle("Optimal\ncompression") +
+  theme(
+    legend.position="none", 
+    panel.border = element_rect(fill = NA, colour = "black"),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    strip.background = element_blank(),
+    strip.text.y = element_text(angle = 0)) -> p1
+
+optimal_results %>% 
+  filter(alg != "left") %>%
+  filter(obs_variances > 10e-3) %>% 
+  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
+  # geom_line(size=0.1, alpha=0.99) +
+  geom_line(size=1, alpha=0.99) +
+  scale_color_manual("Algorithm", 
+                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
+                     guide = guide_legend(nrow = 3)) +
+  theme_classic() +
+  coord_flip() +
+  labs(x="Time (ms)", y="Neuron") +
+  theme(legend.position="none",
+    legend.key.size = unit(.1, "cm"),
+    legend.title = element_text(size=6),
+    legend.text = element_text(size=6),
+    legend.background = element_rect(colour ="black")) +
+  labs(x="Error (ms)", y="Synchrony (ms)") -> p2
+
+# plot_grid <- rbind(
+#   c(1, 1, 1, 1, 1),
+#   c(1, 1, 1, 1, 1),
+#   c(2, 2, 2, 2, NA),
+#   c(2, 2, 2, 2, NA))  
+# 
+# grid.arrange(p1, p2, layout_matrix=plot_grid)
+# rm(p1, p2, plot_grid)
+
+p1 / p2 +
+  plot_layout(heights = c(2.2, 1)) + 
+  plot_annotation(tag_levels = 'a', tag_suffix = ".")
+ggsave("figures/lossy_fig4.png", dpi=600)
+```
+
+# Figure 5 - osc v opt
+```{r, fig.width=1.8, fig.height=3, message=FALSE}
+# Load data
+exp <- "118"
+freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")
+
+exp118_results <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  # df %>%
+    # filter(n_spikes_pop > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  exp118_results <- rbind(exp118_results, df)
+}
+
+exp118_results$freq <- factor(exp118_results$freq, levels=freqs)
+
+exp <- "119"
+freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")
+
+exp119_results <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  # df %>%
+    # filter(n_spikes_pop > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  exp119_results <- rbind(exp119_results, df)
+}
+
+exp119_results$freq <- factor(exp119_results$freq, levels=freqs)
+
+# -
+exp <- "109"
+freqs <- c("4", "8", "12", "20", "24", "30")#, "40", "60")
+
+exp109_results <- NULL
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
+  df <- read_csv(paste(name, sep=""))
+  # df %>%
+    # filter(n_spikes_pop > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  exp109_results <- rbind(exp109_results, df)
+}
+
+exp119_results$freq <- factor(exp119_results$freq, levels=freqs)
+
+# -
+# alg_names <- c("Single cell", "left", "Population", "Information\ntheory")
+exp118_results$alg <- rep("Single cell", nrow(exp118_results))
+exp119_results$alg <- rep("Population", nrow(exp119_results))
+exp109_results$alg <- rep("Information\ntheory", nrow(exp109_results))
+opt_v_osc_results <- rbind(exp118_results, exp119_results, exp109_results)
+
+# Process a bit
+hospital_names <- list(
+  '8'="Frequency\n\n8 Hz",
+  '12'="12 Hz",
+  '20'="20 Hz",
+  '30'="30 Hz"
+)
+hospital_labeller <- function(variable,value){
+  return(hospital_names[as.character(value)])
+}
+
+# Plot....
+opt_v_osc_results %>% 
+  filter(errors_pop > 0, freq %in% c("8")) %>%
+  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
+  geom_point(size=0.2, alpha=0.99) + 
+  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
+             alpha=0.99, size=0.6) +
+  scale_y_continuous(trans='log10') +
+  annotation_logticks(sides = "l") +
+  # facet_grid(freq~., labeller=hospital_labeller) +
+  scale_color_manual("Algorithm", 
+                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
+                     guide = guide_legend(nrow = 3)) +
+  labs(x="Synchrony (ms)", y="Error (ms)") +
+  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
+  ggtitle("Optimal versus\noscillation") +
+  theme_classic() +
+  theme(legend.position="right",
+    legend.key.size = unit(.1, "cm"),
+    legend.title = element_text(size=6),
+    legend.text = element_text(size=6),
+    legend.background = element_rect(colour ="black"),
+    strip.text.y = element_text(angle = 0), 
+    panel.grid.minor = element_blank(),
+    legend.key.width=unit(0.05,"cm"),
+    strip.background = element_blank()) -> p1
+
+opt_v_osc_results %>% 
+  filter(errors_pop > 0, freq %in% c("8")) %>%
+  ggplot(aes(x=variances_pop*ms, y=variances_opt*ms, color=alg)) +
+  geom_point(size=0.8, alpha=0.3) +
+  geom_abline(intercept = 0, color="black", alpha=1) +
+  labs(x="Oscillation\nsynchrony (ms)", y="Optimal\nsynchrony (ms)") +
+  scale_color_manual("Algorithm:", 
+                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
+                     guide = "none") +
+  theme_classic() +
+  theme(plot.title = element_text(size = 10)) -> p2
+
+opt_v_osc_results %>% 
+  filter(errors_pop > 0, freq %in% c("8")) %>%
+  ggplot(aes(x=errors_pop*ms, y=errors_opt*ms, color=alg)) +
+  geom_point(size=0.8, alpha=0.5) +
+  lims(x=c(0,25),y=c(0,25)) +
+  geom_abline(intercept = 0, color="black", alpha=1) +
+  labs(x="Oscillation\nerror (ms)", y="Optimal\nerror (ms)") +
+  scale_color_manual("Algorithm:", 
+                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
+                     guide = "none") +
+  ggtitle(" ") +
+  theme_classic() -> p3
+
+p1 / p2 / p3 +
+  plot_layout(heights = c(2, 1, 1)) + 
+  plot_annotation(tag_levels = 'a', tag_suffix = ".")
+ggsave("figures/lossy_fig5.png", dpi=600)
+```
+
+# Figure 6 - osc freq v optimal
+```{r, fig.width=2, fig.height=3, message=FALSE}
+# Plot....
+opt_v_osc_results %>% 
+  filter(errors_pop > 0, freq %in% c("8","12","20","30")) %>%
+  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
+  geom_point(size=0.2, alpha=0.99) + 
+  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
+             alpha=0.99, size=0.6) +
+  scale_y_continuous(trans='log10') +
+  annotation_logticks(sides = "l") +
+  facet_grid(freq~., labeller=hospital_labeller) +
+  scale_color_manual("Algorithm", 
+                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
+                     guide = guide_legend(nrow = 3)) +
+  labs(x="Synchrony (ms)", y="Error (ms)") +
+  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
+  ggtitle("Optimal versus\nfrequency") +
+  theme_classic() +
+  theme(legend.position="right",
+    legend.key.size = unit(.1, "cm"),
+    legend.title = element_text(size=8),
+    legend.text = element_text(size=8),
+    legend.background = element_rect(colour ="black"),
+    strip.text.y = element_text(angle = 0), 
+    panel.grid.minor = element_blank(),
+    legend.key.width=unit(0.05,"cm"),
+    strip.background = element_blank()) -> p1
+
+p1
+ggsave("figures/lossy_fig6.png", dpi=600)
+```
+
+# Figure 7 - shape
+- TODO?

### 2020-03-20 voltagebudget/analysis/paper_figures_lossy.Rmd
Tweak axis in Fig1-6 Other misc These are locked now

@@
   ggplot(aes(x=ts*1e3, y=ns)) +
-  geom_point(alpha=0.8) +
+  geom_point(alpha=0.8, size=0.6) +
   labs(x="Time (ms)", y="Neuron") +
@@
   ggplot(aes(x=ts*1e3, y=ns)) +
-  geom_point(alpha=0.8, size=1.2, shape=1) +
   geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns), 
@@
                color="palegreen4",
-               alpha=0.99,
+               alpha=0.8,
                # arrow=arrow(length = unit(.08, "npc")),
@@
                linejoin = 'round') +
+  geom_point(alpha=0.8, size=0.6) +
   labs(x="Time (ms)", y="Neuron") +
@@
   ggplot(aes(x=ts*ms, y=ns)) +
-  geom_point(alpha=0.8, shape=1) +
   geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns), 
@@
                linejoin = 'round') +
+  geom_point(alpha=0.8, size=0.6) +
   facet_wrap(~exp) +
@@
   geom_density(alpha=0.8, color="palegreen4") +
-  labs(y="Count", x="Error (ms)") +
+  labs(y="Count", x="Error\nvariance (ms)") +
   lims(x=c(-0.25, 0.25)) +
@@
   geom_density(alpha=0.8) +
-  labs(y="Count", x="Synchrony (ms)") +
+  labs(y="Count", x="Compression\nvariance (ms)") +
   lims(x=c(-0.25, 0.25)) +
@@
 
-p1 / (p3 + p2 + plot_spacer()) + 
+p1 / (p3 + p2) + 
   plot_layout(heights = c(3, 1)) + 
@@
   ggplot(aes(x=ts*ms, y=ns)) +
-  geom_point(size=1.2, alpha=0.8, shape=1) +
   geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns, color=alg), 
@@
                linejoin = 'round') +
+  geom_point(alpha=0.8, size=0.6) +
   facet_grid(alg~.) +
@@
   ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
-  # geom_line(size=0.1, alpha=0.99) +
-  geom_line(size=1, alpha=0.99) +
+  geom_line(size=1, alpha=0.8) +
   scale_color_manual("Algorithm", 
@@
     legend.background = element_rect(colour ="black")) +
-  labs(x="Error (ms)", y="Synchrony (ms)") -> p2
+  labs(x="Error (ms)", y="Compression (ms)") -> p2
 
@@
   geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
-             alpha=0.99, size=0.6) +
+             alpha=0.99, size=0.4) +
   scale_y_continuous(trans='log10') +
@@
                      guide = guide_legend(nrow = 3)) +
-  labs(x="Synchrony (ms)", y="Error (ms)") +
+  labs(x="Compression (ms)", y="Error (ms)") +
   scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
@@
   geom_abline(intercept = 0, color="black", alpha=1) +
-  labs(x="Oscillation\nsynchrony (ms)", y="Optimal\nsynchrony (ms)") +
+  labs(x="Oscillation\ncompression (ms)", y="Optimal\ncompression (ms)") +
   scale_color_manual("Algorithm:", 

### 2020-03-21 voltagebudget/analysis/paper_figures_lossy.Rmd
Fig 8 - WIP

@@
   plot_annotation(tag_levels = 'a', tag_suffix = ".")
-ggsave("figures/lossy_fig1.png", dpi=600)
+ggsave("figures/lossy_vb_results.png", dpi=600)
 ```
@@
 p1 
-ggsave("figures/lossy_fig2.png", dpi=600)
+ggsave("figures/lossy_vb_mean_results.png", dpi=600)
 ```
@@
 - TODO?
+
+# Figure 8 - error50
+
+HERE - need to add osc shit examples to the top of this figure. Next up is E50 intro figure.
+
+```{r, message=FALSE}
+# --------------------------------------------------------------------
+vb_results <- NULL
+
+exp <- "96"
+freqs <- c(20, 30)
+
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
+  df <- read_csv(paste(name, sep=","))
+  df %>%
+    filter(n_spikes > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  vb_results <- rbind(vb_results, df)
+}
+
+# --------------------------
+# SLOW
+exp <- "94"
+freqs <- c(6, 8, 10, 12, 14, 16, 18)
+
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
+  df <- read_csv(paste(name, sep=","))
+  df %>%
+    filter(n_spikes > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  vb_results <- rbind(vb_results, df)
+}
+
+# --------------------------
+# FAST
+exp <- "95"
+freqs <- c(22, 24, 26, 28)#, 32, 34 ,36, 38)
+for(freq in freqs){
+  name <- paste("../../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
+  df <- read_csv(paste(name, sep=","))
+  df %>%
+    filter(n_spikes > 0) -> df
+
+  df$freq <- rep(freq, nrow(df))
+  vb_results <- rbind(vb_results, df)
+}
+
+# Process
+vb_results %>% 
+  filter(n_spikes_ref > 0) %>% 
+  # Add delta_spikes
+  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
+  # Re-norm V_osc
+  mutate(V_osc = V_osc - V_osc_ref) -> vb_results
+
+vb_results %>% 
+  group_by(As, freq) %>% 
+  summarise(
+    N = 0,
+    delta_spikes = mean(delta_spikes), 
+    V_b = mean(V_b), 
+    V_osc = mean(V_osc), 
+    V_free = mean(V_free), 
+    V_comp = mean(V_comp), 
+    V_comp_ref = mean(V_comp_ref), 
+    n_spikes_pop = mean(n_spikes), 
+    errors = mean(errors), 
+    errors_pop = mean(errors_pop), 
+    variances_pop = mean(variances_pop), 
+    variances = mean(variances)) -> vb_mean_results
+
+# Ratio ests
+vb_mean_results_ratios <- NULL
+freqs <- unique(vb_mean_results$freq)
+for (f in freqs) {
+  tmp <- filter(vb_mean_results, f == freq, V_osc/V_comp < 5)
+  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
+  row <- c(pnts, f)
+  vb_mean_results_ratios <- rbind(vb_mean_results_ratios, row)
+}
+vb_mean_results_ratios <- as.data.frame(vb_mean_results_ratios, stringsAsFactors=FALSE)
+colnames(vb_mean_results_ratios) <- c("error_50", "ratio", "freq")
+```
+```{r, message=FALSE, fig.width=4, fig.height=1.8}
+
+vb_results %>% 
+  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
+  ggplot(aes(x=As, y=variances_pop*ms, color=As*1e9)) +
+  geom_point(alpha=0.8, size=0.6) +
+  labs(x="Peak amplitude (namps)", y="Compression (ms)") +
+  lims(y=c(7,9)) +
+  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
+  theme_classic() + 
+  theme(legend.position="none") -> p1
+
+vb_norm_results %>% 
+  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
+  ggplot(aes(x=As, y=errors_pop*ms, group=N, color=As)) +
+  geom_point(alpha=0.8, size=0.6) +
+  labs(x="Peak amplitude (namps)", y="Error (ms)") +
+  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
+  theme_classic() +
+  theme(legend.position="none") -> p2
+
+vb_norm_results %>% 
+  filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
+  ggplot(aes(y=variances_pop*ms, x=errors_pop*ms, group=N, color=As)) +
+  geom_point(alpha=0.8, size=1) +
+  labs(x="Error (ms)", y="Compression (ms)") +
+  lims(y=c(7,9)) +
+  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
+  ggtitle("The compression/error trade-off") +
+  theme_classic() -> p3
+
+((p1 / p2) | p3) +
+  plot_layout(widths = c(1, 2)) + 
+  plot_annotation(tag_levels = 'a', tag_suffix = ".")
+```

### 2020-03-21 voltagebudget/analysis/paper_figures_lossy.Rmd
- Added Fig 8 and 9 - Tweak labels/colors in others

@@
 
-# Figure 8 - error50
+# Figure 8 - osc intro
+```{r, fig.width=2, fig.height=1, message=FALSE}
+# Load example spikes
+ref_times <- read_csv("../../data/stim1.csv")
+ref_times %>% 
+   mutate(ts = ts - min(ts)) -> ref_times
 
-HERE - need to add osc shit examples to the top of this figure. Next up is E50 intro figure.
+# Make waves a function
+time <- seq(0,0.4*2,length.out=1000)
+freq <- 8
+A <- 1
+wave <- A/2 + A/2*sin(freq * time)
 
+# As a test, plot an example of the wave
+# plot(time, wave, xlab = "Time", ylab="Amplitude (namps)")
+
+# Build a wave datafrome
+amps <- c(
+  min(vb_results$As[vb_results$As > 0]), 
+  median(vb_results$As[vb_results$As > 0]), 
+  max(vb_results$As[vb_results$As > 0]))
+
+wave_results <- NULL
+for (a in amps){
+  df <- data.frame(time=time, 
+                   wave=a*wave, 
+                   As=rep(a, length(time)))
+  wave_results <- bind_rows(wave_results, df)
+}
+
+# TODO - run simulations with As from above
+
+```
+```{r, fig.width=3, fig.height=2, message=FALSE}
+# Make the figure
+p1 <- ref_times %>% 
+  ggplot(aes(x=ts*1e3, y=ns)) +
+  geom_point(alpha=0.8, size=0.6) +
+  labs(x="Time (ms)", y="Neuron") +
+  lims(x=c(0, 50)) +
+  theme_classic() +
+  ggtitle("Original\nmessage")
+
+p2 <- wave_results %>% 
+  ggplot(aes(x=time, y=wave, color=As, group=As)) +
+  geom_line() +
+  labs(x="Time (ms)", y="Amplitude") +
+  lims(x=c(0, 0.8)) +
+  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
+  theme_classic() +
+  ggtitle("Compression\n'algorithm'")
+
+# HERE - need to run sims to make the osc_times df
+p3 <- osc_times %>% 
+  ggplot(aes(x=ts*1e3, y=ns, color=As)) +
+  geom_point(alpha=0.8, size=0.6) +
+  labs(x="Time (ms)", y="Neuron") +
+  lims(x=c(0, 50)) +
+  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
+  facet_grid(.~As) +
+  theme_classic() +
+  theme(legend.position = "none",
+        strip.background = element_blank(),
+        strip.text.x = element_blank()) +
+  ggtitle("Compression\nby oscillation")
+
+# Build figure 
+(p1 | p2) / p3 +
+  plot_layout(guides = 'collect') +
+  plot_annotation(tag_levels = 'a', tag_suffix = ".")
+ggsave("figures/lossy_fig8.png", dpi=600)
+```
+
+# Figure 9 - trade-off (with osc)
 ```{r, message=FALSE}
@@
 ```
-```{r, message=FALSE, fig.width=4, fig.height=1.8}
+```{r, message=FALSE, fig.width=3.8, fig.height=1.8}
 
@@
   scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
-  ggtitle("The compression/error trade-off") +
+  ggtitle("Compression/error trade-off\nfor oscillation") +
   theme_classic() -> p3
@@
   plot_annotation(tag_levels = 'a', tag_suffix = ".")
+ggsave("figures/lossy_fig9.png", dpi=600)
 ```

### 2020-03-22 voltagebudget/analysis/paper_figures_lossy.Rmd
- Added Fig 10 - Reorg shared data import for VB plots

@@
 
-# Figure 8 - osc intro
-```{r, fig.width=2, fig.height=1, message=FALSE}
-# Load example spikes
-ref_times <- read_csv("../../data/stim1.csv")
-ref_times %>% 
-   mutate(ts = ts - min(ts)) -> ref_times
-
-# Make waves a function
-time <- seq(0,0.4*2,length.out=1000)
-freq <- 8
-A <- 1
-wave <- A/2 + A/2*sin(freq * time)
-
-# As a test, plot an example of the wave
-# plot(time, wave, xlab = "Time", ylab="Amplitude (namps)")
-
-# Build a wave datafrome
-amps <- c(
-  min(vb_results$As[vb_results$As > 0]), 
-  median(vb_results$As[vb_results$As > 0]), 
-  max(vb_results$As[vb_results$As > 0]))
-
-wave_results <- NULL
-for (a in amps){
-  df <- data.frame(time=time, 
-                   wave=a*wave, 
-                   As=rep(a, length(time)))
-  wave_results <- bind_rows(wave_results, df)
-}
-
-# TODO - run simulations with As from above
-
-```
-```{r, fig.width=3, fig.height=2, message=FALSE}
-# Make the figure
-p1 <- ref_times %>% 
-  ggplot(aes(x=ts*1e3, y=ns)) +
-  geom_point(alpha=0.8, size=0.6) +
-  labs(x="Time (ms)", y="Neuron") +
-  lims(x=c(0, 50)) +
-  theme_classic() +
-  ggtitle("Original\nmessage")
-
-p2 <- wave_results %>% 
-  ggplot(aes(x=time, y=wave, color=As, group=As)) +
-  geom_line() +
-  labs(x="Time (ms)", y="Amplitude") +
-  lims(x=c(0, 0.8)) +
-  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
-  theme_classic() +
-  ggtitle("Compression\n'algorithm'")
-
-# HERE - need to run sims to make the osc_times df
-p3 <- osc_times %>% 
-  ggplot(aes(x=ts*1e3, y=ns, color=As)) +
-  geom_point(alpha=0.8, size=0.6) +
-  labs(x="Time (ms)", y="Neuron") +
-  lims(x=c(0, 50)) +
-  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
-  facet_grid(.~As) +
-  theme_classic() +
-  theme(legend.position = "none",
-        strip.background = element_blank(),
-        strip.text.x = element_blank()) +
-  ggtitle("Compression\nby oscillation")
-
-# Build figure 
-(p1 | p2) / p3 +
-  plot_layout(guides = 'collect') +
-  plot_annotation(tag_levels = 'a', tag_suffix = ".")
-ggsave("figures/lossy_fig8.png", dpi=600)
-```
-
-# Figure 9 - trade-off (with osc)
+# Load shared VB data
 ```{r, message=FALSE}
@@
 ```
+
+# Figure 8 - osc intro
+```{r, fig.width=2, fig.height=1, message=FALSE}
+# Load example spikes
+ref_times <- read_csv("../../data/stim1.csv")
+ref_times %>% 
+   mutate(ts = ts - min(ts)) -> ref_times
+
+# Make waves a function
+time <- seq(0,0.4*2,length.out=1000)
+freq <- 8
+A <- 1
+wave <- A/2 + A/2*sin(freq * time)
+
+# As a test, plot an example of the wave
+# plot(time, wave, xlab = "Time", ylab="Amplitude (namps)")
+
+# Build a wave datafrome
+amps <- c(
+  min(vb_results$As[vb_results$As > 0]), 
+  median(vb_results$As[vb_results$As > 0]), 
+  max(vb_results$As[vb_results$As > 0]))
+
+wave_results <- NULL
+for (a in amps){
+  df <- data.frame(time=time, 
+                   wave=a*wave, 
+                   As=rep(a, length(time)))
+  wave_results <- bind_rows(wave_results, df)
+}
+
+# TODO - run simulations with As from above
+
+```
+```{r, fig.width=3, fig.height=2, message=FALSE}
+# Make the figure
+p1 <- ref_times %>% 
+  ggplot(aes(x=ts*1e3, y=ns)) +
+  geom_point(alpha=0.8, size=0.6) +
+  labs(x="Time (ms)", y="Neuron") +
+  lims(x=c(0, 50)) +
+  theme_classic() +
+  ggtitle("Original\nmessage")
+
+p2 <- wave_results %>% 
+  ggplot(aes(x=time, y=wave, color=As, group=As)) +
+  geom_line() +
+  labs(x="Time (ms)", y="Amplitude") +
+  lims(x=c(0, 0.8)) +
+  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
+  theme_classic() +
+  ggtitle("Compression\n'algorithm'")
+
+# HERE - need to run sims to make the osc_times df
+osc_times <- NULL
+p3 <- osc_times %>% 
+  ggplot(aes(x=ts*1e3, y=ns, color=As)) +
+  geom_point(alpha=0.8, size=0.6) +
+  labs(x="Time (ms)", y="Neuron") +
+  lims(x=c(0, 50)) +
+  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
+  facet_grid(.~As) +
+  theme_classic() +
+  theme(legend.position = "none",
+        strip.background = element_blank(),
+        strip.text.x = element_blank()) +
+  ggtitle("Compression\nby oscillation")
+
+# Build figure 
+(p1 | p2) / p3 +
+  plot_layout(guides = 'collect') +
+  plot_annotation(tag_levels = 'a', tag_suffix = ".")
+ggsave("figures/lossy_fig8.png", dpi=600)
+```
+
+# Figure 9 - trade-off (with osc)
 ```{r, message=FALSE, fig.width=3.8, fig.height=1.8}
-
 vb_results %>% 
@@
 
-vb_norm_results %>% 
+vb_results %>% 
   filter(freq == "8", V_osc/V_comp < 5, N == 1) %>% 
@@
 ```
+
+# Figure 10 - E50 intro
+```{r, message=FALSE, fig.width=3, fig.height=2.8}
+# Norm and annotate health versus path
+vb_mean_results %>% 
+  filter(V_osc/V_comp <= 5) %>%
+  group_by(freq, N) %>%
+  mutate(errors_pop = normalize(errors_pop)) %>%
+  mutate(variances_pop = normalize(variances_pop)) -> vb_norm_results
+
+vb_norm_results$state <- rep("pathological", nrow(vb_norm_results))
+m <- vb_norm_results$errors_pop <= 0.5
+vb_norm_results$state[m] <- "healthy"
+
+# Create plots
+vb_norm_results %>% 
+  filter(freq == 8) %>% 
+  ggplot(aes(x=As*1e9, normalize(errors_pop))) +
+  geom_point(size=0.8, alpha=0.9) +
+  labs(x="Peak\namplitude (namps)", y="Normalized\nError") +
+  geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
+  annotate("text", x = 0.1, y = 0.62, label = expression(paste("E"[50]))) +
+  theme_classic() -> p1
+
+vb_norm_results %>% 
+  filter(freq == 8) %>% 
+  ggplot(aes(x=As*1e9, normalize(variances_pop))) +
+  geom_point(size=0.8, alpha=0.9) +
+  labs(x="Peak\namplitude (namps)", y="Normalized\ncompression") +
+  geom_vline(xintercept = 0.032, alpha=1, color="grey", linetype="dashed") +
+  annotate("text", x = 0.046, y = 0.93, label = expression(paste("E"[50]))) +
+  theme_classic() -> p2
+
+vb_norm_results %>% 
+  filter(freq == 8) %>% 
+  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
+  geom_point(size=1.2, alpha=1) +
+  geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
+  annotate("text", x = 1, y = 0.54, label = expression(paste("E"[50]))) +
+  labs(y="Normalized\nError", x="Normalized\ncompression") +
+  ggtitle("A prediction for\npathological oscillation") +
+  scale_color_manual("State", values=c("palevioletred3", "peachpuff3")) +
+  theme_classic() +
+  theme(legend.background = element_rect(colour ="black"),
+        legend.position = "right") -> p3
+
+(p1 | p2) / p3 +
+  plot_layout(heights = c(1, 3)) + 
+  plot_layout(guides = 'collect') +
+  plot_annotation(tag_levels = 'a', tag_suffix = ".") 
+ggsave("figures/lossy_fig10.png", dpi=600)
+```

### 2020-03-22 voltagebudget/analysis/paper_figures_lossy.Rmd
Misc tweaks for lossy Figus

@@
   ggtitle("Compression\nby oscillation")
+p3 <- plot_spacer()
 
@@
   labs(y="Normalized\nError", x="Normalized\ncompression") +
-  ggtitle("A prediction for\npathological oscillation") +
+  ggtitle("The pathological\ncompression hypothesis") +
   scale_color_manual("State", values=c("palevioletred3", "peachpuff3")) +
@@
 
+# Build figure
 (p1 | p2) / p3 +
@@
 ```
+
+# Figure 11 - VB intro
+We don't have a reference, or there is no practical reference. Voltage budget analysis to the rescue!
+```{r}
+# HERE...
+# Create VB intro
+```
+
+# Figure 12 - VB and E50
+```{r}
+# HERE
+```

### 2020-03-22 voltagebudget/analysis/paper_figures_lossy.Rmd
Unified facet box style

@@
     legend.position="none", 
-    panel.border = element_rect(fill = NA, colour = "black"),
+    panel.border = element_rect(fill = NA, colour = "grey"),
     panel.grid.major = element_blank(),
@@
     legend.text = element_text(size=8),
+    panel.border = element_rect(fill = NA, colour = "grey"),
     legend.background = element_rect(colour ="black"),
@@
   theme(legend.position = "none",
+        panel.border = element_rect(fill = NA, colour = "grey"),
         strip.background = element_blank(),
@@
 # Figure 9 - trade-off (with osc)
-```{r, message=FALSE, fig.width=3.8, fig.height=1.8}
+```{r, message=FALSE, fig.width=3.6, fig.height=1.8}
 vb_results %>% 
